### 2019-07-26 appendix/appendix.Rmd
upload templates

---
title: |
       | Supplementary Materials for "PAPER"
author: 
- "Danilo Freire[^freire]"
- "Manoel Galdino[^galdino]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Jessica Voigt[^voigt]"
date: July 26, 2019
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.

[^galdino]: Executive Diretor, Transparência Brazil, São Paulo, SP, Brazil, [mcz.fea@gmail.com](mailto:mcz.fea@gmail.com), <https://www.transparencia.org.br>.

[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [umberto.mig@nyu.edu](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>. Corresponding author.

[^voigt]: Data Scientist, Transparência Brasil, São Paulo, SP, Brazil, [voigt.jessica@gmail.com](mailto:voigt.jessica@gmail.com), <https://www.linkedin.com/in/voigtjessica>.

```{r setup, echo=FALSE}
```

# Latin American Elite Survey \label{sec:latam}

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

Lorem ipsum.

# Bibliography

### 2019-07-26 article/article.Rmd
upload templates

---
title:  |
        | Paper title
author: 
- "Danilo Freire[^freire]"
- "Manoel Galdino[^galdino]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Jessica Voigt[^voigt]"
date: \today
thanks: "The authors thank Professors John and Jane Doe for their helpful comments."
abstract: "This is a personal article template for RMarkdown. It uses Linux Libertine and Inconsolata fonts, British English, double-spaced text and numbered sections. The colours are personalised too: URLs are in dark blue, internal links are in mahogany and the table of contents is in black. The template also has pre-formatted entries for the abstract, keywords and JEL classification codes. You need to install `R` (and the `rmarkdown` package), `pandoc` and a `TeX` system to compile the pdf. In case you don't want to download large `TeX` binaries, I recommend you to install the great `TinyTeX R` package. A quick note: if you want to use colons in the abstract or the `thanks` entry, please don't forget to put the whole text in quotes. Otherwise, YAML might not parse it correctly. I hope you find this template useful and feel free to send me a message if you have any suggestions."
abstractspacing: double
keywords: R Markdown; pandoc; template
jelcodes: A00, B11, C22
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
```

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.

[^galdino]: Executive Diretor, Transparência Brazil, São Paulo, SP, Brazil, [mcz.fea@gmail.com](mailto:mcz.fea@gmail.com), <https://www.transparencia.org.br>.

[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [umberto.mig@nyu.edu](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>. Corresponding author.

[^voigt]: Data Scientist, Transparência Brasil, São Paulo, SP, Brazil, [voigt.jessica@gmail.com](mailto:voigt.jessica@gmail.com), <https://www.linkedin.com/in/voigtjessica>.

\newpage

# Introduction\label{sec:intro}

This is section \ref{sec:intro}. *Italics*, **boldface**, `typewriter`.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

### 2019-07-30 article/article.Rmd
add intro, estimation paragraphs

@@
 title:  |
-        | Paper title
+        | The Pitfalls of Bottom-Up Accountability: Evidence from Brazil
 author: 
@@
 date: \today
-thanks: "The authors thank Professors John and Jane Doe for their helpful comments."
-abstract: "This is a personal article template for RMarkdown.
-It uses Linux Libertine and Inconsolata fonts, British English, double-spaced text and numbered sections.
-The colours are personalised too: URLs are in dark blue, internal links are in mahogany and the table of contents is in black.
-The template also has pre-formatted entries for the abstract, keywords and JEL classification codes.
-You need to install `R` (and the `rmarkdown` package), `pandoc` and a `TeX` system to compile the pdf.
-In case you don't want to download large `TeX` binaries, I recommend you to install the great `TinyTeX R` package.
-A quick note: if you want to use colons in the abstract or the `thanks` entry, please don't forget to put the whole text in quotes.
-Otherwise, YAML might not parse it correctly.
-I hope you find this template useful and feel free to send me a message if you have any suggestions."
+thanks: "We thank Guilherme Fasolin, Stephen Herzog, and David Skarbek for their helpful comments.
+We are specially grateful to the staff of Transparência Brasil for their excellent research and technical assistance.
+Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
+abstract: "We study the effect of a mobile phone application designed to increase citizens' ability to monitor public works in Brazil.
+The app allowed individuals to find delayed school constructions in XXX Brazilian cities and send anonymous messages to politicians requestions information about construction delays and expected completion times.
+Our results show that the app has a null impact on the completion times subsequently reported by the municipalities.
+Additionally, we find that few politicians reacted to citizens' requests.
+These findings suggest it is difficult to motivate bottom-up accountability in new democracies, especially when politicians are unresponsive to non-electoral pressures.
+This paper has implications for the design of bottom-up accountability mechanisms."
 abstractspacing: double
-keywords: R Markdown; pandoc; template
-jelcodes: A00, B11, C22
+keywords: accountability, Brazil, field experiment, impact evaluation, state capacity, technology
 fontsize: 12pt
@@
 
-This is section \ref{sec:intro}. *Italics*, **boldface**, `typewriter`.
+One of the key determinants of efficient public service provision is a robust accountability system \citep{besley2003incentives,cameron2004public,o1998horizontal}.
+In its standard definition, accountability is the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
+Recent studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
+Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital \citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.
+
+However, accountability systems can take many forms.
+One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials \citep{kosack2014does, molina2016community,raffler2018weakness}.
+Proponents suggest bottom-up is an effective method of accountability because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities \citep[570]{serra2011combining}.
+In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve \citep[2]{raffler2018weakness}.
+
+Here we assess the impact of a technology-driven solution that lowers the costs of evaluating public works and punishing political representatives in Brazil.
+The _Tá de Pé_ (TDP) mobile phone application allows Brazilian citizens to go to school construction sites, check their status, and request information to public authorities.
+TDP users can also take pictures from delayed works and submit them to a group of trained engineers, who then evaluate the execution of the project.
+If the engineers classify the construction as delayed, TDP sends a message to the mayor's office asking for completion estimates and explanations about why the building is unfinished.
+TDP received the 2016 Google Social Impact grant, earning more than 200 thousand popular votes, and it has been online since April 2017 in 1030 Brazilian municipalities.
+
+Contrary to our expectations, the TDP app has delivered mixed results.
+Two findings are positive and in line with our theoretical predictions.
+From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX).
+Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = XXX).
+In contrast, our results show the app had a null impact on school constructions statistics.
+Brazilian politicians did not respond to the citizen's requests placed via the application.
+Therefore, our findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
+
+# The _Tá de Pé_ App
+
+# Methods
+
+## Estimation
+
+Our regression model is specified as follows:
+
+$$Y_{i} = \alpha + \beta T_{i} + \gamma X_{i} + \theta Z_i + \epsilon_{i} $$
+
+Where $i$ indexes the case.
+$Y_i$ in one the outcomes we described in the previous subsection.
+The $\beta$ coefficient is the quantity of interest (Average Treatment Effect).
+$T_i$ is a binary treatment indicator in which zero denotes that $i$ is in the control group, while 1 indicates that $i$ received the treatment.
+$\gamma$ is a vector of fixed effects and $X_i$ is a matrix of 27 Brazilian states' fixed effects.
+$\theta$ is a vector of additional controls and $Z_i$ is an array of control variables for the case $i$.
+Lastly, $\epsilon_i$ is the error term.
+
+We cluster the standard errors at the municipal level, as the investment decisions are taken by the mayor’s offices.
+As robustness, we fit two extra models.
+First, we re-run the main model where we have the following: (i) we ran a model without controls or fixed effects; (ii) we run the models adding the control variables, which are the same as the ones used in the covariate balance tests; (iii) we run the regression model with State fixed effects.
+The results are in the Appendix.
+Second, we run the main models using inverse probability weights where we used block randomization and a one-to-one nearest neighborhood matching.
+We use the control variables as matching characteristics.
+These robustness checks are intended to correct the imbalance caused by the minimal control group approach that we employed in all three interventions.
+
+# Results
+
+# Discussion
+
+# Conclusion
 

### 2019-07-30 article/article.tex
add intro, estimation paragraphs

% !TEX program = XeLaTeX
\documentclass[12pt,a4paper,]{article}

% Fonts
\usepackage{libertine}
% This is a nice mathfont, it fits well with Libertine
% Comment the line if you want to use a different one
\usepackage[libertine]{newtxmath}
% The default monofont 
% Again, comment the line below if you want to change it
\usepackage[scaled=.95]{inconsolata}

% Add the following packages to support kableExtra
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{etoolbox}
\usepackage{tocloft}

% Dots in toc
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

% Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}

% Spacing
\usepackage{setspace}

% Margin
\usepackage[margin=2cm]{geometry}

% Packages I've been using for different reasons...
\usepackage[backref,pagebackref]{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}

% UK English
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon

% Penalties
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000

% Back references
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        Cited on page~#2.%
    \else      Cited on pages~#2.%
    \fi}
\renewcommand{\backreftwosep}{ and~} 
\renewcommand{\backreflastsep}{ and~}

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; Manoel Galdino; Umberto Mignozzetti; Jessica Voigt},
      pdfkeywords={accountability, Brazil, field experiment, impact evaluation, state
capacity, technology},
  }

% If XeTex, LuaLaTeX, etc
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{amssymb,amsmath}
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

% Language

% Bibliography
\usepackage{natbib}
\bibliographystyle{apalike}
\makeatletter
% Remove comma after author
\setcitestyle{aysep={}}
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother

% Listings

% Verbatim

% Tables

% Graphics

% Make links footnotes instead of hotlinks:
%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Numbered sections
\setcounter{secnumdepth}{5}
% % % Redefines (sub)paragraphs to behave more like sections
% \ifx\paragraph\undefined\else
% \let\oldparagraph\paragraph
% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
% \fi
% \ifx\subparagraph\undefined\else
% \let\oldsubparagraph\subparagraph
% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
% \fi
% 
% Spacing
\doublespacing

% Title
\title{The Pitfalls of Bottom-Up Accountability: Evidence from Brazil\thanks{We thank Guilherme Fasolin, Stephen Herzog, and David Skarbek for their
helpful comments. We are specially grateful to the staff of
Transparência Brasil for their excellent research and technical
assistance. Replication data and code are available at
\url{http://github.com/umbertomignozzetti/tdp-accountability}.}}

% Author
\author{Danilo Freire\footnote{Postdoctoral Research Associate, The Political
  Theory Project, Brown University, Providence, RI 02912, USA,
  \href{mailto:danilofreire@brown.edu}{\nolinkurl{danilofreire@brown.edu}},
  \url{http://danilofreire.github.io}.} \and Manoel Galdino\footnote{Executive Diretor, Transparência Brazil, São
  Paulo, SP, Brazil,
  \href{mailto:mcz.fea@gmail.com}{\nolinkurl{mcz.fea@gmail.com}},
  \url{https://www.transparencia.org.br}.} \and Umberto Mignozzetti\footnote{School of International Relations, Fundação
  Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of
  Politics, NYU, NY, USA,
  \href{mailto:umberto.mig@nyu.edu}{\nolinkurl{umberto.mig@nyu.edu}},
  \url{http://umbertomig.com}. Corresponding author.} \and Jessica Voigt\footnote{Data Scientist, Transparência Brasil, São Paulo,
  SP, Brazil,
  \href{mailto:voigt.jessica@gmail.com}{\nolinkurl{voigt.jessica@gmail.com}},
  \url{https://www.linkedin.com/in/voigtjessica}.}}

% Date
\date{\today}

% Begin document
\begin{document}
\maketitle

% Abstract
\begin{abstract}
\doublespacing \noindent We study the effect of a mobile phone application designed to increase
citizens' ability to monitor public works in Brazil. The app allowed
individuals to find delayed school constructions in XXX Brazilian cities
and send anonymous messages to politicians requestions information about
construction delays and expected completion times. Our results show that
the app has a null impact on the completion times subsequently reported
by the municipalities. Additionally, we find that few politicians
reacted to citizens' requests. These findings suggest it is difficult to
motivate bottom-up accountability in new democracies, especially when
politicians are unresponsive to non-electoral pressures. This paper has
implications for the design of bottom-up accountability mechanisms.
\vspace{.25cm}

\noindent \textbf{Keywords}: accountability, Brazil, field experiment, impact evaluation, state
capacity, technology
\vspace{.25cm}

\end{abstract}

% Table of Contents
\newpage

\hypertarget{introduction}{%
\section{\texorpdfstring{Introduction\label{sec:intro}}{Introduction}}\label{introduction}}

One of the key determinants of efficient public service provision is a
robust accountability system
\citep{besley2003incentives,cameron2004public,o1998horizontal}. In its
standard definition, accountability is the process of holding
authorities into account for their actions
\citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
Recent studies show that accountability ensures that politicians act on
behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing},
reduces the opportunities for rent-seeking and corruption
\citep{deininger2005does,wenar2006accountability} and increases the
efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
Moreover, greater accountability is associated with higher levels of
economic growth, not only because it limits state discretion in the
economy, but also because it promotes social cohesion and long-term
investments in human capital
\citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.

However, accountability systems can take many forms. One promising model
for democratic oversight is \emph{bottom-up accountability}, in which
citizens receive information about the shortcomings of a given project
to help them monitor and pressure underperforming public officials
\citep{kosack2014does, molina2016community,raffler2018weakness}.
Proponents suggest bottom-up is an effective method of accountability
because 1) constituents have first-hand information about the outcomes
of local policies; 2) citizens have incentives to avoid corruption that
directly affects them; 3) policy-makers are particularly sensitive to
social punishment from their own communities
\citep[570]{serra2011combining}. In a nutshell, bottom-up accountability
offers a potential solution to the principal-agent dilemma in public
service by aligning the interests of politicians and bureaucrats with
those of the constituency they serve \citep[2]{raffler2018weakness}.

Here we assess the impact of a technology-driven solution that lowers
the costs of evaluating public works and punishing political
representatives in Brazil. The \emph{Tá de Pé} (TDP) mobile phone
application allows Brazilian citizens to go to school construction
sites, check their status, and request information to public
authorities. TDP users can also take pictures from delayed works and
submit them to a group of trained engineers, who then evaluate the
execution of the project. If the engineers classify the construction as
delayed, TDP sends a message to the mayor's office asking for completion
estimates and explanations about why the building is unfinished. TDP
received the 2016 Google Social Impact grant, earning more than 200
thousand popular votes, and it has been online since April 2017 in 1030
Brazilian municipalities.

Contrary to our expectations, the TDP app has delivered mixed results.
Two findings are positive and in line with our theoretical predictions.
From August 2017 to February 2019, TDP increased the likelihood of
school completion by 6.8 percent (SE = X.X, t-test = XXX). Additionally,
we find that pressure over the bureaucracy increased the investments in
the schools by 157.5 percent (SE = X.XX, t-test = XXX). In contrast, our
results show the app had a null impact on school constructions
statistics. Brazilian politicians did not respond to the citizen's
requests placed via the application. Therefore, our findings raise
questions about the ability of citizens to hold representatives
accountable using bottom-up strategies.

\hypertarget{the-ta-de-pe-app}{%
\section{\texorpdfstring{The \emph{Tá de Pé}
App}{The Tá de Pé App}}\label{the-ta-de-pe-app}}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{estimation}{%
\subsection{Estimation}\label{estimation}}

Our regression model is specified as follows:

\[Y_{i} = \alpha + \beta T_{i} + \gamma X_{i} + \theta Z_i + \epsilon_{i} \]

Where \(i\) indexes the case. \(Y_i\) in one the outcomes we described
in the previous subsection. The coefficient for \(\beta\) is the
quantity of interest (Average Treatment Effect). \(T_i\) is a binary
treatment indicator in which zero denotes that \(i\) is in the control
group, while 1 indicates that \(i\) received the treatment. \(\gamma\)
is a vector of fixed effects and \(X_i\) is a matrix of 27 Brazilian
states' fixed effects. \(\theta\) is a vector of additional controls and
\(Z_i\) is an array of control variables for the case \(i\). Lastly,
\(\epsilon_i\) is the error term.

We cluster the standard errors at the municipal level, as the investment
decisions are taken by the mayor's offices. As robustness, we fit two
extra models. First, we re-run the main model where we have the
following: (i) we ran a model without controls or fixed effects; (ii) we
run the models adding the control variables, which are the same as the
ones used in the covariate balance tests; (iii) we run the regression
model with State fixed effects. The results are in the Appendix. Second,
we run the main models using inverse probability weights where we used
block randomization and a one-to-one nearest neighborhood matching. We
use the control variables as matching characteristics. These robustness
checks are intended to correct the imbalance caused by the minimal
control group approach that we employed in all three interventions.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

% More bibliography
\bibliography{references.bib}

\end{document}

### 2019-07-30 article/article.Rmd
small fixes

@@
 
-# Introduction\label{sec:intro}
+# Introduction
+\label{sec:intro}
 
@@
 In its standard definition, accountability is the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
-Recent studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
+Past studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
 Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital \citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.
@@
 One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials \citep{kosack2014does, molina2016community,raffler2018weakness}.
-Proponents suggest bottom-up is an effective method of accountability because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities \citep[570]{serra2011combining}.
+Proponents suggest bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities \citep[570]{serra2011combining}.
 In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve \citep[2]{raffler2018weakness}.
@@
 # The _Tá de Pé_ App
+\label{sec:tdp}
 
 # Methods
+\label{sec:methods}
 
 ## Estimation
+\label{sub:estimation}
 
@@
 # Results
+\label{sec:results}
 
 # Discussion
+\label{sec:discussion}
 
 # Conclusion
+\label{sec:conclusion}
 

### 2019-07-30 article/article.tex
add files

@@
 \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
-Recent studies show that accountability ensures that politicians act on
+Past studies show that accountability ensures that politicians act on
 behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing},
@@
 \citep{kosack2014does, molina2016community,raffler2018weakness}.
-Proponents suggest bottom-up is an effective method of accountability
-because 1) constituents have first-hand information about the outcomes
-of local policies; 2) citizens have incentives to avoid corruption that
-directly affects them; 3) policy-makers are particularly sensitive to
-social punishment from their own communities
-\citep[570]{serra2011combining}. In a nutshell, bottom-up accountability
-offers a potential solution to the principal-agent dilemma in public
-service by aligning the interests of politicians and bureaucrats with
-those of the constituency they serve \citep[2]{raffler2018weakness}.
+Proponents suggest bottom-up accountability is effective because 1)
+constituents have first-hand information about the outcomes of local
+policies; 2) citizens have incentives to avoid corruption that directly
+affects them; 3) policy-makers are particularly sensitive to social
+punishment from their own communities \citep[570]{serra2011combining}.
+In a nutshell, bottom-up accountability offers a potential solution to
+the principal-agent dilemma in public service by aligning the interests
+of politicians and bureaucrats with those of the constituency they serve
+\citep[2]{raffler2018weakness}.
 
@@
 Where \(i\) indexes the case. \(Y_i\) in one the outcomes we described
-in the previous subsection. The coefficient for \(\beta\) is the
-quantity of interest (Average Treatment Effect). \(T_i\) is a binary
-treatment indicator in which zero denotes that \(i\) is in the control
-group, while 1 indicates that \(i\) received the treatment. \(\gamma\)
-is a vector of fixed effects and \(X_i\) is a matrix of 27 Brazilian
-states' fixed effects. \(\theta\) is a vector of additional controls and
-\(Z_i\) is an array of control variables for the case \(i\). Lastly,
+in the previous subsection. The \(\beta\) coefficient is the quantity of
+interest (Average Treatment Effect). \(T_i\) is a binary treatment
+indicator in which zero denotes that \(i\) is in the control group,
+while 1 indicates that \(i\) received the treatment. \(\gamma\) is a
+vector of fixed effects and \(X_i\) is a matrix of 27 Brazilian states'
+fixed effects. \(\theta\) is a vector of additional controls and \(Z_i\)
+is an array of control variables for the case \(i\). Lastly,
 \(\epsilon_i\) is the error term.

### 2019-07-30 tdp/analysis3.Rmd
add files

---
title: "Analysis Tá de Pé"
author: "Umberto Mignozzetti"
date: "7/26/2019"
header-includes:
   - \usepackage[utf8]{inputenc}
   - \usepackage{tipa}
   - \usepackage{caption,tabularx,booktabs,dcolumn}
output: pdf_document
---

```{r, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
####
## Pre-processing
####

# Needed packages
pkgs <- c('tidyverse', 'dummies',
          'haven', 'compareGroups',
          'devtools', 'lubridate', 'brazilmaps',
          'abjutils', 'lfe', 'cobalt', 'stargazer',
          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
          'flextable', 'officer')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T)
} 
lapply(pkgs, installIfNot)

# Load scripts
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)
rm(list=ls())
```

```{r, include=FALSE, warning=FALSE, cache=TRUE}
####
## Load data 
####

# Data block randomization
setwd("~/Dropbox/Academic/Projects/TDP/2_analysis/")
load('./bucket/final_bucket.RData')

# Aux function
calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  if(is.null(wts)) {
    dat <- dat %>%
      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
      na.omit()
  } else {
    dat <- dat %>%
      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
      na.omit()
    wts <- dat[,wts]
  }
  k <- 1
  for (i in treats) {
    for (j in outcs) {
      # No controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = F))
      print(k); k = k+1
      # Controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = F))
      print(k); k = k+1
      # No controls and fes
      mods[[k]] <- felm(
        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
                         collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = T))
      print(k); k = k+1
      # Controls and fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = T))
      print(k); k = k+1
    }
  }
  return(list(moddescr, mods))
}

####
## Analysis Intervention 1
####

## Covariate balance
aux <- select(impEvalph1, 
              treatOriginal, logPop2015,
              ideb_ai_2015, ideb_af_2015, log_poorFam2010,
              log_totTransf2016) %>%
  unique()
resu1 <- compareGroups(treatOriginal ~ 
                         logPop2015 + 
                         log_poorFam2010 +
                         log_totTransf2016 +
                         ideb_ai_2015 + 
                         ideb_af_2015, 
                       data = aux)
tabIE1balance <- createTable(resu1, digits = 3)
row.names(tabIE1balance$descr) <- 
  c('Log Population (2015)', 
    'Log Poor Families (2010)', 
    'Log Total Transfers (2016)', 
    'IDEB Inicial Years (2015)', 
    'IDEB Final Years (2015)')

## Manipulation Stats

## Map GA intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- left_join(gaaux2, gaaux); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
pMapDownloadsInt1 <-
  plot_brmap(mapbr,
             data_to_join = gaaux,
             join_by = c("City" = "City"),
             var = "Downloads") +
  labs(title = 'App Downloads -- Intervention 1')

# Frequency downloads
tab <- filter(ga, phase1 == 1) %>%
  group_by(data) %>%
  summarize(NewUsers = sum(novos_usuarios))
names(tab) <- c('Date', 'Frequency')
pFreqUserDownloadsInt1 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
  geom_line() + geom_point()

## ATEs 
outcs <- c('percExecBegin', 'percExecEnd',
           'deltaPercExec', 'isFinished',
           'isCancelled', 'updDate')
treats <- c('treat')
ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
           'log_poorFam2010', 'log_totTransf2016')
fes <- c('state')
cls <- c('municipality')

resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)

## Nearest Neighborhood Matching
datMatchIPW <- impEvalph1 %>%
  select(treat, logPop2015, ideb_ai_2015, ideb_af_2015,
         log_poorFam2010, log_totTransf2016,
         percExecBegin, percExecEnd, deltaPercExec, isFinished,
         isCancelled, updDate, state, municipality) %>%
  na.omit() %>%
  mutate(treat = 2-as.numeric(treat))

row.names(datMatchIPW) <- NULL

resMatch <- matchit(treat ~ logPop2015 + ideb_ai_2015 + ideb_af_2015 + 
                      log_poorFam2010 + log_totTransf2016,
                    method = "nearest", data = datMatchIPW, distance = 'mahalanobis')

datMatch <- match.data(resMatch)

datMatch <- datMatch %>% 
  mutate(treat = 1-treat) %>%
  mutate(treat = factor(treat, levels = c(0, 1), 
                        labels = c('Control', 'Treatment')))

resInt1match <- calcATEs(outcs, treats, ctrls, fes, cls, dat = datMatch)

# Propensity score matching not used because of simple inference

####
## Analysis Intervention 2
####

## Covariate balance
aux <- select(impEvalph2, logPop2015,
              treatApp, ideb_ai_2015,
              ideb_af_2015, log_poorFam2010,
              log_totTransf2016)
resu1 <- compareGroups(treatApp ~ 
                         logPop2015 + 
                         log_poorFam2010 +
                         log_totTransf2016 +
                         ideb_ai_2015 + 
                         ideb_af_2015,
                       data = aux)
tabIE2Balance <- createTable(resu1, digits = 3)
row.names(tabIE2Balance$descr) <- 
  c('Log Population (2015)', 
    'Log Poor Families (2010)', 
    'Log Total Transfers (2016)', 
    'IDEB Inicial Years (2015)', 
    'IDEB Final Years (2015)')

## ATEs
resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)

## Genetic Neighborhood Matching
datMatchIPW <- impEvalph2 %>%
  select(id_project, treatApp, logPop2015, ideb_ai_2015, ideb_af_2015,
         log_poorFam2010, log_totTransf2016,
         percExecBegin, percExecEnd, deltaPercExec, isFinished,
         isCancelled, updDate, state, municipality) %>%
  na.omit() %>%
  mutate(treatApp = 2-as.numeric(treatApp))

row.names(datMatchIPW) <- NULL

resMatch <- matchit(treatApp ~ logPop2015 + ideb_ai_2015 + ideb_af_2015 + 
                      log_poorFam2010 + log_totTransf2016,
                    method = "nearest", data = datMatchIPW, distance = 'mahalanobis')

datMatch <- match.data(resMatch)

datMatch <- datMatch %>% 
  mutate(treatApp = 1-treatApp) %>%
  mutate(treatApp = factor(treatApp, levels = c(0, 1), labels = c('Control', 'Treatment')))

resInt2match <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = datMatch)

# Regression applying inverse probability weights
resInt2IPW <- 
  calcATEs(outcs, 'treatApp', ctrls, fes, 
                       cls, dat = impEvalph2, wts = 'IPW_intheapp')

####
## Analysis Intervention 3
####

# Covariate balance
aux <- select(impEvalph2, logPop2015,
              treatCampaign, ideb_ai_2015,
              ideb_af_2015, log_poorFam2010,
              log_totTransf2016)
resu1 <- compareGroups(treatCampaign ~ 
                         logPop2015 + 
                         log_poorFam2010 +
                         log_totTransf2016 +
                         ideb_ai_2015 + 
                         ideb_af_2015, 
                       data = aux)
tabIE3Balance <- createTable(resu1, digits = 3)
row.names(tabIE3Balance$descr) <- 
  c('Log Population (2015)', 
    'Log Poor Families (2010)', 
    'Log Total Transfers (2016)',
    'IDEB Inicial Years (2015)', 
    'IDEB Final Years (2015)')

# ATE Campaign
outcs <- c('percExecBegin', 'percExecEnd',
           'deltaPercExec', 'isFinished',
           'isCancelled', 'updDate')
treats <- c('treatCampaign')
ctrls <- c('logPop2015','ideb_ai_2015','ideb_af_2015',
           'log_poorFam2010', 'log_totTransf2016')
fes <- c('state')
cls <- c('municipality')

res <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph2)

## Nearest Neighborhood Matching
datMatchIPW <- impEvalph2 %>%
  select(id_project, treatCampaign, logPop2015, ideb_ai_2015, ideb_af_2015,
         log_poorFam2010, log_totTransf2016,
         percExecBegin, percExecEnd, deltaPercExec, isFinished,
         isCancelled, updDate, state, municipality) %>%
  na.omit() %>%
  mutate(treatCampaign = 2-as.numeric(treatCampaign))

row.names(datMatchIPW) <- NULL

resMatch <- matchit(treatCampaign ~ logPop2015 + ideb_ai_2015 + 
                      ideb_af_2015 + log_totTransf2016 + log_poorFam2010,
                    method = "nearest", data = datMatchIPW, distance = 'mahalanobis')

datMatch <- match.data(resMatch)

datMatch <- datMatch %>% 
  mutate(treatCampaign = 1-treatCampaign) %>%
  mutate(treatCampaign = factor(treatCampaign, levels = c(0, 1), labels = c('Control', 'Treatment')))

resInt3match <- calcATEs(outcs, 'treatCampaign', ctrls, fes, 
                         cls, dat = datMatch)

# Regression applying inverse probability weights
resInt3IPW <- calcATEs(outcs, 'treatCampaign', ctrls, fes, 
                       cls, dat = impEvalph2, wts = 'IPW_campaign')
```

# Executive Summary

## What have we done?

In this impact evaluation, we study the effect of the **Tá de Pé** App and Campaign. **Tá de Pé** (TDP) is an initiative to improve the responsiveness in Education Infrastructure public expenditures. From August 2017 to February 2019, we studied the impact of the App and the impact of an online email campaign designed to pressure all municipalities known to have delayed school constructions according to the Brazilian Federal government Ministry of Education.

## Why should we care?

Despite being among the ten largest economies in the world, Brazil scores consistently in the last positions at the PISA education exam. Many public school constructions in Brazil are delayed or unfinished due to inefficiencies and corruption. This impacts the long-run productivity and welfare in the country and limits the returns of investments in the country.

## How did we do?

We evaluated three interventions:

1. The effect of the App introduction, from August 2017 to February 2018.
2. The effect of the App introduction, from August 2018 to February 2019.
3. The effect of the TDP Campaign, where the schools with delayed constructions received an automated email requesting information, in December 2018.

To access the impact, we randomize a set of schools and municipalities not to receive the intervention. We then studied construction execution statistics, construction status, and construction finishing dates.

## What did we find?

The first intervention found that the introduction of the App increased the likelihood of school completion by `r round(100*resInt1[[2]][[16]]$coefficients[1], 2)` percent. The second intervention found that the App pressure over the bureaucracy increased the investment in the schools by `r round(100*resInt2match[[2]][[12]]$coefficients[1], 2)` percent. The last intervention had a null impact on school constructions statistics.

## How can we improve?

For further development, we suggest the following:

1. Gamification of the App, to attract younger users: younger people have more time to use the App. Focusing on this group may improve App usage and the end-line impact on school constructions. For example, a partnership with *Pokemon Go*, to put Pokemons over the school constructions, together with banners embedded in the game that incentivize reporting, could increase the end-line impact.

2. Expansion of the intervention scope: school construction is only part of a much broader set of educational services provided. School quality and teacher attendance are also essential and problematic in Brazil. Moreover, the design can be easily transported to other fields, such as health care. This could make the App a comprehensive whistleblowing tool for both education and health care systems.

3. Shocks in the cost-benefits of using the App: improve the cost-benefit equation could increase the potential number of users. This can be done by providing *Tinder*, *Rappi*, *Uber*, or *Google Play* credits for users that effectively report.

# The TDP Project

The **Tá de Pé** project is an initiative carried out by the Transparência Brasil (Brazilian Transparency) to foster bottom-up accountability. The App was built to facilitate people to go to school construction sites, check their status, and request information to the public authorities about the steps toward finishing the school constructions.

The app works as follows. From a list of constructions available in the Ministry of Education website, the Brazilian Transparency mapped all the schools and made them available in the Ta de Pé App. Any person with the App can go to a construction site and take pictures. The Ta de Pé bot sends the images for engineers to evaluate the execution and suggest whether to report the construction site as *delayed*. If the construction is reported, then the App sends a request to the mayor's office asking the public officials to explain why the building is unfinished and requesting better completion estimates.

The App has received the 2016 Google Social Impact grant, with more than 200 thousand popular votes and it has been online since April 2017.

## Impact evaluation design

We divided the impact evaluation into three interventions. The first two interventions will evaluate the impact of the App on reported school constructions outcomes. The last intervention will assess the result of a campaign run by the **Tá de Pé** bot, that reported all the school constructions marked as delayed in the Ministry of Education dataset.

## Randomization

In the first intervention, we use simple randomization, placing 150 municipalities in the control group. In the second and third interventions, we use block randomization, randomizing by three characteristics: Brazilian State, Construction Status (delayed, ongoing, stopped), and above median executed indicator.

To evaluate the random assignment, we used the following pre-treatment variables:

1. Log of Municipal Population in 2015
2. Log of Number of Poor Families (2010 IBGE Census)
3. Log of Total Federal Transfers to the Municipality in 2016
4. IDEB Indicator for primary school quality (2015 Ministry of Education)
5. IDEB Indicator for secondary school quality (2015 Ministry of Education)

For the first randomization, we used the core R function `sample.` For the block randomization, we use the package `randomizr` for R. We take the approach of a small control group, as this was a sensitive condition to not prevent the app from being evaluated. In the first intervention, we select 150 municipalities. In the second and third interventions, we selected around 600 construction sites. The difference in the randomization procedure is due to better information about construction sites during the second and third interventions.

Qualitatively, the intervention in each step consists of the following:

1. *Intervention 1*: We selected `r as.numeric(table(impEvalph1$treatOriginal)[1])` construction sites to not appear in the app.

2. *Intervention 2*: We selected `r as.numeric(table(impEvalph2$treatApp)[1])` construction sites to not appear in the app.

3. *Intervention 3*: We select `r as.numeric(table(impEvalph2$treatCampaign)[1])` construction sites to not receive the TDP bot campaign.

## Outcomes

We investigated the impact on six outcomes of interest:

1. Percentage of the investment executed before the impact evaluation started (placebo)
2. Percentage of the investment performed by the end of the impact evaluation period
3. The difference of the percentage invested in the end and at the beginning of the impact evaluation period
4. Indicator for a construction finished during the impact evaluation period
5. Indicator for a construction canceled during the impact evaluation period
6. Indicator for an updated conclusion date for the construction during the impact evaluation period

Our hypothesis, conditional on the app having a positive effect in terms of welfare, is to find that:

1. The *percentage of the investment executed before the impact evaluation started* should **remain unchanged**
2. The *percentage of the investment executed by the end of the impact evaluation period* should **increase**, meaning that the App is speeding up the construction.
3. The *difference of the percentage invested in the end and at the beginning of the impact evaluation period* should **increase** meaning that the app is increasing the amount invested in the project.
4. The *indicator for a construction finished during the impact evaluation period* should **increase** meaning that constructions are being finished at a higher rate.
5. The *indicator for a construction canceled during the impact evaluation period* should **increase** is **ambiguous**, as it is good to cancel constructions that were not started, but not as much to cancel constructions that are half-way through the work.
6. The *indicator for an updated conclusion date for the construction during the impact evaluation period* should **increase**, meaning that the public officials are giving better estimates of the finishing times.

## Manipulation

To check the manipulation, we look at the number and places of app download.

## Estimation

For the estimation, we use the following regression equation:

$$ Y_i \ = \ \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i $$

$i$ indexes the case. $Y_i$ in an outcome, as described in the previous section. $\beta$ is the quantity of interest (Average Treatment Effect). $T_i$ is the treatment that in our case, is an intervention occurrence indicator with two values, zero (no intervention) and one (intervention). $\gamma$ is a vector of fixed effects, and $X_i$ is a matrix of Brazilian states' fixed effects. $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$. $\varepsilon_i$ is the error term.

We cluster the standard errors at the municipal level, as the investment decisions are taken by the mayor's offices.

As robustness, we fit two extra models. First, we re-run the main model where we have the following: (i) we ran a model without controls or fixed effects; (ii) we run the models adding the control variables, which are the same as the ones used in the covariate balance tests; (iii) we run the regression model with State fixed effects. The results are in the Appendix.

Second, we run the main models using inverse probability weights where we used block randomization and a one-to-one nearest neighborhood matching. We use the control variables as matching characteristics. These robustness checks are intended to correct the imbalance caused by the minimal control group approach that we employed in all three interventions.

## Partial implementation and potential issues in the causal identification

In the first intervention, the municipalities in the control group were displayed in the treatment group for about two weeks, in January 2018. When the mistake was detected, the towns were removed promptly. A few municipalities have App activity, but controlling and/or excluding these municipalities from the estimation does not change the results. Note also that this problem lowers the chance to detect an existant effect, making the estimator more conservative.

In the second and third interventions, there were no threats to the identification, with the treatment being fully implemented.

# Intervention 1

The intervention one was designed to evaluate the impact of launching the first version of the App. The first version was built for Android only, and was launched in August 2017 and lasted until February 2018.

## Randomization

The randomization was performed at the municipal level. We selected 150 municipalities for the control group while the rest were placed in the treatment group. The control group worked by deleting all the construction sites in control assigned cities.

In the next Table, we display the balance test, showing that the covariates are balanced in the treatment and control groups.

```{r impeval2, echo=FALSE}
tabIE1balance
```

As expected, in the treatment and the control, there are no statistically significant differences in terms of Population in 2015, the number of Poor Families in the 2010 IBGE Census, total and FUNDEB transfers to the municipality in 2016, and the IDEB education quality indicators.

## Manipulation

Manipulation in experiments is defined as the extent through which the treatment was successfully delivered. In the case of the App intervention, it represents whether having the App improved the results in terms of school construction completion rates. We present two manipulation indicators. First, we look into the municipalities where we had a successful download and use of the App.

```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width=4.5, fig.height=4.5}
pMapDownloadsInt1
```

Second, we look into App downloads during the intervention 1 period in the following graph.

```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width=4.5, fig.height=4.5}
pFreqUserDownloadsInt1
```

The map displays a good territorial variability. There were `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impEvalph1$municipality[impEvalph1$treatOriginal==1]))` municipalities originally in the dataset at the beginning of the impact evaluation. Downloads peak during the Facebook TDP campaign, right after the App launch in August, then diminishes over time.

In terms of manipulation, there were downloads in 44.6% of the municipalities, and the downloads were temporally concentrated. This indicates that the Facebook campaign worked, but in terms of manipulation, represents a weak treatment delivery. This because the step-by-step usage of the App involves:

1. Download the App.
2. Find a school nearby.
3. Go to school and take pictures.

As the App download is the first step, this represents low manipulation.

## Results

```{r, results = 'asis', echo=FALSE}
# Results intervention 1
stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
          resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 1', 
          keep='treatTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

The intervention was sufficient to improve the school completion rate. It increased in `r round(100*resInt1[[2]][[16]]$coefficients[1], 2)` percent the chance that a school construction becomes reported as finished by the end of the intervention. All other coefficients were not statistically significant at conventional levels.

This finding is positive in the sense that bottom-up pressure exerted by the App worked to increase the completion rate of constructions.

## Results using nearest neighborhood matching

In the randomization, we adopted a minimal control group approach. This has implications for statistical power and sensitivity of the results, as much of the variation is placed on the treatment versus the control group. To increase the reliability of the results, we run the main using one-to-one Nearest Neighborhood Matching with Mahalanobis distance. The findings follow below.

```{r, results = 'asis', echo=FALSE}
stargazer(resInt1match[[2]][[4]],resInt1match[[2]][[8]],resInt1match[[2]][[12]],
          resInt1match[[2]][[16]],resInt1match[[2]][[20]],resInt1match[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 1 (matched results)', 
          keep='treatTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

As we can see, the impact of the App on the school construction completion resists the robustness checks. This reinforces the reliability of this effect.

## Discussion

The introduction of App had a positive effect on the school construction completion rates.

# Intervention 2

In intervention 2, we study the impact of the presence of the App on school construction outcomes. Intervention 2 is similar to intervention 1 in all but three characteristics. First, the TDP App was now available for iOS devices. Second, the randomization is now performed at the school level, blocking by characteristics noted below. Finally, the intervention period is August 2018 to February 2019.

## Randomization

We randomize the App at the school level, placing 15% of schools that could potentially appear in the App in the control group. We used block randomization, blocking by four characteristics:

1. The Brazilian State
2. Status (Under construction, stopped, unfinished)
3. Above median spent resources

The blocks and the inverse probability weights are located in the Appendix. The next table shows that the randomization is balanced by the municipal pre-treatment variables.

```{r, echo=FALSE}
tabIE2Balance
```

## Manipulation

In terms of manipulation, we analyze two outcomes: municipality App downloads and downloads over time.

*Downloads by municipality*:
```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width=4.5, fig.height=4.5}
## Map GA phase 2: number downloads
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- left_join(gaaux2, gaaux); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
p <- plot_brmap(mapbr,
                data_to_join = gaaux,
                join_by = c("City" = "City"),
                var = "Downloads") +
  labs(title = 'App Downloads -- Phase 2')
p
```

*Downloads over time -- Intervention 2*:
```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width=4.5, fig.height=4.5}
# Phase 2 -- manipulation
tab <- filter(ga, phase2 == 1) %>%
  group_by(data) %>%
  summarize(NewUsers = sum(novos_usuarios))
names(tab) <- c('Date', 'Frequency')
p <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
  geom_line() + geom_point()
p
```

The total number of municipalities that had downloads of the App is `r sum(gaaux$Downloads == 'Downloads')`. There are two spikes in the usage of the App. One in August, right after the intervention start and a second spike around December. The first spike is a result of a TDP social media campaign for boosting App usage. The second spike is a spillover from the TDP reporting campaign, here known as the intervention 3.

The number of downloads is considerably smaller in this second intervention when compared with intervention 1. As we discussed, this represents a weak manipulation, making detecting treatment effects a hard task.

## Results from the full model

The full model shows us null effects in all the studied outcomes.

```{r, results = 'asis', echo=FALSE}
# Results intervention 2
stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 2', 
          keep='treatAppTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

## Results using inverse probability weights

As we used block randomization, the treatment effect is only corrected estimated when we use the inverse probability weights to reweight the outcomes. The results follow in the table below, showing null effects.

```{r, results = 'asis', echo=FALSE}
stargazer(resInt2IPW[[2]][[4]],resInt2IPW[[2]][[8]],resInt2IPW[[2]][[12]],
          resInt2IPW[[2]][[16]],resInt2IPW[[2]][[20]],resInt2IPW[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 2 (IPW)', 
          keep='treatAppTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

## Results using nearest neighborhood matching

Using nearest neighborhood matching the results improve a little, and we can see that the App improved the difference between the baseline and the end-line reported investment by `r round(100*resInt2match[[2]][[12]]$coefficients[1], 2)` percent.

```{r, results = 'asis', echo=FALSE}
stargazer(resInt2match[[2]][[4]],resInt2match[[2]][[8]],resInt2match[[2]][[12]],
          resInt2match[[2]][[16]],resInt2match[[2]][[20]],resInt2match[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 2 (nearest neighborhood matching)', 
          keep='treatAppTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

Although there were no completion effects as in intervention 1, we had a substantial impact investment in the nearest neighborhood matched sample.

## Discussion

We have null treatment effects in all but one outcome, in the nearest neighborhood matched sample. In the NN-matching, we find that the App improves the percentage of the executed budget.

# Intervention 3

Intervention 3 focused on the effect of a TDP Campaign to boost response, in a top-down email campaign to select schools in December 2018.

## Randomization

We randomize the TDP Campaign, placing 15% of schools that could potentially receive the email campaign advocacy in the control group. We used block randomization, blocking by four characteristics:

1. The Brazilian State
2. Status (Under construction, stopped, unfinished)
3. Above median spent resources

The blocks and the inverse probability weights are located in the Appendix. The next table shows that the randomization is balanced by the municipal pre-treatment variables.

```{r, echo=FALSE, warning=FALSE}
tabIE3Balance
```

## Manipulation

In the manipulation, let us analyze the ex-post effect by looking into responses.

First, we have the following chart for the validity of the responses. We coded the validity of responses in three categories. First, a valid answer provides a minimal explanation that covers the inquiries made by the campaign email. An invalid answer represents an answer without any explanation. Not answer means that the campaign email has not been addressed by the :

```{r, echo=FALSE, warning=FALSE, fig.align='center', fig.width=4.5, fig.height=4.5}
# Status answer by state
tab <- data.frame(table(allalert$status2, allalert$state))
names(tab) <- c('Status', 'State', 'Frequency')
p<-ggplot(data=tab, aes(x=State, y=Frequency, fill=Status)) +
  geom_bar(stat="identity") + coord_flip()
p
```

As we can see, the state with the most valid responses was the Rio Grande do Sul, while the state with the most significant number of non-response was Maranhao. Maranhao is also the state with most school constructions in the Campaign, which can partially explain their rates. Para is a positive outlier in this analysis, as it has the second-largest number of schools in the campaign, but it managed to answer almost half of the requests with valid answers. Amapa is a negative outlier in the analysis, as no campaign emails have been answered.

The campaign has a higher manipulation impact, which is expected since it consists of sending emails and monitoring responses. One caveat is that the advantage of the App is that it has a more personal component attached to it. Combining these elements could be a good alternative here.

## Results from the full model

In the model below, we show that the campaign, despite the sizeable manipulation, had null effects on the studied outcomes.

```{r, results = 'asis', echo=FALSE}
stargazer(res[[2]][[4]],res[[2]][[8]],res[[2]][[12]],
          res[[2]][[16]],res[[2]][[20]],res[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 3', 
          keep='treatCampaignTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

## Results using inverse probability weights

Using inverse probability weights given by the block randomization, we show again that the campaign had null effects on the studied outcomes.

```{r, results = 'asis', echo=FALSE}
stargazer(resInt3IPW[[2]][[4]],resInt3IPW[[2]][[8]],resInt3IPW[[2]][[12]],
          resInt3IPW[[2]][[16]],resInt3IPW[[2]][[20]],resInt3IPW[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 3 (IPW)', 
          keep='treatCampaignTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

## Results using nearest neighborhood matching

Finally, using the nearest neighborhood matching, we still have a consistent null effect of the campaign on the studied outcomes.

```{r, results = 'asis', echo=FALSE}
stargazer(resInt3match[[2]][[4]],resInt3match[[2]][[8]],resInt3match[[2]][[12]],
          resInt3match[[2]][[16]],resInt3match[[2]][[20]],resInt3match[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 3 (nearest neighborhood matching)', 
          keep='treatCampaignTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Inv. Before','Inv. After',
                             'Delta Inv.','Finished Constr.',
                             'Cancel. Constr.','Updt. Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje',
          align=T, digits=3,
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T, header=FALSE)
```

## Discussion

The campaign had a consistent null effect across all treatments. This goes per most email campaigns aimed at improving development outcomes.

# Conclusion

In this report, we evaluated the TDP App (interventions 1 and 2) and the TDP campaign (intervention 3). We find that the campaign has a consistent null effect across all the analysis.

In terms of suggestions, for the first two interventions, we strongly suggest measures to improve the manipulation, such as gamification of the App and shocks in the cost-benefit calculations (such as bonuses for using the App, discount coupons in widely used Apps, and others). For the third intervention, a recent paper by Larreguy et al. (2019) showed that repeating Facebook boosting campaign has a strong effect, as saturation is key for achieving positive results in terms of online campaigns. Therefore, repeating the intervention for small periods of time (i.e., monthly, could improve the effects).

# Appendix

In this appendix, we put the APSA Experimental Section report.

## APSA Experimental Section Standard Report for Experimental Research

### A. Hypothesis

* **Main intervention questions:** The experiment studies two problems. First, whether the introduction of the Ta de Pe App improved the governmental school constructions in Brazil. Second, whether a top-down campaign to pressure the bureaucracies to deliver the school infrastructure enhanced outcomes. Therefore, the project here studies how technology facilitates bottom-up and top-down pressure to improve service provision.

* **Hypothesis**: There is a set of findings showing that bottom-up peer pressure improves outcomes in developing economies. The main work in the field shows positive peer-pressure effects:

  + Bjorkman, Martina and Jakob Svensson. 2009. “Power to the People: Evidence from a randomized field experiment of a community-based monitoring project in Uganda.” Quarterly Journal of Economics 124(2):735–769.

  + Bjorkman, Martina and Jakob Svensson. 2010. “When is community-based monitoring effective? Evidence from a randomized experiment in primary health in Uganda.” Journal of the European Economic Association 8(2-3):571–581.

  + Bjorkman Nyqvist, Martina, Damien de Walque and Jakob Svensson. 2017. “Experimental evidence on the long-run impact of community-based monitoring.” American Economic Journal: Applied Economics 9(1):33–69.

However, a set of recent papers set out to recheck these hypotheses, finding an overall null result:

  + Raffler, Pia, Dan Posner, and Doug Parkerson. The Weakness of Bottom-up Accountability: Experimental evidence from the Ugandan health sector. URL: (http://egap.org/sites/default/files/Posner%2C%20Dan_Paper.pdf)

This project is essential to reevaluate this dispute and try to propose new means to understand how bottom-up accountability works. First, we are conducting this experiment in a middle-income country, that within the country has municipalities with social indicators close to developed European countries in some areas and developing economies such as African countries, in some other areas. Second, we are evaluating school constructions, and the presence of schools have essential consequences in terms of long-run economic development, the household income composition, and woman empowerment.

### B. Subjects and Context

* **Eligibility and Exclusion criteria**: We selected all school projects that received Federal fundings from the Brazilian Ministry of Education. By an agreement with the Brazilian Ministry of Education, they allowed us to have the data of all school constructions receiving funds from them.

All schools constructions funded by the Brazilian Ministry of Education participated in this study. We had no schools excluded from the program.

* **Interventions' dates**: We had three interventions here:

1. *App impact evaluation 1*: From August 2017 to February 2018. We call this Intervention 1 throughout the text.
2. *App impact evaluation 2*: From August 2018 to February 2019. We call this Intervention 2 throughout the text.
3. *Top-down pressure by email impact evaluation*: In December 2018, the TDP bot sent an email to all delayed school constructions in the dataset.

### C. Allocation Methods

* **Assignment procedure**: The treatment here was assigned by the municipality in the first intervention, and at the school level in the second and third interventions.

1. For intervention one, we selected 150 municipalities that were placed in the control group.

The randomization code was:

```
vectreat <- c(rep(0,150), rep(1, nrow(dat)-150))

AIC_info = numeric()
for (i in 1:5000) {
  vectreat <- sample(vectreat, length(vectreat))
  mod <- glm(formula(paste('vectreat', vars, sep = '~')), 
             family = binomial, data = dat)
  if(sum(summary(mod)$coefficients[-1,4]<.2)==0) {
    dat = data.frame(dat, vtreat = vectreat)
    AIC_info = c(AIC_info, AIC(mod))
  }
}
```

And then we checked whether the randomization had one of the covariates selected here significantly predicting the random assignment. We presented a vector of acceptable random assignment in these grounds, and the Brazilian Transparency selected the one we are using in the first intervention.

2. For interventions 2 and 3, we selected 15% of the schools in the dataset that could either be placed in the treatment or in control in each of the interventions.

In interventions 1 and 2, the schools in the control group did not show up in the App. In the intervention 3, the mayors' office has not received emails from the Ta de Pe bot.

The `randomizr` code for intervention 2 follows below. `OnApp` means treatment and `OffApp` means the control for this intervention:

```
decl_intheapp <- declare_ra(blocks = dat_intheapp$var_blocking, 
                            prob_each = c(.85,.15),
                            conditions = c('OnApp', 'OffApp'))

dat_intheapp$Z_intheapp <- block_ra(blocks = dat_intheapp$var_blocking, 
                       conditions = c('OnApp', 'OffApp'),
                       prob_each = c(.85,.15))

dat_intheapp$IPW_intheapp <- 1/obtain_condition_probabilities(decl_intheapp, 
                                                              dat_intheapp$Z_intheapp)
```

The `randomizr` code for intervention 3 follows below. `Campaign` means treatment and `ControlCampaign` means the control for this intervention:

```
decl_campaign <- declare_ra(blocks = dat_campaign$var_blocking, 
                          prob_each = c(.85,.15),
                          conditions = c('Campaign', 'ControlCampaign'))

dat_campaign$Z_campaign <- block_ra(blocks = dat_campaign$var_blocking, 
              conditions = c('Campaign', 'ControlCampaign'),
              prob_each = c(.85,.15))

dat_campaign$IPW_campaign <- 1/obtain_condition_probabilities(decl_campaign, 
                                                              dat_campaign$Z_campaign)
```

***Block randomization**: We used simple randomization in the first assignment. In the second and third interventions, we blocked by the Brazilian State, the construction status, and above the median execution. The summary of the blocks, with the IPWs assigned follow below.

```{r, echo=FALSE, results='asis'}
aux <- rand2018 %>%
  select(state, status, above_median_executed, 
         var_blocking, Z_campaign, IPW_campaign) %>% 
  unique() %>%
  na.omit()
kable(aux, caption = 'Block randomization -- Intervention 2')
```

```{r, echo=FALSE, results='asis'}
aux <- rand2018 %>%
  select(state, status, above_median_executed, 
         var_blocking, Z_intheapp, IPW_intheapp) %>% 
  unique() %>%
  na.omit()
kable(aux, caption = 'Block randomization -- Intervention 3')
```

As pre-treatment variables, we used the municipal-level characteristics below:

1. Log of Municipal Population in 2015
2. Log of Number of Poor Families (2010 IBGE Census)
3. Log of Total Federal Transfers to the Municipality in 2016
4. IDEB Indicator for primary school quality (2015 Ministry of Education)
5. IDEB Indicator for secondary school quality (2015 Ministry of Education)

All the pre-treatment variables were not significant, as displayed in the main text.

### D. Treatments

* **Treatment groups**:
  + *Intervention 1*: Municipality with all schools funded by the Ministry of Education showing up in the App.
  + *Intervention 2*: School construction showing up in the App.
  + *Intervention 3*: Mayor's office received an email from the Ta de Pe bot requesting information about why the construction is delayed.

* **Control groups**:
  + *Intervention 1*: Municipality with all schools funded by the Ministry of Education **not** showing up in the App.
  + *Intervention 2*: Selected school constructions **not** showing up in the App.
  + *Intervention 3*: Mayor's office **not** receiving an email from the Ta de Pe bot.

* **Method of manipulation delivery**:
  + *Intervention 1*: The municipalities in the treatment had all their school constructions showing up in the App.
  + *Intervention 2*: The schools in the treatment group were showing up in the App.
  + *Intervention 3*: The mayor's office in the treatment group received a message from the Ta de Pe bot, requesting information about the school construction.

* **Software**: The TDP App is an Android and iOS Application developed to facilitate bottom-up pressure on school constructions in Brazil.

### E. Results

* **Outcome measures**: We use six outcome measures, all taken from the Ministry of Education biannual report:

1. Percentage of the investment executed before the impact evaluation started (placebo)
2. Percentage of the investment executed by the end of the impact evaluation period
3. The difference of the percentage invested in the end and in the beginning of the impact evaluation period
4. Indicator for a construction finished during the impact evaluation period
5. Indicator for a construction canceled during the impact evaluation period
6. Indicator for an updated conclusion date for the construction during the impact evaluation period

* **CONSORT**

Below follows the CONSORT chartflow:

  + *Intervention 1*:

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impEvalph1)[1]

# Excluded
excld <- sum(is.na(impEvalph1$treat))

# Total used randomization
diffrand <- ntotini-excld

# On treatment
tralloc <- sum(impEvalph1$treat=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impEvalph1$treat=='Control', na.rm = T)

# Attrition treatment
lostfollowuptreat <- 0

# Attrition control
lostfollowupctrl <- 0

# Analyzed treatment
analtreat <- tralloc-lostfollowuptreat

# Analyzed control
analctrl <- ctrlalloc-lostfollowupctrl

values <- c(ntotini, excld, diffrand, tralloc, ctrlalloc, 
            lostfollowuptreat, lostfollowupctrl, analtreat, analctrl)

# Defining Text Labels ----------------------------------------------------
text <- c('Assessment for\neligibility',
          'Excluded',
          'Randomized',
          'Allocated to\nTreatment',
          'Allocated to\nControl',
          'Lost to follow-up',
          'Lost to follow-up',
          'Analysed',
          'Analysed')

# Defining Function -------------------------------------------------------
paste1 <- function(x, y){
  paste0(x, ' (n=', y, ')')
}

# Concatenating Values and Text Labels ------------------------------------
LABS <- paste1(text, values)

ndf <-
  create_node_df(
    n = 21,
    label = c('Enrollment', 'Allocation', 'Follow-Up', 'Analysis',
              LABS, rep("", 8)),
    style = c(rep("solid", 13), rep('invis', 8)),
    shape = c(rep("plaintext", 4), 
              rep("box", 9),
              rep("point", 8)),
    width = c(rep(2, 4), rep(2.5, 9), rep(0.001, 8)),
    hight = c(rep(0.5, 13), rep(0.001, 8)),
    fontsize = c(rep(14, 4), rep(10, 17)),
    fontname = c(rep('Arial Rounded MT Bold', 4), rep('Courier New', 17)),
    penwidth = 2.0,
    fixedsize = "true")

edf <-
  create_edge_df(
    arrowhead = c(rep('none', 3), rep("vee", 3), rep('none', 2), "vee", rep('none', 6),
                  rep("vee", 3), rep("none", 3), "vee", rep("none", 10)),
    color = c(rep('#00000000', 3), rep('black', 6), rep('#00000000', 6),
              rep('black', 3), rep('#00000000', 3), rep('black', 1),
              rep('#00000000', 2), rep('black', 2), 
              rep('#00000000', 6)),
    constraint = c(rep("true", 18), rep('false', 14)),
    from = c(1, 19, 20, 16, 8, 10, # column 1
             5, 14, 7, 15, 2, 3, # column 2
             18, 6, 21, 17, 9, 11, # column 3
             1, 5, # row 1
             19, 14, # row 2
             20, 7, # row 3
             16, 15, # row 4
             8, 2, # row 5
             10, 3, # row 6
             12, 4), # row 7
    to = c(19, 20, 16, 8, 10, 12, # column 1
           14, 7, 15, 2, 3, 4, # column 2
           6, 21, 17, 9, 11, 13, # column 3
           5, 18, # row 1
           14, 6, # row 2
           7, 21, # row 3
           15, 17, # row 4
           2, 9, # row 5
           3, 11, # row 6
           4, 13)) # row 7

# Create Graph ------------------------------------------------------------
g <- create_graph(ndf, 
                  edf,
                  attr_theme = NULL)

# Plotting ----------------------------------------------------------------
render_graph(g)
```

  + *Intervention 2*:

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impEvalph2)[1]

# Excluded
excld <- sum(is.na(impEvalph2$treatApp))

# Total used randomization
diffrand <- ntotini-excld

# On treatment
tralloc <- sum(impEvalph2$treatApp=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impEvalph2$treatApp=='Control', na.rm = T)

# Attrition treatment
lostfollowuptreat <- 0

# Attrition control
lostfollowupctrl <- 0

# Analyzed treatment
analtreat <- tralloc-lostfollowuptreat

# Analyzed control
analctrl <- ctrlalloc-lostfollowupctrl

values <- c(ntotini, excld, diffrand, tralloc, ctrlalloc, 
            lostfollowuptreat, lostfollowupctrl, analtreat, analctrl)

# Defining Text Labels ----------------------------------------------------
text <- c('Assessment for\neligibility',
          'Excluded',
          'Randomized',
          'Allocated to\nTreatment',
          'Allocated to\nControl',
          'Lost to follow-up',
          'Lost to follow-up',
          'Analysed',
          'Analysed')

# Defining Function -------------------------------------------------------
paste1 <- function(x, y){
  paste0(x, ' (n=', y, ')')
}

# Concatenating Values and Text Labels ------------------------------------
LABS <- paste1(text, values)

ndf <-
  create_node_df(
    n = 21,
    label = c('Enrollment', 'Allocation', 'Follow-Up', 'Analysis',
              LABS, rep("", 8)),
    style = c(rep("solid", 13), rep('invis', 8)),
    shape = c(rep("plaintext", 4), 
              rep("box", 9),
              rep("point", 8)),
    width = c(rep(2, 4), rep(2.5, 9), rep(0.001, 8)),
    hight = c(rep(0.5, 13), rep(0.001, 8)),
    fontsize = c(rep(14, 4), rep(10, 17)),
    fontname = c(rep('Arial Rounded MT Bold', 4), rep('Courier New', 17)),
    penwidth = 2.0,
    fixedsize = "true")

edf <-
  create_edge_df(
    arrowhead = c(rep('none', 3), rep("vee", 3), rep('none', 2), "vee", rep('none', 6),
                  rep("vee", 3), rep("none", 3), "vee", rep("none", 10)),
    color = c(rep('#00000000', 3), rep('black', 6), rep('#00000000', 6),
              rep('black', 3), rep('#00000000', 3), rep('black', 1),
              rep('#00000000', 2), rep('black', 2), 
              rep('#00000000', 6)),
    constraint = c(rep("true", 18), rep('false', 14)),
    from = c(1, 19, 20, 16, 8, 10, # column 1
             5, 14, 7, 15, 2, 3, # column 2
             18, 6, 21, 17, 9, 11, # column 3
             1, 5, # row 1
             19, 14, # row 2
             20, 7, # row 3
             16, 15, # row 4
             8, 2, # row 5
             10, 3, # row 6
             12, 4), # row 7
    to = c(19, 20, 16, 8, 10, 12, # column 1
           14, 7, 15, 2, 3, 4, # column 2
           6, 21, 17, 9, 11, 13, # column 3
           5, 18, # row 1
           14, 6, # row 2
           7, 21, # row 3
           15, 17, # row 4
           2, 9, # row 5
           3, 11, # row 6
           4, 13)) # row 7

# Create Graph ------------------------------------------------------------
g <- create_graph(ndf, 
                  edf,
                  attr_theme = NULL)

# Plotting ----------------------------------------------------------------
render_graph(g)
```

*Intervention 3*:

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impEvalph2)[1]

# Excluded
excld <- sum(is.na(impEvalph2$treatCampaign))

# Total used randomization
diffrand <- ntotini-excld

# On treatment
tralloc <- sum(impEvalph2$treatCampaign=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impEvalph2$treatCampaign=='Control', na.rm = T)

# Attrition treatment
lostfollowuptreat <- 0

# Attrition control
lostfollowupctrl <- 0

# Analyzed treatment
analtreat <- tralloc-lostfollowuptreat

# Analyzed control
analctrl <- ctrlalloc-lostfollowupctrl

values <- c(ntotini, excld, diffrand, tralloc, ctrlalloc, 
            lostfollowuptreat, lostfollowupctrl, analtreat, analctrl)

# Defining Text Labels ----------------------------------------------------
text <- c('Assessment for\neligibility',
          'Excluded',
          'Randomized',
          'Allocated to\nTreatment',
          'Allocated to\nControl',
          'Lost to follow-up',
          'Lost to follow-up',
          'Analysed',
          'Analysed')

# Defining Function -------------------------------------------------------
paste1 <- function(x, y){
  paste0(x, ' (n=', y, ')')
}

# Concatenating Values and Text Labels ------------------------------------
LABS <- paste1(text, values)

ndf <-
  create_node_df(
    n = 21,
    label = c('Enrollment', 'Allocation', 'Follow-Up', 'Analysis',
              LABS, rep("", 8)),
    style = c(rep("solid", 13), rep('invis', 8)),
    shape = c(rep("plaintext", 4), 
              rep("box", 9),
              rep("point", 8)),
    width = c(rep(2, 4), rep(2.5, 9), rep(0.001, 8)),
    hight = c(rep(0.5, 13), rep(0.001, 8)),
    fontsize = c(rep(14, 4), rep(10, 17)),
    fontname = c(rep('Arial Rounded MT Bold', 4), rep('Courier New', 17)),
    penwidth = 2.0,
    fixedsize = "true")

edf <-
  create_edge_df(
    arrowhead = c(rep('none', 3), rep("vee", 3), rep('none', 2), "vee", rep('none', 6),
                  rep("vee", 3), rep("none", 3), "vee", rep("none", 10)),
    color = c(rep('#00000000', 3), rep('black', 6), rep('#00000000', 6),
              rep('black', 3), rep('#00000000', 3), rep('black', 1),
              rep('#00000000', 2), rep('black', 2), 
              rep('#00000000', 6)),
    constraint = c(rep("true", 18), rep('false', 14)),
    from = c(1, 19, 20, 16, 8, 10, # column 1
             5, 14, 7, 15, 2, 3, # column 2
             18, 6, 21, 17, 9, 11, # column 3
             1, 5, # row 1
             19, 14, # row 2
             20, 7, # row 3
             16, 15, # row 4
             8, 2, # row 5
             10, 3, # row 6
             12, 4), # row 7
    to = c(19, 20, 16, 8, 10, 12, # column 1
           14, 7, 15, 2, 3, 4, # column 2
           6, 21, 17, 9, 11, 13, # column 3
           5, 18, # row 1
           14, 6, # row 2
           7, 21, # row 3
           15, 17, # row 4
           2, 9, # row 5
           3, 11, # row 6
           4, 13)) # row 7

# Create Graph ------------------------------------------------------------
g <- create_graph(ndf, 
                  edf,
                  attr_theme = NULL)

# Plotting ----------------------------------------------------------------
render_graph(g)
```

* **Reasons for exclusion in the CONSORT:**

  + *Intervention 1*: Constructions that were not in the App when the intervention started.

  + *Intervention 2*: Constructions that were not in the App when the intervention started.

  + *Intervention 3*: Constructions that e-mail contact information was not provided by the Ministry of Education website.

* **Statistical analysis**:

For all interventions, we run the following regression model:

$$ Y_i \quad = \quad \alpha + \beta T_i + \gamma X_i + \theta F_i + \varepsilon_i $$

Where $i$ indexes a given school observed in the intervention. $Y_i$ represents an outcome variable. $T_i$ represents a treatment indicator. $\beta$ represents the estimated Average Treatment Effect. $\gamma$ is a vector of pre-treatment coefficient effects and $X_i$ a vector of pre-treatment covariates. $\theta$ represents a vector of fixed effects estimands and $F_i$ the Brazilian state level fixed effects indicator vector. $\varepsilon_i$ is the common error term.

We run three types of analysis:

1. Full regressions with all data available
2. Full regressions using Inverse Probability Weights
3. Regression where we match the control group with a same-size treatment group on the proximity of covariates using Genetic matching.

All models use municipal-level cluster robust standard errors and state-level fixed effects. For all models, we also run regressions without clustering and without fixed effects.

* **Software**: We use `r R.version.string`. For the regression models estimation, we use the package `lfe`. For the Genetic matching, we use the package `MatchIt`. Everything in this report is fully automated and can be reproduced using R Markdown.

Further information about the workstation follows below:

```{r}
sessionInfo()
```

### F. Other information

* **IRB**: FGV exempted the primary investigator from getting IRB approval because this research mostly worked online data and was approved by the Brazilian Ministry of Education.

* **Pre-registration**: this research has been pre-registered on the EGAP pre-registry tool: (https://egap.org/registration/4505)

* **Replication materials**: The replication materials for this project are available here: (https://github.com/umbertomig/TDPImpactEval)

* **Funding**: This research received funding from the Google Social Impact initiative. Google did not interfere in any aspects of the research design and analysis.

* **Conflict of interests**: The authors of this analysis declare no conflict of interest.

## Intervention 1

### Percentage concluded before the intervention started (placebo test)

```{r, echo=FALSE, warning=FALSE}
# Percentage Concluded before intervention (placebo)
stargazer(resInt1[[2]][[1]],resInt1[[2]][[2]],resInt1[[2]][[3]],resInt1[[2]][[4]],
          title = 'Percentage Concluded Before (placebo)', 
          keep='treatTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F, label='placph1',
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust SEs at the Municipal Level.',
          notes.append = T)
```

The placebo test remains not significant, as expected. Note that we are using a p-value of 10%, adding extra sensitivy to the hypothesis tests carried out here.

### Percentage concluded by the end of the intervention

Next, consider the percentage of construction that was carried out in this phase of the impact evaluation. The table below displays the results, presenting a null effect of the app over this indicator.

```{r, echo=FALSE, warning=FALSE}
# Percentage Concluded
stargazer(resInt1[[2]][[5]],resInt1[[2]][[6]],resInt1[[2]][[7]],resInt1[[2]][[8]],
          title = 'Percentage Concluded', 
          keep='treatTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F, label='placph1',
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

### Delta Percentage of Execution

We take the difference between the inicial and final percentage of the executed construction in this impact evaluation. This aims to capture changes in the construction pace, that the app could have positively impacted.

```{r impevaldeltapercph1, echo=FALSE, warning=FALSE}
# Delta Percentage
stargazer(resInt1[[2]][[9]],resInt1[[2]][[10]],resInt1[[2]][[11]],resInt1[[2]][[12]],
          title = 'Difference Percentage Begin and End', 
          keep='treatTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F, label='placph1',
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

### Finished indicator

A finished school in the period was labelled the schools that were still not concluded by the begining of the intervention, in August 2017, but that were finished by March 2018, when the intervention stopped. The regressions here are linear probability models, and the coefficients can be interpreted as improving the chance of XXXX.

```{r impevaldisfinishph1, echo=FALSE, warning=FALSE}
# Is it finished?
stargazer(resInt1[[2]][[13]],resInt1[[2]][[14]],resInt1[[2]][[15]],resInt1[[2]][[16]],
          title = 'Finished Construction Indicator', 
          keep='treatTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F, label='placph1',
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

In this indicator, we witness a strong and consistent effect around of 5% impact. This represents that the presence of the App increased in around 5% the chance that the construction finished.

### Cancelled indicator

A cancelled school in the period is the schools that were still not concluded by the begining of the intervention, in August 2017, but that the construction was abandoned by March 2018, when the intervention stopped. The regressions here are linear probability models, and the coefficients can be interpreted as improving the chance of a cancellation, whenever the coefficient is positive.

```{r impevaliscancelledph1, echo=FALSE, warning=FALSE}
# Is it cancelled?
stargazer(resInt1[[2]][[17]],resInt1[[2]][[18]],resInt1[[2]][[19]],resInt1[[2]][[20]],
          title = 'Cancelled Construction Indicator', 
          keep='treatTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F, label='placph1',
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = 
            list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                 c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

Again, the results are significant, and around 2.8%. We interpret this result as the App pressure making the policy-makers more resolute. They either work toward finish the constructions, or they report them cancelled, voiding the impact of the App.

### Updated end date for the construction

This indicator reports whether the construction date was updated in the Federal Government databases. An update can mean a change toward a more realistic conclusion date, ameliorating the expectations of the citizens. The results below show that there were no changes in this indicator.

```{r impevalupddateph1, echo=FALSE, warning=FALSE}
# End Date Update Indicator
stargazer(resInt1[[2]][[21]],resInt1[[2]][[22]],resInt1[[2]][[23]],resInt1[[2]][[24]],
          title = 'End Date Update Indicator', 
          keep='treatTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F, label='placph1',
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)

```

## Intervention 2

### Percentage concluded before the intervention (placebo)

```{r impevalp2plac, echo=FALSE, warning=FALSE}
# Percentage Concluded before intervention (placebo)
stargazer(resInt2[[2]][[1]],resInt2[[2]][[2]],resInt2[[2]][[3]],resInt2[[2]][[4]],
          title = 'Percentage Concluded Before (placebo)', 
          keep='treatApp', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = 
            list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                 c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

Placebo not significant, as expected.

### Percentage construction concluded

```{r impevalp2pctconcl, echo=FALSE, warning=FALSE}
# Percentage Concluded
stargazer(resInt2[[2]][[5]],resInt2[[2]][[6]],resInt2[[2]][[7]],resInt2[[2]][[8]],
          title = 'Percentage Concluded', 
          keep='treatApp', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

App did not affected the percentage concluded. Moreover, the sign is flipped, suggesting that it could potentially have a negative impact on the percentage concluded.

### Difference between begin and end of percentage concluded

```{r impevalp2deltaapp, echo=FALSE, warning=FALSE}
# Delta Percentage
stargazer(resInt2[[2]][[9]],resInt2[[2]][[10]],resInt2[[2]][[11]],resInt2[[2]][[12]],
          title = 'Difference Percentage Begin and End', 
          keep='treatApp', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

No effect in the difference between begin and end.

### Finished construction indicator

```{r impevalp2appfinish, echo=FALSE, warning=FALSE}
# Is it finished?
stargazer(resInt2[[2]][[13]],resInt2[[2]][[14]],resInt2[[2]][[15]],resInt2[[2]][[16]],
          title = 'Finished Construction Indicator', 
          keep='treatApp', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

No impact in the second phase of the app on the finishing of a construction.

### Indicator for cancelled construction

```{r impevalp2appcancelled, echo=FALSE, warning=FALSE}
# Is it cancelled?
stargazer(resInt2[[2]][[17]],resInt2[[2]][[18]],resInt2[[2]][[19]],resInt2[[2]][[20]],
          title = 'Cancelled Construction Indicator', 
          keep='treatApp', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

No effect of the App on cancelling of constructions.

### Updating end date

```{r impevalp2appupd, echo=FALSE, warning=FALSE}
# End Date Update Indicator
stargazer(resInt2[[2]][[21]],resInt2[[2]][[22]],resInt2[[2]][[23]],resInt2[[2]][[24]],
          title = 'End Date Update Indicator', 
          keep='treatApp', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

Small effect on update, in the model without Fixed effects and with controls. Very weak evidence to conclude anything concrete here.

## Campaign Impact Evaluation

All covariate balanced. Note that the data is not sufficient to compute the differences in the campaign for the FUNDEB transfers indicator.

##### Percentage concluded before (placebo)

```{r, echo=FALSE, warning=FALSE}
# Percentage Concluded before intervention (placebo)
stargazer(res[[2]][[1]],res[[2]][[2]],res[[2]][[3]],res[[2]][[4]],
          title = 'Percentage Concluded Before (placebo)', 
          keep='treatCampaignTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

No effect of the campaign on the placebo.

##### Campaign impact on percentage concluded

```{r impevalp2percconclcamp, echo=FALSE, warning=FALSE}
# Percentage Concluded
stargazer(res[[2]][[5]],res[[2]][[6]],res[[2]][[7]],res[[2]][[8]],
          title = 'Percentage Concluded', 
          keep='treatCampaignTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

No effect of campaign on percentage concluded.

##### Impact of campaign on the difference between begin and end percentage concluded

```{r impevalp2deltaperccamp, echo=FALSE, warning=FALSE}
# Delta Percentage
stargazer(res[[2]][[9]],res[[2]][[10]],res[[2]][[11]],res[[2]][[12]],
          title = 'Difference Percentage Begin and End', 
          keep='treatCampaignTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

Small negative effect in the uncontrolled models. Not strong evidence enough to conclude that the campaign affected the changes in percentages reported.

##### Impact of campaign in constructions reported finished in the period

```{r impevalp2isfinishcamp, echo=FALSE, warning=FALSE}
# Is it finished?
stargazer(res[[2]][[13]],res[[2]][[14]],res[[2]][[15]],res[[2]][[16]],
          title = 'Finished Construction Indicator', 
          keep='treatCampaignTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

Again, very small evidence on the uncontrolled models. Suspicion: the controls have missings in particular points that make the models insignificant. Suggestion: run Amelia, or another missing data simulation device to check for the possibility of differential missing.

##### Campaign impact on constructions reported cancelled

```{r impevalp2cancelcamp, echo=FALSE, warning=FALSE}
# Is it cancelled?
stargazer(res[[2]][[17]],res[[2]][[18]],res[[2]][[19]],res[[2]][[20]],
          title = 'Cancelled Construction Indicator', 
          keep='treatCampaignTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)
```

Here the results are strong and robust. The campaign reduces the amount of constructions reported as cancelled by around 9%. This represents an important outcome in terms of constructions, as fewer constructions were abandoned as an effect of the campaign.

##### Campaign effect on enddate updating

```{r impevalp2updcamp, echo=FALSE, warning=FALSE}
# End Date Update Indicator
stargazer(res[[2]][[21]],res[[2]][[22]],res[[2]][[23]],res[[2]][[24]],
          title = 'End Date Update Indicator', 
          keep='treatCampaignTreatment', type = 'text',
          covariate.labels = 'ATE',
          column.labels = NULL,
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='qje', 
          model.numbers = T, align=T, digits=3,
          add.lines = list(c('FEs', 'No', 'No', 'Yes', 'Yes'),
                           c('Controls', 'No', 'Yes', 'No', 'Yes')),
          notes = 'Cluster-robust Standard Errors at the Municipal Level.',
          notes.append = T)

```

Small effect, specially in the controlled and fixed effect model. However, the effect is small and we advice caution in interpreting this as an evidence that the implementer changed the dates for a better estimate.

## Descriptive stats

```{r descrpt}
# Visible App Begin
tab <- data.frame(table(impEvalph1$visAppIni))
names(tab) <- c('VisibleApp', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=VisibleApp, y=Frequency)) +
  geom_bar(stat="identity")
p
```

```{r, echo=FALSE, warning=FALSE}
# Control and Treatment
tab <- data.frame(table(impEvalph1$treat))
names(tab) <- c('TreatmentStatus', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=TreatmentStatus, y=Frequency)) +
  geom_bar(stat="identity")
p
```

```{r, echo=FALSE, warning=FALSE}
# Schooling responsible
tab <- data.frame(table(impEvalph1$govLevelAdmin))
names(tab) <- c('ResponsibleParty', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=ResponsibleParty, y=Frequency)) +
  geom_bar(stat="identity")
p
```

```{r, echo=FALSE, warning=FALSE}
## Alerts Graphs
# Graph alert date
tab <- data.frame(table(allalert$year_month[allalert$campaign_alert=='App']))
names(tab) <- c('Date', 'Frequency')
tab
p <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
  geom_line() + geom_point()
p
```

```{r, echo=FALSE, warning=FALSE}
# Graph phase alert
tab <- data.frame(table(allalert$phase[allalert$campaign_alert=='App']))
names(tab) <- c('Phase', 'Alerts')
tab
p<-ggplot(data=tab, aes(x=Phase, y=Alerts)) +
  geom_bar(stat="identity")
p
```

```{r, echo=FALSE, warning=FALSE}
# Campaign x app alert
tab <- data.frame(table(allalert$campaign_alert))
names(tab) <- c('Source', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=Source, y=Frequency)) +
  geom_bar(stat="identity")
p
```

```{r, echo=FALSE, warning=FALSE}
## Map GA phase 1: city with
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- left_join(gaaux2, gaaux); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
head(gaaux)
plot_brmap(mapbr,
           data_to_join = gaaux,
           join_by = c("City" = "City"),
           var = "Downloads") +
  labs(title = 'App Downloads -- Phase 1')
```

```{r, echo=FALSE, warning=FALSE}
## Map GA phase 2: number downloads
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- left_join(gaaux2, gaaux); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
head(gaaux)
p <- plot_brmap(mapbr,
                data_to_join = gaaux,
                join_by = c("City" = "City"),
                var = "Downloads") +
  labs(title = 'App Downloads -- Phase 2')
p
```

```{r, echo=FALSE, warning=FALSE}
## Aggregate by date and graph daily downloads

# Phase 1
tab <- filter(ga, phase1 == 1) %>%
  group_by(data) %>%
  summarize(NewUsers = sum(novos_usuarios))
names(tab) <- c('Date', 'Frequency')
tab
p <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
  geom_line() + geom_point()
p
```

## Alerts

## Analyzing the campaign alerts

#### Alerts by Date

```{r alertbydate}
tab <- data.frame(table(allalert$answeredBy))
names(tab) <- c('AnsweredBy', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=AnsweredBy, y=Frequency)) +
  geom_bar(stat="identity")
p
```

#### Alerts by construction

```{r numconstr}
# Number by construction
tab <- data.frame(table(table(allalert$project_id)))
names(tab) <- c('AlertsSameConstruction', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=AlertsSameConstruction, y=Frequency)) +
  geom_bar(stat="identity")
p
```

#### Alert Answers

```{r alertsAnswered}
# Alerts Answered
tab <- data.frame(table(allalert$status))
names(tab) <- c('Status', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=Status, y=Frequency)) +
  geom_bar(stat="identity")
p
```

#### Alerts by validity

```{r statusAlert}
tab <- data.frame(table(allalert$status2))
names(tab) <- c('Status', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=Status, y=Frequency)) +
  geom_bar(stat="identity")
p
```

#### Frequency of Alerts by State

```{r alertsByState}
# Alerts by state
tab <- data.frame(sort(table(allalert$state)))
names(tab) <- c('State', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=State, y=Frequency)) +
  geom_bar(stat="identity") + coord_flip()
p
```

#### Frequency of Alerts by State by Total of State's Construction

Barchart with frequency of alerts by each construction. This Figure shows the amount of alerts divided by the amount of schools in a given State. Increasing this number denotes that more schools are

```{r alertsByStateRelative}
# Alerts by state over total
tab <- data.frame(sort(table(allalert$state)))
tab2 <- data.frame(sort(table(unique(impEvalph2[,c('id_project','state')])$state)))
names(tab) <- c('State', 'Frequency')
names(tab2) <- c('State', 'Total')
tab <- left_join(tab, tab2)
tab$Proportion = 100*(tab$Frequency/tab$Total)
tab <- tab[order(tab$Proportion),]
tab$State <- factor(tab$State, levels = tab$State[order(tab$Proportion)])
tab
p<-ggplot(data=tab, aes(x=State, y=Proportion)) +
  geom_bar(stat="identity") + coord_flip()
p
```

#### Frequency of Alerts by State and Status

```{r statusByState}
# Status answer by state
tab <- data.frame(table(allalert$status2, allalert$state))
names(tab) <- c('Status', 'State', 'Frequency')
tab
p<-ggplot(data=tab, aes(x=State, y=Frequency, fill=Status)) +
  geom_bar(stat="identity") + coord_flip()
p
```

```{r mapNotAnsweredByState}
# Map not answered by state
stateCode <- pop2015[,c('ibge_code7', 'state')]
stateCode$State <- substr(stateCode$ibge_code7, 1,2)
stateCode$ibge_code7 <- NULL
stateCode <- unique(stateCode)
tab <- data.frame(table(allalert$status2, allalert$state))
tab <- tab[tab$Var1=='Not Answered',]; row.names(tab) <- NULL
names(tab) <- c('Status', 'state', 'NotAnswered')
tab <- left_join(tab, stateCode)
tab$State <- as.numeric(tab$State)
rm(stateCode)
tab$state <- NULL
tab
mapbr <- get_brmap('State')
plot_brmap(mapbr,
           data_to_join = tab,
           join_by = c("State" = "State"),
           var = "NotAnswered") +
  labs(title = 'Frequency Not Answered by State')
```

```{r mapValidAnsByState}
# Map valid answer by state
stateCode <- pop2015[,c('ibge_code7', 'state')]
stateCode$State <- substr(stateCode$ibge_code7, 1,2)
stateCode$ibge_code7 <- NULL
stateCode <- unique(stateCode)
tab <- data.frame(table(allalert$status2, allalert$state))
tab <- tab[tab$Var1=='Valid Answer',]; row.names(tab) <- NULL
names(tab) <- c('Status', 'state', 'ValidAnswer')
tab <- left_join(tab, stateCode)
tab$State <- as.numeric(tab$State)
rm(stateCode)
tab$state <- NULL
tab
mapbr <- get_brmap('State')
plot_brmap(mapbr,
           data_to_join = tab,
           join_by = c("State" = "State"),
           var = "ValidAnswer") +
  labs(title = 'Frequency Valid Answer by State')
```

### 2019-07-31 article/article.Rmd
add pars section 2

@@
 One of the key determinants of efficient public service provision is a robust accountability system \citep{besley2003incentives,cameron2004public,o1998horizontal}.
-In its standard definition, accountability is the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
+In its standard definition, accountability is understood as the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
 Past studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
@@
 Here we assess the impact of a technology-driven solution that lowers the costs of evaluating public works and punishing political representatives in Brazil.
-The _Tá de Pé_ (TDP) mobile phone application allows Brazilian citizens to go to school construction sites, check their status, and request information to public authorities.
-TDP users can also take pictures from delayed works and submit them to a group of trained engineers, who then evaluate the execution of the project.
-If the engineers classify the construction as delayed, TDP sends a message to the mayor's office asking for completion estimates and explanations about why the building is unfinished.
-TDP received the 2016 Google Social Impact grant, earning more than 200 thousand popular votes, and it has been online since April 2017 in 1030 Brazilian municipalities.
+Developed by Transparência Brasil[^transparencia], the _Tá de Pé_ (TDP) mobile phone application allows Brazilian citizens to know the location of public school construction sites, check their completion status, and anonymously request information from competent authorities.
+TDP users can also take pictures of delayed works and submit them to a group of trained engineers for examination.
+If the engineers classify the construction as delayed, TDP sends a message to the mayor's office asking for completion estimates and explanations about the construction status.
+TDP has been online since April 2017 in 1030 Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200 thousand popular votes[^google].
 
+[^transparencia]: Transparência Brasil is an non-governmental organisation whose mission is to 'promote transparency and social control of public power' in Brazil.
+It has been active since April 2000, is non-partisan and receives no public funding.
+More information is available at <http://transparencia.org.br> (access: July 2019).
+
+[^google]: About 1,000 Brazilian charities participated in the 2016 Google Social Impact Challenge and an independent selection committee selected 10 of them as finalists.
+Transparência Brasil was then the highest voted NGO by the public.
+To know more about the contest, please visit <https://impactchallenge.withgoogle.com/brazil2016> (access: July 2019).
+
+We used TDP to conduct three experimental interventions.
+We tested whether the app has a positive impact on school completion rates, school construction status and complaints to competent authorities.
 Contrary to our expectations, the TDP app has delivered mixed results.
-Two findings are positive and in line with our theoretical predictions.
+Two of the findings are positive and in line with our theoretical predictions.
 From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX).
@@
 Therefore, our findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
+**Nota**: _Reescrever essa última frase e colocar mais explicações sobre possíveis mecanismos, etc_
 
-# The _Tá de Pé_ App
-\label{sec:tdp}
+# The _Tá de Pé_ Project \label{sec:tdp}
+
+The _Tá de Pé_[^tdp] cell phone application is an initiative carried out by Transparência Brasil to foster bottom-up accountability in the Brazilian public sector.
+More specifically, the main goal of the TDP project is to improve the responsiveness in education infrastructure public expenditures.
+As we mentioned above, TDP incentivises citizens to provide up-to-date information about unfinished schools in their neighbourhoods, and these pictures are then assessed by engineers.
+In the case the construction is behind schedule, citizens are also provided with tools to contact their representatives quickly and anonymously.
+The app sends a notification to the mayor's office which has 15 days to answer.
+If they fail answer by the deadline, a notification goes to the federal government, making it harder to the municipality to access federal funds in the future.
+The motivation for the intervention is that information delivery causes individuals to closely monitor public works.
+This, in turn, results in better social outcomes as public agents become more responsible to community demands.
+
+[^tdp]: _Tá de Pé_ is an informal Brazilian expression for 'is it done?'. Literally, it means 'standing on its feet' in Portuguese.
+
+We built the app in the first three months of 2017 and tested it in May 2017.
+The first stable Android version was deployed on Google Play on 14 August 2017.
+A version for iOS appeared two weeks later.
+At the same time, a massive Facebook campaign started in order to publicise the app.
+Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
+The campaigns were concentrated in October 2017, investing around BRL 14.333,74 (US$ 4.479,29), and attracting 2028 new users in October 2017 only.
+
+\vspace{.2cm}
+
+\begin{figure}
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
+       \includegraphics[scale=0.25]{tdp01.jpg}
+       \label{}
+     \end{minipage}
+     \hfill
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
+       \includegraphics[scale=0.25]{tdp02.jpg}
+     \end{minipage}
+     \hfill
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
+       \includegraphics[scale=0.25]{tdp03.jpg}
+     \end{minipage}
+\caption{The \textit{Tá de Pé} mobile phone application.
+The first image shows that a school construction is delayed by 9 months.
+The second image shows how citizens can add information to the photos they submit via the app.
+The last image presents a list of the closest school construction sites.}
+\label{fig:screenshots}
+\end{figure}
+
+Transparência Brasil established a partnership with the Brazilian branch of _Engineers without Borders_ (EWB), a non-governmental organisation dedicated to promote international development[^ewb], to provide unbiased evaluations of school completion rates.
+Their assessment is based on photos and GPS location sent through the app.
+All data are collected anonymously and neither organisation are able to identify which user uploaded the images.
+Information on users' alerts are stored on their mobile devices, so citizens can track whether their request has been answered by public authorities.
+
+[^ewb]: Please visit <http://www.ewb-international.org> to know more about Engineers without Borders International and <https://esf.org.br> for information on the Brazilian office.
+
+The TDP has also received feedback from Brazilian computer programmers and policy analists.
+In 2017 and 2018, Transparência Brasil announced two team programming competitions, called 'Tá de Pé Hackathons', where contributors could fix code bugs and suggest new functionalities to TDP.
+In total, 75 participants
 

### 2019-07-31 tdp/analysis3.Rmd
add pars section 2

@@
 title: "Analysis Tá de Pé"
-author: "Umberto Mignozzetti"
+author: ''
 date: "7/26/2019"
+output:
+  html_document:
+    df_print: paged
 header-includes:
@@
 - \usepackage{caption,tabularx,booktabs,dcolumn}
-output: pdf_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+r <- getOption("repos")
+r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
+options(repos = r)
+
 ####
@@
 # Data block randomization
-setwd("~/Dropbox/Academic/Projects/TDP/2_analysis/")
-load('./bucket/final_bucket.RData')
+setwd("/Users/danilo/Documents/github/TDPImpactEval/tdp/")
+load('final_bucket.RData')
 

### 2019-07-31 article/article.Rmd
update

@@
 date: \today
-thanks: "We thank Guilherme Fasolin, Stephen Herzog, and David Skarbek for their helpful comments.
+thanks: "We thank Guilherme Fasolin, Stephen Herzog and David Skarbek for their helpful comments.
 We are specially grateful to the staff of Transparência Brasil for their excellent research and technical assistance.
@@
 
-One of the key determinants of efficient public service provision is a robust accountability system \citep{besley2003incentives,cameron2004public,o1998horizontal}.
-In its standard definition, accountability is understood as the process of holding authorities into account for their actions \citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
-Past studies show that accountability ensures that politicians act on behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the opportunities for rent-seeking and corruption \citep{deininger2005does,wenar2006accountability} and increases the efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
-Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital \citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.
+One of the key determinants of efficient public service provision is a robust accountability system [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
+In its standard definition, accountability is understood as the process of holding authorities into account for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
+Past studies show that accountability ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and increases the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
+Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
 
 However, accountability systems can take many forms.
-One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials \citep{kosack2014does, molina2016community,raffler2018weakness}.
-Proponents suggest bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities \citep[570]{serra2011combining}.
-In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve \citep[2]{raffler2018weakness}.
+One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
+Proponents suggest bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities [@serra2011combining, 570].
+In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
 
@@
 It has been active since April 2000, is non-partisan and receives no public funding.
-More information is available at <http://transparencia.org.br> (access: July 2019).
+More information at <http://transparencia.org.br> (access: July 2019).
 
@@
 
-We used TDP to conduct three experimental interventions.
-We tested whether the app has a positive impact on school completion rates, school construction status and complaints to competent authorities.
+We used TDP to conduct **two/three?** experimental interventions.
+We tested whether the app has a positive impact on **school completion rates, school construction status and complaints to competent authorities**.
 Contrary to our expectations, the TDP app has delivered mixed results.
-Two of the findings are positive and in line with our theoretical predictions.
+**One/Two** of the findings are positive and in line with our theoretical predictions.
 From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX).
@@
 The motivation for the intervention is that information delivery causes individuals to closely monitor public works.
-This, in turn, results in better social outcomes as public agents become more responsible to community demands.
+This, in turn, results in better social outcomes as public agents become more responsive to community demands.
 
@@
 The first stable Android version was deployed on Google Play on 14 August 2017.
-A version for iOS appeared two weeks later.
-At the same time, a massive Facebook campaign started in order to publicise the app.
+A version for iOS appeared six months later.
+A massive Facebook campaign started in order to publicise the app.
 Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
-The campaigns were concentrated in October 2017, investing around BRL 14.333,74 (US$ 4.479,29), and attracting 2028 new users in October 2017 only.
+The campaigns were concentrated in October 2017, investing around BRL 14.333,74 (US$ 4.479,29), and attracting 2,028 new users in October 2017 only.
 
@@
        \centering
+       \includegraphics[scale=0.25]{tdp03.jpg}
+       \label{}
+     \end{minipage}
+     \hfill
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
        \includegraphics[scale=0.25]{tdp01.jpg}
-       \label{}
      \end{minipage}
@@
      \end{minipage}
-     \hfill
-     \begin{minipage}[t]{.3\textwidth}
-       \centering
-       \includegraphics[scale=0.25]{tdp03.jpg}
-     \end{minipage}
 \caption{The \textit{Tá de Pé} mobile phone application.
-The first image shows that a school construction is delayed by 9 months.
-The second image shows how citizens can add information to the photos they submit via the app.
-The last image presents a list of the closest school construction sites.}
+The first image presents a list of the closest school construction sites.
+The second image shows that a school construction is delayed by 9 months.
+The last image shows how citizens can add information to the photos they submit via the app.}
 \label{fig:screenshots}

### 2019-07-31 article/article.Rmd
light editing intro

@@
 One of the key determinants of efficient public service provision is a robust accountability system [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
-In its standard definition, accountability is understood as the process of holding authorities into account for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
-Past studies show that accountability ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and increases the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
-Moreover, greater accountability is associated with higher levels of economic growth, not only because it limits state discretion in the economy, but also because it promotes social cohesion and long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
+In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
+Past studies show that accountability ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
+Moreover, greater accountability leads to higher economic growth as it limits state discretion in the economy, promotes social cohesion and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
 
 However, accountability systems can take many forms.
-One promising model for democratic oversight is _bottom-up accountability_, in which citizens receive information about the shortcomings of a given project to help them monitor and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
+One promising model for democratic oversight is _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project to help them evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
 Proponents suggest bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities [@serra2011combining, 570].
@@
 The _Tá de Pé_[^tdp] cell phone application is an initiative carried out by Transparência Brasil to foster bottom-up accountability in the Brazilian public sector.
-More specifically, the main goal of the TDP project is to improve the responsiveness in education infrastructure public expenditures.
-As we mentioned above, TDP incentivises citizens to provide up-to-date information about unfinished schools in their neighbourhoods, and these pictures are then assessed by engineers.
-In the case the construction is behind schedule, citizens are also provided with tools to contact their representatives quickly and anonymously.
-The app sends a notification to the mayor's office which has 15 days to answer.
-If they fail answer by the deadline, a notification goes to the federal government, making it harder to the municipality to access federal funds in the future.
+More specifically, the main goal of the TDP project is to improve responsiveness in government education expenditures.
+The TDP app incentivises citizens to provide up-to-date information about unfinished schools in their neighbourhoods, and the data will be assessed by a group of independent specialists.
+In the case the construction is behind schedule, TDP provides a writing platform whereby citizens can contact their representatives quickly and anonymously.
+The app then sends a notification to the mayor's office, which has 15 days to reply.
+If they do not respond to the request, a notification goes to the federal government, making it harder to the municipality to access federal funds in the future.
 The motivation for the intervention is that information delivery causes individuals to closely monitor public works.

### 2019-08-01 article/article.Rmd
small changes

@@
 One promising model for democratic oversight is _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project to help them evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
-Proponents suggest bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities [@serra2011combining, 570].
+Proponents argue bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities [@serra2011combining, 570].
 In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
@@
 Here we assess the impact of a technology-driven solution that lowers the costs of evaluating public works and punishing political representatives in Brazil.
-Developed by Transparência Brasil[^transparencia], the _Tá de Pé_ (TDP) mobile phone application allows Brazilian citizens to know the location of public school construction sites, check their completion status, and anonymously request information from competent authorities.
+Developed by Transparência Brasil[^transparencia], the _Tá de Pé_ (TDP) mobile phone application allows Brazilian citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
 TDP users can also take pictures of delayed works and submit them to a group of trained engineers for examination.
-If the engineers classify the construction as delayed, TDP sends a message to the mayor's office asking for completion estimates and explanations about the construction status.
-TDP has been online since April 2017 in 1030 Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200 thousand popular votes[^google].
+If the engineers classify the construction as delayed, TDP allows users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
+TDP has been online since April 2017 in 1030 Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
 
@@
 
-We used TDP to conduct **two/three?** experimental interventions.
-We tested whether the app has a positive impact on **school completion rates, school construction status and complaints to competent authorities**.
-Contrary to our expectations, the TDP app has delivered mixed results.
+We use the TDP app to conduct **two/three?** experimental interventions.
+We test whether the app has a positive impact on **school completion rates, school construction status and complaints to competent authorities**.
+Contrary to our expectations, our experiments have delivered mixed results.
 **One/Two** of the findings are positive and in line with our theoretical predictions.
@@
 Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = XXX).
-In contrast, our results show the app had a null impact on school constructions statistics.
+In contrast, our results show the app has a null impact on school constructions statistics.
 Brazilian politicians did not respond to the citizen's requests placed via the application.
@@
 More specifically, the main goal of the TDP project is to improve responsiveness in government education expenditures.
-The TDP app incentivises citizens to provide up-to-date information about unfinished schools in their neighbourhoods, and the data will be assessed by a group of independent specialists.
+The TDP app incentivises citizens to provide up-to-date information about unfinished schools in their neighbourhoods, and that information will be assessed by a group of independent specialists.
 In the case the construction is behind schedule, TDP provides a writing platform whereby citizens can contact their representatives quickly and anonymously.
-The app then sends a notification to the mayor's office, which has 15 days to reply.
-If they do not respond to the request, a notification goes to the federal government, making it harder to the municipality to access federal funds in the future.
+The app then prompts citizen to write a notification to the mayor's office, which has 15 days to reply.
+If they do not respond to the request, the app forwards the notification to the Brazilian federal government, making it harder to the municipality to access federal funds in the future.
 The motivation for the intervention is that information delivery causes individuals to closely monitor public works.
@@
 Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
-The campaigns were concentrated in October 2017, investing around BRL 14.333,74 (US$ 4.479,29), and attracting 2,028 new users in October 2017 only.
+The campaigns were concentrated in October 2017 and cost US$ 4,479.29.
+Facebook advertisements attracted 2,028 new users to the platform in October 2017 only.
 
@@
 Their assessment is based on photos and GPS location sent through the app.
-All data are collected anonymously and neither organisation are able to identify which user uploaded the images.
+All data are collected anonymously.
 Information on users' alerts are stored on their mobile devices, so citizens can track whether their request has been answered by public authorities.

### 2019-08-06 article/article.Rmd
add text

@@
 title:  |
-        | The Pitfalls of Bottom-Up Accountability: Evidence from Brazil
+        | Bottom-Up Accountability and Infrastructure Delivery: Mixed Evidence from Brazil
 author: 
@@
 date: \today
-thanks: "We thank Guilherme Fasolin, Stephen Herzog and David Skarbek for their helpful comments.
-We are specially grateful to the staff of Transparência Brasil for their excellent research and technical assistance.
+thanks: "We thank Fábio Barros, Guilherme Fasolin, Stephen Herzog and David Skarbek for their helpful comments.
+We are specially grateful to the staff of Transparência Brasil for their excellent research assistance.
+This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education.
+The authors thank the 2016 Google Social Impact Challenge for financial support and declare there are no conflict of interest.
 Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
 abstract: "We study the effect of a mobile phone application designed to increase citizens' ability to monitor public works in Brazil.
-The app allowed individuals to find delayed school constructions in XXX Brazilian cities and send anonymous messages to politicians requestions information about construction delays and expected completion times.
-Our results show that the app has a null impact on the completion times subsequently reported by the municipalities.
-Additionally, we find that few politicians reacted to citizens' requests.
+The app allows individuals to find delayed school constructions in 1030 Brazilian cities and send anonymous messages to politicians requesting information about construction delays and completion times.
+Our results show the app has a null impact on the completion times subsequently reported by the municipalities.
+Additionally, we find that few politicians react to citizens' requests.
 These findings suggest it is difficult to motivate bottom-up accountability in new democracies, especially when politicians are unresponsive to non-electoral pressures.
@@
 fontsize: 12pt
-margin: 2cm
+margin: 
 urlcolor: darkblue
@@
 
-[^galdino]: Executive Diretor, Transparência Brazil, São Paulo, SP, Brazil, [mcz.fea@gmail.com](mailto:mcz.fea@gmail.com), <https://www.transparencia.org.br>.
+[^galdino]: Executive Diretor, Transparência Brazil, São Paulo, SP, Brazil, [mgaldino@transparencia.org.br](mailto:mgaldino@transparencia.org.br), <https://www.transparencia.org.br>.
 
@@
 
-[^voigt]: Data Scientist, Transparência Brasil, São Paulo, SP, Brazil, [voigt.jessica@gmail.com](mailto:voigt.jessica@gmail.com), <https://www.linkedin.com/in/voigtjessica>.
+[^voigt]: Data Scientist, Transparência Brasil, São Paulo, SP, Brazil, [jvoigt@transparencia.org.br](mailto:jvoigt@transparencia.org.br), <https://www.linkedin.com/in/voigtjessica>.
 
@@
 
-One of the key determinants of efficient public service provision is a robust accountability system [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
+One of the key determinants of efficient public services provision is a robust accountability system [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
 In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
-Past studies show that accountability ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
-Moreover, greater accountability leads to higher economic growth as it limits state discretion in the economy, promotes social cohesion and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
+Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
+Recent research also suggests accountability leads to higher economic growth because it limits state discretion in the economy and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
 
-However, accountability systems can take many forms.
-One promising model for democratic oversight is _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project to help them evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
-Proponents argue bottom-up accountability is effective because 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to avoid corruption that directly affects them; 3) policy-makers are particularly sensitive to social punishment from their own communities [@serra2011combining, 570].
-In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of politicians and bureaucrats with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
+However, accountability systems take many forms.
+One promising model is that of _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project so they can evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
+Proponents argue bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects them; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
+In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
 
-Here we assess the impact of a technology-driven solution that lowers the costs of evaluating public works and punishing political representatives in Brazil.
-Developed by Transparência Brasil[^transparencia], the _Tá de Pé_ (TDP) mobile phone application allows Brazilian citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
-TDP users can also take pictures of delayed works and submit them to a group of trained engineers for examination.
-If the engineers classify the construction as delayed, TDP allows users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
+Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.
+Developed by Transparência Brasil[^transparencia], TDP allows Brazilian citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
+TDP users can also take pictures of the construction sites and submit them to volunteering engineers for examination.
+If the engineers classify the construction as delayed, TDP prompts users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
 TDP has been online since April 2017 in 1030 Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
@@
 
-[^google]: About 1,000 Brazilian charities participated in the 2016 Google Social Impact Challenge and an independent selection committee selected 10 of them as finalists.
-Transparência Brasil was then the highest voted NGO by the public.
+[^google]: About 1,000 Brazilian charities participated in the 2016 Google Social Impact Challenge.
+An independent committee selected 10 organisations as finalists, and Transparência Brasil won the challenge with about 200,000 popular votes.
 To know more about the contest, please visit <https://impactchallenge.withgoogle.com/brazil2016> (access: July 2019).
 
-We use the TDP app to conduct **two/three?** experimental interventions.
-We test whether the app has a positive impact on **school completion rates, school construction status and complaints to competent authorities**.
-Contrary to our expectations, our experiments have delivered mixed results.
-**One/Two** of the findings are positive and in line with our theoretical predictions.
+We use the TDP app to conduct two experimental interventions.
+We test whether the app has a positive impact on three outcomes of interest: school completion rates, school construction status and complaints to competent authorities.
+We find that our experiments have delivered mixed results.
+Two of the findings are positive and in line with our theoretical predictions.
 From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX).
@@
 Brazilian politicians did not respond to the citizen's requests placed via the application.
-Therefore, our findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-**Nota**: _Reescrever essa última frase e colocar mais explicações sobre possíveis mecanismos, etc_
 
-# The _Tá de Pé_ Project \label{sec:tdp}
+Our findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies. Although
+
+**Nota**: _Reescrever os dois últimos parágrafos e colocar mais explicações sobre possíveis mecanismos, etc_
+
+# The _Tá de Pé_ Project 
+\label{sec:tdp}
 
@@
 
-Transparência Brasil established a partnership with the Brazilian branch of _Engineers without Borders_ (EWB), a non-governmental organisation dedicated to promote international development[^ewb], to provide unbiased evaluations of school completion rates.
-Their assessment is based on photos and GPS location sent through the app.
-All data are collected anonymously.
-Information on users' alerts are stored on their mobile devices, so citizens can track whether their request has been answered by public authorities.
+Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), a non-governmental organisation[^ewb], to provide technical evaluations of school completion rates.
+The EWB bases their assessment on photos and GPS location sent through the app.
+The engineers' reports are later uploaded to the database and stored on the users' mobile devices so citizens can track the progress of the constructions.
 
@@
 The TDP has also received feedback from Brazilian computer programmers and policy analists.
-In 2017 and 2018, Transparência Brasil announced two team programming competitions, called 'Tá de Pé Hackathons', where contributors could fix code bugs and suggest new functionalities to TDP.
-In total, 75 participants
+In 2017 and 2018, Transparência Brasil announced two team programming competitions, called 'Tá de Pé Hackathons', where contributors could fix code bugs and suggest new functionalities to the TDP project.
+One of these innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which posts a message on the social network each time a user submits a new picture for evaluation.
+This allows interested parties to track the progress of construction sites as well as add new public works to the TDP database.
 
-# Methods
+# Data and Methods
 \label{sec:methods}
+
+We assessed the impact of the TDP app on
 

### 2019-08-07 article/article.Rmd
add text

@@
 
-We use the TDP app to conduct two experimental interventions.
-We test whether the app has a positive impact on three outcomes of interest: school completion rates, school construction status and complaints to competent authorities.
-We find that our experiments have delivered mixed results.
-Two of the findings are positive and in line with our theoretical predictions.
-From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX).
-Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = XXX).
-In contrast, our results show the app has a null impact on school constructions statistics.
-Brazilian politicians did not respond to the citizen's requests placed via the application.
+We use the TDP app to conduct two experimental interventions and test whether it has an impact on six outcomes related to school completion rates and complains to public authorities.
+We find that the TDP app increased the likelihood of school completion by 6.8 percent (SE = X.XX, t-test = X.XX) in the first experiment, although the effect is null in the second intervention.
+Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = X.XX) in the second experiment.
+However, our results show that providing information to citizens does not change the percentage invested in all other outcomes.
+
+In contrast, our results show the app has a null impact on school constructions statistics. Brazilian politicians did not respond to the citizen's requests placed via the application.
 

### 2019-08-08 article/article.Rmd
add more stuff

--- 2019-08-06 article/article.Rmd
@@
 
-We use the TDP app to conduct two experimental interventions.
-We test whether the app has a positive impact on three outcomes of interest: school completion rates, school construction status and complaints to competent authorities.
-We find that our experiments have delivered mixed results.
-Two of the findings are positive and in line with our theoretical predictions.
-From August 2017 to February 2019, TDP increased the likelihood of school completion by 6.8 percent (SE = X.X, t-test = XXX).
-Additionally, we find that pressure over the bureaucracy increased the investments in the schools by 157.5 percent (SE = X.XX, t-test = XXX).
-In contrast, our results show the app has a null impact on school constructions statistics.
-Brazilian politicians did not respond to the citizen's requests placed via the application.
+We use the TDP app to conduct two experimental interventions and test its impact on six outcomes related to school completion rates and complaints to public authorities.
+Overall, our results show that providing information to citizens has very limited impact on policy outcomes.
+We find that the TDP app increased the likelihood of school completion by 6.8 percent in the first experiment, but the effect is null in the second intervention.
+We also find that pressure over the bureaucracy increased by 157.5 percent (SE = X.XX, t-test = X.XX) in our second experiment, although not in the first.
+Importantly, our two interventions have no significant impact on any of the four measures of school investment and completion rates we employed in this study.
+Community monitoring does not consistently change the behaviour of Brazilian politicians or civil servants.
 
-Our findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies. Although
-
-**Nota**: _Reescrever os dois últimos parágrafos e colocar mais explicações sobre possíveis mecanismos, etc_
+Our results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
+@banerjee2018tangible, @bjorkman2009power and @fiala2017social find significant policy improvements after providing information to local communities, but our experiment is in line with @banerjee2010pitfalls, @keefer2014mass, @olken2007monitoring and @raffler2018weakness and offers little evidence in favour of information interventions.
+Our study suggests that other models of political accountability may be more effective for public service provision.
 
@@
 
-We assessed the impact of the TDP app on
+The
 

### 2019-08-09 article/article.Rmd
edits intro, 1st par methods

@@
 Developed by Transparência Brasil[^transparencia], TDP allows Brazilian citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
-TDP users can also take pictures of the construction sites and submit them to volunteering engineers for examination.
+TDP users can also take pictures of the construction sites and submit them to independent engineers for examination.
 If the engineers classify the construction as delayed, TDP prompts users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
@@
 We find that the TDP app increased the likelihood of school completion by 6.8 percent in the first experiment, but the effect is null in the second intervention.
-We also find that pressure over the bureaucracy increased by 157.5 percent (SE = X.XX, t-test = X.XX) in our second experiment, although not in the first.
+We also find that pressure over the bureaucracy increased by 157.5 percent in our second experiment, although not in the first.
 Importantly, our two interventions have no significant impact on any of the four measures of school investment and completion rates we employed in this study.
-Community monitoring does not consistently change the behaviour of Brazilian politicians or civil servants.
 
-Our results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-@banerjee2018tangible, @bjorkman2009power and @fiala2017social find significant policy improvements after providing information to local communities, but our experiment is in line with @banerjee2010pitfalls, @keefer2014mass, @olken2007monitoring and @raffler2018weakness and offers little evidence in favour of information interventions.
-Our study suggests that other models of political accountability may be more effective for public service provision.
+The results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
+Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @olken2007monitoring and @raffler2018weakness and offer mixed evidence that information interventions lead to greater government responsiveness.
+Our analysis suggests that grassroots monitoring does not affect government behaviour in Brazil, and other models of political accountability may be more effective for public service provision.
 
@@
 
-Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), a non-governmental organisation[^ewb], to provide technical evaluations of school completion rates.
-The EWB bases their assessment on photos and GPS location sent through the app.
+Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide technical assessment of school completion rates.
+The EWB bases their evaluations on photos and GPS location sent through the app.
 The engineers' reports are later uploaded to the database and stored on the users' mobile devices so citizens can track the progress of the constructions.
@@
 
-The
+We implemented two interventions to measure the effect of the TDP app on school constructions outcomes.
+The first experiment ran from August 2017 to February 2018 and we carried out a follow-up study one year later, from August 2018 to February 2019.
 

### 2019-08-09 article/article.Rmd
add methods

@@
 
-We implemented two interventions to measure the effect of the TDP app on school constructions outcomes.
-The first experiment ran from August 2017 to February 2018 and we carried out a follow-up study one year later, from August 2018 to February 2019.
+Between August 2017 and August 2018, we implemented two interventions to measure the effect of the TDP app on six school construction outcomes.
+The outcomes are: 1) the percentage of public investment allocated to school constructions; 2) the difference between the percentage invested in the beginning and the end of the interventions; 3) the number of finished constructions; 4) the number of cancelled constructions; 5) the number of updated conclusion dates; 6) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started.
+We expect the first five factors to increase the last to remain unchanged.
 
-## Estimation
-\label{sub:estimation}
+The first intervention was carried out from August 2017 to February 2018 using the Android version of the TDP app.
+The unit of analysis for this experiment is the Brazilian municipality.
+We randomly selected 150 cities to the control group and included 1030 municipalities in the treatment group.
+Our control condition consisted in removing all school constructions in the chosen municipalities so that citizens were unable to add information on them.
 
-Our regression model is specified as follows:
+To evaluate the random assignment, we used the following pre-treatment variables: 1) log of municipal population in 2015; 2) log of number of poor families in each city; 3) log of total federal transfers to the municipality in 2016; 4) federal government indicator for primary school quality; 4) federal government indicator for secondary school quality.
+The data come from the Brazilian Ministry of Education and the Census.
+Balance tests show that randomisation was successful and are available in the Supplementary Material.
+Figure \ref{fig:manipulation1} presents two manipulation checks, TDP app downloads by municipality and app downloads over time.
 
-$$Y_{i} = \alpha + \beta T_{i} + \gamma X_{i} + \theta Z_i + \epsilon_{i} $$
+** FIGURE 2 ABOUT HERE: MANIPULATION CHECKS FOR INTERVENTION 1**
 
-Where $i$ indexes the case.
-$Y_i$ in one the outcomes we described in the previous subsection.
-The $\beta$ coefficient is the quantity of interest (Average Treatment Effect).
-$T_i$ is a binary treatment indicator in which zero denotes that $i$ is in the control group, while 1 indicates that $i$ received the treatment.
-$\gamma$ is a vector of fixed effects and $X_i$ is a matrix of 27 Brazilian states' fixed effects.
-$\theta$ is a vector of additional controls and $Z_i$ is an array of control variables for the case $i$.
-Lastly, $\epsilon_i$ is the error term.
+The map displays a good territorial variability.
+There were 455 downloads in the 1030 municipalities originally in the dataset at the beginning of the impact evaluation.
+Downloads peak during the Facebook TDP campaign, right after the TDP app launch in August, then diminishes over time.
+Users downloaded the app in 44.6% of the municipalities, and the downloads were temporally concentrated.
 
-We cluster the standard errors at the municipal level, as the investment decisions are taken by the mayor’s offices.
-As robustness, we fit two extra models.
-First, we re-run the main model where we have the following: (i) we ran a model without controls or fixed effects; (ii) we run the models adding the control variables, which are the same as the ones used in the covariate balance tests; (iii) we run the regression model with State fixed effects.
-The results are in the Appendix.
-Second, we run the main models using inverse probability weights where we used block randomization and a one-to-one nearest neighborhood matching.
-We use the control variables as matching characteristics.
-These robustness checks are intended to correct the imbalance caused by the minimal control group approach that we employed in all three interventions.
+The second intervention is similar to intervention 1 in all but three characteristics.
+First, the TDP app was then available for iOS devices.
+Also, the randomisation procedure was performed at the school level, with 654 control and 3895 treatment units.
+We used blocked randomisation stratified by Brazilian state, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
+Finally, the intervention period lasted from August 2018 to February 2019.
+
+** FIGURE 3 ABOUT HERE: MANIPULATION CHECKS FOR INTERVENTION 2**
+
+In total, 433 municipalities downloaded the app.
+There is one download peak in August 2017, right after the intervention starts, and a second spike around December.
+The number of downloads is considerably smaller in this second intervention when compared with intervention 1.
 
@@
 \label{sec:results}
+
+Table \ref{tab:results1} summarises the main results of intervention 1.
+We estimated the models including the five control variables described in the previous section and Brazilian states' fixed effects.
+Standard errors are clustered at the level of the municipality.
+As robustness tests, we run the main models using inverse probability weights where we used block randomisation and one-to-one nearest neighbourhood matching.
+The results are substantively identical and are available in the Supplementary Materials.
+
+** TABLE 1 ABOUT HERE -- MAIN RESULTS INTERVENTION 1 **
 

### 2019-08-10 article/article.Rmd
methods section

@@
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Fasolin, Stephen Herzog and David Skarbek for their helpful comments.
+thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments.
 We are specially grateful to the staff of Transparência Brasil for their excellent research assistance.
@@
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
-# If you need to install any package while knitting the document
+```{r setup, include=FALSE, warning=FALSE, cache=TRUE}
+knitr::opts_chunk$set(echo = TRUE)
 r <- getOption("repos")
-r["CRAN"] <- "https://cran.rstudio.com/"
+r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
 options(repos = r)
+
+## Pre-processing
+
+# Required packages
+pkgs <- c('tidyverse', 'dummies', 'kableExtra',
+          'haven', 'compareGroups', 'grid', 'gridExtra',
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer')
+
+# Install required packages
+installIfNot <- function(x) {
+  if(x %in% rownames(installed.packages()) == FALSE) 
+    install.packages(x, dependencies = T)
+} 
+lapply(pkgs, installIfNot)
+
+# Load scripts
+lapply(pkgs, require, character.only = T)
+rm(pkgs, installIfNot)
+rm(list=ls())
 ```
@@
 
-# Data and Methods
-\label{sec:methods}
+# Experimental Design
+\label{sec:design}
 
 Between August 2017 and August 2018, we implemented two interventions to measure the effect of the TDP app on six school construction outcomes.
-The outcomes are: 1) the percentage of public investment allocated to school constructions; 2) the difference between the percentage invested in the beginning and the end of the interventions; 3) the number of finished constructions; 4) the number of cancelled constructions; 5) the number of updated conclusion dates; 6) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started.
-We expect the first five factors to increase the last to remain unchanged.
+The outcomes are: 1) the percentage of public investment allocated to school constructions; 2) the difference between the percentage invested before and after the interventions; 3) the number of finished constructions; 4) the number of cancelled constructions; 5) the number of updated conclusion dates; 6) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started.
+We expect the first five factors to increase the last one to remain unchanged.
 
@@
 We randomly selected 150 cities to the control group and included 1030 municipalities in the treatment group.
-Our control condition consisted in removing all school constructions in the chosen municipalities so that citizens were unable to add information on them.
+Our control condition consisted in removing all school constructions in the chosen municipalities so that citizens were unable to add information about them.
 
@@
 The data come from the Brazilian Ministry of Education and the Census.
-Balance tests show that randomisation was successful and are available in the Supplementary Material.
-Figure \ref{fig:manipulation1} presents two manipulation checks, TDP app downloads by municipality and app downloads over time.
+Balance tests show that the randomisation was successful and are available in the Supplementary Materials.
 
-** FIGURE 2 ABOUT HERE: MANIPULATION CHECKS FOR INTERVENTION 1**
+We also conducted two manipulation checks and analysed the number of TDP app downloads by municipality and app downloads over time.
+Figure \ref{fig:manipulation1} displays the results.
+The checks display good territorial variability.
+There were 455 downloads in the 1030 municipalities in the treatment condition.
+Downloads peak during the Facebook TDP campaign, right after the TDP app launch in August, then diminish over time.
+Please refer to the Supplementary Materials for a detailed description of the tests.
 
-The map displays a good territorial variability.
-There were 455 downloads in the 1030 municipalities originally in the dataset at the beginning of the impact evaluation.
-Downloads peak during the Facebook TDP campaign, right after the TDP app launch in August, then diminishes over time.
-Users downloaded the app in 44.6% of the municipalities, and the downloads were temporally concentrated.
+```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, cache=TRUE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
+# Load data 
+load('tdp.RData')
+
+# Aux function
+calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
+      # No controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = F))
+      print(k); k = k+1
+      # Controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = F))
+      print(k); k = k+1
+      # No controls and fes
+      mods[[k]] <- felm(
+        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
+                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+                         collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = T))
+      print(k); k = k+1
+      # Controls and fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = T))
+      print(k); k = k+1
+    }
+  }
+  return(list(moddescr, mods))
+}
+
+## Analysis Intervention 1
+
+## Covariate balance
+aux <- select(impEvalph1, 
+              treatOriginal, logPop2015,
+              ideb_ai_2015, ideb_af_2015, log_poorFam2010,
+              log_totTransf2016) %>%
+  unique()
+resu1 <- compareGroups(treatOriginal ~ 
+                         logPop2015 + 
+                         log_poorFam2010 +
+                         log_totTransf2016 +
+                         ideb_ai_2015 + 
+                         ideb_af_2015, 
+                       data = aux)
+tabIE1balance <- createTable(resu1, digits = 3)
+row.names(tabIE1balance$descr) <- 
+  c('Log Population (2015)', 
+    'Log Poor Families (2010)', 
+    'Log Total Transfers (2016)', 
+    'IDEB Inicial Years (2015)', 
+    'IDEB Final Years (2015)')
+
+## Manipulation Stats
+
+## Map GA intervention 1
+mapbr <- get_brmap('City')
+gaaux <- filter(ga, phase1 == 1)
+gaaux <- select(gaaux, ibge_code7, downl)
+gaaux <- rename(gaaux, City = ibge_code7)
+gaaux <- unique(gaaux)
+gaaux$City <- as.numeric(gaaux$City)
+gaaux2 <- data.frame(City = mapbr$City)
+gaaux <- merge(gaaux2, gaaux,all.x=TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
+pMapDownloadsInt1 <- plot_brmap(mapbr,
+                                data_to_join = gaaux,
+                                join_by = c("City" = "City"),
+                                var = "Downloads") 
+pMapDownloadsInt1
+
+# Frequency downloads
+tab <- filter(ga, phase1 == 1) %>%
+  group_by(data) %>%
+  summarize(NewUsers = sum(novos_usuarios))
+names(tab) <- c('Date', 'Frequency')
+pFreqUserDownloadsInt1 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+  geom_line() + geom_point()
+pFreqUserDownloadsInt1
+```
 
 The second intervention is similar to intervention 1 in all but three characteristics.
-First, the TDP app was then available for iOS devices.
-Also, the randomisation procedure was performed at the school level, with 654 control and 3895 treatment units.
+First, the TDP app was available for Android and iOS devices.
+Also, we randomised the intervention at the school level, with 654 control and 3895 treatment units.
 We used blocked randomisation stratified by Brazilian state, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
@@
 
-** FIGURE 3 ABOUT HERE: MANIPULATION CHECKS FOR INTERVENTION 2**
+Balance tests and manipulation checks were also successful for intervention 2.
+In total, 433 municipalities downloaded the app.
+There is one download peak in August 2018, right after the intervention starts, and a second spike around December.
+The number of downloads is considerably smaller in this second intervention when compared to intervention 1 as there was no associated social media campaign in that period.
 
-In total, 433 municipalities downloaded the app.
-There is one download peak in August 2017, right after the intervention starts, and a second spike around December.
-The number of downloads is considerably smaller in this second intervention when compared with intervention 1.
+```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, cache=TRUE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
+# Load data 
+load('tdp.RData')
+
+## Manipulation Stats
+
+## Map intervention 2
+mapbr <- get_brmap('City')
+gaaux <- filter(ga, phase2 == 1)
+gaaux <- select(gaaux, ibge_code7, downl)
+gaaux <- rename(gaaux, City = ibge_code7)
+gaaux <- unique(gaaux)
+gaaux$City <- as.numeric(gaaux$City)
+gaaux2 <- data.frame(City = mapbr$City)
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
+p1 <- plot_brmap(mapbr,
+                data_to_join = gaaux,
+                join_by = c("City" = "City"),
+                var = "Downloads") 
+p1
+
+# Downloads over time -- Intervention 2:
+# Phase 2 -- manipulation
+tab <- filter(ga, phase2 == 1) %>%
+  group_by(data) %>%
+  summarize(NewUsers = sum(novos_usuarios))
+names(tab) <- c('Date', 'Frequency')
+p2 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+  geom_line() + geom_point()
+p2
+```
+
+We estimated all models using the following regression equation:
+
+$$ Y_i \ = \ \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i $$
+
+where $i$ indexes the experiment units.
+$Y_i$ in one of the six outcomes described above and $\beta$ denotes the average treatment effect.
+$T_i$ is a binary treatment indicator, $\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed effects, $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$.
+The error term is denoted by $\varepsilon_i$.
+We cluster the standard errors at the municipal level as mayors are responsible for school investment decisions.
 
@@
 Table \ref{tab:results1} summarises the main results of intervention 1.
-We estimated the models including the five control variables described in the previous section and Brazilian states' fixed effects.
-Standard errors are clustered at the level of the municipality.
-As robustness tests, we run the main models using inverse probability weights where we used block randomisation and one-to-one nearest neighbourhood matching.
-The results are substantively identical and are available in the Supplementary Materials.
+All models reported here include the five control variables described in the previous section and Brazilian states' fixed effects.
+We also estimated the models without control variables and fixed effects and the results are unchanged.
+They are available in the Supplementary Materials.
 
@@
 
-# Conclusion
-\label{sec:conclusion}
-
 \newpage

### 2019-08-10 article/article.tex
methods section

@@
 \usepackage{tocloft}
+\usepackage{subcaption}
 
@@
 % Margin
-\usepackage[margin=2cm]{geometry}
+\usepackage[top=2.3cm,bottom=2.3cm,left=2cm,right=2cm]{geometry}
 
@@
 % Title
-\title{The Pitfalls of Bottom-Up Accountability: Evidence from Brazil\thanks{We thank Guilherme Fasolin, Stephen Herzog, and David Skarbek for their
-helpful comments. We are specially grateful to the staff of
-Transparência Brasil for their excellent research and technical
-assistance. Replication data and code are available at
+\title{Bottom-Up Accountability and Infrastructure Delivery: Mixed Evidence
+from Brazil\thanks{We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David
+Skarbek for their helpful comments. We are specially grateful to the
+staff of Transparência Brasil for their excellent research assistance.
+This research was pre-registered on the EGAP pre-registry tool
+(\url{https://egap.org/registration/4505}) and approved by the Brazilian
+Ministry of Education. The authors thank the 2016 Google Social Impact
+Challenge for financial support and declare there are no conflict of
+interest. Replication data and code are available at
 \url{http://github.com/umbertomignozzetti/tdp-accountability}.}}
@@
   Paulo, SP, Brazil,
-  \href{mailto:mcz.fea@gmail.com}{\nolinkurl{mcz.fea@gmail.com}},
+  \href{mailto:mgaldino@transparencia.org.br}{\nolinkurl{mgaldino@transparencia.org.br}},
   \url{https://www.transparencia.org.br}.} \and Umberto Mignozzetti\footnote{School of International Relations, Fundação
@@
   SP, Brazil,
-  \href{mailto:voigt.jessica@gmail.com}{\nolinkurl{voigt.jessica@gmail.com}},
+  \href{mailto:jvoigt@transparencia.org.br}{\nolinkurl{jvoigt@transparencia.org.br}},
   \url{https://www.linkedin.com/in/voigtjessica}.}}
@@
 \doublespacing \noindent We study the effect of a mobile phone application designed to increase
-citizens' ability to monitor public works in Brazil. The app allowed
-individuals to find delayed school constructions in XXX Brazilian cities
-and send anonymous messages to politicians requestions information about
-construction delays and expected completion times. Our results show that
-the app has a null impact on the completion times subsequently reported
-by the municipalities. Additionally, we find that few politicians
-reacted to citizens' requests. These findings suggest it is difficult to
-motivate bottom-up accountability in new democracies, especially when
-politicians are unresponsive to non-electoral pressures. This paper has
-implications for the design of bottom-up accountability mechanisms.
+citizens' ability to monitor public works in Brazil. The app allows
+individuals to find delayed school constructions in 1030 Brazilian
+cities and send anonymous messages to politicians requesting information
+about construction delays and completion times. Our results show the app
+has a null impact on the completion times subsequently reported by the
+municipalities. Additionally, we find that few politicians react to
+citizens' requests. These findings suggest it is difficult to motivate
+bottom-up accountability in new democracies, especially when politicians
+are unresponsive to non-electoral pressures. This paper has implications
+for the design of bottom-up accountability mechanisms.
 \vspace{.25cm}
@@
 \hypertarget{introduction}{%
-\section{\texorpdfstring{Introduction\label{sec:intro}}{Introduction}}\label{introduction}}
+\section{Introduction}\label{introduction}}
 
-One of the key determinants of efficient public service provision is a
+\label{sec:intro}
+
+One of the key determinants of efficient public services provision is a
 robust accountability system
-\citep{besley2003incentives,cameron2004public,o1998horizontal}. In its
-standard definition, accountability is the process of holding
-authorities into account for their actions
-\citep{finer1941administrative,mulgan2000accountability,o1990bureaucratic}.
-Past studies show that accountability ensures that politicians act on
-behalf of voters \citep{freire2010ngp, moncrieffe1998reconceptualizing},
-reduces the opportunities for rent-seeking and corruption
-\citep{deininger2005does,wenar2006accountability} and increases the
-efficiency of the public sector \citep{adsera2003you,bjorkman2009power}.
-Moreover, greater accountability is associated with higher levels of
-economic growth, not only because it limits state discretion in the
-economy, but also because it promotes social cohesion and long-term
-investments in human capital
-\citep{benhabib2010economic, cox2018executive, suebvises2018social,ponzetto2018social}.
+\citep{besley2003incentives, cameron2004public, ferejohn1986incumbent, o1998horizontal}.
+In its standard definition, accountability is understood as the process
+of holding authorities responsible for their actions
+\citep{finer1941administrative, mulgan2000accountability, o1990bureaucratic}.
+Past studies show that accountability has a positive impact on
+governance, as it ensures that politicians act on behalf of voters
+\citep{freire2010ngp, moncrieffe1998reconceptualizing}, reduces the
+opportunities for rent-seeking and corruption
+\citep{deininger2005does, wenar2006accountability} and improves the
+efficiency of the public sector
+\citep{adsera2003you, bjorkman2009power}. Recent research also suggests
+accountability leads to higher economic growth because it limits state
+discretion in the economy and increases long-term investments in human
+capital
+\citep{benhabib2010economic, suebvises2018social, ponzetto2018social}.
 
-However, accountability systems can take many forms. One promising model
-for democratic oversight is \emph{bottom-up accountability}, in which
-citizens receive information about the shortcomings of a given project
-to help them monitor and pressure underperforming public officials
-\citep{kosack2014does, molina2016community,raffler2018weakness}.
-Proponents suggest bottom-up accountability is effective because 1)
+However, accountability systems take many forms. One promising model is
+that of \emph{bottom-up monitoring}, in which citizens receive
+information about the shortcomings of a given project so they can
+evaluate and pressure underperforming public officials
+\citep{kosack2014does, molina2016community, raffler2018weakness}.
+Proponents argue bottom-up accountability is effective because: 1)
 constituents have first-hand information about the outcomes of local
-policies; 2) citizens have incentives to avoid corruption that directly
-affects them; 3) policy-makers are particularly sensitive to social
-punishment from their own communities \citep[570]{serra2011combining}.
-In a nutshell, bottom-up accountability offers a potential solution to
-the principal-agent dilemma in public service by aligning the interests
-of politicians and bureaucrats with those of the constituency they serve
-\citep[2]{raffler2018weakness}.
+policies; 2) citizens have incentives to attack corruption that directly
+affects them; 3) policy-makers are sensitive to social punishment from
+their own communities \citep[570]{serra2011combining}. In a nutshell,
+bottom-up accountability offers a potential solution to the
+principal-agent dilemma in public service by aligning the interests of
+state officials with those of the constituency they serve
+\citep[2]{barro1973control, raffler2018weakness}.
 
-Here we assess the impact of a technology-driven solution that lowers
-the costs of evaluating public works and punishing political
-representatives in Brazil. The \emph{Tá de Pé} (TDP) mobile phone
-application allows Brazilian citizens to go to school construction
-sites, check their status, and request information to public
-authorities. TDP users can also take pictures from delayed works and
-submit them to a group of trained engineers, who then evaluate the
-execution of the project. If the engineers classify the construction as
-delayed, TDP sends a message to the mayor's office asking for completion
-estimates and explanations about why the building is unfinished. TDP
-received the 2016 Google Social Impact grant, earning more than 200
-thousand popular votes, and it has been online since April 2017 in 1030
-Brazilian municipalities.
+Here we assess the impact of \emph{Tá de Pé} (TDP), a mobile phone
+application designed to lower the costs of evaluating public works and
+punishing political representatives in Brazil. Developed by
+Transparência Brasil\footnote{Transparência Brasil is an
+  non-governmental organisation whose mission is to `promote
+  transparency and social control of public power' in Brazil. It has
+  been active since April 2000, is non-partisan and receives no public
+  funding. More information at \url{http://transparencia.org.br}
+  (access: July 2019).}, TDP allows Brazilian citizens to know the
+location of public school construction sites, check their completion
+status and anonymously request information from competent authorities.
+TDP users can also take pictures of the construction sites and submit
+them to independent engineers for examination. If the engineers classify
+the construction as delayed, TDP prompts users to send a message to the
+mayor's office asking for completion estimates and explanations about
+the construction status. TDP has been online since April 2017 in 1030
+Brazilian municipalities and was the winner of the 2016 Google Social
+Impact grant with more than 200,000 popular votes\footnote{About 1,000
+  Brazilian charities participated in the 2016 Google Social Impact
+  Challenge. An independent committee selected 10 organisations as
+  finalists, and Transparência Brasil won the challenge with about
+  200,000 popular votes. To know more about the contest, please visit
+  \url{https://impactchallenge.withgoogle.com/brazil2016} (access: July
+  2019).}.
 
-Contrary to our expectations, the TDP app has delivered mixed results.
-Two findings are positive and in line with our theoretical predictions.
-From August 2017 to February 2019, TDP increased the likelihood of
-school completion by 6.8 percent (SE = X.X, t-test = XXX). Additionally,
-we find that pressure over the bureaucracy increased the investments in
-the schools by 157.5 percent (SE = X.XX, t-test = XXX). In contrast, our
-results show the app had a null impact on school constructions
-statistics. Brazilian politicians did not respond to the citizen's
-requests placed via the application. Therefore, our findings raise
-questions about the ability of citizens to hold representatives
-accountable using bottom-up strategies.
+We use the TDP app to conduct two experimental interventions and test
+its impact on six outcomes related to school completion rates and
+complaints to public authorities. Overall, our results show that
+providing information to citizens has very limited impact on policy
+outcomes. We find that the TDP app increased the likelihood of school
+completion by 6.8 percent in the first experiment, but the effect is
+null in the second intervention. We also find that pressure over the
+bureaucracy increased by 157.5 percent in our second experiment,
+although not in the first. Importantly, our two interventions have no
+significant impact on any of the four measures of school investment and
+completion rates we employed in this study.
 
-\hypertarget{the-ta-de-pe-app}{%
+The results raise questions about the ability of citizens to hold
+representatives accountable using bottom-up strategies. Although studies
+like \citet{bjorkman2009power}, \citet{fiala2017social} and
+\citet{reinikka2005fighting} report better policy outcomes after
+providing information to local communities, our findings are closer to
+\citet{banerjee2010pitfalls}, \citet{keefer2014mass},
+\citet{olken2007monitoring} and \citet{raffler2018weakness} and offer
+mixed evidence that information interventions lead to greater government
+responsiveness. Our analysis suggests that grassroots monitoring does
+not affect government behaviour in Brazil, and other models of political
+accountability may be more effective for public service provision.
+
+\hypertarget{the-ta-de-pe-project}{%
 \section{\texorpdfstring{The \emph{Tá de Pé}
-App}{The Tá de Pé App}}\label{the-ta-de-pe-app}}
+Project}{The Tá de Pé Project}}\label{the-ta-de-pe-project}}
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\label{sec:tdp}
 
-\hypertarget{estimation}{%
-\subsection{Estimation}\label{estimation}}
+The \emph{Tá de Pé}\footnote{\emph{Tá de Pé} is an informal Brazilian
+  expression for `is it done?'. Literally, it means `standing on its
+  feet' in Portuguese.} cell phone application is an initiative carried
+out by Transparência Brasil to foster bottom-up accountability in the
+Brazilian public sector. More specifically, the main goal of the TDP
+project is to improve responsiveness in government education
+expenditures. The TDP app incentivises citizens to provide up-to-date
+information about unfinished schools in their neighbourhoods, and that
+information will be assessed by a group of independent specialists. In
+the case the construction is behind schedule, TDP provides a writing
+platform whereby citizens can contact their representatives quickly and
+anonymously. The app then prompts citizen to write a notification to the
+mayor's office, which has 15 days to reply. If they do not respond to
+the request, the app forwards the notification to the Brazilian federal
+government, making it harder to the municipality to access federal funds
+in the future. The motivation for the intervention is that information
+delivery causes individuals to closely monitor public works. This, in
+turn, results in better social outcomes as public agents become more
+responsive to community demands.
 
-Our regression model is specified as follows:
+We built the app in the first three months of 2017 and tested it in May
+2017. The first stable Android version was deployed on Google Play on 14
+August 2017. A version for iOS appeared six months later. A massive
+Facebook campaign started in order to publicise the app. Facebook is the
+most widely used social media network in Brazil with around 72 million
+users in 2017 \citep{statista2019facebook}. The campaigns were
+concentrated in October 2017 and cost US\$ 4,479.29. Facebook
+advertisements attracted 2,028 new users to the platform in October 2017
+only.
 
-\[Y_{i} = \alpha + \beta T_{i} + \gamma X_{i} + \theta Z_i + \epsilon_{i} \]
+\vspace{.2cm}
 
-Where \(i\) indexes the case. \(Y_i\) in one the outcomes we described
-in the previous subsection. The \(\beta\) coefficient is the quantity of
-interest (Average Treatment Effect). \(T_i\) is a binary treatment
-indicator in which zero denotes that \(i\) is in the control group,
-while 1 indicates that \(i\) received the treatment. \(\gamma\) is a
-vector of fixed effects and \(X_i\) is a matrix of 27 Brazilian states'
-fixed effects. \(\theta\) is a vector of additional controls and \(Z_i\)
-is an array of control variables for the case \(i\). Lastly,
-\(\epsilon_i\) is the error term.
+\begin{figure}
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
+       \includegraphics[scale=0.25]{tdp03.jpg}
+       \label{}
+     \end{minipage}
+     \hfill
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
+       \includegraphics[scale=0.25]{tdp01.jpg}
+     \end{minipage}
+     \hfill
+     \begin{minipage}[t]{.3\textwidth}
+       \centering
+       \includegraphics[scale=0.25]{tdp02.jpg}
+     \end{minipage}
+\caption{The \textit{Tá de Pé} mobile phone application.
+The first image presents a list of the closest school construction sites.
+The second image shows that a school construction is delayed by 9 months.
+The last image shows how citizens can add information to the photos they submit via the app.}
+\label{fig:screenshots}
+\end{figure}
 
-We cluster the standard errors at the municipal level, as the investment
-decisions are taken by the mayor's offices. As robustness, we fit two
-extra models. First, we re-run the main model where we have the
-following: (i) we ran a model without controls or fixed effects; (ii) we
-run the models adding the control variables, which are the same as the
-ones used in the covariate balance tests; (iii) we run the regression
-model with State fixed effects. The results are in the Appendix. Second,
-we run the main models using inverse probability weights where we used
-block randomization and a one-to-one nearest neighborhood matching. We
-use the control variables as matching characteristics. These robustness
-checks are intended to correct the imbalance caused by the minimal
-control group approach that we employed in all three interventions.
+Transparência Brasil partnered with the Brazilian branch of
+\emph{Engineers without Borders} (EWB), an independent non-governmental
+organisation\footnote{Please visit
+  \url{http://www.ewb-international.org} to know more about Engineers
+  without Borders International and \url{https://esf.org.br} for
+  information on the Brazilian office.}, to provide technical assessment
+of school completion rates. The EWB bases their evaluations on photos
+and GPS location sent through the app. The engineers' reports are later
+uploaded to the database and stored on the users' mobile devices so
+citizens can track the progress of the constructions.
+
+The TDP has also received feedback from Brazilian computer programmers
+and policy analists. In 2017 and 2018, Transparência Brasil announced
+two team programming competitions, called `Tá de Pé Hackathons', where
+contributors could fix code bugs and suggest new functionalities to the
+TDP project. One of these innovations consists of a Twitter bot
+(\url{https://twitter.com/tadepeapp}) which posts a message on the
+social network each time a user submits a new picture for evaluation.
+This allows interested parties to track the progress of construction
+sites as well as add new public works to the TDP database.
+
+\hypertarget{experimental-design}{%
+\section{Experimental Design}\label{experimental-design}}
+
+\label{sec:design}
+
+Between August 2017 and August 2018, we implemented two interventions to
+measure the effect of the TDP app on six school construction outcomes.
+The outcomes are: 1) the percentage of public investment allocated to
+school constructions; 2) the difference between the percentage invested
+before and after the interventions; 3) the number of finished
+constructions; 4) the number of cancelled constructions; 5) the number
+of updated conclusion dates; 6) a placebo outcome indicating the
+percentage of the investment executed before the impact evaluation
+started. We expect the first five factors to increase the last one to
+remain unchanged.
+
+The first intervention was carried out from August 2017 to February 2018
+using the Android version of the TDP app. The unit of analysis for this
+experiment is the Brazilian municipality. We randomly selected 150
+cities to the control group and included 1030 municipalities in the
+treatment group. Our control condition consisted in removing all school
+constructions in the chosen municipalities so that citizens were unable
+to add information about them.
+
+To evaluate the random assignment, we used the following pre-treatment
+variables: 1) log of municipal population in 2015; 2) log of number of
+poor families in each city; 3) log of total federal transfers to the
+municipality in 2016; 4) federal government indicator for primary school
+quality; 4) federal government indicator for secondary school quality.
+The data come from the Brazilian Ministry of Education and the Census.
+Balance tests show that the randomisation was successful and are
+available in the Supplementary Materials.
+
+We also conducted two manipulation checks and analysed the number of TDP
+app downloads by municipality and app downloads over time. Figure
+\ref{fig:manipulation1} displays the results. The checks display good
+territorial variability. There were 455 downloads in the 1030
+municipalities in the treatment condition. Downloads peak during the
+Facebook TDP campaign, right after the TDP app launch in August, then
+diminish over time. Please refer to the Supplementary Materials for a
+detailed description of the tests.
+
+\begin{figure}
+
+{\centering \includegraphics[width=.49\linewidth]{article_files/figure-latex/man1-1} \includegraphics[width=.49\linewidth]{article_files/figure-latex/man1-2}
+
+}
+
+\caption{\label{fig:manipulation1}Manipulation checks for intervention 1.
+The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.}\label{fig:man1}
+\end{figure}
+
+The second intervention is similar to intervention 1 in all but three
+characteristics. First, the TDP app was available for Android and iOS
+devices. Also, we randomised the intervention at the school level, with
+654 control and 3895 treatment units. We used blocked randomisation
+stratified by Brazilian state, school construction status (under
+construction, stopped, unfinished) and whether the municipality spent
+more on school construction that the distribution median. Finally, the
+intervention period lasted from August 2018 to February 2019.
+
+Balance tests and manipulation checks were also successful for
+intervention 2. In total, 433 municipalities downloaded the app. There
+is one download peak in August 2018, right after the intervention
+starts, and a second spike around December. The number of downloads is
+considerably smaller in this second intervention when compared to
+intervention 1 as there was no associated social media campaign in that
+period.
+
+\begin{figure}
+
+{\centering \includegraphics[width=.49\linewidth]{article_files/figure-latex/man2-1} \includegraphics[width=.49\linewidth]{article_files/figure-latex/man2-2}
+
+}
+
+\caption{\label{fig:manipulation2}Manipulation checks for intervention 2.
+The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.}\label{fig:man2}
+\end{figure}
+
+We estimated all models using the following regression equation:
+
+\[ Y_i \ = \ \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i \]
+
+where \(i\) indexes the experiment units. \(Y_i\) in one of the six
+outcomes described above and \(\beta\) denotes the average treatment
+effect. \(T_i\) is a binary treatment indicator, \(\gamma\) is a vector
+of fixed effects, \(X_i\) is a matrix of Brazilian states' fixed
+effects, \(\theta\) is a vector of controls and \(Z_i\) an array of
+controls for the case \(i\). The error term is denoted by
+\(\varepsilon_i\). We cluster the standard errors at the municipal level
+as mayors are responsible for school investment decisions.
 
@@
 
+\label{sec:results}
+
+Table \ref{tab:results1} summarises the main results of intervention 1.
+All models reported here include the five control variables described in
+the previous section and Brazilian states' fixed effects. We also
+estimated the models without control variables and fixed effects and the
+results are unchanged. They are available in the Supplementary
+Materials.
+
+** TABLE 1 ABOUT HERE -- MAIN RESULTS INTERVENTION 1 **
+
 \hypertarget{discussion}{%
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\label{sec:discussion}
 

### 2019-08-10 article/article.Rmd
update

@@
 Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
-Recent research also suggests accountability leads to higher economic growth because it limits state discretion in the economy and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
+Recent research also suggests that accountability leads to higher economic growth because it limits state discretion in the economy and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
 
@@
 Proponents argue bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects them; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
-In a nutshell, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
+In this regard, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
 
@@
 
-[^transparencia]: Transparência Brasil is an non-governmental organisation whose mission is to 'promote transparency and social control of public power' in Brazil.
+[^transparencia]: Transparência Brasil is an non-governmental organisation whose mission is to 'promote transparency and social control of public power'.
 It has been active since April 2000, is non-partisan and receives no public funding.
@@
 
-The _Tá de Pé_[^tdp] cell phone application is an initiative carried out by Transparência Brasil to foster bottom-up accountability in the Brazilian public sector.
+The _Tá de Pé_[^tdp] (TDP) cell phone application is an initiative carried out by Transparência Brasil to foster bottom-up accountability in the Brazilian public sector.
 More specifically, the main goal of the TDP project is to improve responsiveness in government education expenditures.
@@
 In the case the construction is behind schedule, TDP provides a writing platform whereby citizens can contact their representatives quickly and anonymously.
-The app then prompts citizen to write a notification to the mayor's office, which has 15 days to reply.
+The app then prompts citizens to write a notification to the mayor's office, which has 15 days to reply.
 If they do not respond to the request, the app forwards the notification to the Brazilian federal government, making it harder to the municipality to access federal funds in the future.
@@
 A version for iOS appeared six months later.
-A massive Facebook campaign started in order to publicise the app.
+In October 2017, we started a Facebook campaign in order to publicise the app.
 Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
-The campaigns were concentrated in October 2017 and cost US$ 4,479.29.
-Facebook advertisements attracted 2,028 new users to the platform in October 2017 only.
+The campaigns cost US$ 4,479.29 and Facebook advertisements attracted 2,028 new users to the platform in October 2017 only.
 
@@
 Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide technical assessment of school completion rates.
-The EWB bases their evaluations on photos and GPS location sent through the app.
-The engineers' reports are later uploaded to the database and stored on the users' mobile devices so citizens can track the progress of the constructions.
+The EWB bases their evaluations on photos and GPS coordinates sent through the app.
+The engineers' reports are later uploaded to the TDP database and stored on the users' mobile devices so citizens can follow the progress of the constructions.
 
@@
 One of these innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which posts a message on the social network each time a user submits a new picture for evaluation.
-This allows interested parties to track the progress of construction sites as well as add new public works to the TDP database.
+This allows any interested parties, including those who do not use the TDP app, to check the state of school construction sites.
 
@@
 The outcomes are: 1) the percentage of public investment allocated to school constructions; 2) the difference between the percentage invested before and after the interventions; 3) the number of finished constructions; 4) the number of cancelled constructions; 5) the number of updated conclusion dates; 6) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started.
-We expect the first five factors to increase the last one to remain unchanged.
+We expect the first five factors to increase and the last one to remain unchanged.
 
-The first intervention was carried out from August 2017 to February 2018 using the Android version of the TDP app.
+The first intervention was carried out from August 2017 to February 2018 using the Android version of TDP.
 The unit of analysis for this experiment is the Brazilian municipality.
@@
 
-We also conducted two manipulation checks and analysed the number of TDP app downloads by municipality and app downloads over time.
-Figure \ref{fig:manipulation1} displays the results.
-The checks display good territorial variability.
-There were 455 downloads in the 1030 municipalities in the treatment condition.
-Downloads peak during the Facebook TDP campaign, right after the TDP app launch in August, then diminish over time.
-Please refer to the Supplementary Materials for a detailed description of the tests.
+We also conducted two manipulation checks and analysed the number of TDP app downloads by municipality and over time.
+Figure \ref{fig:manipulation1} displays the results and indicates that the treatment has good territorial variability.
+There are 455 downloads in the 1030 municipalities in the treatment condition.
+Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.
 
@@
 The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
+
 # Load data 
@@
 The second intervention is similar to intervention 1 in all but three characteristics.
-First, the TDP app was available for Android and iOS devices.
-Also, we randomised the intervention at the school level, with 654 control and 3895 treatment units.
-We used blocked randomisation stratified by Brazilian state, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
+First, the TDP app was available for both Android and iOS devices.
+Second, we randomised the intervention at the school level, with 654 control and 3895 treatment units.
+We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
 Finally, the intervention period lasted from August 2018 to February 2019.
@@
 
-$$ Y_i \ = \ \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i $$
+\begin{equation} 
+Y_i \ = \ \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i 
+\end{equation}
 
 where $i$ indexes the experiment units.
-$Y_i$ in one of the six outcomes described above and $\beta$ denotes the average treatment effect.
-$T_i$ is a binary treatment indicator, $\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed effects, $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$.
+$Y_i$ in one of the six outcomes described above, $\alpha$ is the intercept, $\beta$ denotes the average treatment effect and $T_i$ is a binary treatment indicator.
+$\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed effects, $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$.
 The error term is denoted by $\varepsilon_i$.
-We cluster the standard errors at the municipal level as mayors are responsible for school investment decisions.
+We cluster the standard errors at the municipality level as mayors are responsible for school investment decisions in Brazil.
 
@@
 
-** TABLE 1 ABOUT HERE -- MAIN RESULTS INTERVENTION 1 **
-
 # Discussion

### 2019-08-14 article/article.Rmd
add discussion, results

@@
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments.
+thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog, Catarina Roman and David Skarbek for their helpful comments.
 We are specially grateful to the staff of Transparência Brasil for their excellent research assistance.
@@
 We also find that pressure over the bureaucracy increased by 157.5 percent in our second experiment, although not in the first.
-Importantly, our two interventions have no significant impact on any of the four measures of school investment and completion rates we employed in this study.
+Importantly, our two interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.
 
 The results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @olken2007monitoring and @raffler2018weakness and offer mixed evidence that information interventions lead to greater government responsiveness.
+Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness and offer mixed evidence that information interventions lead to greater government responsiveness.
 Our analysis suggests that grassroots monitoring does not affect government behaviour in Brazil, and other models of political accountability may be more effective for public service provision.
@@
 The app then prompts citizens to write a notification to the mayor's office, which has 15 days to reply.
-If they do not respond to the request, the app forwards the notification to the Brazilian federal government, making it harder to the municipality to access federal funds in the future.
+If they do not respond to the request, the app forwards the notification to the Brazilian federal government, making it harder for the municipality to access federal funds in the future.
 The motivation for the intervention is that information delivery causes individuals to closely monitor public works.
@@
 The first stable Android version was deployed on Google Play on 14 August 2017.
-A version for iOS appeared six months later.
+A version for iOS came about six months later.
 In October 2017, we started a Facebook campaign in order to publicise the app.
@@
 The unit of analysis for this experiment is the Brazilian municipality.
-We randomly selected 150 cities to the control group and included 1030 municipalities in the treatment group.
-Our control condition consisted in removing all school constructions in the chosen municipalities so that citizens were unable to add information about them.
+We randomly selected 150 to the control group and included 1030 municipalities in the treatment group.
+Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens had no incentive to use the app.
 
@@
 where $i$ indexes the experiment units.
-$Y_i$ in one of the six outcomes described above, $\alpha$ is the intercept, $\beta$ denotes the average treatment effect and $T_i$ is a binary treatment indicator.
+$Y_i$ is one of the six outcomes described above, $\alpha$ is the intercept, $\beta$ denotes the average treatment effect and $T_i$ is a binary treatment indicator.
 $\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed effects, $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$.
@@
 Table \ref{tab:results1} summarises the main results of intervention 1.
+Each column represents the treatment effect of the TDP app on one of the six outcomes we measured for this study.
 All models reported here include the five control variables described in the previous section and Brazilian states' fixed effects.
-We also estimated the models without control variables and fixed effects and the results are unchanged.
-They are available in the Supplementary Materials.
+We also estimated the models without control variables, without fixed effects and with nearest-neighbour matching.
+The results are very similar to the ones below and can be found in the Supplementary Material.
+
+\vspace{.5cm}
+**TABLE 1 ABOUT HERE: RESULTS INTERVENTION 1**
+\vspace{.5cm}
+
+We find that the intervention was sufficient to improve the school completion rate.
+The TDP application increases in 6.85 percent the chance that a school construction is reported as finished by the end of the intervention.
+This is in line with our theoretical expectations, but as we discuss below, the finding is not consistent.
+All other coefficients are not statistically significant at conventional levels.
+On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted.
+On the other hand, we expected the four remaining outcomes to increase after the introduction of the app.
+The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies.
+Our results do not lend support to that hypothesis.
+
+\vspace{.5cm}
+**TABLE 2 ABOUT HERE: RESULTS INTERVENTION 2**
+\vspace{.5cm}
+
+We observe a similar pattern in the second intervention.
+Table \ref{tab:results2} shows that the treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo.
+This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion.
+Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent.
+This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomization and one-to-one nearest neighbourhood matching.
+
+Figure \ref{fig:permtest} shows the results of our randomisation inference tests.
+Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field].
 
@@
 
-\newpage
+In this paper, we discuss whether a mobile phone application can foster grassroots mobilisation and political accountability in Brazil.
+Our two interventions show that the results are mixed.
+Although we find an effect on school construction in the first intervention and on the number of complaints in the second one, the app has no consistent impact on our outcomes of interest.
+The findings add further evidence to the studies that cast doubts on the relationship between bottom-up accountability and local policy performance [e.g., @banerjee2010pitfalls;  @lieberman2014does; @bjorkman2017experimental; @raffler2018weakness].
+
+What factors, then, are driving these results?
+It seems unlikely that the null results derive from flaws in the research design.
+First, our study is well powered.
+About 1,000 municipalities were included in the treatment groups, thus we should be able to capture average treatment effects, even small ones, if they indeed exist.
+Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures.
+Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no evidence of treatment effect.
+
+A plausible explanation is that individuals were unable to differentiate the effect of political corruption from those of spending cuts.
+Due to the severe economic crisis in 2014--2016, the Brazilian federal government introduced discretionary spending limits that affected public investment [@mello2016fix; @rossi2016impactos].
+Politicians may argue that delays in school constructions are not derived from their misuse of government funds, but from the austerity measures.
+If this is the case, citizens will not blame local politicians for the underprovision of public goods.
+Consequently, representatives can dismiss individual requests as the issue is unlikely to escalate.
+
+Moreover, it is possible that a mobile app like TDP is simply not sufficient to promote collective action.
+@raffler2018weakness [29] point out several reasons why information interventions might lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives.
+Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring into personal costs [@olson1965logic].
+
+In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery.
+Nevertheless, the null findings are informative to researchers and policy-makers.
+The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, may render better policy outcomes than those focused at the grassroots levels.
+Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication.
+Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions.
+
 \setlength{\parindent}{0cm}

### 2019-08-15 article/article.Rmd
results, discussion

@@
 We find that the TDP app increased the likelihood of school completion by 6.8 percent in the first experiment, but the effect is null in the second intervention.
-We also find that pressure over the bureaucracy increased by 157.5 percent in our second experiment, although not in the first.
-Importantly, our two interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.
+We also find that the app increased the percentage of the executed budget by 157.5 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
+No result reported in the first intervention or in the unmatched sample.
+Importantly, both interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.
 
@@
 
-# Aux function
-calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
-  ctrls_mod <- paste(ctrls, collapse = '+')
-  fes_mod <- paste(fes, collapse = '+')
-  moddescr <- data.frame()
-  mods <- list()
-  if(is.null(wts)) {
-    dat <- dat %>%
-      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
-      na.omit()
-  } else {
-    dat <- dat %>%
-      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
-      na.omit()
-    wts <- dat[,wts]
-  }
-  k <- 1
-  for (i in treats) {
-    for (j in outcs) {
-      # No controls and no fes
-      mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = F,
-                                   hFEs = F))
-      print(k); k = k+1
-      # Controls and no fes
-      mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = T,
-                                   hFEs = F))
-      print(k); k = k+1
-      # No controls and fes
-      mods[[k]] <- felm(
-        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
-                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-                         collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = F,
-                                   hFEs = T))
-      print(k); k = k+1
-      # Controls and fes
-      mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = T,
-                                   hFEs = T))
-      print(k); k = k+1
-    }
-  }
-  return(list(moddescr, mods))
-}
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 'kableExtra',
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer')
+invisible(lapply(pkgs, require, character.only = T))
 
@@
 
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 'kableExtra',
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer')
+invisible(lapply(pkgs, require, character.only = T))
+
 ## Manipulation Stats
@@
 
-\vspace{.5cm}
-**TABLE 1 ABOUT HERE: RESULTS INTERVENTION 1**
-\vspace{.5cm}
+```{r model1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 'kableExtra',
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer')
+invisible(lapply(pkgs, require, character.only = T))
+
+# Auxiliary function: calculate coefficients
+calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
+      # No controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = F))
+      print(k); k = k+1
+      # Controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = F))
+      print(k); k = k+1
+      # No controls and fes
+      mods[[k]] <- felm(
+        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
+                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+                         collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = T))
+      print(k); k = k+1
+      # Controls and fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = T))
+      print(k); k = k+1
+    }
+  }
+  return(list(moddescr, mods))
+}
+
+####
+## Analysis Intervention 1
+####
+
+## ATEs 
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+treats <- c('treat')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)
+```
+
+```{r results1, results='asis', echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
+# Results intervention 1
+library(stargazer)
+stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
+          resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
+          title = 'Impact Evaluation -- Intervention 1', 
+          keep='treatTreatment', type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c('Investment\\\\ Before','Invest\\\\ After',
+                             'Delta\\\\ Investment','Finished\\\\ Construction',
+                             'Cancelled\\\\ Construction','Updated\\\\ Date'),
+          dep.var.labels.include=F,
+          omit.stat=c('adj.rsq', 'ser'), style='apsr',
+          align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipal level.',
+          notes.append = T, header=FALSE)
+```
 
@@
 
-\vspace{.5cm}
-**TABLE 2 ABOUT HERE: RESULTS INTERVENTION 2**
-\vspace{.5cm}
-
 We observe a similar pattern in the second intervention.
@@
 This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomization and one-to-one nearest neighbourhood matching.
+The result is in the Supplementary Material.
+
+```{r table3, echo=FALSE, warning=FALSE, message=FALSE}
+```
 
@@
 Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field].
+We fail to reject the null in all specifications.
+
+We also note that the effect sizes are notably small in each of all our original models.
+Therefore, even if the treatment effects were statistically significant, the TDP app would have a reduced impact over the outcomes.
+This has an important substantive meaning, as it poses a direct challenge to the bottom-up accountability theory, at least for the school construction outcomes we estimated here.
 

### 2019-08-15 article/article.Rmd

@@
 Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
-abstract: "We study the effect of a mobile phone application designed to increase citizens' ability to monitor public works in Brazil.
-The app allows individuals to find delayed school constructions in 1030 Brazilian cities and send anonymous messages to politicians requesting information about construction delays and completion times.
-Our results show the app has a null impact on the completion times subsequently reported by the municipalities.
-Additionally, we find that few politicians react to citizens' requests.
-These findings suggest it is difficult to motivate bottom-up accountability in new democracies, especially when politicians are unresponsive to non-electoral pressures.
-This paper has implications for the design of bottom-up accountability mechanisms."
+abstract: "Does grassroots participation improve public service provision?
+We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1030 Brazilian municipalities.
+The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact their representatives about project delays.
+Our results show the app has a null impact on public spending and school completion times.
+Additionally, we find that politicians do not react to individual requests.
+The results suggest it is difficult to motivate bottom-up accountability in new democracies and question the impact of local monitoring on the quality of public services."
 abstractspacing: double
-keywords: accountability, Brazil, field experiment, impact evaluation, state capacity, technology
+keywords: accountability, Brazil, impact evaluation, state capacity, technology
 fontsize: 12pt
@@
 Overall, our results show that providing information to citizens has very limited impact on policy outcomes.
-We find that the TDP app increased the likelihood of school completion by 6.8 percent in the first experiment, but the effect is null in the second intervention.
+We find that the TDP app increased the likelihood of school completion by 7 percent in the first experiment, but the effect is null in the second intervention.
 We also find that the app increased the percentage of the executed budget by 157.5 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
@@
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 'kableExtra',
+pkgs <- c('tidyverse', 'dummies', 
           'haven', 'compareGroups', 
@@
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 'kableExtra',
+pkgs <- c('tidyverse', 'dummies',
           'haven', 'compareGroups', 
@@
 
-```{r model1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
 load('tdp.RData')
@@
 resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)
-```
 
-```{r results1, results='asis', echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
 # Results intervention 1
@@
           resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
-          title = 'Impact Evaluation -- Intervention 1', 
+          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1', 
           keep='treatTreatment', type = 'latex',
           covariate.labels = 'ATE',
-          column.labels = c('Investment\\\\ Before','Invest\\\\ After',
-                             'Delta\\\\ Investment','Finished\\\\ Construction',
-                             'Cancelled\\\\ Construction','Updated\\\\ Date'),
-          dep.var.labels.include=F,
-          omit.stat=c('adj.rsq', 'ser'), style='apsr',
-          align=F, digits=2,
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-1pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
           notes = 'Cluster-robust SEs at the municipal level.',
+          add.lines = list(c("Controls", "X", "X", "X", "X", "X", "X"),
+            c("State fixed effects", "X", "X", "X", "X", "X", "X")),
           notes.append = T, header=FALSE)
@@
 
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-1pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$0.29 & $-$0.97 & $-$0.68 & 0.07$^{***}$ & 0.001 & 0.06 \\ 
+  & (2.40) & (2.48) & (1.26) & (0.01) & (0.001) & (0.04) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & X & X & X & X & X & X \\ 
+State fixed effects & X & X & X & X & X & X \\ 
+Observations & 2,352 & 2,352 & 2,352 & 2,352 & 2,352 & 2,352 \\ 
+R$^{2}$ & 0.04 & 0.05 & 0.08 & 0.03 & 0.01 & 0.08 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipal level.} \\ 
+\end{tabular} 
+\end{table}
+
 We find that the intervention was sufficient to improve the school completion rate.
-The TDP application increases in 6.85 percent the chance that a school construction is reported as finished by the end of the intervention.
+The TDP application increases in 7 percent the chance that a school construction is reported as finished by the end of the intervention.
 This is in line with our theoretical expectations, but as we discuss below, the finding is not consistent.
@@
 
+```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer')
+invisible(lapply(pkgs, require, character.only = T))
+
+# Auxiliary function: calculate coefficients
+calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
+      # No controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = F))
+      print(k); k = k+1
+      # Controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = F))
+      print(k); k = k+1
+      # No controls and fes
+      mods[[k]] <- felm(
+        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
+                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+                         collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = T))
+      print(k); k = k+1
+      # Controls and fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = T))
+      print(k); k = k+1
+    }
+  }
+  return(list(moddescr, mods))
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+treats <- c('treat')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)
+
+# Results intervention 2
+library(stargazer)
+stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
+          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
+          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
+          dep.var.labels.include=F, 
+          keep='treatAppTreatment', type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          column.sep.width = '-1pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipal level.',
+          add.lines = list(c("Controls", "X", "X", "X", "X", "X", "X"),
+            c("State fixed effects", "X", "X", "X", "X", "X", "X")),
+          notes.append = T, header=FALSE)
+```
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-1pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$0.60 & 0.05 & 0.65 & 0.003 & 0.002 & 0.00 \\ 
+  & (1.63) & (1.70) & (0.62) & (0.02) & (0.003) & (0.00) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & X & X & X & X & X & X \\ 
+State fixed effects & X & X & X & X & X & X \\ 
+Observations & 2,304 & 2,304 & 2,304 & 2,304 & 2,304 & 2,304 \\ 
+R$^{2}$ & 0.06 & 0.08 & 0.05 & 0.03 & 0.02 &  \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipal level.} \\ 
+\end{tabular} 
+\end{table}
+
 We observe a similar pattern in the second intervention.
@@
 Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent.
-This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomization and one-to-one nearest neighbourhood matching.
-The result is in the Supplementary Material.
-
-```{r table3, echo=FALSE, warning=FALSE, message=FALSE}
-```
+This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
 
@@
 
-We also note that the effect sizes are notably small in each of all our original models.
+We also note that the effect sizes are small in each of our original models.
 Therefore, even if the treatment effects were statistically significant, the TDP app would have a reduced impact over the outcomes.

### 2019-08-15 article/article.Rmd
change title

@@
 title:  |
-        | Bottom-Up Accountability and Infrastructure Delivery: Mixed Evidence from Brazil
+        | Bottom-Up Accountability and Infrastructure Provision: Evidence from a Field Experiment in Brazil
 author: 
@@
 Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
-abstract: "Does grassroots participation improve public service provision?
+abstract: "Does grassroots participation improve public service delivery?
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1030 Brazilian municipalities.

### 2019-08-15 article/article.Rmd
abstract

@@
 The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact their representatives about project delays.
-Our results show the app has a null impact on public spending and school completion times.
+Our results show that the app has a null impact on public spending and school completion times.
 Additionally, we find that politicians do not react to individual requests.
-The results suggest it is difficult to motivate bottom-up accountability in new democracies and question the impact of local monitoring on the quality of public services."
+The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
 abstractspacing: double
@@
 @raffler2018weakness [29] point out several reasons why information interventions might lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives.
-Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring into personal costs [@olson1965logic].
+Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
 

### 2019-08-15 article/article.Rmd
title

@@
 title:  |
-        | Bottom-Up Accountability and Infrastructure Provision: Evidence from a Field Experiment in Brazil
+        | Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil
 author: 

### 2019-08-15 article/article.Rmd
small edits

@@
 We also estimated the models without control variables, without fixed effects and with nearest-neighbour matching.
-The results are very similar to the ones below and can be found in the Supplementary Material.
+The results are very similar to those below.
 
@@
           column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
-          dep.var.labels.include=F, column.sep.width = '-1pt',
+          dep.var.labels.include=F, column.sep.width = '-2pt',
           omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = 'Cluster-robust SEs at the municipal level.',
-          add.lines = list(c("Controls", "X", "X", "X", "X", "X", "X"),
-            c("State fixed effects", "X", "X", "X", "X", "X", "X")),
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
+            c("State fixed effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
           notes.append = T, header=FALSE)
 ```
+
+\vspace{.5cm}
 
@@
   \label{} 
-\begin{tabular}{@{\extracolsep{-1pt}}lcccccc} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
 \\[-1.8ex]\hline 
@@
 \hline \\[-1.8ex] 
-Controls & X & X & X & X & X & X \\ 
-State fixed effects & X & X & X & X & X & X \\ 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
 Observations & 2,352 & 2,352 & 2,352 & 2,352 & 2,352 & 2,352 \\ 
@@
 \textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
- & \multicolumn{6}{r}{Cluster-robust SEs at the municipal level.} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
 \end{tabular} 
@@
           column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
-          column.sep.width = '-1pt',
+          column.sep.width = '-2pt',
           omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = 'Cluster-robust SEs at the municipal level.',
-          add.lines = list(c("Controls", "X", "X", "X", "X", "X", "X"),
-            c("State fixed effects", "X", "X", "X", "X", "X", "X")),
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
+            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
           notes.append = T, header=FALSE)
 ```
+\vspace{.5cm}
 
@@
 \hline \\[-1.8ex] 
-Controls & X & X & X & X & X & X \\ 
-State fixed effects & X & X & X & X & X & X \\ 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
 Observations & 2,304 & 2,304 & 2,304 & 2,304 & 2,304 & 2,304 \\ 
@@
 Although we find an effect on school construction in the first intervention and on the number of complaints in the second one, the app has no consistent impact on our outcomes of interest.
-The findings add further evidence to the studies that cast doubts on the relationship between bottom-up accountability and local policy performance [e.g., @banerjee2010pitfalls;  @lieberman2014does; @bjorkman2017experimental; @raffler2018weakness].
+The findings add further evidence to the studies that cast doubts on the relationship between bottom-up accountability and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
 
@@
 Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
-
 In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery.

### 2019-08-16 article/article.Rmd
small edits, again

@@
 In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
-Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the efficiency of the public sector [@adsera2003you; @bjorkman2009power].
+Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the quality of public services [@adsera2003you; @bjorkman2009power].
 Recent research also suggests that accountability leads to higher economic growth because it limits state discretion in the economy and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
@@
 We use the TDP app to conduct two experimental interventions and test its impact on six outcomes related to school completion rates and complaints to public authorities.
-Overall, our results show that providing information to citizens has very limited impact on policy outcomes.
+Overall, our results show that providing information to citizens has no consistent impact on policy outcomes.
 We find that the TDP app increased the likelihood of school completion by 7 percent in the first experiment, but the effect is null in the second intervention.
 We also find that the app increased the percentage of the executed budget by 157.5 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
-No result reported in the first intervention or in the unmatched sample.
 Importantly, both interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.
@@
 The results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness and offer mixed evidence that information interventions lead to greater government responsiveness.
+Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness and offer little evidence that information interventions lead to greater government responsiveness.
 Our analysis suggests that grassroots monitoring does not affect government behaviour in Brazil, and other models of political accountability may be more effective for public service provision.
@@
 
-Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide technical assessment of school completion rates.
-The EWB bases their evaluations on photos and GPS coordinates sent through the app.
+Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide technical assessment of school completion rates based on user-submitted photos and GPS coordinates.
 The engineers' reports are later uploaded to the TDP database and stored on the users' mobile devices so citizens can follow the progress of the constructions.
@@
 Between August 2017 and August 2018, we implemented two interventions to measure the effect of the TDP app on six school construction outcomes.
-The outcomes are: 1) the percentage of public investment allocated to school constructions; 2) the difference between the percentage invested before and after the interventions; 3) the number of finished constructions; 4) the number of cancelled constructions; 5) the number of updated conclusion dates; 6) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started.
-We expect the first five factors to increase and the last one to remain unchanged.
+The outcomes are: 1) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started; 2) the percentage of public investment allocated to school constructions; 3) the difference between the percentage invested before and after the interventions; 4) the number of finished constructions; 5) the number of cancelled constructions; 6) the number of updated conclusion dates.
+We expect the first outcome to remain unchanged and the five remaining ones to increase.
 
@@
 
+We observe a similar pattern in the second intervention.
+Table \ref{tab:results2} shows that the treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo.
+This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion.
+Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent.
+This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
+
+\newpage
+
 ```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
@@
 
-We observe a similar pattern in the second intervention.
-Table \ref{tab:results2} shows that the treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo.
-This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion.
-Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent.
-This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
-
 Figure \ref{fig:permtest} shows the results of our randomisation inference tests.
@@
 Moreover, it is possible that a mobile app like TDP is simply not sufficient to promote collective action.
-@raffler2018weakness [29] point out several reasons why information interventions might lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives.
+@raffler2018weakness [29] point out several reasons why information interventions does not lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives.
 Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
+
 In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery.

### 2019-08-16 article/article.Rmd
add rmd code

@@
 - "Umberto Mignozzetti[^mignozzetti]"
-- "Jessica Voigt[^voigt]"
 date: \today
@@
 
-```{r setup, include=FALSE, warning=FALSE, cache=TRUE}
+```{r setup, include=FALSE, warning=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 rm(pkgs, installIfNot)
-rm(list=ls())
+load('tdp.RData')
 ```
@@
 Corresponding author.
-
-[^voigt]: Data Scientist, Transparência Brasil, São Paulo, SP, Brazil, [jvoigt@transparencia.org.br](mailto:jvoigt@transparencia.org.br), <https://www.linkedin.com/in/voigtjessica>.
 
@@
 The unit of analysis for this experiment is the Brazilian municipality.
-We randomly selected 150 to the control group and included 1030 municipalities in the treatment group.
+We randomly selected `r as.numeric(table(impEvalph1$treatOriginal)[1])` municipalities to the control group and included `r as.numeric(table(impEvalph1$treatOriginal)[2])` in the treatment group.
 Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens had no incentive to use the app.
@@
 Figure \ref{fig:manipulation1} displays the results and indicates that the treatment has good territorial variability.
-There are 455 downloads in the 1030 municipalities in the treatment condition.
+There are `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impEvalph1$municipality[impEvalph1$treatOriginal==1]))` municipalities in the treatment condition.
 Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.
 
-```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, cache=TRUE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
 The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
@@
 First, the TDP app was available for both Android and iOS devices.
-Second, we randomised the intervention at the school level, with 654 control and 3895 treatment units.
+Second, we randomised the intervention at the school level, with `r as.numeric(table(impEvalph2$treatApp)[1])` control and `r as.numeric(table(impEvalph2$treatApp)[2])` treatment units.
 We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
@@
 Balance tests and manipulation checks were also successful for intervention 2.
-In total, 433 municipalities downloaded the app.
-There is one download peak in August 2018, right after the intervention starts, and a second spike around December.
+In total, `r sum(gaaux$Downloads == 'Downloads')` municipalities downloaded the app.
+There is one download peak in August 2018, right after intervention 2 starts, and a second spike around December.
 The number of downloads is considerably smaller in this second intervention when compared to intervention 1 as there was no associated social media campaign in that period.
 
-```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, cache=TRUE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
 The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
@@
 
-```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
 load('tdp.RData')
@@
 We find that the intervention was sufficient to improve the school completion rate.
-The TDP application increases in 7 percent the chance that a school construction is reported as finished by the end of the intervention.
+The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 1)` percent the chance that a school construction is reported as finished by the end of the intervention.
 This is in line with our theoretical expectations, but as we discuss below, the finding is not consistent.
@@
 
-```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
 load('tdp.RData')

### 2019-08-16 article/article.Rmd
small edits

@@
 
-We find that the intervention was sufficient to improve the school completion rate.
+We find that the intervention is sufficient to improve school completion rates.
 The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 1)` percent the chance that a school construction is reported as finished by the end of the intervention.
@@
 First, our study is well powered.
-About 1,000 municipalities were included in the treatment groups, thus we should be able to capture average treatment effects, even small ones, if they indeed exist.
+We included 1000 municipalities in the treatment groups, thus we should be able to capture small average treatment effects if they exist.
 Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures.
-Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no evidence of treatment effect.
+Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no firm evidence of treatment effect.
 
@@
 @raffler2018weakness [29] point out several reasons why information interventions does not lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives.
-Furthermore, individuals may also believe they are better-off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
+Furthermore, individuals may also believe they are better off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
 

### 2019-08-16 article/article.Rmd
typos

@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [`danilofreire@brown.edu`[mailto:danilofreire@brown.edu], <http://danilofreire.github.io>, +1 (401) 584-2494.
+Corresponding author.
 
-[^galdino]: Executive Diretor, Transparência Brazil, São Paulo, SP, Brazil, [mgaldino@transparencia.org.br](mailto:mgaldino@transparencia.org.br), <https://www.transparencia.org.br>.
+[^galdino]: Executive Diretor, Transparência Brasil, São Paulo, SP, Brazil, [`mgaldino@transparencia.org.br`](mailto:mgaldino@transparencia.org.br), <https://www.transparencia.org.br>.
 
-[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [umberto.mig@nyu.edu](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
-Corresponding author.
+[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [`umberto.mig@nyu.edu`](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
 

### 2019-08-19 article/article.Rmd
mignozzetti-commit

@@
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1030 Brazilian municipalities.
-The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact their representatives about project delays.
-Our results show that the app has a null impact on public spending and school completion times.
-Additionally, we find that politicians do not react to individual requests.
+The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact mayor's office about project delays.
+Our results show that the app has a null impact on the school construction outcomes.
+Additionally, we find that politicians are unresponsive to individual requests.
 The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
@@
 One of the key determinants of efficient public services provision is a robust accountability system [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
-In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
+[XXXX A robust accountability system is crucial for efficient public services provision XXXX] In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
 Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the quality of public services [@adsera2003you; @bjorkman2009power].
@@
 One promising model is that of _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project so they can evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
-Proponents argue bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects them; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
+Proponents argue bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects themselves; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
 In this regard, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
+[XXXX However não tá howevering...
+XXXX]
 
-Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.
-Developed by Transparência Brasil[^transparencia], TDP allows Brazilian citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
+Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.[XXXX] Developed by Transparência Brasil[^transparencia], TDP allows citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
 TDP users can also take pictures of the construction sites and submit them to independent engineers for examination.
 If the engineers classify the construction as delayed, TDP prompts users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
-TDP has been online since April 2017 in 1030 Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
+TDP has been online since April 2017 in XXXX Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
 
@@
 
-We use the TDP app to conduct two experimental interventions and test its impact on six outcomes related to school completion rates and complaints to public authorities.
+We use the TDP app to conduct two experimental interventions and test its impact on five outcomes related to school completion rates and complaints to public authorities.
 Overall, our results show that providing information to citizens has no consistent impact on policy outcomes.
 We find that the TDP app increased the likelihood of school completion by 7 percent in the first experiment, but the effect is null in the second intervention.
-We also find that the app increased the percentage of the executed budget by 157.5 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
-Importantly, both interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.
+We also find that the app increased the percentage of the reported construction completion by 1.75 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
+Importantly, both interventions have no significant impact on any of the other measures of school completion we employed in this study.
+[XXXX TOPIC Phrase: our results show that providing information to citizens has no consistent impact on policy outcomes.!!!
+XXXX]
 
 The results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness and offer little evidence that information interventions lead to greater government responsiveness.
-Our analysis suggests that grassroots monitoring does not affect government behaviour in Brazil, and other models of political accountability may be more effective for public service provision.
+Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness offering little evidence that information-based interventions lead to greater government responsiveness.
+Our analysis suggests that grassroots monitoring is ineffective in altering government behaviour in Brazil, and other models of political accountability may be more effective for public service provision.
+[XXXX CORTAR ISSO: and other models of political accountability may be more effective for public service provision XXXX]
 
@@
 More specifically, the main goal of the TDP project is to improve responsiveness in government education expenditures.
-The TDP app incentivises citizens to provide up-to-date information about unfinished schools in their neighbourhoods, and that information will be assessed by a group of independent specialists.
-In the case the construction is behind schedule, TDP provides a writing platform whereby citizens can contact their representatives quickly and anonymously.
+The TDP app incentivises citizens to provide up-to-date information about unfinished school constructions in their neighbourhoods, and that information will be assessed by a group of independent specialists.
+In the case the construction is behind schedule, TDP provides a writing platform whereby citizens can report to public officials quickly and anonymously.
 The app then prompts citizens to write a notification to the mayor's office, which has 15 days to reply.
-If they do not respond to the request, the app forwards the notification to the Brazilian federal government, making it harder for the municipality to access federal funds in the future.
-The motivation for the intervention is that information delivery causes individuals to closely monitor public works.
+If they do not respond to the request, the app forwards the notification to the Brazilian federal government office that grants the funds for the construction, making it harder for the municipality to access federal funds in the future.
+The motivation behind this intervention is that bottom-up pressure from citizens empowers individuals to closely monitor public works.
 This, in turn, results in better social outcomes as public agents become more responsive to community demands.
@@
 
-We built the app in the first three months of 2017 and tested it in May 2017.
+Transparencia Brazil built the app in the first three months of 2017 and tested it in May 2017.
 The first stable Android version was deployed on Google Play on 14 August 2017.
 A version for iOS came about six months later.
-In October 2017, we started a Facebook campaign in order to publicise the app.
+In October 2017, Transparencia Brazil started a Facebook campaign in order to publicise the app.
 Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
@@
 \caption{The \textit{Tá de Pé} mobile phone application.
-The first image presents a list of the closest school construction sites.
-The second image shows that a school construction is delayed by 9 months.
+The first image presents a list of school construction sites closer to the users' location.
+The second image shows that the school construction selected by the user is delayed by 9 months.
 The last image shows how citizens can add information to the photos they submit via the app.}
@@
 Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide technical assessment of school completion rates based on user-submitted photos and GPS coordinates.
-The engineers' reports are later uploaded to the TDP database and stored on the users' mobile devices so citizens can follow the progress of the constructions.
+The engineers' reports are later uploaded to the TDP database and stored on the users' mobile devices so citizens can follow the progress of the reported constructions.
 
@@
 In 2017 and 2018, Transparência Brasil announced two team programming competitions, called 'Tá de Pé Hackathons', where contributors could fix code bugs and suggest new functionalities to the TDP project.
-One of these innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which posts a message on the social network each time a user submits a new picture for evaluation.
+One of these innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which posts a message on the social network each time a user submits a new picture for evaluation or a municipality responds to a citizen's request.
 This allows any interested parties, including those who do not use the TDP app, to check the state of school construction sites.
@@
 
-Between August 2017 and August 2018, we implemented two interventions to measure the effect of the TDP app on six school construction outcomes.
-The outcomes are: 1) a placebo outcome indicating the percentage of the investment executed before the impact evaluation started; 2) the percentage of public investment allocated to school constructions; 3) the difference between the percentage invested before and after the interventions; 4) the number of finished constructions; 5) the number of cancelled constructions; 6) the number of updated conclusion dates.
-We expect the first outcome to remain unchanged and the five remaining ones to increase.
+Between August 2017 and February 2019, we implemented two interventions to measure the effect of the TDP app on five school construction outcomes plus a placebo outcome.
+The outcomes are: 1) a placebo outcome indicating the percentage of the project completed before the impact evaluation started; 2) the percentage of the project completed by the end of the interventions; 3) the difference between the percentage reported as completed before and after the interventions; 4) the number of finished constructions; 5) the number of cancelled constructions; 6) the number of schools where construction companies updated the conclusion dates.
+In terms of expectations, Table \ref{tableOuctExp} depicts the expected effects for each of the studied outcomes.
+
+\begin{table}[htb!]
+\centering
+\caption{Outcomes and expected effect of the TDP intervention}
+\label{tableOuctExp}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{lcl}
+\hline
+\multicolumn{1}{c}{\textbf{}} & \textbf{\begin{tabular}[c]{@{}c@{}}Expected\\ impact\end{tabular}} & \multicolumn{1}{c}{\textbf{Meaning}} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Placebo:\\ Percentage of the project completed before\\ the impact evaluation started\end{tabular} & Null & \begin{tabular}[c]{@{}l@{}}The placebo outcome, as reported before the intervention, \\ should have a null impact.
+This represents the absence of\\ differences between treatment and control prior to the\\ intervention.\end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 1:\\ Percentage of the project reported as completed\\ by the end of the intervention period\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, the firms should\\ increase their efforts toward finishing the construction\\ more quickly.\end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 2:\\ Difference between the percentage reported as\\ completed before and after the intervention\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive impact, the difference\\ between before and after the intervention should reflect\\ this.\end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 3:\\ Dummy indicator for finished constructions\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, more schools\\ should be reported as finished in the treatment group.\end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 4:\\ Dummy indicator for cancelled construction\end{tabular} & Negative & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive impact, less \\ constructions should be abandoned and reported as \\ finished in the treatment group.\end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 5:\\ Number of schools where construction \\ companies updated the conclusion dates\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, firms and \\ mayor's offices should be responsive to the public,\\ and update their finishing dates.\end{tabular} \\ \hline
+\end{tabular}%
+}
+\end{table}
 
 The first intervention was carried out from August 2017 to February 2018 using the Android version of TDP.
-The unit of analysis for this experiment is the Brazilian municipality.
+The randomization was conduct at the municipal level.
 We randomly selected `r as.numeric(table(impEvalph1$treatOriginal)[1])` municipalities to the control group and included `r as.numeric(table(impEvalph1$treatOriginal)[2])` in the treatment group.
-Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens had no incentive to use the app.
+Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens were unable to report constructions in the control municipalities.
 
@@
 Table \ref{tab:results1} summarises the main results of intervention 1.
-Each column represents the treatment effect of the TDP app on one of the six outcomes we measured for this study.
+Each column represents the treatment effect of the TDP app on one of the outcomes we measured for this study.
 All models reported here include the five control variables described in the previous section and Brazilian states' fixed effects.
@@
 On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted.
-On the other hand, we expected the four remaining outcomes to increase after the introduction of the app.
+On the other hand, we expected the four remaining outcomes to improve after the introduction of the app.
 The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies.
@@
 This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion.
-Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent.
-This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
+Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 1.57 percent.
+This effect only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
 
@@
 Therefore, even if the treatment effects were statistically significant, the TDP app would have a reduced impact over the outcomes.
-This has an important substantive meaning, as it poses a direct challenge to the bottom-up accountability theory, at least for the school construction outcomes we estimated here.
+This has an important substantive meaning, as it poses a direct challenge to the bottom-up accountability theory, at least for the school construction outcomes we investigated here.
 
@@
 First, our study is well powered.
-We included 1000 municipalities in the treatment groups, thus we should be able to capture small average treatment effects if they exist.
+Although the treatment is indirect, meaning that the person has to download the app, find a school construction, and then report it, we included a substantial number of municipalities in treatment groups.
+We should be able to capture small average treatment effects if they exist.
 Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures.
 Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no firm evidence of treatment effect.
+Finally, note that the sign of the coefficients are frequently contrary to our theoretical expectations.
+This rules out a possible concern about statistical power with our small control group approach.
 
@@
 
-In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery.
+In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery in the case of school constructions in Brazil.
 Nevertheless, the null findings are informative to researchers and policy-makers.

### 2019-08-19 article/article.Rmd
fix tables and graphs

@@
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1030 Brazilian municipalities.
-The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact mayor's office about project delays.
+The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
 Our results show that the app has a null impact on the school construction outcomes.
@@
 
-One of the key determinants of efficient public services provision is a robust accountability system [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
-[XXXX A robust accountability system is crucial for efficient public services provision XXXX] In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
+A robust accountability system is crucial for efficient public services provision [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
+In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
 Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the quality of public services [@adsera2003you; @bjorkman2009power].
@@
 In this regard, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
-[XXXX However não tá howevering...
-XXXX]
 
-Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.[XXXX] Developed by Transparência Brasil[^transparencia], TDP allows citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
+Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.
+Developed by Transparência Brasil[^transparencia], TDP allows citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
 TDP users can also take pictures of the construction sites and submit them to independent engineers for examination.
@@
 We also find that the app increased the percentage of the reported construction completion by 1.75 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
-Importantly, both interventions have no significant impact on any of the other measures of school completion we employed in this study.
-[XXXX TOPIC Phrase: our results show that providing information to citizens has no consistent impact on policy outcomes.!!!
-XXXX]
+Importantly, our results show that providing information to citizens has no consistent impact on any policy outcomes.
 
@@
 Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness offering little evidence that information-based interventions lead to greater government responsiveness.
-Our analysis suggests that grassroots monitoring is ineffective in altering government behaviour in Brazil, and other models of political accountability may be more effective for public service provision.
-[XXXX CORTAR ISSO: and other models of political accountability may be more effective for public service provision XXXX]
+Our analysis suggests that grassroots monitoring is ineffective in altering government behaviour in Brazil.
 
@@
 
-Transparencia Brazil built the app in the first three months of 2017 and tested it in May 2017.
+Transparência Brazil built the app in the first three months of 2017 and tested it in May 2017.
 The first stable Android version was deployed on Google Play on 14 August 2017.
 A version for iOS came about six months later.
-In October 2017, Transparencia Brazil started a Facebook campaign in order to publicise the app.
+In October 2017, Transparência Brazil started a Facebook campaign in order to publicise the app.
 Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
@@
 \multicolumn{1}{c}{\textbf{}} & \textbf{\begin{tabular}[c]{@{}c@{}}Expected\\ impact\end{tabular}} & \multicolumn{1}{c}{\textbf{Meaning}} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Placebo:\\ Percentage of the project completed before\\ the impact evaluation started\end{tabular} & Null & \begin{tabular}[c]{@{}l@{}}The placebo outcome, as reported before the intervention, \\ should have a null impact.
-This represents the absence of\\ differences between treatment and control prior to the\\ intervention.\end{tabular} \\
-\begin{tabular}[c]{@{}l@{}}Outcome 1:\\ Percentage of the project reported as completed\\ by the end of the intervention period\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, the firms should\\ increase their efforts toward finishing the construction\\ more quickly.\end{tabular} \\
-\begin{tabular}[c]{@{}l@{}}Outcome 2:\\ Difference between the percentage reported as\\ completed before and after the intervention\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive impact, the difference\\ between before and after the intervention should reflect\\ this.\end{tabular} \\
-\begin{tabular}[c]{@{}l@{}}Outcome 3:\\ Dummy indicator for finished constructions\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, more schools\\ should be reported as finished in the treatment group.\end{tabular} \\
-\begin{tabular}[c]{@{}l@{}}Outcome 4:\\ Dummy indicator for cancelled construction\end{tabular} & Negative & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive impact, less \\ constructions should be abandoned and reported as \\ finished in the treatment group.\end{tabular} \\
-\begin{tabular}[c]{@{}l@{}}Outcome 5:\\ Number of schools where construction \\ companies updated the conclusion dates\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, firms and \\ mayor's offices should be responsive to the public,\\ and update their finishing dates.\end{tabular} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Placebo:\\ Percentage of the project completed before\\ the impact evaluation started.\end{tabular} & Null & \begin{tabular}[c]{@{}l@{}}The placebo outcome, as reported before the intervention, \\ should have a null impact.
+This represents the absence of\\ differences between treatment and control prior to the\\ intervention.
+\vspace{.2cm} \end{tabular} \\
+\begin{tabular}[c]{@{}l@{}} Outcome 1:\\ Percentage of the project reported as completed\\ by the end of the intervention period.
+\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, the firms should\\  increase their efforts toward finishing the construction\\ more quickly.
+\vspace{.2cm} \end{tabular} \\
+\begin{tabular}[c]{@{}l@{}} Outcome 2:\\ Difference between the percentage reported as\\ completed before and after the intervention.
+\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive impact, the difference\\ between before and after the intervention should reflect\\ this.
+\vspace{.2cm} \end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 3:\\ Dummy indicator for finished constructions.
+\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, more schools\\ should be reported as finished in the treatment group.\vspace{.2cm} \end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 4:\\ Dummy indicator for cancelled construction.
+\end{tabular} & Negative & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive impact, less \\ constructions should be abandoned and reported as \\ finished in the treatment group.\vspace{.2cm} \end{tabular} \\
+\begin{tabular}[c]{@{}l@{}}Outcome 5:\\ Number of schools where construction \\ companies updated the conclusion dates.
+\end{tabular} & Positive & \begin{tabular}[c]{@{}l@{}}If the intervention has a positive effect, firms and \\ mayor's offices should be responsive to the public,\\ and update their finishing dates.\vspace{.2cm} \end{tabular} \\ \hline
 \end{tabular}%
@@
 
-```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.1, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
 The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
@@
 
-```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.2, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
 The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
@@
 
-```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
+```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
 load('tdp.RData')
@@
 
-```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
+```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
 load('tdp.RData')

### 2019-08-19 article/article.Rmd
maps and ri

@@
           'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer')
+          'flextable', 'officer', 'ggthemes')
 
@@
           'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer')
+          'flextable', 'officer', 'ggthemes')
 invisible(lapply(pkgs, require, character.only = T))
@@
 gaaux$City <- as.numeric(gaaux$City)
+gaaux <- impEvalph2 %>%
+  select(ibge_code7) %>%
+  transmute(City = as.numeric(ibge_code7)) %>%
+  unique() %>%
+  left_join(gaaux)
+gaaux$downl[is.na(gaaux$downl)] = 0
 gaaux2 <- data.frame(City = mapbr$City)
-gaaux <- merge(gaaux2, gaaux,all.x=TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 0
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
-pMapDownloadsInt1 <- plot_brmap(mapbr,
-                                data_to_join = gaaux,
-                                join_by = c("City" = "City"),
-                                var = "Downloads") 
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 2
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
+mapbr <- join_data(mapbr, gaaux, by = 'City')
+pMapDownloadsInt1 <- ggplot() + 
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
+  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  theme_map()
 pMapDownloadsInt1
@@
 gaaux$City <- as.numeric(gaaux$City)
+gaaux <- impEvalph2 %>%
+  select(ibge_code7) %>%
+  transmute(City = as.numeric(ibge_code7)) %>%
+  unique() %>%
+  left_join(gaaux)
+gaaux$downl[is.na(gaaux$downl)] = 0
 gaaux2 <- data.frame(City = mapbr$City)
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 0
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads'))
-p1 <- plot_brmap(mapbr,
-                data_to_join = gaaux,
-                join_by = c("City" = "City"),
-                var = "Downloads") 
+gaaux$downl[is.na(gaaux$downl)] = 2
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
+mapbr <- join_data(mapbr, gaaux, by = 'City')
+p1 <- ggplot() + 
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
+  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  theme_map()
 p1
@@
 
+```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer', 'ggthemes')
+invisible(lapply(pkgs, require, character.only = T))
+
+# Prep data
+dat <- data.frame(
+  Y = c(8, 6, 2, 0, 3, 1, 1, 1, 2, 2, 0, 1, 0, 2, 2, 4, 1, 1),
+  Z = c(1, 1, 0, 0, 1, 1, 0, 0, 1, 1, 1, 1, 0, 0, 1, 1, 0, 0),
+  cluster = c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5, 6, 6, 7, 7, 8, 8, 9, 9),
+  block = c(rep(1, 4), rep(2, 6), rep(3, 8))
+)
+
+# clusters in blocks 1 and 3 have a 1/2 probability of treatment
+# but clusters in block 2 have a 2/3 probability of treatment
+block_m <- with(dat, tapply(Z, block, sum) / 2)
+declaration <- 
+  with(dat,{
+    declare_ra(
+      blocks = block,
+      clusters = cluster,
+      block_m = block_m)
+  })
+
+declaration
+
+ri2_out <- conduct_ri(
+  Y ~ Z,
+  sharp_hypothesis = 0,
+  declaration = declaration,
+  data = dat
+)
+summary(ri2_out)
+
+# Randomization inference
+felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = T))
+
+# Auxiliary function: calculate coefficients
+calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
+      # No controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = F))
+      print(k); k = k+1
+      # Controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = F))
+      print(k); k = k+1
+      # No controls and fes
+      mods[[k]] <- felm(
+        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
+                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+                         collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = T))
+      print(k); k = k+1
+      # Controls and fes
+
+      print(k); k = k+1
+    }
+  }
+  return(list(moddescr, mods))
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+treats <- c('treat')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)
+
+# Results intervention 2
+library(stargazer)
+stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
+          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
+          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
+          dep.var.labels.include=F, 
+          keep='treatAppTreatment', type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
+            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
+          notes.append = T, header=FALSE)
+```
+
 We also note that the effect sizes are small in each of our original models.

### 2019-08-19 article/article.Rmd
minor edits

@@
 
-The results raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
+The findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
 Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness offering little evidence that information-based interventions lead to greater government responsiveness.
@@
 
-```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.1, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=3.1, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
 The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
@@
 
-```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.2, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=3.2, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
 The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
@@
 
-\newpage
-
-```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
+```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
 load('tdp.RData')
@@
 
-```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
 load('tdp.RData')
@@
 # Auxiliary function: calculate coefficients
-calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+calcATEs <- function(outcs, treats, ctrls, fes, cls, zdat, wts = NULL, ...) {
   ctrls_mod <- paste(ctrls, collapse = '+')

### 2019-08-19 article/article.Rmd
remove message maps

@@
 If the engineers classify the construction as delayed, TDP prompts users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
-TDP has been online since April 2017 in XXXX Brazilian municipalities and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
+TDP has been online since April 2017 and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
 
@@
 gaaux$City <- as.numeric(gaaux$City)
-gaaux <- impEvalph2 %>%
+gaaux2 <- impEvalph2 %>%
   select(ibge_code7) %>%
   transmute(City = as.numeric(ibge_code7)) %>%
-  unique() %>%
-  left_join(gaaux)
+  unique()
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
 gaaux$downl[is.na(gaaux$downl)] = 0

### 2019-08-20 article/article.Rmd
small edits

@@
 abstract: "Does grassroots participation improve public service delivery?
-We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1030 Brazilian municipalities.
+We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1020 Brazilian municipalities.
 The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
@@
 Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.
-Developed by Transparência Brasil[^transparencia], TDP allows citizens to know the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
+Developed by Transparência Brasil[^transparencia], TDP allows citizens to learn the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
 TDP users can also take pictures of the construction sites and submit them to independent engineers for examination.
@@
 
-To evaluate the random assignment, we used the following pre-treatment variables: 1) log of municipal population in 2015; 2) log of number of poor families in each city; 3) log of total federal transfers to the municipality in 2016; 4) federal government indicator for primary school quality; 4) federal government indicator for secondary school quality.
+To evaluate the random assignment, we used the following pre-treatment variables: 1) log of municipal population in 2015; 2) log of number of poor families in each city; 3) log of total federal transfers to the municipality in 2016; 4) federal government indicator for primary school quality; 5) federal government indicator for secondary school quality.
 The data come from the Brazilian Ministry of Education and the Census.

### 2019-08-22 article/article.Rmd
almost-final draft

@@
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog, Catarina Roman and David Skarbek for their helpful comments.
-We are specially grateful to the staff of Transparência Brasil for their excellent research assistance.
+thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments.
+We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance.
 This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education.
@@
     toc: no
-    toc_depth: 3
     template: article-template.latex
@@
 ```{r setup, include=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-r <- getOption("repos")
-r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
-options(repos = r)
-
-## Pre-processing
-
-# Required packages
 pkgs <- c('tidyverse', 'dummies', 'kableExtra',
@@
           'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes')
+          'flextable', 'officer', 'ggthemes', 
+          'stargazer')
 
@@
 [^transparencia]: Transparência Brasil is an non-governmental organisation whose mission is to 'promote transparency and social control of public power'.
-It has been active since April 2000, is non-partisan and receives no public funding.
+It has been active since April 2000, receives no public funding, and is non-partisan.
 More information at <http://transparencia.org.br> (access: July 2019).
@@
 Overall, our results show that providing information to citizens has no consistent impact on policy outcomes.
-We find that the TDP app increased the likelihood of school completion by 7 percent in the first experiment, but the effect is null in the second intervention.
+In the first experiment, we find that the TDP app increased the likelihood of school completion by 5 percent and the number of cancelled schools by 3 percent, but the effects are null in the second intervention.
 We also find that the app increased the percentage of the reported construction completion by 1.75 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
@@
        \centering
-       \includegraphics[scale=0.25]{tdp03.jpg}
-       \label{}
+       \includegraphics[scale=.2]{tdp03.jpg}
      \end{minipage}
@@
        \centering
-       \includegraphics[scale=0.25]{tdp01.jpg}
+       \includegraphics[scale=.2]{tdp01.jpg}
      \end{minipage}
@@
        \centering
-       \includegraphics[scale=0.25]{tdp02.jpg}
+       \includegraphics[scale=.2]{tdp02.jpg}
      \end{minipage}
@@
 The outcomes are: 1) a placebo outcome indicating the percentage of the project completed before the impact evaluation started; 2) the percentage of the project completed by the end of the interventions; 3) the difference between the percentage reported as completed before and after the interventions; 4) the number of finished constructions; 5) the number of cancelled constructions; 6) the number of schools where construction companies updated the conclusion dates.
-In terms of expectations, Table \ref{tableOuctExp} depicts the expected effects for each of the studied outcomes.
+In terms of expectations, Table \ref{tab:outcomes} depicts the expected effects for each of the studied outcomes.
 
@@
 \caption{Outcomes and expected effect of the TDP intervention}
-\label{tableOuctExp}
+\label{tab:outcomes}
 \resizebox{\textwidth}{!}{%
@@
 
-```{r man1, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=3.1, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+```{r man1, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.5, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
 The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
@@
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 
+pkgs <- c('tidyverse', 'dummies', 'ggpubr',
           'haven', 'compareGroups', 
@@
 
-```{r man2, echo=FALSE, warning=FALSE, messages=FALSE, error=FALSE, out.width='.49\\linewidth', fig.width=4, fig.height=3.2, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+```{r man2, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.3, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
 The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
@@
 # Load packages
-pkgs <- c('tidyverse', 'dummies',
+pkgs <- c('tidyverse', 'dummies', 'ggpubr',
           'haven', 'compareGroups', 
@@
   mods <- list()
+  dataux <- dat
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
       if(is.null(wts)) {
-    dat <- dat %>%
-      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
+        dat <- dataux %>%
+          select(one_of(c(j, treats, ctrls, fes, cls))) %>%
           na.omit()
         } else {
-    dat <- dat %>%
-      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
+          dat <- dataux %>%
+            select(one_of(c(j, treats, ctrls, fes, cls, wts))) %>%
             na.omit()
@@
         }
-  k <- 1
-  for (i in treats) {
-    for (j in outcs) {
       # No controls and no fes
@@
         as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
-                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+                                   paste('',fes_mod,0,cls, sep = '|'), 
+                                   sep = '')),
                          collapse = '~')), data = dat, weights = wts)
@@
 # Results intervention 1
-library(stargazer)
 stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
@@
           title = '\\label{tab:results1} Impact Evaluation -- Intervention 1', 
-          keep='treatTreatment', type = 'latex',
+          keep='treatTreatment', 
+          type = 'latex',
           covariate.labels = 'ATE',
@@
           notes = 'Cluster-robust SEs at the municipality level.',
-          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
-            c("State fixed effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
+                             "Yes", "Yes", "Yes"),
+            c("State fixed effects", "Yes", "Yes", "Yes",
+              "Yes", "Yes", "Yes")),
           notes.append = T, header=FALSE)
@@
 \cline{2-7} 
- & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
 \\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
 \hline \\[-1.8ex] 
- ATE & $-$0.29 & $-$0.97 & $-$0.68 & 0.07$^{***}$ & 0.001 & 0.06 \\ 
-  & (2.40) & (2.48) & (1.26) & (0.01) & (0.001) & (0.04) \\ 
+ ATE & 1.26 & 1.83 & 0.57 & 0.05$^{***}$ & 0.03$^{***}$ & 0.06 \\ 
+  & (2.69) & (3.06) & (0.93) & (0.01) & (0.01) & (0.04) \\ 
   & & & & & & \\ 
@@
 Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 2,352 & 2,352 & 2,352 & 2,352 & 2,352 & 2,352 \\ 
-R$^{2}$ & 0.04 & 0.05 & 0.08 & 0.03 & 0.01 & 0.08 \\ 
+State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 3,602 & 3,602 & 3,602 & 3,602 & 3,602 & 2,352 \\ 
+R$^{2}$ & 0.13 & 0.13 & 0.05 & 0.03 & 0.05 & 0.08 \\ 
 \hline 
@@
 
-We find that the intervention is sufficient to improve school completion rates.
-The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 1)` percent the chance that a school construction is reported as finished by the end of the intervention.
-This is in line with our theoretical expectations, but as we discuss below, the finding is not consistent.
+We find that the intervention is sufficient to improve school completion and cancellation rates.
+The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 0)` percent the chance that a school construction is reported as finished by the end of the intervention.
+The treatment also increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 0)` percent.
+While the first result is in line with our theoretical expectations, the second one goes in the opposite direction.
+But as we discuss below, the findings are inconsistent and do not replicate in the second experiment.
 All other coefficients are not statistically significant at conventional levels.
@@
 
-We observe a similar pattern in the second intervention.
-Table \ref{tab:results2} shows that the treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo.
-This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion.
+Table \ref{tab:results2} shows the results of the second intervention.
+The treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo.
+This raises further questions about the effect of the TDP app on school completion.
 Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 1.57 percent.
-This effect only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
+However, the coefficient only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
 
-```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
+```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
 load('tdp.RData')
@@
           'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes')
+          'flextable', 'officer', 'ggthemes', 
+          'stargazer')
 invisible(lapply(pkgs, require, character.only = T))
@@
            'isCancelled', 'updDate')
-treats <- c('treat')
-ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
-           'log_poorFam2010', 'log_totTransf2016')
-fes <- c('state')
-cls <- c('municipality')
-
-resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)
-
-# Results intervention 2
-library(stargazer)
-stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
-          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
-          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
-          dep.var.labels.include=F, 
-          keep='treatAppTreatment', type = 'latex',
-          covariate.labels = 'ATE',
-          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
-          column.sep.width = '-2pt',
-          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = 'Cluster-robust SEs at the municipality level.',
-          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
-            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
-          notes.append = T, header=FALSE)
-```
-\vspace{.5cm}
-
-\begin{table}[!htbp] \centering 
-  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-7} 
- & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
-\hline \\[-1.8ex] 
- ATE & $-$0.60 & 0.05 & 0.65 & 0.003 & 0.002 & 0.00 \\ 
-  & (1.63) & (1.70) & (0.62) & (0.02) & (0.003) & (0.00) \\ 
-  & & & & & & \\ 
-\hline \\[-1.8ex] 
-Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 2,304 & 2,304 & 2,304 & 2,304 & 2,304 & 2,304 \\ 
-R$^{2}$ & 0.06 & 0.08 & 0.05 & 0.03 & 0.02 &  \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
- & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
-\end{tabular} 
-\end{table}
-
-Figure \ref{fig:permtest} shows the results of our randomisation inference tests.
-Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field].
-We fail to reject the null in all specifications.
-
-```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
-load('tdp.RData')
-
-# Load packages
-pkgs <- c('tidyverse', 'dummies', 
-          'haven', 'compareGroups', 
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes')
-invisible(lapply(pkgs, require, character.only = T))
-
-# Prep data
-dat <- data.frame(
-  Y = c(8, 6, 2, 0, 3, 1, 1, 1, 2, 2, 0, 1, 0, 2, 2, 4, 1, 1),
-  Z = c(1, 1, 0, 0, 1, 1, 0, 0, 1, 1, 1, 1, 0, 0, 1, 1, 0, 0),
-  cluster = c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5, 6, 6, 7, 7, 8, 8, 9, 9),
-  block = c(rep(1, 4), rep(2, 6), rep(3, 8))
-)
-
-# clusters in blocks 1 and 3 have a 1/2 probability of treatment
-# but clusters in block 2 have a 2/3 probability of treatment
-block_m <- with(dat, tapply(Z, block, sum) / 2)
-declaration <- 
-  with(dat,{
-    declare_ra(
-      blocks = block,
-      clusters = cluster,
-      block_m = block_m)
-  })
-
-declaration
-
-ri2_out <- conduct_ri(
-  Y ~ Z,
-  sharp_hypothesis = 0,
-  declaration = declaration,
-  data = dat
-)
-summary(ri2_out)
-
-# Randomization inference
-felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j,
-                                   treat = i,
-                                   hCtrls = T,
-                                   hFEs = T))
-
-# Auxiliary function: calculate coefficients
-calcATEs <- function(outcs, treats, ctrls, fes, cls, zdat, wts = NULL, ...) {
-  ctrls_mod <- paste(ctrls, collapse = '+')
-  fes_mod <- paste(fes, collapse = '+')
-  moddescr <- data.frame()
-  mods <- list()
-  if(is.null(wts)) {
-    dat <- dat %>%
-      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
-      na.omit()
-  } else {
-    dat <- dat %>%
-      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
-      na.omit()
-    wts <- dat[,wts]
-  }
-  k <- 1
-  for (i in treats) {
-    for (j in outcs) {
-      # No controls and no fes
-      mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = F,
-                                   hFEs = F))
-      print(k); k = k+1
-      # Controls and no fes
-      mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = T,
-                                   hFEs = F))
-      print(k); k = k+1
-      # No controls and fes
-      mods[[k]] <- felm(
-        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
-                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-                         collapse = '~')), data = dat, weights = wts)
-      moddescr <- rbind(moddescr, 
-                        data.frame(outc = j, 
-                                   treat = i,
-                                   hCtrls = F,
-                                   hFEs = T))
-      print(k); k = k+1
-      # Controls and fes
-
-      print(k); k = k+1
-    }
-  }
-  return(list(moddescr, mods))
-}
-
-outcs <- c('percExecBegin', 'percExecEnd',
-           'deltaPercExec', 'isFinished',
-           'isCancelled', 'updDate')
-treats <- c('treat')
 ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
@@
 
-We also note that the effect sizes are small in each of our original models.
-Therefore, even if the treatment effects were statistically significant, the TDP app would have a reduced impact over the outcomes.
-This has an important substantive meaning, as it poses a direct challenge to the bottom-up accountability theory, at least for the school construction outcomes we investigated here.
+\vspace{.5cm}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$1.16 & $-$1.01 & 0.14 & $-$0.002 & $-$0.0001 & 0.00 \\ 
+  & (1.40) & (1.50) & (0.54) & (0.01) & (0.01) & (0.00) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 3,364 & 3,364 & 3,364 & 3,364 & 3,364 & 2,304 \\ 
+R$^{2}$ & 0.10 & 0.10 & 0.03 & 0.02 & 0.18 &  \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+\end{tabular} 
+\end{table}
+
+Figure \ref{fig:randomisation-inference} shows the results of our randomisation inference tests.
+Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field].
+We fail to reject the null in all but the finished school indicator in experiment 1.
+
+```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE, fig.width=6.5, fig.height=8, fig.show='hold', fig.align='center', fig.cap='\\label{fig:randomisation-inference}Sampling distribution of the estimated coefficient for our six outcomes in two interventions.
+Graphs on the left correspond to randomisation inference estimates for intervention 1 and those on the right describe the results for intervention 2.'}
+# Chunk randomization inference
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer', 'ggthemes', 'ggpubr')
+invisible(lapply(pkgs, require, character.only = T))
+
+# Function for custom randomization inference
+test_fun <- function(dat, outc, treat, wts = NULL) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  aux <- 
+    felm(as.formula(
+      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+  return(aux$coefficients[1])
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+# First experiment
+set.seed(543129) #Random.org
+auxdat <- impEvalph1[,c('ibge_code7', outcs, ctrls, fes, cls)]
+aux2 <- unique(impEvalph1[,c('ibge_code7', 'treat')]) %>% na.omit()
+N = sum(table(aux2$treat))
+Ctrl = 150
+resri1 <- data.frame(1:1000)
+for (k in 1:1000) {
+    treat <- c(rep(1,N-Ctrl), rep(0,Ctrl))
+    treat <- sample(treat, N)
+    aux2 <- data.frame(aux2, treat = treat)
+}
+auxdat <- left_join(auxdat, aux2)
+for (i in outcs) {
+  res <- numeric()
+  for (k in 1:1000) 
+    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
+  resri1 <- data.frame(resri1, res)
+  names(resri1)[names(resri1)=='res'] = i
+}
+resri1 <- resri1[,-1]
+i1h1 <- ggplot(data=resri1, aes(resri1$percExecBegin)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'percExecBegin', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
+i1h2 <- ggplot(data=resri1, aes(resri1$percExecEnd)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'percExecEnd', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed End Intervention", y="Frequency")
+i1h3 <- ggplot(data=resri1, aes(resri1$deltaPercExec)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'deltaPercExec', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
+i1h4 <- ggplot(data=resri1, aes(resri1$isFinished)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'isFinished', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Finished School Construction Indicator", y="Frequency")
+i1h5 <- ggplot(data=resri1, aes(resri1$isCancelled)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'isCancelled', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Cancelled School Construction Indicator", y="Frequency")
+i1h6 <- ggplot(data=resri1, aes(resri1$updDate)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'updDate', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Updated Endline Date School Construction", y="Frequency")
+
+## Intervention 2
+# Declare RA
+aux <- filter(rand2018, !is.na(Z_intheapp))
+declRA <- declare_ra(blocks = aux$var_blocking,
+                     prob_each = c(.85,.15), 
+                     conditions = c(1, 0))
+
+# Function for custom randomization inference
+test_fun <- function(dat, outc, treat, wts = NULL) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  aux <- 
+    felm(as.formula(
+      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+  return(aux$coefficients[1])
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+# First experiment
+set.seed(543129) #Random.org
+auxdat <- impEvalph2[,c('id_project', outcs, ctrls, fes, cls)]
+aux2 <- unique(aux[,c('id', 'Z_intheapp', 'IPW_intheapp')]) %>%
+  na.omit() %>%
+  rename(id_project = id,
+         treat = Z_intheapp,
+         wts = IPW_intheapp) %>%
+  mutate(treat = as.numeric(as.factor(treat))-1)
+resri2 <- data.frame(1:1000)
+for (k in 1:1000) {
+    Z <- block_ra(blocks = aux$var_blocking, 
+                  conditions = c(1, 0),
+                  prob_each = c(.85,.15))
+    IPW <- 1/obtain_condition_probabilities(declRA, Z)
+    aux2 <- data.frame(aux2, treat = Z, wts = IPW)
+}
+auxdat <- left_join(auxdat, aux2)
+for (i in outcs) {
+  res <- numeric()
+  for (k in 1:1000) 
+    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
+  resri2 <- data.frame(resri2, res)
+  names(resri2)[names(resri2)=='res'] = i
+}
+resri2 <- resri2[,-1]
+i2h1 <- ggplot(data=resri2, aes(resri2$percExecBegin)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'percExecBegin', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
+i2h2 <- ggplot(data=resri2, aes(resri2$percExecEnd)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'percExecEnd', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed End Intervention", y="Frequency")
+i2h3 <- ggplot(data=resri2, aes(resri2$deltaPercExec)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'deltaPercExec', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
+i2h4 <- ggplot(data=resri2, aes(resri2$isFinished)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'isFinished', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Finished School Construction Indicator", y="Frequency")
+i2h5 <- ggplot(data=resri2, aes(resri2$isCancelled)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'isCancelled', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Cancelled School Construction Indicator", y="Frequency")
+i2h6 <- ggplot(data=resri2, aes(resri2$updDate)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'updDate', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Updated Endline Date School Construction", y="Frequency")
+
+ggarrange(i1h1, i2h1, 
+          i1h2, i2h2, 
+          i1h3, i2h3, 
+          i1h4, i2h4, 
+          i1h5, i2h5, 
+          i1h6, i2h6, 
+          labels = rep(c("Int. 1", "Int. 2"), 6),
+          label.x = .1,
+          ncol = 2, nrow = 6)
+```
+
+We also note that effect sizes are small in all estimations and coefficients flip signs in all but one of our six dependent variables.
+This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts.
+At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works.
 
@@
 In this paper, we discuss whether a mobile phone application can foster grassroots mobilisation and political accountability in Brazil.
-Our two interventions show that the results are mixed.
-Although we find an effect on school construction in the first intervention and on the number of complaints in the second one, the app has no consistent impact on our outcomes of interest.
-The findings add further evidence to the studies that cast doubts on the relationship between bottom-up accountability and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
+Our two interventions show that the results are at best mixed.
+Although we find an effect on school construction completion and cancelling rates in the first intervention, the app has no consistent impact on our outcomes of interest.
+These findings add to the studies that cast doubts on the relationship between bottom-up accountability and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
 
@@
 First, our study is well powered.
-Although the treatment is indirect, meaning that the person has to download the app, find a school construction, and then report it, we included a substantial number of municipalities in treatment groups.
-We should be able to capture small average treatment effects if they exist.
+Although the treatment is indirect, meaning that the person has to download the app, find a school construction, and then report it, we included a substantial number of schools in the treatment groups.
 Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures.
-Third, after doing a series of robustness tests --- including matching and randomised inference --- we still find no firm evidence of treatment effect.
+Third, after doing a series of robustness tests, we still find no firm evidence of treatment effect.
 Finally, note that the sign of the coefficients are frequently contrary to our theoretical expectations.

### 2019-08-24 appendix/appendix.Rmd
upload appendix v0.1

@@
 title: |
-       | Supplementary Materials for "PAPER"
+       | Supplementary Materials for "Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil"
 author: 
@@
 - "Umberto Mignozzetti[^mignozzetti]"
-- "Jessica Voigt[^voigt]"
-date: July 26, 2019
+date: \today
+thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments.
+We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance.
+This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education.
+The authors thank the 2016 Google Social Impact Challenge for financial support and declare there are no conflict of interest.
+Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
+abstract: "Does grassroots participation improve public service delivery?
+We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1020 Brazilian municipalities.
+The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
+Our results show that the app has a null impact on the school construction outcomes.
+Additionally, we find that politicians are unresponsive to individual requests.
+The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
+abstractspacing: double
+keywords: accountability, Brazil, impact evaluation, state capacity, technology
 fontfamily: libertine
@@
     number_sections: yes
-    toc: true
+    toc: false
     keep_tex: no
@@
 
-[^voigt]: Data Scientist, Transparência Brasil, São Paulo, SP, Brazil, [voigt.jessica@gmail.com](mailto:voigt.jessica@gmail.com), <https://www.linkedin.com/in/voigtjessica>.
+\newpage
 
-```{r setup, echo=FALSE}
+# Balance Tests \label{sec:bal-tests}
+
+The tables below show the results of the balance tests for interventions 1 and 2.
+Our list of covariates are: 1) log of municipal population in 2015; 2) log of number of poor families in each city; 3) log of total federal transfers to the municipality in 2016; 4) federal government indicator for primary school quality; 5) federal government indicator for secondary school quality.
+The data come from the Brazilian Ministry of Education and the National Census.
+
+In intervention 1, we randomised the treatment at the municipality level.
+We selected 150 municipalities for the control group while the rest were placed in the treatment group.
+The control group worked by deleting all the construction sites in control assigned cities.
+No difference between control and treatment variables is statistically significant.
+
+```{r balance1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, tidy=TRUE}
+# R options
+r <- getOption("repos")
+r["CRAN"] <- "http://cran.cnr.berkeley.edu/"; options(repos = r)
+
+# Install required packages
+pkgs <- c('tidyverse', 'dummies', 'kableExtra', 'haven', 'compareGroups',
+          'grid', 'gridExtra', 'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 'MatchIt', 'ri2', 'DeclareDesign',
+          'knitr', 'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 'flextable',
+          'officer', 'ggthemes', 'stargazer')
+
+installIfNot <- function(x) {
+  if(x %in% rownames(installed.packages()) == FALSE) 
+    install.packages(x, dependencies = T)
+} 
+invisible(lapply(pkgs, installIfNot))
+
+# Load packages
+invisible(lapply(pkgs, require, character.only = T)); rm(pkgs, installIfNot)
+
+# Load Data 
+load('tdp.RData')
+
+# Covariate Balance -- Intervention 1
+aux <- select(impEvalph1, treatOriginal, logPop2015, ideb_ai_2015, 
+              ideb_af_2015, log_poorFam2010, log_totTransf2016) %>% unique()
+
+resu1 <- compareGroups(treatOriginal ~ logPop2015 + log_poorFam2010 +
+                         log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
+                       data = aux)
+
+tabIE1balance <- createTable(resu1, digits = 2)
+row.names(tabIE1balance$descr) <- c('Log Population (2015)',
+                                    'Log Poor Families (2010)',
+                                    'Log Total Transfers (2016)',
+                                    'IDEB Initial Years (2015)',
+                                    'IDEB Final Years (2015)')
+
+print(tabIE1balance)
 ```
 
-# Latin American Elite Survey \label{sec:latam}
+In intervention 2, we randomised the treatment at the school level.
+We placed 15% of schools that could potentially appear in the App in the control group.
+We used block randomization, blocking by three characteristics:
+
+* Brazilian State
+* Construction Status (under construction, stopped, unfinished)
+* School expenditures above the national median
+
+```{r}
+## Covariate balance
+aux <- select(impEvalph2, logPop2015, treatApp, ideb_ai_2015,
+              ideb_af_2015, log_poorFam2010, log_totTransf2016)
+
+resu1 <- compareGroups(treatApp ~ logPop2015 + log_poorFam2010 +
+                         log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
+                       data = aux)
+
+tabIE2Balance <- createTable(resu1, digits = 2)
+row.names(tabIE2Balance$descr) <-  c('Log Population (2015)', 
+                                     'Log Poor Families (2010)', 
+                                     'Log Total Transfers (2016)', 
+                                     'IDEB Inicial Years (2015)', 
+                                     'IDEB Final Years (2015)')
+print(tabIE2Balance)
+```
+
+\newpage
+# Manipulation Checks
+
+In randomised experiments, manipulation is defined as the extent through which the treatment was successfully delivered to the control and treated units.
+In the case of the *Tá de Pé* app intervention, the manipulation indicates whether the app improves school construction completion rates.
+We present two manipulation indicators.
+First, we look into municipalities which did or did not download the app.
+Next, we see the number of app downloads during intervention 1 (February 2017--August 2018) and intervention 2 (August 2018--February 2019).
+The code replicates figures 2 and 3 in the article.
+
+```{r man1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
+# Map manipulation test -- Intervention 1
+mapbr <- get_brmap('City')
+gaaux <- filter(ga, phase1 == 1)
+gaaux <- select(gaaux, ibge_code7, downl)
+gaaux <- rename(gaaux, City = ibge_code7)
+gaaux <- unique(gaaux)
+gaaux$City <- as.numeric(gaaux$City)
+gaaux2 <- impEvalph2 %>%
+  select(ibge_code7) %>%
+  transmute(City = as.numeric(ibge_code7)) %>%
+  unique()
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux2 <- data.frame(City = mapbr$City)
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 2
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
+                                                  'Not in App'))
+mapbr <- join_data(mapbr, gaaux, by = 'City')
+pMapDownloadsInt1 <- ggplot() + 
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
+  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  theme_map()
+pMapDownloadsInt1
+
+# App downloads over time -- Intervention 1
+tab <- filter(ga, phase1 == 1) %>%
+  group_by(data) %>%
+  summarize(NewUsers = sum(novos_usuarios))
+names(tab) <- c('Date', 'Frequency')
+pFreqUserDownloadsInt1 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+  geom_line() + geom_point()
+pFreqUserDownloadsInt1
+```
+
+```{r man2, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
+## Map manipulation test -- Intervention 2
+mapbr <- get_brmap('City')
+gaaux <- filter(ga, phase2 == 1)
+gaaux <- select(gaaux, ibge_code7, downl)
+gaaux <- rename(gaaux, City = ibge_code7)
+gaaux <- unique(gaaux)
+gaaux$City <- as.numeric(gaaux$City)
+gaaux2 <- impEvalph2 %>%
+  select(ibge_code7) %>%
+  transmute(City = as.numeric(ibge_code7)) %>%
+  unique()
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux2 <- data.frame(City = mapbr$City)
+gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
+gaaux$downl[is.na(gaaux$downl)] = 2
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
+                                                  'Not in App'))
+mapbr <- join_data(mapbr, gaaux, by = 'City')
+p1 <- ggplot() + 
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
+  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  theme_map()
+p1
+
+# App downloads over time -- Intervention 2
+tab <- filter(ga, phase2 == 1) %>%
+  group_by(data) %>%
+  summarize(NewUsers = sum(novos_usuarios))
+names(tab) <- c('Date', 'Frequency')
+p2 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+  geom_line() + geom_point()
+p2
+```
+
+\newpage
+# Main Results
+
+## Intervention 1
+
+The code below replicates the findings of table 1 in the manuscript.
+
+```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 'ggpubr',
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer', 'ggthemes')
+invisible(lapply(pkgs, require, character.only = T))
+
+# Auxiliary function: calculate coefficients
+calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  dataux <- dat
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
+      if(is.null(wts)) {
+        dat <- dataux %>%
+          select(one_of(c(j, treats, ctrls, fes, cls))) %>%
+          na.omit()
+        } else {
+          dat <- dataux %>%
+            select(one_of(c(j, treats, ctrls, fes, cls, wts))) %>%
+            na.omit()
+          wts <- dat[,wts]
+        }
+      # No controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = F))
+      print(k); k = k+1
+      # Controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = F))
+      print(k); k = k+1
+      # No controls and fes
+      mods[[k]] <- felm(
+        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
+                                   paste('',fes_mod,0,cls, sep = '|'), 
+                                   sep = '')),
+                         collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = T))
+      print(k); k = k+1
+      # Controls and fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = T))
+      print(k); k = k+1
+    }
+  }
+  return(list(moddescr, mods))
+}
+
+####
+## Analysis Intervention 1
+####
+
+## ATEs
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+treats <- c('treat')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)
+
+# Results intervention 1
+stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
+          resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
+          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
+                             "Yes", "Yes", "Yes"),
+            c("State fixed effects", "Yes", "Yes", "Yes",
+              "Yes", "Yes", "Yes")),
+          notes.append = T, header=FALSE)
+```
+
+\vspace{.5cm}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & 1.26 & 1.83 & 0.57 & 0.05$^{***}$ & 0.03$^{***}$ & 0.06 \\ 
+  & (2.69) & (3.06) & (0.93) & (0.01) & (0.01) & (0.04) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 3,602 & 3,602 & 3,602 & 3,602 & 3,602 & 2,352 \\ 
+R$^{2}$ & 0.13 & 0.13 & 0.05 & 0.03 & 0.05 & 0.08 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+\end{tabular} 
+\end{table}
+
+\newpage
+
+## Intervention 2
+
+Below, the code required to replicate the main findings of intervention 2.
+
+```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 'ggpubr',
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer', 'ggthemes', 
+          'stargazer')
+invisible(lapply(pkgs, require, character.only = T))
+
+# Auxiliary function: calculate coefficients
+calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  dataux <- dat
+  k <- 1
+  for (i in treats) {
+    for (j in outcs) {
+      if(is.null(wts)) {
+        dat <- dataux %>%
+          select(one_of(c(j, treats, ctrls, fes, cls))) %>%
+          na.omit()
+        } else {
+          dat <- dataux %>%
+            select(one_of(c(j, treats, ctrls, fes, cls, wts))) %>%
+            na.omit()
+          wts <- dat[,wts]
+        }
+      # No controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = F))
+      print(k); k = k+1
+      # Controls and no fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',0,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = F))
+      print(k); k = k+1
+      # No controls and fes
+      mods[[k]] <- felm(
+        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
+                                   paste('',fes_mod,0,cls, sep = '|'), 
+                                   sep = '')),
+                         collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = F,
+                                   hFEs = T))
+      print(k); k = k+1
+      # Controls and fes
+      mods[[k]] <- felm(as.formula(
+        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+      moddescr <- rbind(moddescr, 
+                        data.frame(outc = j, 
+                                   treat = i,
+                                   hCtrls = T,
+                                   hFEs = T))
+      print(k); k = k+1
+    }
+  }
+  return(list(moddescr, mods))
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)
+
+# Results intervention 2
+library(stargazer)
+stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
+          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
+          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
+          dep.var.labels.include=F, 
+          keep='treatAppTreatment', type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
+            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
+          notes.append = T, header=FALSE)
+```
+
+\vspace{.5cm}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$1.16 & $-$1.01 & 0.14 & $-$0.002 & $-$0.0001 & 0.00 \\ 
+  & (1.40) & (1.50) & (0.54) & (0.01) & (0.01) & (0.00) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 3,364 & 3,364 & 3,364 & 3,364 & 3,364 & 2,304 \\ 
+R$^{2}$ & 0.10 & 0.10 & 0.03 & 0.02 & 0.18 &  \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+\end{tabular} 
+\end{table}
+
+\newpage
+# Robustness Tests
+
+## Randomisation Inference
+
+We employ randomised inference to estimate to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design.
+We fail to reject the null in all but the finished school indicator in experiment 1.
+
+```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE, fig.width=7, fig.height=8, fig.show='hold', fig.align='center', fig.cap='\\label{fig:randomisation-inference}Sampling distribution of the estimated coefficient for our six outcomes in two interventions.
+Graphs on the left correspond to randomisation inference estimates for intervention 1 and those on the right describe the results for intervention 2.'}
+# Function for custom randomization inference
+test_fun <- function(dat, outc, treat, wts = NULL) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  aux <- 
+    felm(as.formula(
+      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+  return(aux$coefficients[1])
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+# First experiment
+set.seed(543129) #Random.org
+auxdat <- impEvalph1[,c('ibge_code7', outcs, ctrls, fes, cls)]
+aux2 <- unique(impEvalph1[,c('ibge_code7', 'treat')]) %>% na.omit()
+N = sum(table(aux2$treat))
+Ctrl = 150
+resri1 <- data.frame(1:1000)
+for (k in 1:1000) {
+    treat <- c(rep(1,N-Ctrl), rep(0,Ctrl))
+    treat <- sample(treat, N)
+    aux2 <- data.frame(aux2, treat = treat)
+}
+auxdat <- left_join(auxdat, aux2)
+for (i in outcs) {
+  res <- numeric()
+  for (k in 1:1000) 
+    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
+  resri1 <- data.frame(resri1, res)
+  names(resri1)[names(resri1)=='res'] = i
+}
+resri1 <- resri1[,-1]
+i1h1 <- ggplot(data=resri1, aes(resri1$percExecBegin)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'percExecBegin', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
+i1h2 <- ggplot(data=resri1, aes(resri1$percExecEnd)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'percExecEnd', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed End Intervention", y="Frequency")
+i1h3 <- ggplot(data=resri1, aes(resri1$deltaPercExec)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'deltaPercExec', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
+i1h4 <- ggplot(data=resri1, aes(resri1$isFinished)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'isFinished', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Finished School Construction Indicator", y="Frequency")
+i1h5 <- ggplot(data=resri1, aes(resri1$isCancelled)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'isCancelled', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Cancelled School Construction Indicator", y="Frequency")
+i1h6 <- ggplot(data=resri1, aes(resri1$updDate)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph1, 'updDate', 'treat'),
+             lwd = 1, lty = 2) +
+  labs(x="Updated Endline Date School Construction", y="Frequency")
+
+## Intervention 2
+# Declare RA
+aux <- filter(rand2018, !is.na(Z_intheapp))
+declRA <- declare_ra(blocks = aux$var_blocking,
+                     prob_each = c(.85,.15), 
+                     conditions = c(1, 0))
+
+# Function for custom randomization inference
+test_fun <- function(dat, outc, treat, wts = NULL) {
+  ctrls_mod <- paste(ctrls, collapse = '+')
+  fes_mod <- paste(fes, collapse = '+')
+  moddescr <- data.frame()
+  mods <- list()
+  if(is.null(wts)) {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls))) %>%
+      na.omit()
+  } else {
+    dat <- dat %>%
+      select(one_of(c(outc, treat, ctrls, fes, cls, wts))) %>%
+      na.omit()
+    wts <- dat[,wts]
+  }
+  aux <- 
+    felm(as.formula(
+      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
+                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
+              collapse = '~')), data = dat, weights = wts)
+  return(aux$coefficients[1])
+}
+
+outcs <- c('percExecBegin', 'percExecEnd',
+           'deltaPercExec', 'isFinished',
+           'isCancelled', 'updDate')
+ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
+           'log_poorFam2010', 'log_totTransf2016')
+fes <- c('state')
+cls <- c('municipality')
+
+# Second experiment
+set.seed(543129) #Random.org
+auxdat <- impEvalph2[,c('id_project', outcs, ctrls, fes, cls)]
+aux2 <- unique(aux[,c('id', 'Z_intheapp', 'IPW_intheapp')]) %>%
+  na.omit() %>%
+  rename(id_project = id,
+         treat = Z_intheapp,
+         wts = IPW_intheapp) %>%
+  mutate(treat = as.numeric(as.factor(treat))-1)
+resri2 <- data.frame(1:1000)
+for (k in 1:1000) {
+    Z <- block_ra(blocks = aux$var_blocking, 
+                  conditions = c(1, 0),
+                  prob_each = c(.85,.15))
+    IPW <- 1/obtain_condition_probabilities(declRA, Z)
+    aux2 <- data.frame(aux2, treat = Z, wts = IPW)
+}
+auxdat <- left_join(auxdat, aux2)
+for (i in outcs) {
+  res <- numeric()
+  for (k in 1:1000) 
+    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
+  resri2 <- data.frame(resri2, res)
+  names(resri2)[names(resri2)=='res'] = i
+}
+resri2 <- resri2[,-1]
+i2h1 <- ggplot(data=resri2, aes(resri2$percExecBegin)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'percExecBegin', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
+i2h2 <- ggplot(data=resri2, aes(resri2$percExecEnd)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'percExecEnd', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Percentage Completed End Intervention", y="Frequency")
+i2h3 <- ggplot(data=resri2, aes(resri2$deltaPercExec)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'deltaPercExec', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
+i2h4 <- ggplot(data=resri2, aes(resri2$isFinished)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'isFinished', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Finished School Construction Indicator", y="Frequency")
+i2h5 <- ggplot(data=resri2, aes(resri2$isCancelled)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'isCancelled', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Cancelled School Construction Indicator", y="Frequency")
+i2h6 <- ggplot(data=resri2, aes(resri2$updDate)) + 
+  geom_histogram(bins = 100) + 
+  geom_vline(xintercept = test_fun(impEvalph2, 'updDate', 'treatApp'),
+             lwd = 1, lty = 2) +
+  labs(x="Updated Endline Date School Construction", y="Frequency")
+
+ggarrange(i1h1, i2h1, 
+          i1h2, i2h2, 
+          i1h3, i2h3, 
+          i1h4, i2h4, 
+          i1h5, i2h5, 
+          i1h6, i2h6, 
+          labels = rep(c("Int. 1", "Int. 2"), 6),
+          label.x = .1,
+          ncol = 2, nrow = 6)
+```
+
+## Inverse Probability Weights and Genetic Matching
+
+We employ inverse probability weights and genetic matching to assess the robustness of the main results.
+
+\newpage 
+# APSA Experimental Section Standard Report for Experimental Research
+
+## Hypotheses
+
+**Hypotheses**: The experiment studies how technology facilitates bottom-up and top-down pressure to improve service provision.
+More precisely, we test whether the *Tá de Pé* mobile phone app is able to successfully mobilise citizens to exert pressure on local representatives and civil servants.
+We also test whether bottom-up monitoring of public works improves school construction rates and spending.
+
+\noindent 
+**Background**: Recent studies show that grassroots monitoring improves public service outcomes in developing economies.
+Some of the papers find that bottom-up accountability has a significant impact on public service delivery:
+
+  - Bjorkman, Martina and Jakob Svensson.
+2009.
+“Power to the People: Evidence from a randomized field experiment of a community-based monitoring project in Uganda.” Quarterly Journal of Economics 124(2):735–769.
+  - Bjorkman, Martina and Jakob Svensson.
+2010.
+“When is community-based monitoring effective?
+Evidence from a randomized experiment in primary health in Uganda.” Journal of the European Economic Association 8(2-3):571–581.
+  - Bjorkman Nyqvist, Martina, Damien de Walque and Jakob Svensson.
+2017.
+“Experimental evidence on the long-run impact of community-based monitoring.” American Economic Journal: Applied Economics 9(1):33–69.
+
+However, other authors fail to find positive resuls for the same type of intervention, e.g.:
+
+* Banerjee, A.
+V., Banerji, R., Duflo, E., Glennerster, R., and Khemani, S.
+2010.
+Pitfalls of Participatory Programs: Evidence from a Randomized Evaluation in Education in India.
+American Economic Journal: Economic Policy, 2(1):1–30.
+* Lieberman, E. S., Posner, D. N., and Tsai, L. L. 2014. Does Information Lead to More Active Citizenship? Evidence from an Education Intervention in Rural Kenya. World Development, 60:69–83.
+* Raffler, Pia, Dan Posner, and Doug Parkerson.
+2019.
+The Weakness of Bottom-up Accountability: Experimental evidence from the Ugandan health sector.
+URL: [`https://bit.ly/2L36vzI`](http://egap.org/sites/default/files/Posner%2C%20Dan_Paper.pdf)
+
+This project reevaluates this theoretical controversy and proposes a new field experiment to test whether bottom-up accountability is effective to promote better policy outcomes.
+The results are substantively important as well.
+First, we conduct this experiment in a middle-income country, Brazil, but which has municipalities whose social indicators match both those of developed and developing nations.
+Brazil is notably unequal in several characteristics, thus allowing us to infer results for different subgroups if required.
+Second, we are evaluating school constructions, and the presence of schools have essential consequences in terms of long-run economic development, the household income composition, and woman empowerment.
+
+## Subjects and Context
+
+**Eligibility and Exclusion Criteria**: We selected all school projects that received Federal fundings from the Brazilian Ministry of Education.
+By an agreement with the Brazilian Ministry of Education, they allowed us to have the data of all school constructions receiving funds from them.
+
+All schools constructions funded by the Brazilian Ministry of Education participated in this study. We had no schools excluded from the program.
+
+Interventions’ dates: We had three interventions here:
+
+* App impact evaluation 1: From August 2017 to February 2018. We call this Intervention 1 throughout the text.
+* App impact evaluation 2: From August 2018 to February 2019. We call this Intervention 2 throughout the text.
+
+## Allocation Methods
+
+**Assignment procedure**: The treatment here was assigned by the municipality in the first intervention, and at the school level in the second and third interventions.
+
+For intervention one, we selected 150 municipalities that were placed in the control group. The randomization code was:
+
+```{r rand-int1, eval=FALSE}
+vectreat <- c(rep(0,150), rep(1, nrow(dat)-150))
+
+AIC_info = numeric()
+for (i in 1:5000) {
+  vectreat <- sample(vectreat, length(vectreat))
+  mod <- glm(formula(paste('vectreat', vars, sep = '~')), 
+             family = binomial, data = dat)
+  if(sum(summary(mod)$coefficients[-1,4]<.2)==0) {
+    dat = data.frame(dat, vtreat = vectreat)
+    AIC_info = c(AIC_info, AIC(mod))
+  }
+}
+```
+
+And then we checked whether the randomisation had one of the covariates selected here significantly predicting the random assignment.
+We presented a vector of acceptable random assignment in these grounds, and the Brazilian Transparency selected the one we are using in the first intervention.
+
+For intervention 2, we selected 15% of the schools in the dataset that could either be placed in the treatment or in control in each of the interventions.
+The `randomizr` code for intervention 2 follows below.
+`OnApp` means treatment and `OffApp` means the control for this intervention:
+
+```{r rand-int2, eval=FALSE}
+# Install and load required package
+install.packages("randomizr") 
+library(randomizr)
+decl_intheapp <- declare_ra(blocks = dat_intheapp$var_blocking, 
+                            prob_each = c(.85,.15),
+                            conditions = c('OnApp', 'OffApp'))
+
+dat_intheapp$Z_intheapp <- block_ra(blocks = dat_intheapp$var_blocking, 
+                       conditions = c('OnApp', 'OffApp'),
+                       prob_each = c(.85,.15))
+
+dat_intheapp$IPW_intheapp <- 1/obtain_condition_probabilities(decl_intheapp, 
+                                                              dat_intheapp$Z_intheapp)
+```
+
+\noindent
+**Block randomization**: We used simple randomisation in the first assignment.
+In the second intervention, we blocked by the Brazilian State, the construction status, and above the median execution.
+The summary of the blocks, with the IPWs assigned follow below.
+
+```{r block-int2, echo=TRUE, results='asis', cache=TRUE}
+aux <- rand2018 %>%
+  select(state, status, above_median_executed, 
+         var_blocking, Z_campaign, IPW_campaign) %>% 
+  unique() %>%
+  na.omit()
+kable(aux, "latex", caption = "Block randomization -- Intervention 2",
+      booktabs = TRUE, longtable = TRUE) %>%
+  kable_styling(font_size = 8) %>%
+  kable_styling(latex_options = c("hold_position", "repeat_header"))
+```
+
+As pre-treatment variables, we used the following municipality-level characteristics:
+
+1. Log of Municipal Population in 2015
+2. Log of Number of Poor Families (2010 IBGE Census)
+3. Log of Total Federal Transfers to the Municipality in 2016
+4. IDEB Indicator for primary school quality (2015 Ministry of Education)
+5. IDEB Indicator for secondary school quality (2015 Ministry of Education)
+
+All the pre-treatment variables were not significant, as displayed in Section \ref{sec:bal-tests}.
+
+## Treatments
+
+* **Treatment groups**:
+  - *Intervention 1*: Municipality with all schools funded by the Ministry of Education showing up in the App.
+  - *Intervention 2*: School construction showing up in the App.
+
+* **Control groups**:
+  + *Intervention 1*: Municipality with all schools funded by the Ministry of Education **not** showing up in the App.
+  + *Intervention 2*: Selected school constructions **not** showing up in the App.
+
+* **Method of manipulation delivery**:
+  + *Intervention 1*: The municipalities in the treatment had all their school constructions showing up in the App.
+  + *Intervention 2*: The schools in the treatment group were showing up in the App.
+
+* **Software**: The TDP App is an Android and iOS Application developed to facilitate bottom-up pressure on school constructions in Brazil.
+
+## Results
+
+* **Outcome measures**: We use six outcome measures, all taken from the Ministry of Education biannual report:
+
+1. Percentage of the investment executed before the impact evaluation started (placebo)
+2. Percentage of the investment executed by the end of the impact evaluation period
+3. The difference of the percentage invested in the end and in the beginning of the impact evaluation period
+4. Indicator for a construction finished during the impact evaluation period
+5. Indicator for a construction canceled during the impact evaluation period
+6. Indicator for an updated conclusion date for the construction during the impact evaluation period
+
+* **CONSORT**
+
+Below follows the CONSORT chartflow:
+
+  + *Intervention 1*:
+
+```{r, echo=FALSE}
+# Values ------------------------------------------------------------------
+# Total dataset
+ntotini <- dim(impEvalph1)[1]
+
+# Excluded
+excld <- sum(is.na(impEvalph1$treat))
+
+# Total used randomization
+diffrand <- ntotini-excld
+
+# On treatment
+tralloc <- sum(impEvalph1$treat=='Treatment', na.rm = T)
+
+# Control
+ctrlalloc <- sum(impEvalph1$treat=='Control', na.rm = T)
+
+# Attrition treatment
+lostfollowuptreat <- 0
+
+# Attrition control
+lostfollowupctrl <- 0
+
+# Analyzed treatment
+analtreat <- tralloc-lostfollowuptreat
+
+# Analyzed control
+analctrl <- ctrlalloc-lostfollowupctrl
+
+values <- c(ntotini, excld, diffrand, tralloc, ctrlalloc, 
+            lostfollowuptreat, lostfollowupctrl, analtreat, analctrl)
+
+# Defining Text Labels ----------------------------------------------------
+text <- c('Assessment for\neligibility',
+          'Excluded',
+          'Randomized',
+          'Allocated to\nTreatment',
+          'Allocated to\nControl',
+          'Lost to follow-up',
+          'Lost to follow-up',
+          'Analysed',
+          'Analysed')
+
+# Defining Function -------------------------------------------------------
+paste1 <- function(x, y){
+  paste0(x, ' (n=', y, ')')
+}
+
+# Concatenating Values and Text Labels ------------------------------------
+LABS <- paste1(text, values)
+
+ndf <-
+  create_node_df(
+    n = 21,
+    label = c('Enrollment', 'Allocation', 'Follow-Up', 'Analysis',
+              LABS, rep("", 8)),
+    style = c(rep("solid", 13), rep('invis', 8)),
+    shape = c(rep("plaintext", 4), 
+              rep("box", 9),
+              rep("point", 8)),
+    width = c(rep(2, 4), rep(2.5, 9), rep(0.001, 8)),
+    hight = c(rep(0.5, 13), rep(0.001, 8)),
+    fontsize = c(rep(14, 4), rep(10, 17)),
+    fontname = c(rep('Arial Rounded MT Bold', 4), rep('Courier New', 17)),
+    penwidth = 2.0,
+    fixedsize = "true")
+
+edf <-
+  create_edge_df(
+    arrowhead = c(rep('none', 3), rep("vee", 3), rep('none', 2), "vee", rep('none', 6),
+                  rep("vee", 3), rep("none", 3), "vee", rep("none", 10)),
+    color = c(rep('#00000000', 3), rep('black', 6), rep('#00000000', 6),
+              rep('black', 3), rep('#00000000', 3), rep('black', 1),
+              rep('#00000000', 2), rep('black', 2), 
+              rep('#00000000', 6)),
+    constraint = c(rep("true", 18), rep('false', 14)),
+    from = c(1, 19, 20, 16, 8, 10, # column 1
+             5, 14, 7, 15, 2, 3, # column 2
+             18, 6, 21, 17, 9, 11, # column 3
+             1, 5, # row 1
+             19, 14, # row 2
+             20, 7, # row 3
+             16, 15, # row 4
+             8, 2, # row 5
+             10, 3, # row 6
+             12, 4), # row 7
+    to = c(19, 20, 16, 8, 10, 12, # column 1
+           14, 7, 15, 2, 3, 4, # column 2
+           6, 21, 17, 9, 11, 13, # column 3
+           5, 18, # row 1
+           14, 6, # row 2
+           7, 21, # row 3
+           15, 17, # row 4
+           2, 9, # row 5
+           3, 11, # row 6
+           4, 13)) # row 7
+
+# Create Graph ------------------------------------------------------------
+g <- create_graph(ndf, 
+                  edf,
+                  attr_theme = NULL)
+
+# Plotting ----------------------------------------------------------------
+render_graph(g)
+```
+
+  + *Intervention 2*:
+
+```{r, echo=FALSE}
+# Values ------------------------------------------------------------------
+# Total dataset
+ntotini <- dim(impEvalph2)[1]
+
+# Excluded
+excld <- sum(is.na(impEvalph2$treatApp))
+
+# Total used randomization
+diffrand <- ntotini-excld
+
+# On treatment
+tralloc <- sum(impEvalph2$treatApp=='Treatment', na.rm = T)
+
+# Control
+ctrlalloc <- sum(impEvalph2$treatApp=='Control', na.rm = T)
+
+# Attrition treatment
+lostfollowuptreat <- 0
+
+# Attrition control
+lostfollowupctrl <- 0
+
+# Analyzed treatment
+analtreat <- tralloc-lostfollowuptreat
+
+# Analyzed control
+analctrl <- ctrlalloc-lostfollowupctrl
+
+values <- c(ntotini, excld, diffrand, tralloc, ctrlalloc, 
+            lostfollowuptreat, lostfollowupctrl, analtreat, analctrl)
+
+# Defining Text Labels ----------------------------------------------------
+text <- c('Assessment for\neligibility',
+          'Excluded',
+          'Randomized',
+          'Allocated to\nTreatment',
+          'Allocated to\nControl',
+          'Lost to follow-up',
+          'Lost to follow-up',
+          'Analysed',
+          'Analysed')
+
+# Defining Function -------------------------------------------------------
+paste1 <- function(x, y){
+  paste0(x, ' (n=', y, ')')
+}
+
+# Concatenating Values and Text Labels ------------------------------------
+LABS <- paste1(text, values)
+
+ndf <-
+  create_node_df(
+    n = 21,
+    label = c('Enrollment', 'Allocation', 'Follow-Up', 'Analysis',
+              LABS, rep("", 8)),
+    style = c(rep("solid", 13), rep('invis', 8)),
+    shape = c(rep("plaintext", 4), 
+              rep("box", 9),
+              rep("point", 8)),
+    width = c(rep(2, 4), rep(2.5, 9), rep(0.001, 8)),
+    hight = c(rep(0.5, 13), rep(0.001, 8)),
+    fontsize = c(rep(14, 4), rep(10, 17)),
+    fontname = c(rep('Arial Rounded MT Bold', 4), rep('Courier New', 17)),
+    penwidth = 2.0,
+    fixedsize = "true")
+
+edf <-
+  create_edge_df(
+    arrowhead = c(rep('none', 3), rep("vee", 3), rep('none', 2), "vee", rep('none', 6),
+                  rep("vee", 3), rep("none", 3), "vee", rep("none", 10)),
+    color = c(rep('#00000000', 3), rep('black', 6), rep('#00000000', 6),
+              rep('black', 3), rep('#00000000', 3), rep('black', 1),
+              rep('#00000000', 2), rep('black', 2), 
+              rep('#00000000', 6)),
+    constraint = c(rep("true", 18), rep('false', 14)),
+    from = c(1, 19, 20, 16, 8, 10, # column 1
+             5, 14, 7, 15, 2, 3, # column 2
+             18, 6, 21, 17, 9, 11, # column 3
+             1, 5, # row 1
+             19, 14, # row 2
+             20, 7, # row 3
+             16, 15, # row 4
+             8, 2, # row 5
+             10, 3, # row 6
+             12, 4), # row 7
+    to = c(19, 20, 16, 8, 10, 12, # column 1
+           14, 7, 15, 2, 3, 4, # column 2
+           6, 21, 17, 9, 11, 13, # column 3
+           5, 18, # row 1
+           14, 6, # row 2
+           7, 21, # row 3
+           15, 17, # row 4
+           2, 9, # row 5
+           3, 11, # row 6
+           4, 13)) # row 7
+
+# Create Graph ------------------------------------------------------------
+g <- create_graph(ndf, 
+                  edf,
+                  attr_theme = NULL)
+
+# Plotting ----------------------------------------------------------------
+render_graph(g)
+```
+
+* **Reasons for exclusion in the CONSORT:**
+
+  + *Intervention 1*: Constructions that were not in the App when the intervention started.
+
+  + *Intervention 2*: Constructions that were not in the App when the intervention started.
+
+* **Statistical analysis**:
+
+For all interventions, we run the following regression model:
+
+$$ Y_i \quad = \quad \alpha + \beta T_i + \gamma X_i + \theta F_i + \varepsilon_i $$
+
+Where $i$ indexes a given school observed in the intervention.
+$Y_i$ represents an outcome variable.
+$T_i$ represents a treatment indicator.
+$\beta$ represents the estimated Average Treatment Effect.
+$\gamma$ is a vector of pre-treatment coefficient effects and $X_i$ a vector of pre-treatment covariates.
+$\theta$ represents a vector of fixed effects estimands and $F_i$ the Brazilian state level fixed effects indicator vector.
+$\varepsilon_i$ is the common error term.
+
+We run three types of analysis:
+
+1. Full regressions with all data available
+2. Full regressions using inverse probability weights
+3. Regression where we match the control group with a same-size treatment group on the proximity of covariates using genetic matching.
+
+All models use municipal-level cluster robust standard errors and state-level fixed effects. For all models, we also run regressions without clustering and without fixed effects.
+
+# Other information
+
+* **IRB**: FGV exempted the investigators from getting IRB approval because this research used online data and was approved by the Brazilian Ministry of Education.
+
+* **Pre-registration**: this research has been pre-registered on the EGAP pre-registry tool: [`https://egap.org/registration/4505`](https://egap.org/registration/4505)
+
+* **Replication materials**: The replication materials for this project are available here: [`https://github.com/umbertomig/tdp-accountability`](https://github.com/umbertomig/tdp-accountability)
+
+* **Funding**: This research received funding from the Google Social Impact initiative. Google did not interfere in any aspects of the research design and analysis.
+
+* **Conflict of interests**: The authors of this analysis declare no conflict of interest.
+
+# Session Information
+
+We use `r R.version.string` to write the manuscript and this appendix.
+For the regression models estimation, we use the package `lfe`.
+For the Genetic matching, we use the package `MatchIt`.
+Everything in this report is fully automated and can be reproduced using R Markdown.
+
+```{r}
+sessionInfo()
+```
 
@@
 \setlength{\parskip}{0pt}
-
-Lorem ipsum.
-
 # Bibliography

### 2019-08-24 article/article.Rmd
upload appendix v0.1

@@
 
-```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE, fig.width=6.5, fig.height=8, fig.show='hold', fig.align='center', fig.cap='\\label{fig:randomisation-inference}Sampling distribution of the estimated coefficient for our six outcomes in two interventions.
+```{r ri, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE, fig.width=7, fig.height=8, fig.show='hold', fig.align='center', fig.cap='\\label{fig:randomisation-inference}Sampling distribution of the estimated coefficient for our six outcomes in two interventions.
 Graphs on the left correspond to randomisation inference estimates for intervention 1 and those on the right describe the results for intervention 2.'}
@@
           labels = rep(c("Int. 1", "Int. 2"), 6),
-          label.x = .1,
+          label.x = .16, label.y = .9,
+          font.label = list(size = 12, color = "black", face = "plain"),
           ncol = 2, nrow = 6)

### 2019-09-03 article/article.Rmd
Changes Mignozzetti

@@
 abstract: "Does grassroots participation improve public service delivery?
-We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1020 Brazilian municipalities.
+We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
 The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
@@
 
-## Analysis Intervention 1
-
-## Covariate balance
-aux <- select(impEvalph1, 
-              treatOriginal, logPop2015,
-              ideb_ai_2015, ideb_af_2015, log_poorFam2010,
-              log_totTransf2016) %>%
-  unique()
-resu1 <- compareGroups(treatOriginal ~ 
-                         logPop2015 + 
-                         log_poorFam2010 +
-                         log_totTransf2016 +
-                         ideb_ai_2015 + 
-                         ideb_af_2015, 
-                       data = aux)
-tabIE1balance <- createTable(resu1, digits = 3)
-row.names(tabIE1balance$descr) <- 
-  c('Log Population (2015)', 
-    'Log Poor Families (2010)', 
-    'Log Total Transfers (2016)', 
-    'IDEB Inicial Years (2015)', 
-    'IDEB Final Years (2015)')
-
-## Manipulation Stats
-
 ## Map GA intervention 1
@@
 gaaux$City <- as.numeric(gaaux$City)
-gaaux2 <- impEvalph2 %>%
+gaaux2 <- impact_evaluation_phase2 %>%
   select(ibge_code7) %>%
@@
 
-resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)
+resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impact_evaluation_phase1)
 
@@
 \hline \\[-1.8ex] 
- ATE & 1.26 & 1.83 & 0.57 & 0.05$^{***}$ & 0.03$^{***}$ & 0.06 \\ 
-  & (2.69) & (3.06) & (0.93) & (0.01) & (0.01) & (0.04) \\ 
+ ATE & $-$0.99 & $-$1.12 & $-$0.13 & 0.002 & 0.02$^{**}$ & 0.05 \\ 
+  & (2.59) & (2.96) & (1.03) & (0.01) & (0.01) & (0.05) \\ 
   & & & & & & \\ 
@@
 State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 3,602 & 3,602 & 3,602 & 3,602 & 3,602 & 2,352 \\ 
-R$^{2}$ & 0.13 & 0.13 & 0.05 & 0.03 & 0.05 & 0.08 \\ 
+Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
+R$^{2}$ & 0.16 & 0.14 & 0.05 & 0.02 & 0.07 & 0.13 \\ 
 \hline 
@@
 
-We find that the intervention is sufficient to improve school completion and cancellation rates.
-The TDP application increases in `r round(100*resInt1[[2]][[16]]$coefficients[1], 0)` percent the chance that a school construction is reported as finished by the end of the intervention.
-The treatment also increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 0)` percent.
-While the first result is in line with our theoretical expectations, the second one goes in the opposite direction.
-But as we discuss below, the findings are inconsistent and do not replicate in the second experiment.
+We find that only has a small effect on cancellation rates.
+The TDP application increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent.
+While this result goes in the opposite direction of our theoretical expectations, the finding is largely inconsistent, and do not replicate in the second experiment.
 All other coefficients are not statistically significant at conventional levels.
 On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted.
-On the other hand, we expected the four remaining outcomes to improve after the introduction of the app.
+On the other hand, we expected the five remaining outcomes to improve after the introduction of the app.
 The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies.
@@
           na.omit()
+        wtsaux <- NULL
       } else {
@@
             na.omit()
-          wts <- dat[,wts]
+          wtsaux <- dat[,wts]
       }
@@
         paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+              collapse = '~')), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr, 
@@
                         paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+              collapse = '~')), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr, 
@@
                                    sep = '')),
-                         collapse = '~')), data = dat, weights = wts)
+                         collapse = '~')), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr, 
@@
                         paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+              collapse = '~')), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr, 
@@
 
-resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)
+resInt2 <- calcATEs(outcs, 'treat', ctrls, fes, cls, dat = impact_evaluation_phase2, wts = 'IPW_treat')
 
@@
           dep.var.labels.include=F, 
-          keep='treatAppTreatment', type = 'latex',
+          keep='treatTreatment', type = 'latex',
           covariate.labels = 'ATE',
@@
           omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = 'Cluster-robust SEs at the municipality level.',
+          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed by the randomizr package.'),
           add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
@@
 \hline \\[-1.8ex] 
- ATE & $-$1.16 & $-$1.01 & 0.14 & $-$0.002 & $-$0.0001 & 0.00 \\ 
-  & (1.40) & (1.50) & (0.54) & (0.01) & (0.01) & (0.00) \\ 
+ ATE & $-$1.33 & $-$2.26 & $-$0.94 & $-$0.001 & 0.01 & 0.002 \\ 
+  & (1.45) & (1.56) & (0.61) & (0.01) & (0.01) & (0.02) \\ 
   & & & & & & \\ 
@@
 State Fixed Effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
-Observations & 3,364 & 3,364 & 3,364 & 3,364 & 3,364 & 2,304 \\ 
-R$^{2}$ & 0.10 & 0.10 & 0.03 & 0.02 & 0.18 &  \\ 
+Observations & 3,226 & 3,226 & 3,226 & 3,226 & 3,226 & 3,109 \\ 
+R$^{2}$ & 0.12 & 0.11 & 0.04 & 0.02 & 0.17 & 0.09 \\ 
 \hline 
@@
  & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+ & \multicolumn{6}{r}{IPW computed by the randomizr package.} \\ 
 \end{tabular} 
@@
       na.omit()
+    wtsaux <- NULL
   } else {
@@
       na.omit()
-    wts <- dat[,wts]
+    wtsaux <- dat[,wts]
   }
@@
                         paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+              collapse = '~')), data = dat, weights = wtsaux)
   return(aux$coefficients[1])
@@
 set.seed(543129) #Random.org
-auxdat <- impEvalph1[,c('ibge_code7', outcs, ctrls, fes, cls)]
-aux2 <- unique(impEvalph1[,c('ibge_code7', 'treat')]) %>% na.omit()
+auxdat <- impact_evaluation_phase1[,c('ibge_code7', outcs, ctrls, fes, cls)]
+aux2 <- unique(impact_evaluation_phase1[,c('ibge_code7', 'treat')]) %>% na.omit()
 N = sum(table(aux2$treat))
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph1, 'percExecBegin', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'percExecBegin', 'treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph1, 'percExecEnd', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'percExecEnd', 'treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph1, 'deltaPercExec', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'deltaPercExec', 'treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph1, 'isFinished', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'isFinished', 'treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph1, 'isCancelled', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'isCancelled', 'treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph1, 'updDate', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'updDate', 'treat'),
              lwd = 1, lty = 2) +
@@
 set.seed(543129) #Random.org
-auxdat <- impEvalph2[,c('id_project', outcs, ctrls, fes, cls)]
+auxdat <- impact_evaluation_phase2[,c('id_project', outcs, ctrls, fes, cls)]
 aux2 <- unique(aux[,c('id', 'Z_intheapp', 'IPW_intheapp')]) %>%
@@
   for (k in 1:1000) 
-    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
+    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'), 
+                       wts = paste('wts', k, sep = '.'))
   resri2 <- data.frame(resri2, res)
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph2, 'percExecBegin', 'treatApp'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase2, 
+                                   'percExecBegin', 'treat', wts = 'IPW_treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph2, 'percExecEnd', 'treatApp'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase2, 
+                                   'percExecEnd', 'treat', wts = 'IPW_treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph2, 'deltaPercExec', 'treatApp'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase2, 
+                                   'deltaPercExec', 'treat', wts = 'IPW_treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph2, 'isFinished', 'treatApp'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase2, 
+                                   'isFinished', 'treat', wts = 'IPW_treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph2, 'isCancelled', 'treatApp'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase2, 
+                                   'isCancelled', 'treat', wts = 'IPW_treat'),
              lwd = 1, lty = 2) +
@@
   geom_histogram(bins = 100) + 
-  geom_vline(xintercept = test_fun(impEvalph2, 'updDate', 'treatApp'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase2, 
+                                   'updDate', 'treat', wts = 'IPW_treat'),
              lwd = 1, lty = 2) +
@@
 At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works.
+This inconsistent directions for the effects reassure us that the null is not only a matter of statistical power.
 

### 2019-09-03 appendix/appendix.Rmd
Appendix commit Mignozzetti

@@
 # Load Data 
-load('tdp.RData')
+load('../article/tdp.RData')
 
 # Covariate Balance -- Intervention 1
-aux <- select(impEvalph1, treatOriginal, logPop2015, ideb_ai_2015, 
+aux <- select(impact_evaluation_phase1, treat, logPop2015, ideb_ai_2015, 
               ideb_af_2015, log_poorFam2010, log_totTransf2016) %>% unique()
 
-resu1 <- compareGroups(treatOriginal ~ logPop2015 + log_poorFam2010 +
+resu1 <- compareGroups(treat ~ logPop2015 + log_poorFam2010 +
                          log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
@@
 ## Covariate balance
-aux <- select(impEvalph2, logPop2015, treatApp, ideb_ai_2015,
+aux <- select(impact_evaluation_phase2, treat, logPop2015, ideb_ai_2015,
               ideb_af_2015, log_poorFam2010, log_totTransf2016)
 
-resu1 <- compareGroups(treatApp ~ logPop2015 + log_poorFam2010 +
+resu1 <- compareGroups(treat ~ logPop2015 + log_poorFam2010 +
                          log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
@@
 ```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
-load('tdp.RData')
+load('../article/tdp.RData')
 
@@
           notes.append = T, header=FALSE)
+
+# Results intervention 1 -- No Controls and No Fixed Effects
+stargazer(resInt1[[2]][[1]],resInt1[[2]][[5]],resInt1[[2]][[9]],
+          resInt1[[2]][[13]],resInt1[[2]][[17]],resInt1[[2]][[21]],
+          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1 \\\\ No Controls and No Fixed Effects', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "No", "No", "No", 
+                             "No", "No", "No"),
+            c("State fixed effects", "No", "No", "No",
+              "No", "No", "No")),
+          notes.append = T, header=FALSE)
+
+# Results intervention 1 -- No Controls
+stargazer(resInt1[[2]][[3]],resInt1[[2]][[7]],resInt1[[2]][[11]],
+          resInt1[[2]][[15]],resInt1[[2]][[19]],resInt1[[2]][[23]],
+          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1 \\\\ No Controls', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "No", "No", "No", 
+                             "No", "No", "No"),
+            c("State fixed effects", "Yes", "Yes", "Yes",
+              "Yes", "Yes", "Yes")),
+          notes.append = T, header=FALSE)
+
+# Results intervention 1 -- No Fixed Effects
+stargazer(resInt1[[2]][[2]],resInt1[[2]][[6]],resInt1[[2]][[10]],
+          resInt1[[2]][[14]],resInt1[[2]][[18]],resInt1[[2]][[22]],
+          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1 \\\\ No Fixed Effects', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = 'Cluster-robust SEs at the municipality level.',
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
+                             "Yes", "Yes", "Yes"),
+            c("State fixed effects", "No", "No", "No",
+              "No", "No", "No")),
+          notes.append = T, header=FALSE)
+
 ```
@@
 
+The models without control variables or fixed effects follow below.
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1 \\ No Controls and No Fixed Effects} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$0.21 & $-$0.56 & $-$0.36 & 0.01 & 0.02$^{**}$ & 0.04 \\ 
+  & (4.10) & (4.86) & (1.21) & (0.01) & (0.01) & (0.07) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & No & No & No & No & No & No \\ 
+State fixed effects & No & No & No & No & No & No \\ 
+Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
+R$^{2}$ & 0.0000 & 0.0000 & 0.0001 & 0.0001 & 0.001 & 0.001 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1 \\ No Controls} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$2.20 & $-$2.08 & 0.12 & 0.003 & 0.03$^{**}$ & 0.03 \\ 
+  & (2.87) & (3.33) & (1.06) & (0.01) & (0.01) & (0.05) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & No & No & No & No & No & No \\ 
+State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
+R$^{2}$ & 0.07 & 0.06 & 0.04 & 0.01 & 0.05 & 0.06 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1 \\ No Fixed Effects} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & 1.23 & 0.82 & $-$0.41 & 0.01 & 0.02$^{**}$ & 0.06 \\ 
+  & (3.59) & (4.14) & (1.06) & (0.01) & (0.01) & (0.06) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State fixed effects & No & No & No & No & No & No \\ 
+Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
+R$^{2}$ & 0.11 & 0.10 & 0.02 & 0.01 & 0.02 & 0.08 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+\end{tabular} 
+\end{table}
+
 \newpage
@@
 ```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
-load('tdp.RData')
+load('../article/tdp.RData')
 
@@
           omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = 'Cluster-robust SEs at the municipality level.',
+          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
           add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
             c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
+          notes.append = T, header=FALSE)
+
+# Results intervention 2 -- No Controls and No Fixed Effects
+stargazer(resInt2[[2]][[1]],resInt2[[2]][[5]],resInt2[[2]][[9]],
+          resInt2[[2]][[13]],resInt2[[2]][[17]],resInt2[[2]][[21]],
+          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2 \\\\ No Controls and No Fixed Effects', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
+          add.lines = list(c("Controls", "No", "No", "No", 
+                             "No", "No", "No"),
+            c("State fixed effects", "No", "No", "No",
+              "No", "No", "No")),
+          notes.append = T, header=FALSE)
+
+# Results intervention 1 -- No Controls
+stargazer(resInt2[[2]][[3]],resInt2[[2]][[7]],resInt2[[2]][[11]],
+          resInt2[[2]][[15]],resInt2[[2]][[19]],resInt2[[2]][[23]],
+          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2 \\\\ No Controls', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
+          add.lines = list(c("Controls", "No", "No", "No", 
+                             "No", "No", "No"),
+            c("State fixed effects", "Yes", "Yes", "Yes",
+              "Yes", "Yes", "Yes")),
+          notes.append = T, header=FALSE)
+
+# Results intervention 1 -- No Fixed Effects
+stargazer(resInt2[[2]][[2]],resInt2[[2]][[6]],resInt2[[2]][[10]],
+          resInt2[[2]][[14]],resInt2[[2]][[18]],resInt2[[2]][[22]],
+          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2 \\\\ No Fixed Effects', 
+          keep='treatTreatment', 
+          type = 'latex',
+          covariate.labels = 'ATE',
+          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
+          dep.var.labels.include=F, column.sep.width = '-2pt',
+          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
+          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
+                             "Yes", "Yes", "Yes"),
+            c("State fixed effects", "No", "No", "No",
+              "No", "No", "No")),
           notes.append = T, header=FALSE)
@@
 \hline \\[-1.8ex] 
- ATE & $-$1.16 & $-$1.01 & 0.14 & $-$0.002 & $-$0.0001 & 0.00 \\ 
-  & (1.40) & (1.50) & (0.54) & (0.01) & (0.01) & (0.00) \\ 
-  & & & & & & \\ 
 \hline \\[-1.8ex] 
@@
  & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+ & \multicolumn{6}{r}{IPW computed using the randomizr package} \\ 
 \end{tabular} 
@@
 
+And the models without controls or fixed effects follow below.
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2 \\ No Controls and No Fixed Effects} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$1.02 & $-$1.90 & $-$0.88 & $-$0.001 & 0.01 & $-$0.002 \\ 
+  & (1.52) & (1.66) & (0.61) & (0.01) & (0.02) & (0.02) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & No & No & No & No & No & No \\ 
+State fixed effects & No & No & No & No & No & No \\ 
+Observations & 3,226 & 3,226 & 3,226 & 3,226 & 3,226 & 3,109 \\ 
+R$^{2}$ & 0.0003 & 0.001 & 0.001 & 0.0000 & 0.0004 & 0.0000 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+ & \multicolumn{6}{r}{IPW computed using the randomizr package} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2 \\ No Controls} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$1.46 & $-$2.30 & $-$0.84 & $-$0.002 & 0.02 & $-$0.003 \\ 
+  & (1.49) & (1.62) & (0.61) & (0.01) & (0.02) & (0.02) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & No & No & No & No & No & No \\ 
+State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+Observations & 3,226 & 3,226 & 3,226 & 3,226 & 3,226 & 3,109 \\ 
+R$^{2}$ & 0.05 & 0.06 & 0.03 & 0.01 & 0.09 & 0.05 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+ & \multicolumn{6}{r}{IPW computed using the randomizr package} \\ 
+\end{tabular} 
+\end{table}
+
+\begin{table}[!htbp] \centering 
+  \caption{\label{tab:results2} Impact Evaluation -- Intervention 2 \\ No Fixed Effects} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+ & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ ATE & $-$0.94 & $-$1.90 & $-$0.96 & $-$0.0005 & 0.01 & $-$0.002 \\ 
+  & (1.47) & (1.59) & (0.61) & (0.01) & (0.01) & (0.02) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
+State fixed effects & No & No & No & No & No & No \\ 
+Observations & 3,226 & 3,226 & 3,226 & 3,226 & 3,226 & 3,109 \\ 
+R$^{2}$ & 0.08 & 0.08 & 0.01 & 0.005 & 0.12 & 0.05 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
+ & \multicolumn{6}{r}{IPW computed using the randomizr package} \\ 
+\end{tabular} 
+\end{table}
+
 \newpage
@@
 Graphs on the left correspond to randomisation inference estimates for intervention 1 and those on the right describe the results for intervention 2.'}
+# Chunk randomization inference
+load('tdp.RData')
+
+# Load packages
+pkgs <- c('tidyverse', 'dummies', 
+          'haven', 'compareGroups', 
+          'devtools', 'lubridate', 'brazilmaps',
+          'abjutils', 'lfe', 'cobalt', 
+          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
+          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
+          'flextable', 'officer', 'ggthemes', 'ggpubr')
+invisible(lapply(pkgs, require, character.only = T))
+
 # Function for custom randomization inference
@@
 
-# Second experiment
+# First experiment
 set.seed(543129) #Random.org
-auxdat <- impEvalph2[,c('id_project', outcs, ctrls, fes, cls)]
+auxdat <- impact_evaluation_phase2[,c('id_project', outcs, ctrls, fes, cls)]
 aux2 <- unique(aux[,c('id', 'Z_intheapp', 'IPW_intheapp')]) %>%
@@
           labels = rep(c("Int. 1", "Int. 2"), 6),
-          label.x = .1,
+          label.x = .16, label.y = .9,
+          font.label = list(size = 12, color = "black", face = "plain"),
           ncol = 2, nrow = 6)
 ```
-
-## Inverse Probability Weights and Genetic Matching
-
-We employ inverse probability weights and genetic matching to assess the robustness of the main results.
 
@@
 # Total dataset
-ntotini <- dim(impEvalph1)[1]
+ntotini <- dim(impact_evaluation_phase1)[1]
 
 # Excluded
-excld <- sum(is.na(impEvalph1$treat))
+excld <- sum(is.na(impact_evaluation_phase1$treat))
 
@@
 # On treatment
-tralloc <- sum(impEvalph1$treat=='Treatment', na.rm = T)
+tralloc <- sum(impact_evaluation_phase1$treat=='Treatment', na.rm = T)
 
 # Control
-ctrlalloc <- sum(impEvalph1$treat=='Control', na.rm = T)
+ctrlalloc <- sum(impact_evaluation_phase1$treat=='Control', na.rm = T)
 
@@
 # Total dataset
-ntotini <- dim(impEvalph2)[1]
+ntotini <- dim(impact_evaluation_phase2)[1]
 
 # Excluded
-excld <- sum(is.na(impEvalph2$treatApp))
+excld <- sum(is.na(impact_evaluation_phase2$treat))
 
@@
 # On treatment
-tralloc <- sum(impEvalph2$treatApp=='Treatment', na.rm = T)
+tralloc <- sum(impact_evaluation_phase2$treat=='Treatment', na.rm = T)
 
 # Control
-ctrlalloc <- sum(impEvalph2$treatApp=='Control', na.rm = T)
+ctrlalloc <- sum(impact_evaluation_phase2$treat=='Control', na.rm = T)
 

### 2019-09-03 article/article.Rmd
Fix some small coding errors.

@@
 The randomization was conduct at the municipal level.
-We randomly selected `r as.numeric(table(impEvalph1$treatOriginal)[1])` municipalities to the control group and included `r as.numeric(table(impEvalph1$treatOriginal)[2])` in the treatment group.
+We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])` municipalities to the control group and included `r as.numeric(table(impact_evaluation_phase1$treat)[2])` in the treatment group.
 Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens were unable to report constructions in the control municipalities.
@@
 Figure \ref{fig:manipulation1} displays the results and indicates that the treatment has good territorial variability.
-There are `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impEvalph1$municipality[impEvalph1$treatOriginal==1]))` municipalities in the treatment condition.
+There are `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment']))` municipalities in the treatment condition.
 Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.
@@
 First, the TDP app was available for both Android and iOS devices.
-Second, we randomised the intervention at the school level, with `r as.numeric(table(impEvalph2$treatApp)[1])` control and `r as.numeric(table(impEvalph2$treatApp)[2])` treatment units.
+Second, we randomised the intervention at the school level, with `r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and `r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units.
 We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
@@
 Balance tests and manipulation checks were also successful for intervention 2.
-In total, `r sum(gaaux$Downloads == 'Downloads')` municipalities downloaded the app.
+In total, `r sum(ga$Downloads[ga$phase2 == 1] == 'Downloads')` municipalities downloaded the app.
 There is one download peak in August 2018, right after intervention 2 starts, and a second spike around December.
@@
 This raises further questions about the effect of the TDP app on school completion.
-Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 1.57 percent.
-However, the coefficient only reaches statistical significance when we employ inverse probability weights with block randomisation and one-to-one nearest neighbourhood matching.
+Note that the effect signs are also inconsistent with improving the outcomes, what demonstrates that our results are not likely to result from low statistical power imposed by reduced control group requirement.
 
@@
 This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts.
-At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works.
-This inconsistent directions for the effects reassure us that the null is not only a matter of statistical power.
+At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works in the context of school constructions in Brazil.
 
@@
 Nevertheless, the null findings are informative to researchers and policy-makers.
-The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, may render better policy outcomes than those focused at the grassroots levels.
+The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, might render better policy outcomes than those focused at the grassroots levels.
 Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication.

### 2019-09-03 article/article.Rmd
Change line width borders map.

@@
 pMapDownloadsInt1 <- ggplot() + 
-  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
   scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
@@
 p1 <- ggplot() + 
-  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
   scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +

### 2019-09-03 appendix/appendix.Rmd
small mistake fixed
add new tests

@@
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments.
+thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog, and David Skarbek for their helpful comments.
 We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance.
@@
 * Construction Status (under construction, stopped, unfinished)
-* School expenditures above the national median
+* School construction completion rates above the national median
 
@@
 # Chunk randomization inference
-load('tdp.RData')
+load('../article/tdp.RData')
 
@@
 
-* **Funding**: This research received funding from the Google Social Impact initiative. Google did not interfere in any aspects of the research design and analysis.
-
-* **Conflict of interests**: The authors of this analysis declare no conflict of interest.
+* **Funding**: This research received funding from the 2016 Google Social Impact Challenge. Google did not interfere in any aspect of the research design and analysis.
+
+* **Conflict of interests**: The authors of this analysis declare that there are no conflict of interest.
 

### 2019-09-03 article/article.Rmd
add new tests

--- 2019-09-03 article/article.Rmd
@@
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog and David Skarbek for their helpful comments.
+thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog, and David Skarbek for their helpful comments.
 We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance.
 This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education.
-The authors thank the 2016 Google Social Impact Challenge for financial support and declare there are no conflict of interest.
+The authors thank the 2016 Google Social Impact Challenge for financial support and declare that there are no conflict of interest.
 Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [`danilofreire@brown.edu`[mailto:danilofreire@brown.edu], <http://danilofreire.github.io>, +1 (401) 584-2494.
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [`danilofreire@brown.edu`](mailto:danilofreire@brown.edu), <http://danilofreire.github.io>, +1 (401) 584-2494.
 Corresponding author.
@@
 In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
-Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability] and improves the quality of public services [@adsera2003you; @bjorkman2009power].
+Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability], and improves the quality of public services [@adsera2003you; @bjorkman2009power].
 Recent research also suggests that accountability leads to higher economic growth because it limits state discretion in the economy and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
@@
 One promising model is that of _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project so they can evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
-Proponents argue bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects themselves; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
+Proponents argue that bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects themselves; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
 In this regard, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
 
-Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punishing political representatives in Brazil.
-Developed by Transparência Brasil[^transparencia], TDP allows citizens to learn the location of public school construction sites, check their completion status and anonymously request information from competent authorities.
+Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punish political representatives in Brazil.
+Developed by Transparência Brasil[^transparencia], TDP allows citizens to learn the location of public school construction sites, check their completion status, and anonymously request information from competent authorities.
 TDP users can also take pictures of the construction sites and submit them to independent engineers for examination.
@@
 Overall, our results show that providing information to citizens has no consistent impact on policy outcomes.
-In the first experiment, we find that the TDP app increased the likelihood of school completion by 5 percent and the number of cancelled schools by 3 percent, but the effects are null in the second intervention.
-We also find that the app increased the percentage of the reported construction completion by 1.75 percent in our second experiment, but only after nearest neighbourhood matching adjustment.
-Importantly, our results show that providing information to citizens has no consistent impact on any policy outcomes.
+In the first experiment, we find that the TDP app increased the likelihood of construction cancellation by 2 percent, but the result does not replicate.
+The remaining five models have null results.
+In our second intervention, none of the estimations reach conventional levels of statistical significance.
+Importantly, all coefficients are small, what suggests that even if the TDP app had a significant effect on the outcomes, its substantive impact would be virtually negligible.
 
 The findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-Although studies like @bjorkman2009power, @fiala2017social and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring and @raffler2018weakness offering little evidence that information-based interventions lead to greater government responsiveness.
+Although studies like @bjorkman2009power, @fiala2017social, and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring, and @raffler2018weakness offering little evidence that information-based interventions lead to greater government responsiveness.
 Our analysis suggests that grassroots monitoring is ineffective in altering government behaviour in Brazil.
@@
 The app then prompts citizens to write a notification to the mayor's office, which has 15 days to reply.
-If they do not respond to the request, the app forwards the notification to the Brazilian federal government office that grants the funds for the construction, making it harder for the municipality to access federal funds in the future.
-The motivation behind this intervention is that bottom-up pressure from citizens empowers individuals to closely monitor public works.
+If they do not respond to the request, the app forwards the notification to the Brazilian Ministry of Education, making it harder for the municipality to access federal funds in the future.
+The motivation behind this intervention is that providing information to citizens empowers individuals to closely monitor public works.
 This, in turn, results in better social outcomes as public agents become more responsive to community demands.
@@
 
-Transparência Brazil built the app in the first three months of 2017 and tested it in May 2017.
+Transparência Brazil built the app in from January to March 2017 and tested it in May of that year.
 The first stable Android version was deployed on Google Play on 14 August 2017.
@@
 In October 2017, Transparência Brazil started a Facebook campaign in order to publicise the app.
-Facebook is the most widely used social media network in Brazil with around 72 million users in 2017 [@statista2019facebook].
-The campaigns cost US$ 4,479.29 and Facebook advertisements attracted 2,028 new users to the platform in October 2017 only.
+Facebook is the most widely used social media network in Brazil with around 72 million users  [@statista2019facebook].
+The campaigns attracted 2,028 new users to the platform in October 2017 only.
 
@@
      \caption{The \textit{Tá de Pé} mobile phone application.
-The first image presents a list of school construction sites closer to the users' location.
+The first image presents a list of school construction sites close to the users' location.
 The second image shows that the school construction selected by the user is delayed by 9 months.
@@
 
-The TDP has also received feedback from Brazilian computer programmers and policy analists.
+The TDP also received feedback from Brazilian computer scientists and policy analists.
 In 2017 and 2018, Transparência Brasil announced two team programming competitions, called 'Tá de Pé Hackathons', where contributors could fix code bugs and suggest new functionalities to the TDP project.
@@
 
-Between August 2017 and February 2019, we implemented two interventions to measure the effect of the TDP app on five school construction outcomes plus a placebo outcome.
+Between August 2017 and February 2019, we implemented two interventions to measure the effect of the TDP app on five school construction outcomes plus a placebo test.
 The outcomes are: 1) a placebo outcome indicating the percentage of the project completed before the impact evaluation started; 2) the percentage of the project completed by the end of the interventions; 3) the difference between the percentage reported as completed before and after the interventions; 4) the number of finished constructions; 5) the number of cancelled constructions; 6) the number of schools where construction companies updated the conclusion dates.
@@
 Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.
+
+\vspace{.5cm}
 
@@
 
+\newpage 
 The second intervention is similar to intervention 1 in all but three characteristics.
@@
 Second, we randomised the intervention at the school level, with `r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and `r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units.
-We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished) and whether the municipality spent more on school construction that the distribution median.
+We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished), and whether the municipality spent more on school construction that the distribution median.
 Finally, the intervention period lasted from August 2018 to February 2019.
@@
 Balance tests and manipulation checks were also successful for intervention 2.
-In total, `r sum(ga$Downloads[ga$phase2 == 1] == 'Downloads')` municipalities downloaded the app.
-There is one download peak in August 2018, right after intervention 2 starts, and a second spike around December.
-The number of downloads is considerably smaller in this second intervention when compared to intervention 1 as there was no associated social media campaign in that period.
+In total, `r length(unique(ga$municipality[ga$phase2==1]))` municipalities downloaded the app.
+There is about 1,000 user downloads in August 2018, right after intervention 2 starts, and a second spike around December.
+The number of downloads is smaller in this second intervention as there was no associated social media campaign in that period.
 
-```{r man2, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.3, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+```{r man2, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.5, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
 The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
@@
 
-## Map intervention 2
+## Map manipulation test -- Intervention 2
 mapbr <- get_brmap('City')
@@
 gaaux$downl[is.na(gaaux$downl)] = 2
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
+gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
+                                                  'Not in App'))
 mapbr <- join_data(mapbr, gaaux, by = 'City')
@@
 
-We estimated all models using the following regression equation:
+We estimate all models using the following regression equation:
 
@@
 where $i$ indexes the experiment units.
-$Y_i$ is one of the six outcomes described above, $\alpha$ is the intercept, $\beta$ denotes the average treatment effect and $T_i$ is a binary treatment indicator.
+$Y_i$ is one of the six outcomes described above, $\alpha$ is the intercept, $\beta$ denotes the average treatment effect, and $T_i$ is a binary treatment indicator.
 $\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed effects, $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$.
@@
 All models reported here include the five control variables described in the previous section and Brazilian states' fixed effects.
-We also estimated the models without control variables, without fixed effects and with nearest-neighbour matching.
+We also estimated the models without control variables, without fixed effects, and with nearest-neighbour matching.
 The results are very similar to those below.
@@
 
-We find that only has a small effect on cancellation rates.
+We find that the app only has a small effect on cancellation rates.
 The TDP application increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent.
-While this result goes in the opposite direction of our theoretical expectations, the finding is largely inconsistent, and do not replicate in the second experiment.
+While this result goes in the opposite direction of our theoretical expectations, the finding is largely inconsistent, and it does not replicate in the second experiment.
 All other coefficients are not statistically significant at conventional levels.
@@
 This raises further questions about the effect of the TDP app on school completion.
-Note that the effect signs are also inconsistent with improving the outcomes, what demonstrates that our results are not likely to result from low statistical power imposed by reduced control group requirement.
+Note that the effect signs are also inconsistent with improving the outcomes, what demonstrates that our results do not derive from low statistical power or the reduced control group size.
 
@@
 
-We also note that effect sizes are small in all estimations and coefficients flip signs in all but one of our six dependent variables.
+We also note that effect sizes are small in all estimations and that the coefficients flip signs in all but one of our six dependent variables.
 This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts.

### 2019-09-03 article/article.Rmd
Small change last paragraph.
Map line width changes.

@@
 Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions.
+Finally, whether this study generalises beyond school constructions to other bottom-up programs, and to other contexts, remains to be studied.
 

### 2019-09-03 appendix/appendix.Rmd
Map changes.

@@
 gaaux$City <- as.numeric(gaaux$City)
-gaaux2 <- impact_evaluation_phase2 %>%
+gaaux2 <- impact_evaluation_phase1 %>%
   select(ibge_code7) %>%

### 2019-11-19 appendix/appendix.Rmd
changes appendix

@@
 ```
+
+# Treatment Definition and Mechanism
+
+In the Tá de Pé App, we need people to:
+
+1. Download the app
+
+2. Use the App and report the schools to the mayors office
+
+3. Our team took the reported schools and started implementing the pressure on the mayors’ office.
+
+4. Should the pressure have work, we would witness improvements on governmental data regarding the school construction progress.
+
+The treatment is a compounded treatment comprised of steps (2) to (4). To make sure that the only source of effect comes from step (2), we took the following precautions:
+
+For the step (1), we have implemented Facebook campaigns in the municipalities with school construction agreements between the Federal and Municipal governments.
+We did not discriminated any municipality in this step, and citizens living in municipalities in the treatment and in the control could equally have received the banners about the Tá de Pé App.
+More on the Facebook campaign below, but the Facebook campaign was not randomized.
+
+For the step (3), we put a team of two data scientists dedicated in make sure that upon receiving a denounce, the mayor’s office, the city council, and the Brazilian Federal comptroller would be notified about the denouce, as it proceeds.
+The decision making funnel was:
+
+3.1. We notified the engineers without borders (EWB) about the denounce, sending them the pictures. They issued a report on how much the construction was likely to be delayed.
+
+3.2.
+Having the EWB report, we notified the mayors office by using a Freedom of Information Act.
+We communicated that a person anonymously made a denounce about a school (fully identifying the school construction that we are referring), and that the Engineers Without Borders found the construction delayed by a percentage that EWB provided.
+We submit a request for the mayors office to provide an explanation on why the construction was delayed, and asking for updated statistics on when the construction will be finished.
+According to the FOI law, they had twenty days to respond.
+
+3.3.
+If the response was found insufficient, we proceed with the same steps to the city council and to the Brazilian Federal Comptroller (CGU).
+Upon going up in scale, the denounce could harm mayors by restricting access to Federal funds.
+
+3.4. At each step, a Twitter bot constructed by the Brazilian Transparency reported the reception of a denounce, and the mayors, city council, and CGU comptroller responses.
+
+For the step (4), we relied on monthly issued administrative data by the Brazilian Ministry of Education.
+The Ministry of Education provides monthly data on the school constructions that are being build with Federal resources, and that are delayed across the country.
+To compute the delay  we use the finishing dates reported by the municipality at the time they sign the agreement with the Federal Government.
+This data helped us to keep the App updated and the outcomes in the paper are selected to be six months before (pre-treatment) and after the intervention.
+This data was constantly updated by the Ministry of Education, and we found no red flags in the overall quality of the data.
+
+Therefore, steps (1), (3), and (4) were standardized to not vary across the country. The only source of variation in our intervention should come from step (2).
+
+In step (2), we applied the treatment by removing schools within municipalities out of the app.
+In the first intervention, that happened at the municipal level, we excluded all schools within a given randomly selected municipality.
+In the second intervention, we excluded randomly selected schools out of the App.
+Removing a school means that the school was in the dataset provided by the Brazilian Ministry of Education, but it did not show up in the App.
+Therefore, our treatment effect represents the school being present (treatment) or absent (control) in the App.
+
+In terms of what this represents, we argue that the App is promoting two crucial features for bottom-up accountability: first, it is facilitating people to connect with information that would be otherwise be in an obscure spreadsheet at the Ministry of Education website; second, whenever people find this information troublesome, we are providing an easy way to them to act upon the information.
+As the design was intuitive and straightforward, we believe that most of Brazilians would find it easy to use the App.
+
+Moreover, the treatment to be successful does not require that everyone in the municipality uses the App.
+Clearly that more usage means more pictures and denounces, and this represents more pressure over the mayors office, what could revert into a higher effect.
+However, just one denounce would be enough, as it can be directed to the Brazilian General Comptroller (CGU), and this could potentially deny future funding to the municipality.
+
+# Outcome data collection
+
+In this paper, we collect the main outcomes using the data reported by the municipality to the Ministry of Education in Brazil.
+Note that this is the same data as the pre-treatment data that we use to feed in the App with delayed schools.
+
+The outcome data is collected from the Ministry of Education school data. To geolocate the schools, we use the address provided in the school data. The main outcomes used in the paper are:
+
+1.
+**Percentage of the project completed before the impact evaluation started**: This is a column in the Ministry of Education dataset.
+The data when this column was sampled was the beginning of the intervention.
+
+2.
+**Percentage of the project reported as completed by the end of the intervention period**: This is a column in the Ministry of Education dataset.
+The data when this column was sampled was six months after the intervention.
+
+3.
+**Difference between the percentage reported as completed before and after the intervention**: This is the difference between (1) and (2) above.
+Note that according to Gerber and Green (2012), this way to look into outcomes is positive, as having a pre-treatment covariate that highly predicts the outcome reduces the variance in the estimator considerably.
+
+4.
+**Dummy indicator for finished constructions**: The Ministry of Education dataset has a column with the construction status.
+We merely created a dummy to be one when the construction was reported as finished and zero otherwise.
+The data here was sampled six months after the intervention.
+
+5.
+**Dummy indicator for cancelled constructions**: The Ministry of Education dataset has a column with the construction status.
+We merely created a dummy to be one when the construction was reported as cancelled and zero otherwise.
+The data here was sampled six months after the intervention.
+
+6.
+**Number of schools where construction companies updated the conclusion dates**: The Ministry of Education dataset has a column with the construction estimated completion date.
+We took the completion dated reported before and six months after the intervention.
+If the dates differed, we coded as one, and zero otherwise.
+
+All this outcome comes from our manipulation of the Ministry of Education data.
+Collecting the outcomes in this way is superior than the alternative where we collect outcomes by ourselves in two ways.
+First, we would not be able to manipulate the results and find any preferred results of our choice.
+Even with the best intent in heart, the researcher could bias the results just by collecting it.
+For instance, if we send a RA to collect the data, as she knows the App, she could unconsciously have a tendency to over-report the results that were better, and not report the cases that had no effect.
+This would severely bias our results, undermining the credibility of our findings.
+Second, this process makes the results easily reproducible by other researchers, lowering the reproducibility costs and enhancing the credibility in our findings.
+As the Ministry of Education has a regular data collection systematized, it simplifies and facilitate the analysis and reproduction of our findings.
+
+# Facebook Tá de Pé Campaign
+
+The mere existence of the App would probably have had no effect on improving responsiveness of mayors.
+To boost the usage, and publicize the App, the Brazilian Transparency ran 64 Facebook campaigns in the whole country, during the entire period of the research.
+The campaign concentrate the bulk of the investments in the beginning of the intervention.
+The App download data is in the second panel of Figures 2 and 3.
+For the Facebook interaction, we have the following statistics:
+
+1. Impressions
+  - Mean: `r mean(fballt$impressoes)`
+  - Total for all campaigns: `r sum(fballt$impressoes)`
+
+2. App Download link clicks:
+  - Mean: `r mean(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
+  - Total for all campaigns: `r sum(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
+
+As we could see by the actual download activity, the people that indeed carried out the downloads were much fewer than this numbers would suggest.
+
+The choice for Facebook was because the platform offers an easy and cheap method to spread information.
+Moreover, according to the Statista website, Facebook is used by 70 millions of Brazilians (60% of the entire adult population), and the demographics largely match the demographics publicized by the Brazilian Institute of Geography and Statistics.
+For instance, see the following webpages:
+
+1. [Statista Total Facebook Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
+2. [Statista Total Facebook Users by Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
 

### 2019-12-03 article/letter.Rmd
add letter file

---
title:
author:
date:
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
if (!require("kableExtra")) {
    install.packages("kableExtra")
}
```

\noindent Research & Politics

\vspace{.1cm}

\noindent 2 December 2019

\vspace{.5cm}

\noindent Dear Editor and Reviewer,

\vspace{.5cm}

\noindent We would like to thank you for the opportunity to revise our manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144). We have made many revisions to the paper along the lines suggested by the editor and the anonymous reviewer and we believe the manuscript has improved significantly as a result.

We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer. Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns. We explain the precautions we have taken to ensure that the

Related, we have included a discussion regarding app usage as suggested by the reviewer.

Below we discuss in more detail these and other changes we have made to the manuscript in response to comments from the editor and the reviewer. We thank the editor again for the opportunity to revise the manuscript, and the reviewer for his/her extremely helpful comments.

\noindent Sincerely,

\vspace{.5cm}

\noindent The Authors

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

### 2019-12-03 article/letter.Rmd
v2 memo

@@
 Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns.
-We explain the precautions we have taken to ensure that the
+We explain the precautions we have taken to ensure that the we correctly identify the effect of the TDP app on school outcomes.
+Second, we provide a thorough discussion of our additional data sources.
+More specifically, we show how the Brazilian Ministry of Education collects and publicises their data and indicate how our experiment uses that information to evaluate the robustness of our findings.
+We believe the new sections help give the results a clearer interpretation and strenghten our main arguments.
 
 Related, we have included a discussion regarding app usage as suggested by the reviewer.
+We have included information provided by Google Analytics not only on app downloads but also on app usage, which addresses another important concern raised by the reviewer.
+The data show that the app usage was significant, yet it was not enough to trigger any responses from local governments.
+
+Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.We believe our paper now reflects our results more accurately.
 
@@
 We thank the editor again for the opportunity to revise the manuscript, and the reviewer for his/her extremely helpful comments.
+
+\vspace{.5cm}
 

### 2019-12-15 article/article.Rmd
changes in formatting, a few edits to text

@@
 Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
-abstract: "Does grassroots participation improve public service delivery?
+abstract: "Does ~~grassroots participation~~ **local oversight** improve public service delivery?
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
 The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
-Our results show that the app has a null impact on the school construction outcomes.
+Our results show that the app has a null impact on the school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
@@
 ```{r setup, include=FALSE, warning=FALSE}
-pkgs <- c('tidyverse', 'dummies', 'kableExtra',
-          'haven', 'compareGroups', 'grid', 'gridExtra',
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes', 
-          'stargazer')
+pkgs <- c("tidyverse", "dummies", "kableExtra",
+          "haven", "compareGroups", "grid", "gridExtra",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes",
+          "stargazer")
 
 # Install required packages
-installIfNot <- function(x) {
-  if(x %in% rownames(installed.packages()) == FALSE) 
+install_if_not <- function(x) {
+  if (x %in% rownames(installed.packages()) == FALSE)
     install.packages(x, dependencies = T)
 }
-lapply(pkgs, installIfNot)
+lapply(pkgs, install_if_not)
 
@@
 lapply(pkgs, require, character.only = T)
-rm(pkgs, installIfNot)
-load('tdp.RData')
+rm(pkgs, install_if_not)
+load("tdp.RData")
 ```
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, [`danilofreire@brown.edu`](mailto:danilofreire@brown.edu), <http://danilofreire.github.io>, +1 (401) 584-2494.
-Corresponding author.
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown
+University, Providence, RI 02912, USA,
+[`danilofreire@brown.edu`](mailto:danilofreire@brown.edu),
+<http://danilofreire.github.io>, +1 (401) 584-2494. Corresponding author.
 
-[^galdino]: Executive Diretor, Transparência Brasil, São Paulo, SP, Brazil, [`mgaldino@transparencia.org.br`](mailto:mgaldino@transparencia.org.br), <https://www.transparencia.org.br>.
+[^galdino]: Executive Diretor, Transparência Brasil, São Paulo, SP, Brazil,
+[`mgaldino@transparencia.org.br`](mailto:mgaldino@transparencia.org.br),
+<https://www.transparencia.org.br>.
 
-[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [`umberto.mig@nyu.edu`](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
+[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São
+Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA,
+[`umberto.mig@nyu.edu`](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
 
@@
 
-A robust accountability system is crucial for efficient public services provision [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent; @o1998horizontal].
-In its standard definition, accountability is understood as the process of holding authorities responsible for their actions [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic].
-Past studies show that accountability has a positive impact on governance, as it ensures that politicians act on behalf of voters [@freire2010ngp; @moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking and corruption [@deininger2005does; @wenar2006accountability], and improves the quality of public services [@adsera2003you; @bjorkman2009power].
-Recent research also suggests that accountability leads to higher economic growth because it limits state discretion in the economy and increases long-term investments in human capital [@benhabib2010economic; @suebvises2018social; @ponzetto2018social].
+A robust accountability system is crucial for efficient public services
+provision [@besley2003incentives; @cameron2004public; @ferejohn1986incumbent;
+@o1998horizontal]. In its standard definition, accountability is understood as
+the process of holding authorities responsible for their actions
+[@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic]. Past
+studies show that accountability has a positive impact on governance; ~~as~~ it
+ensures that politicians act on behalf of voters [@freire2010ngp;
+@moncrieffe1998reconceptualizing], reduces the opportunities for rent-seeking
+and corruption [@deininger2005does; @wenar2006accountability], and improves the
+quality of public services [@adsera2003you; @bjorkman2009power]. Recent
+research also suggests that accountability leads to higher economic growth
+because it limits state discretion in the economy and increases long-term
+investments in human capital [@benhabib2010economic; @suebvises2018social;
+@ponzetto2018social].
 
-However, accountability systems take many forms.
-One promising model is that of _bottom-up monitoring_, in which citizens receive information about the shortcomings of a given project so they can evaluate and pressure underperforming public officials [@kosack2014does; @molina2016community; @raffler2018weakness].
-Proponents argue that bottom-up accountability is effective because: 1) constituents have first-hand information about the outcomes of local policies; 2) citizens have incentives to attack corruption that directly affects themselves; 3) policy-makers are sensitive to social punishment from their own communities [@serra2011combining, 570].
-In this regard, bottom-up accountability offers a potential solution to the principal-agent dilemma in public service by aligning the interests of state officials with those of the constituency they serve [@barro1973control; @raffler2018weakness, 2].
+However, accountability systems **may** take many forms. One promising model is
+that of _bottom-up monitoring_, in which citizens receive information about the
+shortcomings of a given project so they can evaluate and pressure
+underperforming public officials [@kosack2014does; @molina2016community;
+@raffler2018weakness]. Proponents argue that bottom-up accountability is
+effective because: 1) constituents have first-hand information about the
+outcomes of local policies; 2) citizens have incentives to attack corruption
+that directly affects themselves; 3) policy-makers are sensitive to social
+punishment from their own communities [@serra2011combining, 570]. In this
+regard, bottom-up accountability offers a potential solution to the
+principal-agent dilemma in public service by aligning the interests of state
+officials with those of the constituency they serve [@barro1973control;
+@raffler2018weakness, 2].
 
-Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application designed to lower the costs of evaluating public works and punish political representatives in Brazil.
-Developed by Transparência Brasil[^transparencia], TDP allows citizens to learn the location of public school construction sites, check their completion status, and anonymously request information from competent authorities.
-TDP users can also take pictures of the construction sites and submit them to independent engineers for examination.
-If the engineers classify the construction as delayed, TDP prompts users to send a message to the mayor's office asking for completion estimates and explanations about the construction status.
-TDP has been online since April 2017 and was the winner of the 2016 Google Social Impact grant with more than 200,000 popular votes[^google].
+Here we assess the impact of _Tá de Pé_ (TDP), a mobile phone application
+designed to lower the costs of evaluating public works and punish political
+representatives in Brazil. Developed by Transparência Brasil[^transparencia],
+TDP allows citizens to learn the location of public school construction sites,
+check their completion status, and anonymously request information from
+competent authorities. TDP users can also take pictures of the construction
+sites and submit them to independent engineers for examination. If the
+engineers classify the construction as delayed, TDP prompts users to send
+a message to the mayor's office asking for completion estimates and
+explanations about the construction status. TDP has been online since April
+2017 and was the winner of the 2016 Google Social Impact grant with more than
+200,000 popular votes[^google].
 
-[^transparencia]: Transparência Brasil is an non-governmental organisation whose mission is to 'promote transparency and social control of public power'.
-It has been active since April 2000, receives no public funding, and is non-partisan.
-More information at <http://transparencia.org.br> (access: July 2019).
+[^transparencia]: Transparência Brasil is an non-governmental organisation
+whose mission is to 'promote transparency and social control of public power'.
+It has been active since April 2000, receives no public funding, and is
+non-partisan. More information at <http://transparencia.org.br> (access: July
+2019).
 
-[^google]: About 1,000 Brazilian charities participated in the 2016 Google Social Impact Challenge.
-An independent committee selected 10 organisations as finalists, and Transparência Brasil won the challenge with about 200,000 popular votes.
-To know more about the contest, please visit <https://impactchallenge.withgoogle.com/brazil2016> (access: July 2019).
+[^google]: About 1,000 Brazilian charities participated in the 2016 Google
+Social Impact Challenge. An independent committee selected 10 organisations as
+finalists, and Transparência Brasil won the challenge with about 200,000
+popular votes. To know more about the contest, please visit
+<https://impactchallenge.withgoogle.com/brazil2016> (access: July 2019).
 
-We use the TDP app to conduct two experimental interventions and test its impact on five outcomes related to school completion rates and complaints to public authorities.
-Overall, our results show that providing information to citizens has no consistent impact on policy outcomes.
-In the first experiment, we find that the TDP app increased the likelihood of construction cancellation by 2 percent, but the result does not replicate.
-The remaining five models have null results.
-In our second intervention, none of the estimations reach conventional levels of statistical significance.
-Importantly, all coefficients are small, what suggests that even if the TDP app had a significant effect on the outcomes, its substantive impact would be virtually negligible.
+We use the TDP app to conduct two experimental interventions and test ~~its
+impact~~ **the impact of citizen oversight** on five outcomes related to school
+completion rates and complaints to public authorities. Overall, our results
+show that providing information to citizens has no consistent impact on policy
+outcomes. In the first experiment, we find that the TDP app increased the
+likelihood of construction cancellation by 2 percent, but the result does not
+replicate. The remaining five models have null results. In our second
+intervention, none of the estimations reach conventional levels of statistical
+significance. Importantly, all coefficients are small, what suggests that even
+if the TDP app had a significant effect on the outcomes, its substantive impact
+would be ~~virtually~~ negligible.
 
-The findings raise questions about the ability of citizens to hold representatives accountable using bottom-up strategies.
-Although studies like @bjorkman2009power, @fiala2017social, and @reinikka2005fighting report better policy outcomes after providing information to local communities, our findings are closer to @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does, @bjorkman2017experimental, @olken2007monitoring, and @raffler2018weakness offering little evidence that information-based interventions lead to greater government responsiveness.
-Our analysis suggests that grassroots monitoring is ineffective in altering government behaviour in Brazil.
+The findings raise questions about the ability of citizens to hold
+representatives accountable using bottom-up ~~strategies~~ **monitoring**.
+Although studies like @bjorkman2009power, @fiala2017social, and
+@reinikka2005fighting report better policy outcomes after providing information
+to local communities, our findings are closer to @banerjee2010pitfalls,
+@keefer2014mass, @lieberman2014does, @bjorkman2017experimental,
+@olken2007monitoring, and @raffler2018weakness, offering little evidence that
+information-based interventions lead to greater government responsiveness. Our
+analysis suggests that grassroots monitoring is ineffective in altering
+government behaviour in Brazil.
 
@@
 
-The _Tá de Pé_[^tdp] (TDP) cell phone application is an initiative carried out by Transparência Brasil to foster bottom-up accountability in the Brazilian public sector.
-More specifically, the main goal of the TDP project is to improve responsiveness in government education expenditures.
-The TDP app incentivises citizens to provide up-to-date information about unfinished school constructions in their neighbourhoods, and that information will be assessed by a group of independent specialists.
-In the case the construction is behind schedule, TDP provides a writing platform whereby citizens can report to public officials quickly and anonymously.
-The app then prompts citizens to write a notification to the mayor's office, which has 15 days to reply.
-If they do not respond to the request, the app forwards the notification to the Brazilian Ministry of Education, making it harder for the municipality to access federal funds in the future.
-The motivation behind this intervention is that providing information to citizens empowers individuals to closely monitor public works.
-This, in turn, results in better social outcomes as public agents become more responsive to community demands.
+The _Tá de Pé_[^tdp] (TDP) cell phone application is an initiative carried out
+by Transparência Brasil to foster bottom-up accountability in the Brazilian
+public sector. More specifically, the main goal of the TDP project is to
+improve responsiveness in government education expenditures. The TDP app
+incentivises citizens to provide up-to-date information about unfinished school
+constructions in their neighbourhoods, and that information will be assessed by
+a group of independent specialists. In the case the construction is behind
+schedule, TDP provides a writing platform whereby citizens can report to public
+officials quickly and anonymously. The app then prompts citizens to write
+a notification to the mayor's office, which has 15 days to reply. If they do
+not respond to the request, the app forwards the notification to the Brazilian
+Ministry of Education, making it harder for the municipality to access federal
+funds in the future. The motivation behind this intervention is that providing
+information to citizens empowers individuals to closely monitor public works.
+This, in turn, results in better social outcomes as public agents become more
+responsive to community demands.
 
-[^tdp]: _Tá de Pé_ is an informal Brazilian expression for 'is it done?'. Literally, it means 'standing on its feet' in Portuguese.
+[^tdp]: _Tá de Pé_ is an informal Brazilian expression for 'is it done?'.
+Literally, it means 'standing on its feet' in Portuguese.
 
-Transparência Brazil built the app in from January to March 2017 and tested it in May of that year.
-The first stable Android version was deployed on Google Play on 14 August 2017.
-A version for iOS came about six months later.
-In October 2017, Transparência Brazil started a Facebook campaign in order to publicise the app.
-Facebook is the most widely used social media network in Brazil with around 72 million users  [@statista2019facebook].
-The campaigns attracted 2,028 new users to the platform in October 2017 only.
+Transparência Brazil built the app in from January to March 2017 and tested it
+in May of that year. The first stable Android version was deployed on Google
+Play on 14 August 2017. A version for iOS came about six months later. In
+October 2017, Transparência Brazil started a Facebook campaign in order to
+publicise the app. Facebook is the most widely used social media network in
+Brazil with around 72 million users [@statista2019facebook]. The campaigns
+attracted 2,028 new users to the platform in October 2017 only.
 
@@
      \end{minipage}
-     \caption{The \textit{Tá de Pé} mobile phone application.
-The first image presents a list of school construction sites close to the users' location.
-The second image shows that the school construction selected by the user is delayed by 9 months.
-The last image shows how citizens can add information to the photos they submit via the app.}
-     \label{fig:screenshots}
-\end{figure}
+		 \caption{The \textit{Tá de Pé} mobile phone application. The first image
+		 presents a list of school construction sites close to the users' location.
+		 The second image shows that the school construction selected by the user
+		 is delayed by 9 months. The last image shows how citizens can add
+		 information to the photos they submit via the app.}
+		 \label{fig:screenshots} \end{figure}
 
-Transparência Brasil partnered with the Brazilian branch of _Engineers without Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide technical assessment of school completion rates based on user-submitted photos and GPS coordinates.
-The engineers' reports are later uploaded to the TDP database and stored on the users' mobile devices so citizens can follow the progress of the reported constructions.
+Transparência Brasil partnered with the Brazilian branch of _Engineers without
+Borders_ (EWB), an independent non-governmental organisation[^ewb], to provide
+technical assessment of school completion rates based on user-submitted photos
+and GPS coordinates. The engineers' reports are later uploaded to the TDP
+database and stored on the users' mobile devices so citizens can follow the
+progress of the reported constructions.
 
-[^ewb]: Please visit <http://www.ewb-international.org> to know more about Engineers without Borders International and <https://esf.org.br> for information on the Brazilian office.
+[^ewb]: Please visit <http://www.ewb-international.org> to know more about
+Engineers without Borders International and <https://esf.org.br> for
+information on the Brazilian office.
 
-The TDP also received feedback from Brazilian computer scientists and policy analists.
-In 2017 and 2018, Transparência Brasil announced two team programming competitions, called 'Tá de Pé Hackathons', where contributors could fix code bugs and suggest new functionalities to the TDP project.
-One of these innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which posts a message on the social network each time a user submits a new picture for evaluation or a municipality responds to a citizen's request.
-This allows any interested parties, including those who do not use the TDP app, to check the state of school construction sites.
+The TDP also received feedback from Brazilian computer scientists and policy
+analists. In 2017 and 2018, Transparência Brasil announced two team programming
+competitions, called 'Tá de Pé Hackathons', where contributors could fix code
+bugs and suggest new functionalities to the TDP project. One of these
+innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which
+posts a message on the social network each time a user submits a new picture
+for evaluation or a municipality responds to a citizen's request. This allows
+any interested parties, including those who do not use the TDP app, to check
+the state of school construction sites.
 
@@
 
-Between August 2017 and February 2019, we implemented two interventions to measure the effect of the TDP app on five school construction outcomes plus a placebo test.
-The outcomes are: 1) a placebo outcome indicating the percentage of the project completed before the impact evaluation started; 2) the percentage of the project completed by the end of the interventions; 3) the difference between the percentage reported as completed before and after the interventions; 4) the number of finished constructions; 5) the number of cancelled constructions; 6) the number of schools where construction companies updated the conclusion dates.
-In terms of expectations, Table \ref{tab:outcomes} depicts the expected effects for each of the studied outcomes.
+Between August 2017 and February 2019, we implemented two interventions to
+measure the effect of the TDP app on five school construction outcomes plus
+a placebo test. The outcomes are: 1) a placebo outcome indicating the
+percentage of the project completed before the impact evaluation started; 2)
+the percentage of the project completed by the end of the interventions; 3) the
+difference between the percentage reported as completed before and after the
+interventions; 4) the number of finished constructions; 5) the number of
+cancelled constructions; 6) the number of schools where construction companies
+updated the conclusion dates. In terms of expectations, Table
+\ref{tab:outcomes} depicts the expected effects for each of the studied
+outcomes[^more-details].
+
+[^more-details]: **Please refer to the Online Appendix for further details on
+the treatment implementation and the coding of the outcome variables.**
 
@@
 
-The first intervention was carried out from August 2017 to February 2018 using the Android version of TDP.
-The randomization was conduct at the municipal level.
-We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])` municipalities to the control group and included `r as.numeric(table(impact_evaluation_phase1$treat)[2])` in the treatment group.
-Our control condition consists in removing all information about school construction from the TDP app in the chosen municipalities, so that citizens were unable to report constructions in the control municipalities.
+The first intervention was carried out from August 2017 to February 2018 using
+the Android version of TDP. The randomization was conduct at the municipal
+level. We randomly selected 
+`r as.numeric(table(impact_evaluation_phase1$treat)[1])` municipalities to the
+control group and included 
+`r as.numeric(table(impact_evaluation_phase1$treat)[2])` in the treatment
+group. Our control condition consists in removing all information about school
+construction from the TDP app in the chosen municipalities, so that citizens
+were unable to report constructions in the control municipalities.
 
-To evaluate the random assignment, we used the following pre-treatment variables: 1) log of municipal population in 2015; 2) log of number of poor families in each city; 3) log of total federal transfers to the municipality in 2016; 4) federal government indicator for primary school quality; 5) federal government indicator for secondary school quality.
-The data come from the Brazilian Ministry of Education and the Census.
-Balance tests show that the randomisation was successful and are available in the Supplementary Materials.
+To evaluate the random assignment, we used the following pre-treatment
+variables: 1) log of municipal population in 2015; 2) log of number of poor
+families in each city; 3) log of total federal transfers to the municipality in
+2016; 4) federal government indicator for primary school quality; 5) federal
+government indicator for secondary school quality. The data come from the
+Brazilian Ministry of Education and the Census. Balance tests show that the
+randomisation was successful and are available in the Supplementary Materials.
 
-We also conducted two manipulation checks and analysed the number of TDP app downloads by municipality and over time.
-Figure \ref{fig:manipulation1} displays the results and indicates that the treatment has good territorial variability.
-There are `r length(unique(ga$municipality[ga$phase1==1]))` downloads in the `r length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment']))` municipalities in the treatment condition.
-Downloads peak during the Facebook TDP campaign, launched in October 2017, then diminish in the following months.
+We also conducted two manipulation checks and analysed the number of TDP app
+downloads by municipality and over time. Figure \ref{fig:manipulation1}
+displays the results and indicates that the treatment has good territorial
+variability. There are `r length(unique(ga$municipality[ga$phase1==1]))`
+downloads in the 
+`r length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment']))`
+municipalities in the treatment condition. Downloads peak during the Facebook
+TDP campaign, launched in October 2017, then diminish in the following months.
 
@@
 # Load data
-load('tdp.RData')
+load("tdp.RData")
 
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 'ggpubr',
-          'haven', 'compareGroups', 
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes')
+pkgs <- c("tidyverse", "dummies", "ggpubr",
+          "haven", "compareGroups",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes")
 invisible(lapply(pkgs, require, character.only = T))
@@
 ## Map GA intervention 1
-mapbr <- get_brmap('City')
+mapbr <- get_brmap("City")
 gaaux <- filter(ga, phase1 == 1)
@@
 gaaux <- unique(gaaux)
-gaaux$City <- as.numeric(gaaux$City)
+gaaux$city <- as.numeric(gaaux$City)
 gaaux2 <- impact_evaluation_phase1 %>%
@@
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux$downl[is.na(gaaux$downl)] <- 0
 gaaux2 <- data.frame(City = mapbr$City)
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 2
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads', 'Not in App'))
-mapbr <- join_data(mapbr, gaaux, by = 'City')
-pMapDownloadsInt1 <- ggplot() + 
+gaaux$downl[is.na(gaaux$downl)] <- 2
+gaaux$Downloads <- factor(gaaux$downl,
+													labels = c("No Downloads", "Downloads", "Not in App"))
+mapbr <- join_data(mapbr, gaaux, by = "City")
+plot_downloads_int1 <- ggplot() +
   geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
-  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  scale_fill_manual(values = c("#E69F00", "#0072B2", "#F0E442")) +
   theme_map()
-pMapDownloadsInt1
+plot_downloads_int1
 
@@
   summarize(NewUsers = sum(novos_usuarios))
-names(tab) <- c('Date', 'Frequency')
-pFreqUserDownloadsInt1 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+names(tab) <- c("Date", "Frequency")
+plot_freq_users_int1 <- ggplot(tab, aes(x = Date, y = Frequency, group = 1)) +
   geom_line() + geom_point()
-pFreqUserDownloadsInt1
+plot_freq_users_int1
 ```
@@
 \newpage
-The second intervention is similar to intervention 1 in all but three characteristics.
-First, the TDP app was available for both Android and iOS devices.
-Second, we randomised the intervention at the school level, with `r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and `r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units.
-We used blocked randomisation stratified by Brazilian states, school construction status (under construction, stopped, unfinished), and whether the municipality spent more on school construction that the distribution median.
-Finally, the intervention period lasted from August 2018 to February 2019.
+The second intervention is similar to intervention 1 in all but three
+characteristics. First, the TDP app was **then** available for both Android and
+iOS devices. Second, we randomised the intervention at the school level, with
+`r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
+`r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units. We
+used blocked randomisation stratified by Brazilian states, school construction
+status (under construction, stopped, unfinished), and whether the municipality
+spent more on school construction that the distribution median. Finally, the
+intervention period lasted from August 2018 to February 2019.
 
 Balance tests and manipulation checks were also successful for intervention 2.
-In total, `r length(unique(ga$municipality[ga$phase2==1]))` municipalities downloaded the app.
-There is about 1,000 user downloads in August 2018, right after intervention 2 starts, and a second spike around December.
-The number of downloads is smaller in this second intervention as there was no associated social media campaign in that period.
+In total, `r length(unique(ga$municipality[ga$phase2==1]))` municipalities
+downloaded the app. There is about 1,000 user downloads in August 2018, right
+after intervention 2 starts, and a second spike around December. The number of
+downloads is smaller in this second intervention as there was no associated
+social media campaign in that period.
 
@@
 # Load data
-load('tdp.RData')
+load("tdp.RData")
 
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 'ggpubr',
-          'haven', 'compareGroups', 
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes')
+pkgs <- c("tidyverse", "dummies", "ggpubr",
+          "haven", "compareGroups",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes")
 invisible(lapply(pkgs, require, character.only = T))
 
-## Manipulation Stats
+## Manipulation Statistics
 
 ## Map manipulation test -- Intervention 2
-mapbr <- get_brmap('City')
+mapbr <- get_brmap("City")
 gaaux <- filter(ga, phase2 == 1)
@@
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux$downl[is.na(gaaux$downl)] <- 0
 gaaux2 <- data.frame(City = mapbr$City)
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 2
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
-                                                  'Not in App'))
-mapbr <- join_data(mapbr, gaaux, by = 'City')
+gaaux$downl[is.na(gaaux$downl)] <- 2
+gaaux$Downloads <- factor(gaaux$downl, labels = c("No Downloads", "Downloads",
+                                                  "Not in App"))
+mapbr <- join_data(mapbr, gaaux, by = "City")
 p1 <- ggplot() +
   geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
-  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  scale_fill_manual(values = c("#E69F00", "#0072B2", "#F0E442")) +
   theme_map()
@@
   summarize(NewUsers = sum(novos_usuarios))
-names(tab) <- c('Date', 'Frequency')
-p2 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+names(tab) <- c("Date", "Frequency")
+p2 <- ggplot(tab, aes(x = Date, y = Frequency, group = 1)) +
   geom_line() + geom_point()
@@
 
+**(Short paragraph on whether the app has worked)**
+
 We estimate all models using the following regression equation:
@@
 \begin{equation}
-Y_i \ = \ \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i 
+Y_i = \alpha + \beta T_i + \gamma X_i + \theta Z_i + \varepsilon_i
 \end{equation}
 
-where $i$ indexes the experiment units.
-$Y_i$ is one of the six outcomes described above, $\alpha$ is the intercept, $\beta$ denotes the average treatment effect, and $T_i$ is a binary treatment indicator.
-$\gamma$ is a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed effects, $\theta$ is a vector of controls and $Z_i$ an array of controls for the case $i$.
-The error term is denoted by $\varepsilon_i$.
-We cluster the standard errors at the municipality level as mayors are responsible for school investment decisions in Brazil.
+where $i$ indexes the experiment units. $Y_i$ is one of the six outcomes
+described above, $\alpha$ is the intercept, $\beta$ denotes the average
+treatment effect, and $T_i$ is a binary treatment indicator. $\gamma$ is
+a vector of fixed effects, $X_i$ is a matrix of Brazilian states' fixed
+effects, $\theta$ is a vector of controls, and $Z_i$ an array of controls for
+the case $i$. The error term is denoted by $\varepsilon_i$. We cluster the
+standard errors at the municipality level as mayors are responsible for school
+investment decisions in Brazil.
 
@@
 
-Table \ref{tab:results1} summarises the main results of intervention 1.
-Each column represents the treatment effect of the TDP app on one of the outcomes we measured for this study.
-All models reported here include the five control variables described in the previous section and Brazilian states' fixed effects.
-We also estimated the models without control variables, without fixed effects, and with nearest-neighbour matching.
-The results are very similar to those below.
+Table \ref{tab:results1} summarises the main results of intervention 1. Each
+column represents the treatment effect of the TDP app on one of the outcomes we
+measured for this study. All models reported here include the five control
+variables described in the previous section and Brazilian states' fixed
+effects. We also estimated the models without control variables, without fixed
+effects, and with nearest-neighbour matching. The results are very similar to
+those below.
 
 ```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
-load('tdp.RData')
+load("tdp.RData")
 
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 'ggpubr',
-          'haven', 'compareGroups', 
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes')
+pkgs <- c("tidyverse", "dummies", "ggpubr",
+          "haven", "compareGroups",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes")
 invisible(lapply(pkgs, require, character.only = T))
@@
 # Auxiliary function: calculate coefficients
-calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
-  ctrls_mod <- paste(ctrls, collapse = '+')
-  fes_mod <- paste(fes, collapse = '+')
+calc_ates <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
+  ctrls_mod <- paste(ctrls, collapse = "+")
+  fes_mod <- paste(fes, collapse = "+")
   moddescr <- data.frame()
@@
     for (j in outcs) {
-      if(is.null(wts)) {
+      if (is.null(wts)) {
         dat <- dataux %>%
@@
             na.omit()
-          wts <- dat[,wts]
+          wts <- dat[, wts]
         }
-      # No controls and no fes
+      # No controls and no fixed effects
       mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+        paste(c(j,paste(i,paste("", 0, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wts)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = F))
-      print(k); k = k+1
-      # Controls and no fes
+      print(k); k = k + 1
+      # Controls and no fixed effects
       mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+        paste(c(j,paste(paste(c(i, ctrls_mod), collapse = "+"),
+                        paste("", 0, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wts)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = F))
-      print(k); k = k+1
-      # No controls and fes
+      print(k); k = k + 1
+      # No controls and fixed effects
       mods[[k]] <- felm(
-        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
-                                   paste('',fes_mod,0,cls, sep = '|'), 
-                                   sep = '')),
-                         collapse = '~')), data = dat, weights = wts)
+        as.formula(paste(c(j, paste(paste(c(i), collapse = "+"),
+                                   paste("", fes_mod, 0, cls, sep = "|"),
+                                   sep = "")),
+                         collapse = "~")), data = dat, weights = wts)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = T))
-      print(k); k = k+1
-      # Controls and fes
+      print(k); k = k + 1
+      # Controls and fixed effects
       mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wts)
+        paste(c(j,paste(paste(c(i, ctrls_mod), collapse = "+"),
+                        paste("", fes_mod, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wts)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = T))
-      print(k); k = k+1
+      print(k); k = k + 1
     }
@@
 ## ATEs
-outcs <- c('percExecBegin', 'percExecEnd',
-           'deltaPercExec', 'isFinished',
-           'isCancelled', 'updDate')
-treats <- c('treat')
-ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
-           'log_poorFam2010', 'log_totTransf2016')
-fes <- c('state')
-cls <- c('municipality')
+outcs <- c("percExecBegin", "percExecEnd",
+           "deltaPercExec", "isFinished",
+           "isCancelled", "updDate")
+treats <- c("treat")
+ctrls <- c("logPop2015", "ideb_ai_2015","ideb_af_2015",
+           "log_poorFam2010", "log_totTransf2016")
+fes <- c("state")
+cls <- c("municipality")
 
-resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impact_evaluation_phase1)
+resInt1 <- calc_ates(outcs, treats, ctrls, fes, cls,
+										 dat = impact_evaluation_phase1)
 
@@
           resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
-          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1', 
-          keep='treatTreatment', 
-          type = 'latex',
-          covariate.labels = 'ATE',
+          title = "\\label{tab:results1} Impact Evaluation -- Intervention 1",
+          keep="treatTreatment",
+          type = "latex",
+          covariate.labels = "ATE",
           column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
-          dep.var.labels.include=F, column.sep.width = '-2pt',
-          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = 'Cluster-robust SEs at the municipality level.',
+          dep.var.labels.include = F, column.sep.width = "-2pt",
+          omit.stat=c("adj.rsq", "ser"), align = F, digits = 2,
+          notes = "Cluster-robust SEs at the municipality level.",
           add.lines = list(c("Controls", "Yes", "Yes", "Yes",
@@
               "Yes", "Yes", "Yes")),
-          notes.append = T, header=FALSE)
+          notes.append = T, header = F)
 ```
@@
 
-We find that the app only has a small effect on cancellation rates.
-The TDP application increases the likelihood of cancelling the construction in `r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent.
-While this result goes in the opposite direction of our theoretical expectations, the finding is largely inconsistent, and it does not replicate in the second experiment.
-All other coefficients are not statistically significant at conventional levels.
-On the one hand, the results indicate that our placebo outcome, the percentage of the invested executed before the intervention, indeed behaves as predicted.
-On the other hand, we expected the five remaining outcomes to improve after the introduction of the app.
-The literature on bottom-up accountability argues that more information about the shortcomings of public service provision will mobilise citizens who, in turn, would pressure state agents to produce better social policies.
-Our results do not lend support to that hypothesis.
+We find that the app only has a small effect on cancellation rates. The TDP
+application increases the likelihood of cancelling the construction in 
+`r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent. While this result
+goes in the opposite direction of our theoretical expectations, the finding is
+inconsistent and does not replicate in the second experiment. All other
+coefficients are not statistically significant at conventional levels. On the
+one hand, the results indicate that our placebo outcome, the percentage of the
+invested executed before the intervention, indeed behaves as predicted. On the
+other hand, we expected the five remaining outcomes to improve after the
+introduction of the app. The literature on bottom-up accountability argues that
+delivering more information about the shortcomings of public services provision
+will ~~mobilise citizens who, in turn, would pressure state agents to produce
+better social policies~~ **put citizens in a position where they can monitor
+state agents and improve provider behaviour** [@raffler2018weakness, 2] . Our
+results do not lend support to that hypothesis.
 
-Table \ref{tab:results2} shows the results of the second intervention.
-The treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo.
-This raises further questions about the effect of the TDP app on school completion.
-Note that the effect signs are also inconsistent with improving the outcomes, what demonstrates that our results do not derive from low statistical power or the reduced control group size.
+Table \ref{tab:results2} shows the results of the second intervention. The
+treatment does not have a statistically significant effect on any our outcomes
+of interest, including the placebo. This raises further questions about the
+effect of the TDP app on school completion. Note that the effect signs are also
+inconsistent with improving the outcomes, what demonstrates that our results do
+not derive from low statistical power or the reduced control group size.
 
 ```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
-load('tdp.RData')
+load("tdp.RData")
 
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 'ggpubr',
-          'haven', 'compareGroups', 
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes', 
-          'stargazer')
+pkgs <- c("tidyverse", "dummies", "ggpubr",
+          "haven", "compareGroups",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes",
+          "stargazer")
 invisible(lapply(pkgs, require, character.only = T))
@@
             na.omit()
-          wtsaux <- dat[,wts]
+          wtsaux <- dat[, wts]
       }
-      # No controls and no fes
+      # No controls and no fixed effects
       mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wtsaux)
+        paste(c(j,paste(i,paste("", 0, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = F))
-      print(k); k = k+1
-      # Controls and no fes
+      print(k); k = k + 1
+      # Controls and no fixed effects
       mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',0,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wtsaux)
+        paste(c(j,paste(paste(c(i, ctrls_mod), collapse = "+"),
+                        paste("", 0, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = F))
-      print(k); k = k+1
-      # No controls and fes
+      print(k); k = k + 1
+      # No controls and fixed effects
       mods[[k]] <- felm(
-        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
-                                   paste('',fes_mod,0,cls, sep = '|'), 
+        as.formula(paste(c(j,paste(paste(c(i), collapse = "+"),
+                                   paste("", fes_mod, 0, cls, sep = "|"),
                                    sep = '')),
-                         collapse = '~')), data = dat, weights = wtsaux)
+                         collapse = "~")), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr,
@@
                                    hFEs = T))
-      print(k); k = k+1
-      # Controls and fes
+      print(k); k = k + 1
+      # Controls and fixed effects
       mods[[k]] <- felm(as.formula(
-        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
-                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wtsaux)
+        paste(c(j, paste(paste(c(i, ctrls_mod), collapse = "+"),
+                        paste("", fes_mod, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wtsaux)
       moddescr <- rbind(moddescr,
@@
 
-outcs <- c('percExecBegin', 'percExecEnd',
-           'deltaPercExec', 'isFinished',
-           'isCancelled', 'updDate')
-ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
-           'log_poorFam2010', 'log_totTransf2016')
-fes <- c('state')
-cls <- c('municipality')
+outcs <- c("percExecBegin", "percExecEnd",
+           "deltaPercExec", "isFinished",
+           "isCancelled", "updDate")
+ctrls <- c("logPop2015", "ideb_ai_2015","ideb_af_2015",
+           "log_poorFam2010", "log_totTransf2016")
+fes <- c("state")
+cls <- c("municipality")
 
-resInt2 <- calcATEs(outcs, 'treat', ctrls, fes, cls, dat = impact_evaluation_phase2, wts = 'IPW_treat')
+res_int2 <- calc_ates(outcs, "treat", ctrls, fes, cls, dat = impact_evaluation_phase2, wts = "IPW_treat")
 
@@
 library(stargazer)
-stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
-          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
-          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
-          dep.var.labels.include=F, 
-          keep='treatTreatment', type = 'latex',
-          covariate.labels = 'ATE',
+stargazer(res_int2[[2]][[4]],res_int2[[2]][[8]],res_int2[[2]][[12]],
+          res_int2[[2]][[16]],res_int2[[2]][[20]],res_int2[[2]][[24]],
+          title = "\\label{tab:results2} Impact Evaluation -- Intervention 2",
+          dep.var.labels.include = F,
+          keep="treatTreatment", type = "latex",
+          covariate.labels = "ATE",
           column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
-          column.sep.width = '-2pt',
-          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
-          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed by the randomizr package.'),
-          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
+          column.sep.width = "-2pt",
+          omit.stat = c("adj.rsq", "ser"), align = F, digits = 2,
+          notes = c("Cluster-robust SEs at the municipality level.",
+										"IPW computed by the randomizr package."),
+          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
+														 "Yes", "Yes", "Yes"),
             c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
-          notes.append = T, header=FALSE)
+          notes.append = T, header = F)
 ```
@@
 
-Figure \ref{fig:randomisation-inference} shows the results of our randomisation inference tests.
-Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field].
-We fail to reject the null in all but the finished school indicator in experiment 1.
+Figure \ref{fig:randomisation-inference} shows the results of our randomisation
+inference tests. Randomisation inference allows us to estimate the probability
+of the sharp null hypothesis over all possible randomisations that could have
+occurred under our research design [@coppock2019ri2; @gerber2012field]. We fail
+to reject the null in all but the finished school indicator in experiment 1.
 
@@
 # Chunk randomization inference
-load('tdp.RData')
+load("tdp.RData")
 
 # Load packages
-pkgs <- c('tidyverse', 'dummies', 
-          'haven', 'compareGroups', 
-          'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 
-          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
-          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
-          'flextable', 'officer', 'ggthemes', 'ggpubr')
+pkgs <- c("tidyverse", "dummies",
+          "haven", "compareGroups",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes", "ggpubr")
 invisible(lapply(pkgs, require, character.only = T))
@@
 test_fun <- function(dat, outc, treat, wts = NULL) {
-  ctrls_mod <- paste(ctrls, collapse = '+')
-  fes_mod <- paste(fes, collapse = '+')
+  ctrls_mod <- paste(ctrls, collapse = "+")
+  fes_mod <- paste(fes, collapse = "+")
   moddescr <- data.frame()
   mods <- list()
-  if(is.null(wts)) {
+  if (is.null(wts)) {
     dat <- dat %>%
@@
       na.omit()
-    wtsaux <- dat[,wts]
+    wtsaux <- dat[, wts]
   }
@@
     felm(as.formula(
-      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = '+'),
-                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
-              collapse = '~')), data = dat, weights = wtsaux)
+      paste(c(outc,paste(paste(c(treat,ctrls_mod), collapse = "+"),
+                        paste("", fes_mod, 0, cls, sep = "|"), sep = "")),
+              collapse = "~")), data = dat, weights = wtsaux)
   return(aux$coefficients[1])
@@
 
-outcs <- c('percExecBegin', 'percExecEnd',
-           'deltaPercExec', 'isFinished',
-           'isCancelled', 'updDate')
-ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
-           'log_poorFam2010', 'log_totTransf2016')
-fes <- c('state')
-cls <- c('municipality')
+outcs <- c("percExecBegin", "percExecEnd",
+           "deltaPercExec", "isFinished",
+           "isCancelled", "updDate")
+ctrls <- c("logPop2015", "ideb_ai_2015","ideb_af_2015",
+           "log_poorFam2010", "log_totTransf2016")
+fes <- c("state")
+cls <- c("municipality")
 
@@
 set.seed(543129) #Random.org
-auxdat <- impact_evaluation_phase1[,c('ibge_code7', outcs, ctrls, fes, cls)]
-aux2 <- unique(impact_evaluation_phase1[,c('ibge_code7', 'treat')]) %>% na.omit()
+auxdat <- impact_evaluation_phase1[,c("ibge_code7", outcs, ctrls, fes, cls)]
+aux2 <- unique(impact_evaluation_phase1[,c("ibge_code7", "treat")]) %>% na.omit()
 N = sum(table(aux2$treat))
@@
 for (k in 1:1000) {
-    treat <- c(rep(1,N-Ctrl), rep(0,Ctrl))
+    treat <- c(rep(1, N-Ctrl), rep(0, Ctrl))
     treat <- sample(treat, N)
@@
   for (k in 1:1000)
-    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'))
+    res[k] <- test_fun(auxdat, i, paste("treat", k, sep = "."))
   resri1 <- data.frame(resri1, res)
-  names(resri1)[names(resri1)=='res'] = i
+  names(resri1)[names(resri1) == "res"] = i
 }
-resri1 <- resri1[,-1]
-i1h1 <- ggplot(data=resri1, aes(resri1$percExecBegin)) + 
+resri1 <- resri1[, -1]
+i1h1 <- ggplot(data = resri1, aes(resri1$percExecBegin)) +
   geom_histogram(bins = 100) +
-  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'percExecBegin', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, "percExecBegin", "treat"),
              lwd = 1, lty = 2) +
-  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
+  labs(x = "Percentage Completed Before\n(placebo)", y = "Frequency")
 i1h2 <- ggplot(data=resri1, aes(resri1$percExecEnd)) +
   geom_histogram(bins = 100) +
-  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'percExecEnd', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, "percExecEnd", "treat"),
              lwd = 1, lty = 2) +
-  labs(x="Percentage Completed End Intervention", y="Frequency")
-i1h3 <- ggplot(data=resri1, aes(resri1$deltaPercExec)) + 
+  labs(x = "Percentage Completed End Intervention", y = "Frequency")
+i1h3 <- ggplot(data = resri1, aes(resri1$deltaPercExec)) +
   geom_histogram(bins = 100) +
-  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'deltaPercExec', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, "deltaPercExec", "treat"),
              lwd = 1, lty = 2) +
-  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
-i1h4 <- ggplot(data=resri1, aes(resri1$isFinished)) + 
+  labs(x = "Diff. Pct. Completed Before and After", y = "Frequency")
+i1h4 <- ggplot(data = resri1, aes(resri1$isFinished)) +
   geom_histogram(bins = 100) +
-  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'isFinished', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, "isFinished", "treat"),
              lwd = 1, lty = 2) +
-  labs(x="Finished School Construction Indicator", y="Frequency")
-i1h5 <- ggplot(data=resri1, aes(resri1$isCancelled)) + 
+  labs(x = "Finished School Construction Indicator", y = "Frequency")
+i1h5 <- ggplot(data = resri1, aes(resri1$isCancelled)) +
   geom_histogram(bins = 100) +
-  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'isCancelled', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, "isCancelled", "treat"),
              lwd = 1, lty = 2) +
-  labs(x="Cancelled School Construction Indicator", y="Frequency")
-i1h6 <- ggplot(data=resri1, aes(resri1$updDate)) + 
+  labs(x = "Cancelled School Construction Indicator", y = "Frequency")
+i1h6 <- ggplot(data = resri1, aes(resri1$updDate)) +
   geom_histogram(bins = 100) +
-  geom_vline(xintercept = test_fun(impact_evaluation_phase1, 'updDate', 'treat'),
+  geom_vline(xintercept = test_fun(impact_evaluation_phase1, "updDate", "treat"),
              lwd = 1, lty = 2) +
-  labs(x="Updated Endline Date School Construction", y="Frequency")
+  labs(x = "Updated Endline Date School Construction", y = "Frequency")
 
@@
 aux <- filter(rand2018, !is.na(Z_intheapp))
-declRA <- declare_ra(blocks = aux$var_blocking,
+delc_ra <- declare_ra(blocks = aux$var_blocking,
                      prob_each = c(.85,.15),
@@
 set.seed(543129) #Random.org
-auxdat <- impact_evaluation_phase2[,c('id_project', outcs, ctrls, fes, cls)]
-aux2 <- unique(aux[,c('id', 'Z_intheapp', 'IPW_intheapp')]) %>%
+auxdat <- impact_evaluation_phase2[, c("id_project", outcs, ctrls, fes, cls)]
+aux2 <- unique(aux[,c("id", "Z_intheapp", "IPW_intheapp")]) %>%
   na.omit() %>%
@@
          wts = IPW_intheapp) %>%
-  mutate(treat = as.numeric(as.factor(treat))-1)
+  mutate(treat = as.numeric(as.factor(treat)) - 1)
 resri2 <- data.frame(1:1000)
@@
                   conditions = c(1, 0),
-                  prob_each = c(.85,.15))
-    IPW <- 1/obtain_condition_probabilities(declRA, Z)
+                  prob_each = c(.85, .15))
+    IPW <- 1/obtain_condition_probabilities(delc_ra, Z)
     aux2 <- data.frame(aux2, treat = Z, wts = IPW)
@@
   for (k in 1:1000)
-    res[k] <- test_fun(auxdat, i, paste('treat', k, sep = '.'), 
-                       wts = paste('wts', k, sep = '.'))
+    res[k] <- test_fun(auxdat, i, paste("treat", k, sep = "."),
+                       wts = paste("wts", k, sep = "."))
   resri2 <- data.frame(resri2, res)
-  names(resri2)[names(resri2)=='res'] = i
+  names(resri2)[names(resri2) == "res"] = i
 }
-resri2 <- resri2[,-1]
-i2h1 <- ggplot(data=resri2, aes(resri2$percExecBegin)) + 
+resri2 <- resri2[, -1]
+i2h1 <- ggplot(data = resri2, aes(resri2$percExecBegin)) +
   geom_histogram(bins = 100) +
   geom_vline(xintercept = test_fun(impact_evaluation_phase2,
-                                   'percExecBegin', 'treat', wts = 'IPW_treat'),
+                                   "percExecBegin", "treat", wts = "IPW_treat"),
              lwd = 1, lty = 2) +
-  labs(x="Percentage Completed Before\n(placebo)", y="Frequency")
+  labs(x = "Percentage Completed Before\n(placebo)", y = "Frequency")
 i2h2 <- ggplot(data=resri2, aes(resri2$percExecEnd)) +
@@
   geom_vline(xintercept = test_fun(impact_evaluation_phase2,
-                                   'percExecEnd', 'treat', wts = 'IPW_treat'),
+                                   "percExecEnd", "treat", wts = "IPW_treat"),
              lwd = 1, lty = 2) +
-  labs(x="Percentage Completed End Intervention", y="Frequency")
-i2h3 <- ggplot(data=resri2, aes(resri2$deltaPercExec)) + 
+  labs(x = "Percentage Completed End Intervention", y = "Frequency")
+i2h3 <- ggplot(data = resri2, aes(resri2$deltaPercExec)) +
   geom_histogram(bins = 100) +
   geom_vline(xintercept = test_fun(impact_evaluation_phase2,
-                                   'deltaPercExec', 'treat', wts = 'IPW_treat'),
+                                   "deltaPercExec", "treat", wts = "IPW_treat"),
              lwd = 1, lty = 2) +
-  labs(x="Diff. Pct. Completed Before and After", y="Frequency")
+  labs(x = "Diff. Pct. Completed Before and After", y = "Frequency")
 i2h4 <- ggplot(data=resri2, aes(resri2$isFinished)) +
@@
   geom_vline(xintercept = test_fun(impact_evaluation_phase2,
-                                   'isFinished', 'treat', wts = 'IPW_treat'),
+                                   "isFinished", "treat", wts = "IPW_treat"),
              lwd = 1, lty = 2) +
-  labs(x="Finished School Construction Indicator", y="Frequency")
+  labs(x = "Finished School Construction Indicator", y = "Frequency")
 i2h5 <- ggplot(data=resri2, aes(resri2$isCancelled)) +
@@
   geom_vline(xintercept = test_fun(impact_evaluation_phase2,
-                                   'isCancelled', 'treat', wts = 'IPW_treat'),
+                                   "isCancelled", "treat", wts = "IPW_treat"),
              lwd = 1, lty = 2) +
-  labs(x="Cancelled School Construction Indicator", y="Frequency")
-i2h6 <- ggplot(data=resri2, aes(resri2$updDate)) + 
+  labs(x = "Cancelled School Construction Indicator", y = "Frequency")
+i2h6 <- ggplot(data = resri2, aes(resri2$updDate)) +
   geom_histogram(bins = 100) +
   geom_vline(xintercept = test_fun(impact_evaluation_phase2,
-                                   'updDate', 'treat', wts = 'IPW_treat'),
+                                   "updDate", "treat", wts = "IPW_treat"),
              lwd = 1, lty = 2) +
-  labs(x="Updated Endline Date School Construction", y="Frequency")
+  labs(x = "Updated Endline Date School Construction", y = "Frequency")
 
@@
 
-We also note that effect sizes are small in all estimations and that the coefficients flip signs in all but one of our six dependent variables.
-This provides further evidence for the null results: not only the app would have a low impact even if the treatment were significant, but the results could go against what the bottom-up accountability theory predicts.
-At least in the school construction outcomes we investigate here, we find little evidence that grassroots monitoring works in the context of school constructions in Brazil.
+We also note that effect sizes are small in all estimations and that the
+coefficients flip signs in all but one of our six dependent variables. This
+provides further evidence for the null results: not only the app would have
+a low impact even if the treatment were significant, but the results could go
+against what the bottom-up accountability theory predicts. At least in the
+school construction outcomes we investigate here, we find little evidence that
+grassroots monitoring works in the context of school constructions in Brazil.
 
@@
 
-In this paper, we discuss whether a mobile phone application can foster grassroots mobilisation and political accountability in Brazil.
-Our two interventions show that the results are at best mixed.
-Although we find an effect on school construction completion and cancelling rates in the first intervention, the app has no consistent impact on our outcomes of interest.
-These findings add to the studies that cast doubts on the relationship between bottom-up accountability and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
+In this paper, we discuss **whether delivering information to citizens via** a
+mobile phone application fosters ~~grassroots mobilisation~~ **community
+oversight** and political accountability in Brazil. Our two interventions show
+that the results are at best mixed. Although we find ~~an~~ **some treatment**
+effect on school construction completion and cancelling rates in the first
+intervention, the app has no consistent impact on our outcomes of interest.
+These findings add to the studies that cast doubts on the relationship between
+bottom-up accountability and local policy performance [e.g.,
+@banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
 
-What factors, then, are driving these results?
-It seems unlikely that the null results derive from flaws in the research design.
-First, our study is well powered.
-Although the treatment is indirect, meaning that the person has to download the app, find a school construction, and then report it, we included a substantial number of schools in the treatment groups.
-Second, balance and manipulation tests indicate that the treatment allocation was successful, so we can rule out problems in the randomisation procedures.
-Third, after doing a series of robustness tests, we still find no firm evidence of treatment effect.
-Finally, note that the sign of the coefficients are frequently contrary to our theoretical expectations.
-This rules out a possible concern about statistical power with our small control group approach.
+What factors, then, are driving these results? It seems unlikely that the null
+results derive from flaws in the research design. First, our study is well
+powered. Although the treatment is indirect---the person has to download the
+app, find a school construction, and then report it---,we included
+a substantial number of schools in the treatment groups. Second, balance and
+manipulation tests indicate that the treatment allocation was successful, so we
+can rule out problems in the randomisation procedures. **Third, data from
+Google Analytics confirm that citizens did use the app and provided information
+to our dataset. This indicates that the treatment manipulation was effective.
+In this sense, it is unlikely that our results derive from low user response.**
+Fourth, after doing a series of robustness tests, we still find no firm
+evidence of treatment effect. Finally, note that the sign of the coefficients
+are frequently contrary to our theoretical expectations. This rules out
+a possible concern about statistical power with our small control group
+approach.
 
-A plausible explanation is that individuals were unable to differentiate the effect of political corruption from those of spending cuts.
-Due to the severe economic crisis in 2014--2016, the Brazilian federal government introduced discretionary spending limits that affected public investment [@mello2016fix; @rossi2016impactos].
-Politicians may argue that delays in school constructions are not derived from their misuse of government funds, but from the austerity measures.
-If this is the case, citizens will not blame local politicians for the underprovision of public goods.
-Consequently, representatives can dismiss individual requests as the issue is unlikely to escalate.
+**We discuss some possible reasons why community monitoring did not work in our
+case**. ~~A~~ **One** plausible explanation is that individuals were unable to
+differentiate the effect of political corruption from those of spending cuts.
+Due to the severe economic crisis in 2014--2016, the Brazilian federal
+government introduced discretionary spending limits that affected public
+investment [@mello2016fix; @rossi2016impactos]. Politicians may argue that
+delays in school constructions are not derived from their misuse of government
+funds, but from the austerity measures. If this is the case, citizens will not
+blame local politicians for the underprovision of public goods. Consequently,
+representatives can dismiss individual requests as the issue is unlikely to
+escalate.
 
-Moreover, it is possible that a mobile app like TDP is simply not sufficient to promote collective action.
-@raffler2018weakness [29] point out several reasons why information interventions does not lead to higher pressure on public agents, such as citizens' apathy towards their ability to make public agents accountable, lack of official channels to support popular demands, or that constituents have more pressing needs than monitoring representatives.
-Furthermore, individuals may also believe they are better off by free-riding on other users of the TDP app, thus reaping the benefits of having faster school constructions without incurring personal costs [@olson1965logic].
+**The electoral cycle might have decreased the potential effect of the treatment,
+too. As the experiment was fielded right after Brazil's municipal elections,
+incumbents might have disregarded the requests because they did not see the
+demands as politically costly in the short run. Having just taken office,
+mayors might have focused their attention to the formation of government
+coalitions or to budget concerns. **
 
-In sum, our experiments suggest that popular participation and bottom-up monitoring may not be effective to improve public service delivery in the case of school constructions in Brazil.
-Nevertheless, the null findings are informative to researchers and policy-makers.
-The most important recommendation derived from this study is that interventions targeting elite groups, such as lobbyists or civil servants, might render better policy outcomes than those focused at the grassroots levels.
-Another core lesson is that although digital interventions are promising means to deliver information, perhaps they do not have the same impact as personal, face-to-face communication.
-Since many developing countries share Brazil's issues with education provision, the shortcomings we describe here serve as warnings for future interventions.
-Finally, whether this study generalises beyond school constructions to other bottom-up programs, and to other contexts, remains to be studied.
+~~Moreover, it is possible that a mobile app like TDP is simply not sufficient
+to promote collective action. @raffler2018weakness [29] point out several
+reasons why information interventions does not lead to higher pressure on
+public agents, such as citizens' apathy towards their ability to make public
+agents accountable, lack of official channels to support popular demands, or
+that constituents have more pressing needs than monitoring representatives.
+Furthermore, individuals may also believe they are better off by free-riding on
+other users of the TDP app, thus reaping the benefits of having faster school
+constructions without incurring personal costs [@olson1965logic].~~
+
+In sum, our experiments suggest that popular participation and bottom-up
+monitoring may not be effective to improve public service delivery in the case
+of school constructions in Brazil. Nevertheless, the null findings are
+informative to researchers and policy-makers. The most important recommendation
+derived from this study is that interventions targeting elite groups, such as
+lobbyists or civil servants, might render better policy outcomes than those
+focused at the grassroots levels. Another core lesson is that although digital
+interventions are promising means to deliver information, perhaps they do not
+have the same impact as personal, face-to-face communication. Since many
+developing countries share Brazil's issues with education provision, the
+shortcomings we describe here serve as warnings for future interventions.
+Finally, whether this study generalises beyond school constructions to other
+bottom-up programs, and to other contexts, remains to be studied.
 

### 2019-12-15 article/letter.Rmd
changes in formatting, a few edits to text

@@
     fig_caption: yes
-    number_sections: yes
+    number_sections: no
     keep_tex: no
@@
 Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns.
-We explain the precautions we have taken to ensure that the we correctly identify the effect of the TDP app on school outcomes.
+We explain the precautions we have taken to ensure that we correctly identify the effect of the TDP app on school outcomes.
 Second, we provide a thorough discussion of our additional data sources.
@@
 
-Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.We believe our paper now reflects our results more accurately.
+Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.
+We believe our paper now reflects our results more accurately.
 
@@
 \newpage
+
+# Editor Comments and Responses
+
+**1)** The editor writes:
+
+\noindent 
+**Response:**
+
+\begin{quotation}
+Lorem ipsum.
+\end{quotation}
+
+\newpage
+
+# Reviewer 1 Comments and Responses
+
+**1)** Reviewer 1 writes:
+
+\noindent
+**Response:**
+
+\newpage
 \setlength{\parindent}{0cm}

### 2019-12-17 article/article.Rmd
add revisions

@@
 load("tdp.RData")
+
+# Disable scientific notation
+options(scipen = 999)
 ```
@@
 downloads in the 
-`r length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment']))`
-municipalities in the treatment condition. Downloads peak during the Facebook
-TDP campaign, launched in October 2017, then diminish in the following months.
+`r format(length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment'])),
+big.mark = ",")` municipalities in the treatment condition. Downloads peak
+during the Facebook TDP campaign, launched in October 2017, then diminish in
+the following months. **Overall, 
+`r format(sum(ga$novos_usuarios[ga$phase1==1]), big.mark = ",")` users
+downloaded the app in phase one.**
 
@@
 `r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
-`r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units. We
-used blocked randomisation stratified by Brazilian states, school construction
-status (under construction, stopped, unfinished), and whether the municipality
-spent more on school construction that the distribution median. Finally, the
-intervention period lasted from August 2018 to February 2019.
+`r format(as.numeric(table(impact_evaluation_phase2$treat)[2]), big.mark = ",",
+scientific = FALSE)` treatment units. We used blocked randomisation stratified
+by Brazilian states, school construction status (under construction, stopped,
+unfinished), and whether the municipality spent more on school construction
+that the distribution median. Finally, the intervention period lasted from
+August 2018 to February 2019.
 
@@
 downloaded the app. There is about 1,000 user downloads in August 2018, right
-after intervention 2 starts, and a second spike around December. The number of
-downloads is smaller in this second intervention as there was no associated
-social media campaign in that period.
+after intervention 2 starts, and a second spike around December. 
+**The app gained 
+`r format(sum(ga$novos_usuarios[ga$phase1==0]), big.mark = ",")` new users
+during intervention 2. The number of downloads is smaller in this second
+intervention as there was no associated social media campaign in that period.**
 
@@
 
-**(Short paragraph on whether the app has worked)**
+**Data from Google Analytics suggest that users did engage with the TDP app. On
+average, each user launched `r format(round(mean(as.numeric(gsub('\\.', '',
+ga2$visualizacoes_de_tela))), 2), big.mark = ",")` app sessions, which
+indicates their interest in the application. In total, the app had 
+`r format(sum(as.numeric(gsub('\\.', '', ga2$visualizacoes_de_tela))),
+big.mark = ",", scientific = F)` screen visualisations, with an average of 
+`r round(mean(as.numeric(gsub(',', '.', ga2$telas_sessao))), 2)` screen
+visualisations per session.**
 
@@
 
-**The electoral cycle might have decreased the potential effect of the treatment,
-too. As the experiment was fielded right after Brazil's municipal elections,
-incumbents might have disregarded the requests because they did not see the
-demands as politically costly in the short run. Having just taken office,
-mayors might have focused their attention to the formation of government
-coalitions or to budget concerns. **
-
-~~Moreover, it is possible that a mobile app like TDP is simply not sufficient
-to promote collective action. @raffler2018weakness [29] point out several
-reasons why information interventions does not lead to higher pressure on
-public agents, such as citizens' apathy towards their ability to make public
-agents accountable, lack of official channels to support popular demands, or
-that constituents have more pressing needs than monitoring representatives.
-Furthermore, individuals may also believe they are better off by free-riding on
-other users of the TDP app, thus reaping the benefits of having faster school
-constructions without incurring personal costs [@olson1965logic].~~
+**The electoral cycle might also have decreased the potential effect of the
+treatment. As the experiment was fielded right after Brazil's municipal
+elections, incumbents might have disregarded the requests because they did not
+see the demands as politically costly in the short run. Having just taken
+office, mayors might have focused their attention to the formation of
+government coalitions or to budget concerns. Future research may evaluate how
+electoral dynamics interact with citizen oversight, potentially by replicating
+informational experiments in different stages of the political cycle.**
+
+\sout{Moreover, it is possible that a mobile app like TDP is simply not
+sufficient to promote collective action. Raffler et al (2018, 29) point
+out several reasons why information interventions does not lead to higher
+pressure on public agents, such as citizens' apathy towards their ability to
+make public agents accountable, lack of official channels to support popular
+demands, or that constituents have more pressing needs than monitoring
+representatives. Furthermore, individuals may also believe they are better off
+by free-riding on other users of the TDP app, thus reaping the benefits of
+having faster school constructions without incurring personal costs (Olson
+1965).}
 

### 2019-12-19 appendix/appendix.Rmd
revision main text

@@
 Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
-abstract: "Does grassroots participation improve public service delivery?
-We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1020 Brazilian municipalities.
+abstract: "Does local oversight improve public service delivery?
+We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
 The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
-Our results show that the app has a null impact on the school construction outcomes.
+Our results show that the app has a null impact on the school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.

### 2019-12-19 article/article.Rmd
revision main text

@@
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
-The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
-Our results show that the app has a null impact on the school construction indicators.
+~~The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.~~ **The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.** Our results show that the app has a null impact on the school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
-The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
+The results question the impact of ~~local~~ **bottom-up** monitoring on public service performance and suggest that interventions targeted ~~at other groups~~ **to other groups, or focusing on different issues,** may produce better policy outcomes."
 abstractspacing: double
@@
 
-However, accountability systems **may** take many forms. One promising model is
-that of _bottom-up monitoring_, in which citizens receive information about the
-shortcomings of a given project so they can evaluate and pressure
-underperforming public officials [@kosack2014does; @molina2016community;
-@raffler2018weakness]. Proponents argue that bottom-up accountability is
-effective because: 1) constituents have first-hand information about the
-outcomes of local policies; 2) citizens have incentives to attack corruption
-that directly affects themselves; 3) policy-makers are sensitive to social
-punishment from their own communities [@serra2011combining, 570]. In this
-regard, bottom-up accountability offers a potential solution to the
-principal-agent dilemma in public service by aligning the interests of state
-officials with those of the constituency they serve [@barro1973control;
-@raffler2018weakness, 2].
+However, accountability ~~systems take many forms~~ **mechanisms extend beyond
+elections.** One promising model is that of _bottom-up monitoring_, in which
+citizens receive information about the shortcomings of a given project so they
+can evaluate and pressure underperforming public officials [@kosack2014does;
+@molina2016community; @raffler2018weakness]. Proponents argue that bottom-up
+accountability is effective because: 1) constituents have first-hand
+information about the outcomes of local policies; 2) citizens have incentives
+to attack corruption that directly affects themselves; 3) policy-makers are
+sensitive to social punishment from their own communities [@serra2011combining,
+570]. In this regard, bottom-up accountability offers a potential solution to
+the principal-agent dilemma in public service by aligning the interests of
+state officials with those of the constituency they serve [@barro1973control;
+@raffler2018weakness].
 
@@
 impact~~ **the impact of citizen oversight** on five outcomes related to school
-completion rates and complaints to public authorities. Overall, our results
-show that providing information to citizens has no consistent impact on policy
-outcomes. In the first experiment, we find that the TDP app increased the
-likelihood of construction cancellation by 2 percent, but the result does not
-replicate. The remaining five models have null results. In our second
+completion rates and complaints to public authorities. Overall, ~~our results
+show that~~ providing information to citizens has no consistent impact on
+policy outcomes. In the first experiment, we find that the TDP app increased
+the likelihood of construction cancellation by 2 percent, but the result does
+not replicate. The remaining five models have null results. In our second
 intervention, none of the estimations reach conventional levels of statistical
@@
 representatives accountable using bottom-up ~~strategies~~ **monitoring**. 
-Although studies like @bjorkman2009power, @fiala2017social, and
-@reinikka2005fighting report better policy outcomes after providing information
-to local communities, our findings are closer to @banerjee2010pitfalls,
-@keefer2014mass, @lieberman2014does, @bjorkman2017experimental,
-@olken2007monitoring, and @raffler2018weakness, offering little evidence that
-information-based interventions lead to greater government responsiveness. Our
-analysis suggests that grassroots monitoring is ineffective in altering
-government behaviour in Brazil.
+\sout{Although studies like} **On the one hand,** @bjorkman2009power,
+@lagunes2018guardians, and @reinikka2005fighting report better policy outcomes
+after providing information to local communities. ~~our findings are closer
+to~~ **On the other hand,** @banerjee2010pitfalls, @keefer2014mass,
+@lieberman2014does, @bjorkman2017experimental, @olken2007monitoring, and
+@raffler2018weakness, find little evidence that information-based interventions
+lead to greater government responsiveness. **Our results are in line with the
+latter group and suggest that local oversight is ineffective in altering
+government behaviour in Brazil.**
 
@@
 schedule, TDP provides a writing platform whereby citizens can report to public
-officials quickly and anonymously. The app then prompts citizens to write
-a notification to the mayor's office, which has 15 days to reply. If they do
-not respond to the request, the app forwards the notification to the Brazilian
-Ministry of Education, making it harder for the municipality to access federal
-funds in the future. The motivation behind this intervention is that providing
-information to citizens empowers individuals to closely monitor public works.
-This, in turn, results in better social outcomes as public agents become more
-responsive to community demands.
+officials quickly and anonymously. The app then writes a notification to the
+mayor's office, which has 15 days to reply. If they do not respond to the
+request, the app forwards the notification to the Brazilian Ministry of
+Education, making it harder for the municipality to access federal funds in the
+future. The motivation behind this intervention is that providing information
+to citizens empowers individuals to closely monitor public works. This, in
+turn, results in better social outcomes as public agents become more responsive
+to community demands.
 
@@
 
-Between August 2017 and February 2019, we implemented two interventions to
-measure the effect of the TDP app on five school construction outcomes plus
-a placebo test. The outcomes are: 1) a placebo outcome indicating the
-percentage of the project completed before the impact evaluation started; 2)
-the percentage of the project completed by the end of the interventions; 3) the
-difference between the percentage reported as completed before and after the
+Between August 2017 and July 2019, we implemented two interventions to measure
+the effect of the TDP app on five school construction outcomes plus a placebo
+test. The outcomes are: 1) a placebo outcome indicating the percentage of the
+project completed before the impact evaluation started; 2) the percentage of
+the project completed by the end of the interventions; 3) the difference
+between the percentage reported as completed before and after the
 interventions; 4) the number of finished constructions; 5) the number of
 cancelled constructions; 6) the number of schools where construction companies
-updated the conclusion dates. In terms of expectations, Table
+updated the conclusion dates. ~~In terms of expectations,~~ Table
 \ref{tab:outcomes} depicts the expected effects for each of the studied
@@
 
-The first intervention was carried out from August 2017 to February 2018 using
-the Android version of TDP. The randomization was conduct at the municipal
-level. We randomly selected 
-`r as.numeric(table(impact_evaluation_phase1$treat)[1])` municipalities to the
-control group and included 
-`r as.numeric(table(impact_evaluation_phase1$treat)[2])` in the treatment
-group. Our control condition consists in removing all information about school
-construction from the TDP app in the chosen municipalities, so that citizens
-were unable to report constructions in the control municipalities.
+The first intervention was carried out from August 2017 to July 2018 using the
+Android version of TDP. The randomization was conduct at the municipal level.
+We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])`
+municipalities to the control group and included `r
+format(as.numeric(table(impact_evaluation_phase1$treat)[2]), big.mark = ",")`
+in the treatment group. Our control condition consists in removing all
+information about school construction from the TDP app in the chosen
+municipalities, so that citizens were unable to report constructions in the
+control municipalities.
 
@@
 `r format(sum(ga$novos_usuarios[ga$phase1==1]), big.mark = ",")` users
-downloaded the app in phase one.**
-
-\vspace{.5cm}
-
-```{r man1, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.5, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
-The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
+downloaded the app during intervention 1.**
+
+```{r man1, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to July 2018.'}
 
@@
 plot_downloads_int1 <- ggplot() +
-  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.001) +
   scale_fill_manual(values = c("#E69F00", "#0072B2", "#F0E442")) +
@@
 
-\newpage
 The second intervention is similar to intervention 1 in all but three
@@
 that the distribution median. Finally, the intervention period lasted from
-August 2018 to February 2019.
+August 2018 to July 2019.
 
@@
 
-```{r man2, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.5, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
-The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
+```{r man2, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2.
+The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to July 2019.'}
 # Load data
@@
 p1 <- ggplot() +
-  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.001) +
   scale_fill_manual(values = c("#E69F00", "#0072B2", "#F0E442")) +
@@
 better social policies~~ **put citizens in a position where they can monitor
-state agents and improve provider behaviour** [@raffler2018weakness, 2] . Our
+state agents and improve provider behaviour** [@raffler2018weakness]. Our
 results do not lend support to that hypothesis.
@@
 that the results are at best mixed. Although we find ~~an~~ **some treatment**
-effect on school construction completion and cancelling rates in the first
-intervention, the app has no consistent impact on our outcomes of interest.
-These findings add to the studies that cast doubts on the relationship between
-bottom-up accountability and local policy performance [e.g.,
-@banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
+effect on school cancelling rates in the first intervention, the app has no
+consistent impact on our outcomes of interest. These findings add to the
+studies that cast doubts on the relationship between bottom-up accountability
+and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does;
+@raffler2018weakness].
 
@@
 derived from this study is that interventions targeting elite groups, such as
-lobbyists or civil servants, might render better policy outcomes than those
-focused at the grassroots levels. Another core lesson is that although digital
-interventions are promising means to deliver information, perhaps they do not
-have the same impact as personal, face-to-face communication. Since many
-developing countries share Brazil's issues with education provision, the
-shortcomings we describe here serve as warnings for future interventions.
-Finally, whether this study generalises beyond school constructions to other
-bottom-up programs, and to other contexts, remains to be studied.
+lobbyists or civil servants, might render better ~~policy~~ **school
+construction** outcomes than those focused at the ~~grassroots levels~~
+**community level**. Another core lesson is that although digital interventions
+are promising means to deliver information, perhaps they do not have the same
+impact as personal, face-to-face communication. Since many developing countries
+share Brazil's issues with education provision, the shortcomings we describe
+here serve as warnings for future interventions. Finally, whether this study
+generalises beyond school constructions to other bottom-up programs, and to
+other contexts, remains to be studied.
 

### 2019-12-19 article/letter.Rmd
revision main text

@@
 
-\noindent 2 December 2019
+\noindent 17 December 2019
 
@@
 
-\noindent We would like to thank you for the opportunity to revise our manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144).
-We have made many revisions to the paper along the lines suggested by the editor and the anonymous reviewer and we believe the manuscript has improved significantly as a result.
+\noindent We would like to thank you for the opportunity to revise our
+manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence
+from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144). We have made
+many revisions to the paper along the lines suggested by the editor and the
+anonymous reviewer and we believe the manuscript has improved significantly as
+a result.
 
-We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer.
-Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns.
-We explain the precautions we have taken to ensure that we correctly identify the effect of the TDP app on school outcomes.
-Second, we provide a thorough discussion of our additional data sources.
-More specifically, we show how the Brazilian Ministry of Education collects and publicises their data and indicate how our experiment uses that information to evaluate the robustness of our findings.
-We believe the new sections help give the results a clearer interpretation and strenghten our main arguments.
+We have worked specially hard to clarify the connection between information
+provision and mobilisation, a point emphasised by both the editor and the
+reviewer. Our efforts in that regard include, first, a new section in the SI
+Appendix with a detailed description of _Tá de Pé_'s functionalities and the
+associated Facebook campaigns. We explain the precautions we have taken to
+ensure that we correctly identify the effect of the TDP app on school outcomes.
+Second, we provide a thorough discussion of our additional data sources. More
+specifically, we show how the Brazilian Ministry of Education collects and
+publicises their data and indicate how our experiment uses that information to
+evaluate the robustness of our findings. We believe the new sections help give
+the results a clearer interpretation and strenghten our main arguments.
 
-Related, we have included a discussion regarding app usage as suggested by the reviewer.
-We have included information provided by Google Analytics not only on app downloads but also on app usage, which addresses another important concern raised by the reviewer.
-The data show that the app usage was significant, yet it was not enough to trigger any responses from local governments.
+Related, we have included a discussion regarding app usage as suggested by the
+reviewer. We have included information provided by Google Analytics not only on
+app downloads but also on app usage, which addresses another important concern
+raised by the reviewer. The data show that the app usage was significant, yet
+it was not enough to trigger any responses from local governments.
 
-Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.
-We believe our paper now reflects our results more accurately.
+Lastly, we have rewritten some parts of the main text to highlight that our
+experiment hinges on participation only, and that the effect of mobilisation
+and pressure on school construction outcomes require further analyses. We
+believe our paper now reflects our results more accurately.
 
-Below we discuss in more detail these and other changes we have made to the manuscript in response to comments from the editor and the reviewer.
-We thank the editor again for the opportunity to revise the manuscript, and the reviewer for his/her extremely helpful comments.
+Below we discuss in more detail these and other changes we have made to the
+manuscript in response to comments from the editor and the reviewer. We thank
+the editor again for the opportunity to revise the manuscript, and the reviewer
+for his/her extremely helpful comments.
 
-\vspace{.5cm}
+\vspace{.5cm} \noindent Sincerely,
 
-\noindent Sincerely,
-
-\vspace{.5cm}
-
-\noindent The Authors
+\vspace{.5cm} \noindent The Authors
 
@@
 
-**1)** The editor writes:
+**1)** The editor writes: "_The reviewer confirmed my own sense that the
+manuscript and underlying field experiment are interesting, although you will
+see that the reviewer suggests many ways the manuscript can be improved.  I am
+in full agreement with the reviewer that you need to reflect more deeply about
+the theory and evidence for why information provision via the app could be
+connected to mobilization, -- otherwise the null result is not interesting.  As
+the reviewer notes, the null result could be due to a disconnect between
+information provision and action, or due to who selects into downloading the
+app._"
 
-\noindent 
-**Response:**
+\vspace{.5cm} \noindent \textbf{Response:}
 
 \begin{quotation}
-Lorem ipsum.
+We agree with the editor and the reviewer in regards to the link between
+information provision and mobilisation. We believe the main issue lies in the
+lack of evidence for mobilisation, that is, information on how users interacted
+with the application and whether they have used the app consistently. In the
+revised version of the manuscript, we provide data from Google Analytics which
+indicate that users did engage with the app. According to the service, the app
+had 6,092 active users in intervention 1 and gained 4,078 new users during
+intervention 2. On average, each user launched 60 sessions per app install, an
+indication of their actual engagement with the application. Moreover, the data
+also show that the app had more than 53,000 screen visualisations, with an
+average of 2.42 visualisations per user. We have added this information to the
+main text and the online appendix. The additions are marked in \textbf{boldface}.
+We elaborate further on this issue in the response to Reviewer 1 below.
 \end{quotation}
-
-\newpage
 
@@
 
-**1)** Reviewer 1 writes:
+**1)** Reviewer 1 writes: "_My biggest concern is there is no discussion of the
+actual bottom-up accountability that may (or may not) have occurred. [...] The
+authors have devised a nice experiment and I believe their design to have been
+appropriately administrated. But the design hinges on several critical
+mechanisms that go largely undiscussed: not only must information be available
+to citizens such that they might participate in local oversight, but said
+citizens must 1) access the information and 2) act on said information. This is
+mentioned in the Discussion---that perhaps the app was insufficient to spur
+collective action---but that also seems like an empirical question the authors
+could feasibly address. [...] Once people downloaded the App, did they use
+it?_"
 
-\noindent
-**Response:**
+\vspace{.5cm} \noindent \textbf{Response:}
+
+\begin{quotation}
+This first point raised by the reviewer is connected to the response we have
+provided above. We have made several changes to the main paper and the appendix
+to address this important concern. First, we have added a the following section
+to the appendix in order to clarify how the TDP app works:
+
+\vspace{.5cm}
+
+3. Treatment Definition and Mechanism
+
+The \textit{Tá de Pé} app
+
+1. Users download the app
+2. Use the app and report the schools to the mayors' office
+3. Our team took the reported schools and started implementing the pressure
+on the mayors' office.
+4. Should the pressure have work, we would witness improvements on governmental
+	 data regarding the school construction progress.
+
+For the step (4), we relied on monthly issued administrative data by the
+Brazilian Ministry of Education. The Ministry of Education provides monthly
+data on the school constructions that are being build with Federal resources,
+and that are delayed across the country. To compute the delay we use the
+finishing dates reported by the municipality at the time they sign the
+agreement with the Federal Government. This data helped us to keep the App
+updated and the outcomes in the paper are selected to be six months before
+(pre-treatment) and after the intervention. This data was constantly updated by
+the Ministry of Education, and we found no red flags in the overall quality of
+the data.
+
+Therefore, steps (1), (3), and (4) were standardized to not vary across the
+country. The only source of variation in our intervention should come from step
+(2).
+
+In step (2), we applied the treatment by removing schools within municipalities
+out of the app. In the first intervention, that happened at the municipal
+level, we excluded all schools within a given randomly selected municipality.
+In the second intervention, we excluded randomly selected schools out of the
+App. Removing a school means that the school was in the dataset provided by the
+Brazilian Ministry of Education, but it did not show up in the App. Therefore,
+our treatment effect represents the school being present (treatment) or absent
+(control) in the App.
+
+In terms of what this represents, we argue that the App is promoting two
+crucial features for bottom-up accountability: first, it is facilitating people
+to connect with information that would be otherwise be in an obscure
+spreadsheet at the Ministry of Education website; second, whenever people find
+this information troublesome, we are providing an easy way to them to act upon
+the information. As the design was intuitive and straightforward, we believe
+that most of Brazilians would find it easy to use the App.
+
+Moreover, the treatment to be successful does not require that everyone in the
+municipality uses the App. Clearly that more usage means more pictures and
+denounces, and this represents more pressure over the mayors office, what could
+revert into a higher effect. However, just one denounce would be enough, as it
+can be directed to the Brazilian General Comptroller (CGU), and this could
+potentially deny future funding to the municipality.
+
+\end{quotation}
 

### 2019-12-19 article/letter.tex
revision main text

--- 2019-12-19 article/letter.Rmd
@@
----
-title:
-author:
-date:
-fontsize: 12pt
-margin: 2cm
-urlcolor: darkblue
-linkcolor: Mahogany
-citecolor: Mahogany
-spacing: double
-papersize: a4paper
-bibliography: references.bib
-biblio-style: apalike
-output:
-  pdf_document:
-    citation_package: natbib
-    fig_caption: yes
-    number_sections: no
-    keep_tex: no
-    toc: no
-    toc_depth: 3
-    template: article-template.latex
----
+% !TEX program = XeLaTeX
+\documentclass[12pt,a4paper,]{article}
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
-# If you need to install any package while knitting the document
-r <- getOption("repos")
-r["CRAN"] <- "https://cran.rstudio.com/"
-options(repos = r)
-if (!require("kableExtra")) {
-    install.packages("kableExtra")
+% Fonts
+\usepackage{libertine}
+% This is a nice mathfont, it fits well with Libertine
+% Comment the line if you want to use a different one
+\usepackage[libertine]{newtxmath}
+% The default monofont 
+% Again, comment the line below if you want to change it
+\usepackage[scaled=.95]{inconsolata}
+
+% Add the following packages to support kableExtra
+\usepackage[normalem]{ulem}
+\usepackage{array}
+\usepackage{booktabs}
+\usepackage{colortbl}
+\usepackage{etoolbox}
+\usepackage{longtable}
+\usepackage{makecell}
+\usepackage{multirow}
+\usepackage{pdflscape}
+\usepackage{subcaption}
+\usepackage{tabu}
+\usepackage{threeparttablex}
+\usepackage{threeparttable}
+\usepackage{tocloft}
+\usepackage{wrapfig}
+
+% Dots in toc
+\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
+
+% Colours
+\usepackage[usenames,dvipsnames]{xcolor}
+\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
+
+% Spacing
+\usepackage{setspace}
+
+% Margin
+\usepackage[margin=2cm]{geometry}
+
+% Packages I've been using for different reasons...
+\usepackage{hyperref}
+\usepackage{dcolumn}
+\usepackage{graphicx}
+\usepackage{float}
+\floatplacement{figure}{H}
+\usepackage{pgf}
+\usepackage{mathtools}
+\usepackage{caption}
+
+% UK English
+\usepackage[UKenglish]{babel}
+\usepackage[UKenglish]{isodate}
+\cleanlookdateon
+
+% Penalties
+\exhyphenpenalty=1000
+\hyphenpenalty=1000
+\widowpenalty=1000
+\clubpenalty=1000
+
+% Hypersetup
+\hypersetup{
+  linkcolor=Mahogany,
+  citecolor=Mahogany,
+  urlcolor=darkblue, 
+  breaklinks=true, 
+  colorlinks=true,
       }
-```
 
-\noindent Research & Politics
+% If XeTex, LuaLaTeX, etc
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{amssymb,amsmath}
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+
+% Language
+
+% Bibliography
+\usepackage{natbib}
+\bibliographystyle{apalike}
+\makeatletter
+% Remove comma after author
+\setcitestyle{aysep={}}
+\patchcmd{\NAT@citex}
+	  {\@citea\NAT@hyper@{%
+		 \NAT@nmfmt{\NAT@nm}%
+		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+		 \NAT@date}}
+	  {\@citea\NAT@nmfmt{\NAT@nm}%
+	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+	\patchcmd{\NAT@citex}
+	  {\@citea\NAT@hyper@{%
+		 \NAT@nmfmt{\NAT@nm}%
+		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+		   {\@citeb\@extra@b@citeb}%
+		 \NAT@date}}
+	  {\@citea\NAT@nmfmt{\NAT@nm}%
+	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+	  {}{}
+% Patch case where name and year are separated by aysep
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+% Patch case where name and year are separated by opening bracket
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+       {\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+  {}{}
+\makeatother
+
+% Listings
+
+% Verbatim
+
+% Tables
+
+% Graphics
+
+% Make links footnotes instead of hotlinks:
+%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
+ \providecommand{\tightlist}{%
+   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% Numbered sections
+\setcounter{secnumdepth}{0}
+% % % Redefines (sub)paragraphs to behave more like sections
+% \ifx\paragraph\undefined\else
+% \let\oldparagraph\paragraph
+% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+% \fi
+% \ifx\subparagraph\undefined\else
+% \let\oldsubparagraph\subparagraph
+% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+% \fi
+% 
+% Spacing
+\doublespacing
+
+% Title
+
+% Author
+
+% Date
+\date{}
+
+% Begin document
+\begin{document}
+
+% Abstract
+
+% Table of Contents
+\noindent Research \& Politics
 
@@
 \noindent We would like to thank you for the opportunity to revise our
-manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence
-from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144). We have made
-many revisions to the paper along the lines suggested by the editor and the
-anonymous reviewer and we believe the manuscript has improved significantly as
-a result.
+manuscript, ``Bottom-Up Accountability and Public Service Provision:
+Evidence from a Field Experiment in Brazil'' (Manuscript ID
+RAP-19-0144). We have made many revisions to the paper along the lines
+suggested by the editor and the anonymous reviewer and we believe the
+manuscript has improved significantly as a result.
 
-We have worked specially hard to clarify the connection between information
-provision and mobilisation, a point emphasised by both the editor and the
-reviewer. Our efforts in that regard include, first, a new section in the SI
-Appendix with a detailed description of _Tá de Pé_'s functionalities and the
-associated Facebook campaigns. We explain the precautions we have taken to
-ensure that we correctly identify the effect of the TDP app on school outcomes.
-Second, we provide a thorough discussion of our additional data sources. More
-specifically, we show how the Brazilian Ministry of Education collects and
-publicises their data and indicate how our experiment uses that information to
-evaluate the robustness of our findings. We believe the new sections help give
-the results a clearer interpretation and strenghten our main arguments.
+We have worked specially hard to clarify the connection between
+information provision and mobilisation, a point emphasised by both the
+editor and the reviewer. Our efforts in that regard include, first, a
+new section in the SI Appendix with a detailed description of \emph{Tá
+de Pé}'s functionalities and the associated Facebook campaigns. We
+explain the precautions we have taken to ensure that we correctly
+identify the effect of the TDP app on school outcomes. Second, we
+provide a thorough discussion of our additional data sources. More
+specifically, we show how the Brazilian Ministry of Education collects
+and publicises their data and indicate how our experiment uses that
+information to evaluate the robustness of our findings. We believe the
+new sections help give the results a clearer interpretation and
+strenghten our main arguments.
 
-Related, we have included a discussion regarding app usage as suggested by the
-reviewer. We have included information provided by Google Analytics not only on
-app downloads but also on app usage, which addresses another important concern
-raised by the reviewer. The data show that the app usage was significant, yet
-it was not enough to trigger any responses from local governments.
+Related, we have included a discussion regarding app usage as suggested
+by the reviewer. We have included information provided by Google
+Analytics not only on app downloads but also on app usage, which
+addresses another important concern raised by the reviewer. The data
+show that the app usage was significant, yet it was not enough to
+trigger any responses from local governments.
 
-Lastly, we have rewritten some parts of the main text to highlight that our
-experiment hinges on participation only, and that the effect of mobilisation
-and pressure on school construction outcomes require further analyses. We
-believe our paper now reflects our results more accurately.
+Lastly, we have rewritten some parts of the main text to highlight that
+our experiment hinges on participation only, and that the effect of
+mobilisation and pressure on school construction outcomes require
+further analyses. We believe our paper now reflects our results more
+accurately.
 
-Below we discuss in more detail these and other changes we have made to the
-manuscript in response to comments from the editor and the reviewer. We thank
-the editor again for the opportunity to revise the manuscript, and the reviewer
-for his/her extremely helpful comments.
+Below we discuss in more detail these and other changes we have made to
+the manuscript in response to comments from the editor and the reviewer.
+We thank the editor again for the opportunity to revise the manuscript,
+and the reviewer for his/her extremely helpful comments.
 
-\vspace{.5cm} \noindent Sincerely,
+\vspace{.5cm}
 
-\vspace{.5cm} \noindent The Authors
+\noindent Sincerely,
+
+\vspace{.5cm}
+
+\noindent The Authors
 
@@
 
-# Editor Comments and Responses
+\hypertarget{editor-comments-and-responses}{%
+\section{Editor Comments and
+Responses}\label{editor-comments-and-responses}}
 
-**1)** The editor writes: "_The reviewer confirmed my own sense that the
-manuscript and underlying field experiment are interesting, although you will
-see that the reviewer suggests many ways the manuscript can be improved.  I am
-in full agreement with the reviewer that you need to reflect more deeply about
-the theory and evidence for why information provision via the app could be
-connected to mobilization, -- otherwise the null result is not interesting.  As
-the reviewer notes, the null result could be due to a disconnect between
-information provision and action, or due to who selects into downloading the
-app._"
+\textbf{1)} The editor writes: ``\emph{The reviewer confirmed my own
+sense that the manuscript and underlying field experiment are
+interesting, although you will see that the reviewer suggests many ways
+the manuscript can be improved. I am in full agreement with the reviewer
+that you need to reflect more deeply about the theory and evidence for
+why information provision via the app could be connected to
+mobilization, -- otherwise the null result is not interesting. As the
+reviewer notes, the null result could be due to a disconnect between
+information provision and action, or due to who selects into downloading
+the app.}''
 
-\vspace{.5cm} \noindent \textbf{Response:}
+\vspace{.5cm}
+
+\noindent \textbf{Response:}
 
@@
 
-# Reviewer 1 Comments and Responses
+\hypertarget{reviewer-1-comments-and-responses}{%
+\section{Reviewer 1 Comments and
+Responses}\label{reviewer-1-comments-and-responses}}
 
-**1)** Reviewer 1 writes: "_My biggest concern is there is no discussion of the
-actual bottom-up accountability that may (or may not) have occurred. [...] The
-authors have devised a nice experiment and I believe their design to have been
-appropriately administrated. But the design hinges on several critical
-mechanisms that go largely undiscussed: not only must information be available
-to citizens such that they might participate in local oversight, but said
-citizens must 1) access the information and 2) act on said information. This is
-mentioned in the Discussion---that perhaps the app was insufficient to spur
-collective action---but that also seems like an empirical question the authors
-could feasibly address. [...] Once people downloaded the App, did they use
-it?_"
+\textbf{1)} Reviewer 1 writes: ``\emph{My biggest concern is there is no
+discussion of the actual bottom-up accountability that may (or may not)
+have occurred. {[}\ldots{}{]} The authors have devised a nice experiment
+and I believe their design to have been appropriately administrated. But
+the design hinges on several critical mechanisms that go largely
+undiscussed: not only must information be available to citizens such
+that they might participate in local oversight, but said citizens must
+1) access the information and 2) act on said information. This is
+mentioned in the Discussion---that perhaps the app was insufficient to
+spur collective action---but that also seems like an empirical question
+the authors could feasibly address. {[}\ldots{}{]} Once people
+downloaded the App, did they use it?}''
 
-\vspace{.5cm} \noindent \textbf{Response:}
+\vspace{.5cm}
+
+\noindent \textbf{Response:}
 
@@
 \setlength{\parskip}{5pt}
+
+% More bibliography
+\bibliography{references.bib}
+
+\end{document}

### 2019-12-20 appendix/appendix.Rmd
add appendix

--- 2019-09-03 appendix/appendix.Rmd
@@
 author:
-- "Danilo Freire[^freire]"
-- "Manoel Galdino[^galdino]"
-- "Umberto Mignozzetti[^mignozzetti]"
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog, and David Skarbek for their helpful comments.
-We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance.
-This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education.
-The authors thank the 2016 Google Social Impact Challenge for financial support and declare there are no conflict of interest.
-Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
-abstract: "Does grassroots participation improve public service delivery?
-We study the effect of a mobile phone application that allows citizens to monitor school construction projects in 1020 Brazilian municipalities.
-The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.
-Our results show that the app has a null impact on the school construction outcomes.
+abstract: "Does local oversight improve public service delivery?
+We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
+The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.
+Our results show that the app has a null impact on the school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
-The results question the impact of local monitoring on public service performance and suggest that interventions targeted at other groups may produce better policy outcomes."
+The results question the impact of bottom-up monitoring on public service performance and suggest that interventions targeted to other groups, or focusing on different issues, may produce better policy outcomes."
 abstractspacing: double
@@
     number_sections: yes
-    toc: false
+    toc: true
     keep_tex: no
@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.
-
-[^galdino]: Executive Diretor, Transparência Brazil, São Paulo, SP, Brazil, [mcz.fea@gmail.com](mailto:mcz.fea@gmail.com), <https://www.transparencia.org.br>.
-
-[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, [umberto.mig@nyu.edu](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
-Corresponding author.
-
 \newpage
@@
 
-The tables below show the results of the balance tests for interventions 1 and 2.
-Our list of covariates are: 1) log of municipal population in 2015; 2) log of number of poor families in each city; 3) log of total federal transfers to the municipality in 2016; 4) federal government indicator for primary school quality; 5) federal government indicator for secondary school quality.
+The tables below show the results of the balance tests we conducted for
+interventions 1 and 2. Our list of covariates are:
+
+1. Log of municipal population in 2015; 
+2. Log of number of poor families in each city; 
+3. Log of total federal transfers to the municipality in 2016; 
+4. Federal government indicator for primary school quality; 
+5. Federal government indicator for secondary school quality.
+
 The data come from the Brazilian Ministry of Education and the National Census.
 
-In intervention 1, we randomised the treatment at the municipality level.
-We selected 150 municipalities for the control group while the rest were placed in the treatment group.
-The control group worked by deleting all the construction sites in control assigned cities.
-No difference between control and treatment variables is statistically significant.
-
-```{r balance1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, tidy=TRUE}
+In intervention 1, we randomised the treatment at the municipality level. We
+selected 150 municipalities for the control group while the rest were placed in
+the treatment group. The control group worked by deleting all the construction
+sites in control assigned cities. No difference between control and treatment
+variables is statistically significant.
+
+```{r balance1, echo=TRUE, results='hide', warning=FALSE, message=FALSE, error=FALSE, tidy=TRUE}
 # R options
@@
 # Install required packages
-pkgs <- c('tidyverse', 'dummies', 'kableExtra', 'haven', 'compareGroups',
-          'grid', 'gridExtra', 'devtools', 'lubridate', 'brazilmaps',
-          'abjutils', 'lfe', 'cobalt', 'MatchIt', 'ri2', 'DeclareDesign',
-          'knitr', 'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 'flextable',
-          'officer', 'ggthemes', 'stargazer')
-
-installIfNot <- function(x) {
-  if(x %in% rownames(installed.packages()) == FALSE) 
+pkgs <- c("tidyverse", "dummies", "kableExtra",
+          "haven", "compareGroups", "grid", "gridExtra",
+          "devtools", "lubridate", "brazilmaps",
+          "abjutils", "lfe", "cobalt",
+          "MatchIt", "ri2", "DeclareDesign", "knitr",
+          "DiagrammeR", "DiagrammeRsvg", "rsvg",
+          "flextable", "officer", "ggthemes",
+          "stargazer", "formatR")
+
+# Install required packages
+install_if_not <- function(x) {
+  if (x %in% rownames(installed.packages()) == FALSE)
     install.packages(x, dependencies = T)
 }
-invisible(lapply(pkgs, installIfNot))
-
-# Load packages
-invisible(lapply(pkgs, require, character.only = T)); rm(pkgs, installIfNot)
+lapply(pkgs, install_if_not)
+
+# Load scripts
+lapply(pkgs, require, character.only = T)
+rm(pkgs, install_if_not)
 
 # Load Data
-load('../article/tdp.RData')
-
+load("../article/tdp.RData")
+
+# Disable scientific notation
+options(scipen = 999)
+```
+
+```{r balance1a, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, tidy=TRUE}
 # Covariate Balance -- Intervention 1
@@
 
-tabIE1balance <- createTable(resu1, digits = 2)
-row.names(tabIE1balance$descr) <- c('Log Population (2015)',
-                                    'Log Poor Families (2010)',
-                                    'Log Total Transfers (2016)',
-                                    'IDEB Initial Years (2015)',
-                                    'IDEB Final Years (2015)')
-
-print(tabIE1balance)
+tab_IE1_balance <- createTable(resu1, digits = 2)
+row.names(tab_IE1_balance$descr) <- c("Log Population (2015)",
+                                    "Log Poor Families (2010)",
+                                    "Log Total Transfers (2016)",
+                                    "IDEB Initial Years (2015)",
+                                    "IDEB Final Years (2015)")
+
+print(tab_IE1_balance)
 ```
 
-In intervention 2, we randomised the treatment at the school level.
-We placed 15% of schools that could potentially appear in the App in the control group.
+In intervention 2, we randomised the treatment at the school level. We placed
+15% of schools that could potentially appear in the app in the control group.
 We used block randomization, blocking by three characteristics:
 
-* Brazilian State
-* Construction Status (under construction, stopped, unfinished)
-* School construction completion rates above the national median
+1. Brazilian State
+2. Construction Status (under construction, stopped, unfinished)
+3. School construction completion rates above the national median
 
@@
 
-tabIE2Balance <- createTable(resu1, digits = 2)
-row.names(tabIE2Balance$descr) <-  c('Log Population (2015)', 
-                                     'Log Poor Families (2010)', 
-                                     'Log Total Transfers (2016)', 
-                                     'IDEB Inicial Years (2015)', 
-                                     'IDEB Final Years (2015)')
-print(tabIE2Balance)
+tab_IE2_balance <- createTable(resu1, digits = 2)
+row.names(tab_IE2_balance$descr) <-  c("Log Population (2015)",
+                                     "Log Poor Families (2010)",
+                                     "Log Total Transfers (2016)",
+                                     "IDEB Inicial Years (2015)",
+                                     "IDEB Final Years (2015)")
+print(tab_IE2_balance)
 ```
@@
 \newpage
+
 # Manipulation Checks
 
-In randomised experiments, manipulation is defined as the extent through which the treatment was successfully delivered to the control and treated units.
-In the case of the *Tá de Pé* app intervention, the manipulation indicates whether the app improves school construction completion rates.
-We present two manipulation indicators.
-First, we look into municipalities which did or did not download the app.
-Next, we see the number of app downloads during intervention 1 (February 2017--August 2018) and intervention 2 (August 2018--February 2019).
-The code replicates figures 2 and 3 in the article.
+In randomised experiments, manipulation is defined as the extent through which
+the treatment is successfully delivered to the control and treated units. In
+the case of the *Tá de Pé* app intervention, the manipulation indicates whether
+the app improves school construction completion rates. We present two
+manipulation indicators. First, we look into municipalities which did or did
+not download the app. Next, we see the number of app downloads during
+intervention 1 (February 2017--July 2018) and intervention 2 (August 2018--July
+2019). The code replicates figures 2 and 3 in the article.
 
@@
 # Map manipulation test -- Intervention 1
-mapbr <- get_brmap('City')
+mapbr <- get_brmap("City")
 gaaux <- filter(ga, phase1 == 1)
@@
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 0
+gaaux$downl[is.na(gaaux$downl)] <- 0
 gaaux2 <- data.frame(City = mapbr$City)
 gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
-gaaux$downl[is.na(gaaux$downl)] = 2
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
-                                                  'Not in App'))
-mapbr <- join_data(mapbr, gaaux, by = 'City')
-pMapDownloadsInt1 <- ggplot() + 
-  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
-  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+gaaux$downl[is.na(gaaux$downl)] <- 2
+gaaux$Downloads <- factor(gaaux$downl, labels = c("No Downloads", "Downloads",
+                                                  "Not in App"))
+mapbr <- join_data(mapbr, gaaux, by = "City")
+map_downloads_int1 <- ggplot() +
+  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.001) +
+  scale_fill_manual(values = c("#E69F00", "#0072B2", "#F0E442")) +
   theme_map()
-pMapDownloadsInt1
+map_downloads_int1
 
@@
   summarize(NewUsers = sum(novos_usuarios))
-names(tab) <- c('Date', 'Frequency')
-pFreqUserDownloadsInt1 <- ggplot(tab, aes(x=Date, y=Frequency, group=1)) +
+names(tab) <- c("Date", "Frequency")
+freq_downloads_int1 <- ggplot(tab, aes(x = Date, y = Frequency, group = 1)) +
   geom_line() + geom_point()
-pFreqUserDownloadsInt1
+freq_downloads_int1
 ```
@@
 ## Map manipulation test -- Intervention 2
-mapbr <- get_brmap('City')
+mapbr <- get_brmap("City")
 gaaux <- filter(ga, phase2 == 1)
@@
 gaaux$downl[is.na(gaaux$downl)] = 2
-gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
-                                                  'Not in App'))
-mapbr <- join_data(mapbr, gaaux, by = 'City')
+gaaux$Downloads <- factor(gaaux$downl, labels = c("No Downloads", "Downloads",
+                                                  "Not in App"))
+mapbr <- join_data(mapbr, gaaux, by = "City")
 p1 <- ggplot() +
   geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.01) +
-  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
+  scale_fill_manual(values = c("#E69F00", "#0072B2", "#F0E442")) +
   theme_map()
@@
 
+# Treatment Definition and Mechanism
+
+In this section, we explain in detail how the _Tá de Pé_ app works. The
+treatment involves the following procedures:
+
+1. Users download the app.
+
+2. Users access the app and add new information about school constructions
+	 near to their location.
+
+3. The app sends a message to the mayor's office asking details about the
+	 project. If necessary, the message is also forwarded to other government
+	 oversight institutions such as the city council and the Brazilian Federal
+	 Comptroller. Below, we discuss the cases in which we forwarded the denounce
+	 to the authorities.
+
+4. If the pressure over the mayors has an effect, we expect to witness
+	 improvements on governmental data regarding the school construction
+	 progress.
+
+The treatment is a compounded treatment comprised of steps (2) to (4). To make
+sure that the only source of effect comes from step (2), we took the following
+precautions:
+
+In step (1), we have implemented Facebook campaigns in municipalities that have
+school construction agreements with the Federal government. We did not
+discriminate any municipality in this step, and citizens living in
+municipalities in the treatment and in the control could equally have received
+the banners about the _Tá de Pé_ app. The Facebook campaign was not randomised.
+
+For step (3), we put a team of two data scientists to ensure that upon
+receiving a denounce, the mayor's office, the city council, and the Brazilian
+Federal Comptroller (CGU) would be notified. The decision making funnel was:
+
+3.1. We notified the _Engineers without Borders_ (EWB) about the denounce and
+sent them the user-provided pictures and auxiliary information. They issued a
+report on how much the construction was likely to be delayed.
+
+3.2. After we had the EWB report, we notified the mayor's office in compliance
+with Brazil's Freedom of Information Act. We communicated that a citizen had
+anonymously made a denounce about a school (fully identifying the school
+construction that we were referring to), and that the Engineers Without Borders
+found the construction delayed by a percentage that EWB provided. We submitted
+a request for the mayor's office to provide an explanation on why the
+construction was delayed, and asked for updated statistics on when the
+construction will be finished. According to the FOI law, they had twenty days
+to respond.
+
+3.3. If the response was found insufficient, we forwarded the denounce to
+the city council and to the Brazilian Federal Comptroller (CGU). As the
+denounce goes to these institutions, they can harm mayors by restricting access
+to Federal funds.
+
+3.4. At each stage, a Twitter bot constructed by Transparência Brasil
+(<https://twitter.com/tadepeapp>) reported the reception of a denounce and
+tracked the responses of the mayor, the city council, and the CGU.
+
+In step (4), we relied on administrative data by the Brazilian Ministry of
+Education. The Ministry of Education provides monthly data on school
+constructions build with Federal Government resources and shows how many of
+them are delayed across the country. We use the finishing dates reported by the
+municipality at the time they sign the agreement with the Federal Government as
+our measure of construction delays. This data helped us to keep the app updated
+and the outcomes in the paper are selected to be six months before
+(pre-treatment) and after the intervention. This data was constantly updated by
+the Ministry of Education, and we found no red flags in the overall quality of
+the data.
+
+Therefore, steps (1), (3), and (4) were standardised and do not vary across the
+country. The only source of variation in our intervention should come from step
+(2).
+
+In step (2), we applied the treatment by removing schools within municipalities
+out of the app. In the first intervention, which happened at the municipal
+level, we excluded all schools within a given randomly selected municipality.
+In the second intervention, we excluded randomly selected schools out of the
+app. Removing a school means that the school was in the dataset provided by the
+Brazilian Ministry of Education, but it did not show up in the app. Therefore,
+our treatment effect represents the school being present (treatment) or absent
+(control) in the app.
+
+We argue that the app promotes two crucial features of bottom-up
+accountability. First, it helps people to access information that would
+otherwise be available only in an obscure spreadsheet on the Ministry of
+Education website. Second, whenever people find this information troublesome,
+we are providing an easy way to them to act upon the information. As the _Tá de
+Pé_ design was intuitive and straightforward, we believe that most of
+Brazilians would find it easy to use the app.
+
+Moreover, the success of treatment does not require that everyone in the
+municipality uses it. The more usage means more pictures and denounces, and
+this represents more pressure over the mayors office, what could revert into a
+higher effect. However, just one denounce would be enough for the project to be
+successful, as the denounce can be directed to the Brazilian General
+Comptroller (CGU), and this could potentially deny future funding to the
+municipality.
+
+# Outcome Data Collection
+
+We collect the main outcomes using the data reported by the municipality to the
+Brazilian Ministry of Education. Note that this is the same data as the
+pre-treatment data that we use to feed in the app with delayed schools.
+
+The outcomes used in the paper are:
+
+1. **Percentage of the project completed before the impact evaluation
+	 started**: This is a column in the Ministry of Education dataset. The data
+	 in this column were sampled in the beginning of the intervention.
+
+2. **Percentage of the project reported as completed by the end of the
+	 intervention period**: Another column in the Ministry of Education
+	 dataset. The data  were sampled six months after the intervention.
+
+3. **Difference between the percentage reported as completed before and after
+	 the intervention**: The difference between (1) and (2) above. Note
+	 that according to @gerber2012field, this way to look into outcomes is
+	 positive, as having a pre-treatment covariate that highly predicts the
+	 outcome reduces the variance in the estimator considerably.
+
+4. **Dummy indicator for finished constructions**: The Ministry of Education
+	 dataset has a column with the construction status. We created a dummy to be
+	 one when the construction was reported as finished and zero otherwise. The
+	 data here were sampled six months after the intervention.
+
+5. **Dummy indicator for cancelled constructions**: Similarly, we created a
+	dummy variable from the Ministry of Education dataset indicating when the
+	construction was reported as cancelled. The data here were sampled six months
+	after the intervention.
+
+6. **Number of schools where construction companies updated the conclusion
+	 dates**: Lastly, the Ministry of Education dataset has a column with the
+	 construction estimated completion date. We took the completion dated
+	 reported before and six months after the intervention. If the dates
+	 differed, we coded as one, and zero otherwise.
+
+All these variables come from our manipulation of the Ministry of Education
+data. Collecting the outcomes in this way is superior than the alternative of
+gathering the data ourselves. First, we would not be able to manipulate the
+results and cherry-pick favourable results. Even if they have the best
+intentions, researchers may bias the results just by the choices they make in
+the data collection process. For instance, if we send a RA to collect the data,
+as she knows the app, she could unconsciously have a tendency to over-report
+positive results. This would severely bias our findings and undermine the
+credibility of our experiment. Second, using external data makes the results
+easily reproducible by other researchers. As the Ministry of Education has
+standardised data collection procedures, they greatly simplify and facilitate
+the reproduction of our findings.
+
+# Facebook Tá de Pé Campaign
+
+The app by itself would probably not have had an effect on the responsiveness
+of mayors. To boost usage and publicize the app, Transparência Brasil ran 64
+Facebook campaigns throughout the country. The Facebook campaign concentrates
+the bulk of the investments in the beginning of the intervention. The app
+download data is in the second panel of Figures 2 and 3. For the Facebook
+interaction, we have the following statistics:
+
+1. Impressions
+  - Mean: `r mean(fballt$impressoes)`
+  - Total for all campaigns: `r sum(fballt$impressoes)`
+
+2. App Download link clicks:
+  - Mean: `r mean(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
+  - Total for all campaigns: `r sum(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
+
+As we see from the actual download activity, the people who indeed downloaded
+the app were much fewer than these numbers would suggest.
+
+We have chosen Facebook because the platform offers an easy and cheap method to
+spread information. Moreover, according to the Statista website, Facebook is
+used by 70 million Brazilians (60% of the entire adult population), and the
+demographics largely match the demographics publicised by the Brazilian
+Institute of Geography and Statistics. For instance, see the following
+webpages:
+
+1. [Statista Total Facebook Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
+2. [Statista Total Facebook Users by Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
+
 \newpage
+
 # Main Results
@@
 \newpage
-# Robustness Tests
-
-## Randomisation Inference
-
-We employ randomised inference to estimate to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design.
+
+# Randomisation Inference
+
+We employ randomised inference to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design.
 We fail to reject the null in all but the finished school indicator in experiment 1.
@@
 \newpage
+
 # APSA Experimental Section Standard Report for Experimental Research
@@
 
-**Hypotheses**: The experiment studies how technology facilitates bottom-up and top-down pressure to improve service provision.
-More precisely, we test whether the *Tá de Pé* mobile phone app is able to successfully mobilise citizens to exert pressure on local representatives and civil servants.
-We also test whether bottom-up monitoring of public works improves school construction rates and spending.
-
-\noindent 
-**Background**: Recent studies show that grassroots monitoring improves public service outcomes in developing economies.
-Some of the papers find that bottom-up accountability has a significant impact on public service delivery:
-
-  - Bjorkman, Martina and Jakob Svensson.
-2009.
-“Power to the People: Evidence from a randomized field experiment of a community-based monitoring project in Uganda.” Quarterly Journal of Economics 124(2):735–769.
-  - Bjorkman, Martina and Jakob Svensson.
-2010.
-“When is community-based monitoring effective?
-Evidence from a randomized experiment in primary health in Uganda.” Journal of the European Economic Association 8(2-3):571–581.
-  - Bjorkman Nyqvist, Martina, Damien de Walque and Jakob Svensson.
-2017.
-“Experimental evidence on the long-run impact of community-based monitoring.” American Economic Journal: Applied Economics 9(1):33–69.
-
-However, other authors fail to find positive resuls for the same type of intervention, e.g.:
-
-* Banerjee, A.
-V., Banerji, R., Duflo, E., Glennerster, R., and Khemani, S.
-2010.
-Pitfalls of Participatory Programs: Evidence from a Randomized Evaluation in Education in India.
-American Economic Journal: Economic Policy, 2(1):1–30.
-* Lieberman, E. S., Posner, D. N., and Tsai, L. L. 2014. Does Information Lead to More Active Citizenship? Evidence from an Education Intervention in Rural Kenya. World Development, 60:69–83.
-* Raffler, Pia, Dan Posner, and Doug Parkerson.
-2019.
-The Weakness of Bottom-up Accountability: Experimental evidence from the Ugandan health sector.
-URL: [`https://bit.ly/2L36vzI`](http://egap.org/sites/default/files/Posner%2C%20Dan_Paper.pdf)
-
-This project reevaluates this theoretical controversy and proposes a new field experiment to test whether bottom-up accountability is effective to promote better policy outcomes.
-The results are substantively important as well.
-First, we conduct this experiment in a middle-income country, Brazil, but which has municipalities whose social indicators match both those of developed and developing nations.
-Brazil is notably unequal in several characteristics, thus allowing us to infer results for different subgroups if required.
-Second, we are evaluating school constructions, and the presence of schools have essential consequences in terms of long-run economic development, the household income composition, and woman empowerment.
+**Hypotheses**: The experiment studies how technology facilitates bottom-up and
+top-down pressure to improve service provision. More precisely, we test whether
+the *Tá de Pé* mobile phone app is able to successfully mobilise citizens to
+exert pressure on local representatives and civil servants. We also test
+whether bottom-up monitoring of public works improves school construction rates
+and spending.
+
+\noindent **Background**: Recent studies show that community monitoring
+improves public service outcomes in developing economies. Some of the papers
+find that bottom-up accountability has a significant impact on public service
+delivery:
+
+	- Bjorkman, Martina and Jakob Svensson. 2009. “Power to the People: Evidence
+		from a Randomized Field Experiment of a Community-Based Monitoring Project
+		in Uganda.” Quarterly Journal of Economics 124(2):735–769.
+	- Bjorkman, Martina and Jakob Svensson. 2010. “When Is Community-Based
+		Monitoring Effective? Evidence from a Randomized Experiment in Primary
+		Health in Uganda.” Journal of the European Economic Association
+		8(2-3):571–581. Bjorkman Nyqvist, Martina, Damien de Walque and Jakob
+		Svensson. 2017. “Experimental Evidence on the Long-Run Impact of
+		Community-Based Monitoring.” American Economic Journal: Applied Economics
+		9(1):33–69.
+
+However, other authors fail to find positive resuls for the same type of
+intervention, e.g.:
+
+* Banerjee, A. V., Banerji, R., Duflo, E., Glennerster, R., and Khemani, S.
+	2010. Pitfalls of Participatory Programs: Evidence from a Randomized
+		 Evaluation in Education in India. American Economic Journal: Economic
+		 Policy, 2(1):1–30.
+* Lieberman, E. S., Posner, D. N., and Tsai, L. L. 2014. Does Information Lead
+	to More Active Citizenship? Evidence from an Education Intervention in Rural
+	Kenya. World Development, 60:69–83. Raffler, Pia, Dan Posner, and Doug
+	Parkerson. 2019. The Weakness of Bottom-up Accountability: Experimental
+	evidence from the Ugandan health sector. URL:
+	[`https://bit.ly/2L36vzI`](http://egap.org/sites/default/files/Posner%2C%20Dan_Paper.pdf)
+
+This project re-evaluates this theoretical controversy and proposes a new field
+experiment to test whether bottom-up accountability is effective to promote
+better policy outcomes. The results are substantively important as well. First,
+we conduct this experiment in a middle-income country, Brazil, but which has
+municipalities whose social indicators match both those of developed and
+developing nations. Brazil is notably unequal in several characteristics, thus
+allowing us to infer results for different subgroups if required. Second, we
+are evaluating school constructions, and the presence of schools have essential
+consequences in terms of long-run economic development, the household income
+composition, and woman empowerment.
 
@@
 
-**Eligibility and Exclusion Criteria**: We selected all school projects that received Federal fundings from the Brazilian Ministry of Education.
-By an agreement with the Brazilian Ministry of Education, they allowed us to have the data of all school constructions receiving funds from them.
-
-All schools constructions funded by the Brazilian Ministry of Education participated in this study. We had no schools excluded from the program.
+**Eligibility and Exclusion Criteria**: We selected all school projects that
+received Federal fundings from the Brazilian Ministry of Education. By an
+agreement with the Brazilian Ministry of Education, they allowed us to have the
+data of all school constructions receiving funds from them.
+
+All schools constructions funded by the Brazilian Ministry of Education
+participated in this study. We had no schools excluded from the program.
 
@@
 
-* App impact evaluation 1: From August 2017 to February 2018. We call this Intervention 1 throughout the text.
-* App impact evaluation 2: From August 2018 to February 2019. We call this Intervention 2 throughout the text.
+* App impact evaluation 1: From August 2017 to February 2018. We call this
+	Intervention 1 throughout the text.
+* App impact evaluation 2: From August 2018 to February 2019. We call this
+	Intervention 2 throughout the text.
 
@@
 
-**Assignment procedure**: The treatment here was assigned by the municipality in the first intervention, and at the school level in the second and third interventions.
-
-For intervention one, we selected 150 municipalities that were placed in the control group. The randomization code was:
+**Assignment procedure**: The treatment here was assigned by the municipality
+in the first intervention, and at the school level in the second and third
+interventions.
+
+For intervention one, we selected 150 municipalities that were placed in the
+control group. The randomization code was:
 
@@
 
-And then we checked whether the randomisation had one of the covariates selected here significantly predicting the random assignment.
-We presented a vector of acceptable random assignment in these grounds, and the Brazilian Transparency selected the one we are using in the first intervention.
-
-For intervention 2, we selected 15% of the schools in the dataset that could either be placed in the treatment or in control in each of the interventions.
-The `randomizr` code for intervention 2 follows below.
-`OnApp` means treatment and `OffApp` means the control for this intervention:
+And then we checked whether the randomisation had one of the covariates
+selected here significantly predicting the random assignment. We presented a
+vector of acceptable random assignment in these grounds, and the Brazilian
+Transparency selected the one we are using in the first intervention.
+
+For intervention 2, we selected 15% of the schools in the dataset that could
+either be placed in the treatment or in control in each of the interventions.
+The `randomizr` code for intervention 2 follows below. `OnApp` means treatment
+and `OffApp` means the control for this intervention:
 
@@
 **Block randomization**: We used simple randomisation in the first assignment.
-In the second intervention, we blocked by the Brazilian State, the construction status, and above the median execution.
-The summary of the blocks, with the IPWs assigned follow below.
+In the second intervention, we blocked by the Brazilian State, the construction
+status, and above the median execution. The summary of the blocks, with the
+IPWs assigned follow below.
 
@@
 
-As pre-treatment variables, we used the following municipality-level characteristics:
+As pre-treatment variables, we used the following municipality-level
+characteristics:
 
@@
 
-All the pre-treatment variables were not significant, as displayed in Section \ref{sec:bal-tests}.
+All the pre-treatment variables were not significant, as displayed in Section
+\ref{sec:bal-tests}.
 
@@
 * **Treatment groups**:
-  - *Intervention 1*: Municipality with all schools funded by the Ministry of Education showing up in the App.
-  - *Intervention 2*: School construction showing up in the App.
+	- *Intervention 1*: Municipality with all schools funded by the Ministry of
+		Education showing up in the app.
+	- *Intervention 2*: School construction showing up in the app.
 
 * **Control groups**:
-  + *Intervention 1*: Municipality with all schools funded by the Ministry of Education **not** showing up in the App.
-  + *Intervention 2*: Selected school constructions **not** showing up in the App.
+	- *Intervention 1*: Municipality with all schools funded by the Ministry of
+		Education **not** showing up in the app. 
+	- *Intervention 2*: Selected school constructions **not** showing up in the
+		app.
 
 * **Method of manipulation delivery**:
-  + *Intervention 1*: The municipalities in the treatment had all their school constructions showing up in the App.
-  + *Intervention 2*: The schools in the treatment group were showing up in the App.
-
-* **Software**: The TDP App is an Android and iOS Application developed to facilitate bottom-up pressure on school constructions in Brazil.
+	- *Intervention 1*: The municipalities in the treatment had all their school
+		constructions showing up in the app. 
+	- *Intervention 2*: The schools in the treatment group were showing up in the
+		app.
+
+* **Software**: The TDP app is an Android and iOS application developed to
+	facilitate bottom-up pressure on school constructions in Brazil.
 
@@
 
-* **Outcome measures**: We use six outcome measures, all taken from the Ministry of Education biannual report:
-
-1. Percentage of the investment executed before the impact evaluation started (placebo)
-2. Percentage of the investment executed by the end of the impact evaluation period
-3. The difference of the percentage invested in the end and in the beginning of the impact evaluation period
+* **Outcome measures**: We use six outcome measures, all taken from the
+	Ministry of Education biannual report:
+
+1. Percentage of the investment executed before the impact evaluation started
+	 (placebo)
+2. Percentage of the investment executed by the end of the impact evaluation
+	 period
+3. The difference of the percentage invested in the end and in the beginning of
+	 the impact evaluation period
 4. Indicator for a construction finished during the impact evaluation period
 5. Indicator for a construction canceled during the impact evaluation period
-6. Indicator for an updated conclusion date for the construction during the impact evaluation period
+6. Indicator for an updated conclusion date for the construction during the
+	 impact evaluation period
 
@@
 # Defining Text Labels ----------------------------------------------------
-text <- c('Assessment for\neligibility',
+text <- c("Assessment for\neligibility",
           'Excluded',
-          'Randomized',
-          'Allocated to\nTreatment',
-          'Allocated to\nControl',
-          'Lost to follow-up',
-          'Lost to follow-up',
-          'Analysed',
-          'Analysed')
+          "Randomized",
+          "Allocated to\nTreatment",
+          "Allocated to\nControl",
+          "Lost to follow-up",
+          "Lost to follow-up",
+          "Analysed",
+          "Analysed")
 
@@
 
-  + *Intervention 1*: Constructions that were not in the App when the intervention started.
-
-  + *Intervention 2*: Constructions that were not in the App when the intervention started.
+	+ *Intervention 1*: Constructions that were not in the app when the
+		intervention started.
+
+	+ *Intervention 2*: Constructions that were not in the app when the
+		intervention started.
 
@@
 
-$$ Y_i \quad = \quad \alpha + \beta T_i + \gamma X_i + \theta F_i + \varepsilon_i $$
-
-Where $i$ indexes a given school observed in the intervention.
-$Y_i$ represents an outcome variable.
-$T_i$ represents a treatment indicator.
-$\beta$ represents the estimated Average Treatment Effect.
-$\gamma$ is a vector of pre-treatment coefficient effects and $X_i$ a vector of pre-treatment covariates.
-$\theta$ represents a vector of fixed effects estimands and $F_i$ the Brazilian state level fixed effects indicator vector.
-$\varepsilon_i$ is the common error term.
+$$ Y_i = \alpha + \beta T_i + \gamma X_i + \theta F_i + \varepsilon_i $$
+
+Where $i$ indexes a given school observed in the intervention. $Y_i$ represents
+an outcome variable. $T_i$ represents a treatment indicator. $\beta$ represents
+the estimated Average Treatment Effect. $\gamma$ is a vector of pre-treatment
+coefficient effects and $X_i$ a vector of pre-treatment covariates. $\theta$
+represents a vector of fixed effects estimands and $F_i$ the Brazilian state
+level fixed effects indicator vector. $\varepsilon_i$ is the common error term.
 
@@
 
-* **IRB**: FGV exempted the investigators from getting IRB approval because this research used online data and was approved by the Brazilian Ministry of Education.
-
-* **Pre-registration**: this research has been pre-registered on the EGAP pre-registry tool: [`https://egap.org/registration/4505`](https://egap.org/registration/4505)
-
-* **Replication materials**: The replication materials for this project are available here: [`https://github.com/umbertomig/tdp-accountability`](https://github.com/umbertomig/tdp-accountability)
-
-* **Funding**: This research received funding from the 2016 Google Social Impact Challenge. Google did not interfere in any aspect of the research design and analysis.
-
-* **Conflict of interests**: The authors of this analysis declare that there are no conflict of interest.
+* **IRB**: FGV exempted the investigators from getting IRB approval because
+	this research used online data and was approved by the Brazilian Ministry of
+	Education.
+
+* **Pre-registration**: this research has been pre-registered on the EGAP
+	pre-registry tool: <https://egap.org/registration/4505>.
+
+* **Replication materials**: The replication materials for this project are
+	available here: <https://github.com/umbertomig/tdp-accountability>.
+
+* **Funding**: This research received funding from the 2016 Google Social
+	Impact Challenge. Google did not interfere in any aspect of the research
+	design and analysis.
+
+* **Conflict of interests**: The authors of this analysis declare that there
+	are no conflict of interest.
 
@@
 
-We use `r R.version.string` to write the manuscript and this appendix.
-For the regression models estimation, we use the package `lfe`.
-For the Genetic matching, we use the package `MatchIt`.
-Everything in this report is fully automated and can be reproduced using R Markdown.
+We used `r R.version.string` to write the manuscript and this appendix. For the
+regression models estimation, we used the `lfe` package. We employed the
+`MatchIt` package to improve covariate matching. Everything in this report is
+fully automated and can be reproduced using R Markdown.
 
@@
 \setlength{\parskip}{0pt}
+
 # Bibliography

### 2019-12-20 article/article.Rmd
add appendix

@@
 author:
-- "Danilo Freire[^freire]"
-- "Manoel Galdino[^galdino]"
-- "Umberto Mignozzetti[^mignozzetti]"
 date: \today
-thanks: "We thank Fábio Barros, Guilherme Jardim Duarte, Stephen Herzog, and David Skarbek for their helpful comments.
-We are specially grateful to Catarina Roman and the staff of Transparência Brasil for their excellent research assistance.
-This research was pre-registered on the EGAP pre-registry tool (<https://egap.org/registration/4505>) and approved by the Brazilian Ministry of Education.
-The authors thank the 2016 Google Social Impact Challenge for financial support and declare that there are no conflict of interest.
-Replication data and code are available at <http://github.com/umbertomignozzetti/tdp-accountability>."
 abstract: "Does ~~grassroots participation~~ **local oversight** improve public service delivery?
@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown
-University, Providence, RI 02912, USA,
-[`danilofreire@brown.edu`](mailto:danilofreire@brown.edu),
-<http://danilofreire.github.io>, +1 (401) 584-2494. Corresponding author.
-
-[^galdino]: Executive Diretor, Transparência Brasil, São Paulo, SP, Brazil,
-[`mgaldino@transparencia.org.br`](mailto:mgaldino@transparencia.org.br),
-<https://www.transparencia.org.br>.
-
-[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São
-Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA,
-[`umberto.mig@nyu.edu`](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
-
 \newpage
@@
 We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])`
-municipalities to the control group and included `r
-format(as.numeric(table(impact_evaluation_phase1$treat)[2]), big.mark = ",")`
-in the treatment group. Our control condition consists in removing all
-information about school construction from the TDP app in the chosen
-municipalities, so that citizens were unable to report constructions in the
-control municipalities.
+municipalities to the control group and included 
+`r format(as.numeric(table(impact_evaluation_phase1$treat)[2]),
+big.mark = ",")` in the treatment group. Our control condition consists in
+removing all information about school construction from the TDP app in the
+chosen municipalities, so that citizens were unable to report constructions in
+the control municipalities.
 

### 2019-12-20 article/article.Rmd
small changes

@@
 government introduced discretionary spending limits that affected public
-investment [@mello2016fix; @rossi2016impactos]. Politicians may argue that
+investment [@rossi2016impactos]. Politicians may argue that
 delays in school constructions are not derived from their misuse of government

### 2019-12-25 appendix/appendix.Rmd
small changes
add letter, edit appendix

@@
 The tables below show the results of the balance tests we conducted for
-interventions 1 and 2. Our list of covariates are:
+interventions 1 and 2. Our covariates are:
 
@@
 selected 150 municipalities for the control group while the rest were placed in
-the treatment group. The control group worked by deleting all the construction
-sites in control assigned cities. No difference between control and treatment
-variables is statistically significant.
+the treatment group. We created the control group by deleting all the
+construction sites in the selected cities. No difference between control and
+treatment variables is statistically significant.
 
@@
 15% of schools that could potentially appear in the app in the control group.
-We used block randomization, blocking by three characteristics:
+We used block randomisation, blocking by three characteristics:
 
@@
 
-3. The app sends a message to the mayor's office asking details about the
+3. The app sends a message to the mayor's office requesting details about the
 	 project. If necessary, the message is also forwarded to other government
 	 oversight institutions such as the city council and the Brazilian Federal
-	 Comptroller. Below, we discuss the cases in which we forwarded the denounce
-	 to the authorities.
+	 Comptroller (CGU). Below, we discuss the cases in which we forwarded the
+	 denounce to the authorities.
 
@@
 3.2. After we had the EWB report, we notified the mayor's office in compliance
-with Brazil's Freedom of Information Act. We communicated that a citizen had
-anonymously made a denounce about a school (fully identifying the school
-construction that we were referring to), and that the Engineers Without Borders
-found the construction delayed by a percentage that EWB provided. We submitted
-a request for the mayor's office to provide an explanation on why the
-construction was delayed, and asked for updated statistics on when the
-construction will be finished. According to the FOI law, they had twenty days
-to respond.
-
-3.3. If the response was found insufficient, we forwarded the denounce to
+with Brazil's Freedom of Information Act (FOI). We communicated that a citizen
+had anonymously made a denounce about a school (fully identifying the school
+construction that we were referring to), and that the Engineers without Borders
+found the construction delayed. We submitted a request for the mayor's office
+to provide an explanation on why the construction was delayed, and asked for
+updated statistics on when the construction will be finished. According to the
+FOI law, the mayor had twenty days to respond.
+
+3.3. If the response was deemed insufficient, we forwarded the denounce to
 the city council and to the Brazilian Federal Comptroller (CGU). As the
@@
 municipality at the time they sign the agreement with the Federal Government as
-our measure of construction delays. This data helped us to keep the app updated
-and the outcomes in the paper are selected to be six months before
-(pre-treatment) and after the intervention. This data was constantly updated by
-the Ministry of Education, and we found no red flags in the overall quality of
-the data.
+our measure of construction delays. This data helped us to keep the app
+updated. We selected outcomes six months before and after the treatment. The
+data were constantly updated by the Ministry of Education, and we found no red
+flags in the overall quality of their information.
 
@@
 level, we excluded all schools within a given randomly selected municipality.
-In the second intervention, we excluded randomly selected schools out of the
+In the second intervention, we randomly excluded selected schools out of the
 app. Removing a school means that the school was in the dataset provided by the
@@
 intentions, researchers may bias the results just by the choices they make in
-the data collection process. For instance, if we send a RA to collect the data,
-as she knows the app, she could unconsciously have a tendency to over-report
-positive results. This would severely bias our findings and undermine the
-credibility of our experiment. Second, using external data makes the results
-easily reproducible by other researchers. As the Ministry of Education has
-standardised data collection procedures, they greatly simplify and facilitate
-the reproduction of our findings.
+the data collection process. For instance, if we send an RA to collect the
+data, as she knows the app, she could unconsciously over-report positive
+results. This would bias our findings and undermine the credibility of our
+experiment. Second, using external data makes the results easily reproducible
+by other researchers. As the Ministry of Education has standardised data
+collection procedures, they greatly simplify and facilitate the reproduction of
+our findings.
 
@@
 Institute of Geography and Statistics. For instance, see the following
-webpages:
+websites:
 
@@
 
-The code below replicates the findings of table 1 in the manuscript.
+The code below replicates table 1 in the manuscript.
 
@@
 
-We employ randomised inference to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design.
-We fail to reject the null in all but the finished school indicator in experiment 1.
+We employ randomised inference to estimate the probability of the sharp null
+hypothesis over all possible randomisations that could have occurred under our
+research design. We fail to reject the null in all but the finished school
+indicator in experiment 1.
 
@@
 
-	- Bjorkman, Martina and Jakob Svensson. 2009. “Power to the People: Evidence
+	- Bjorkman, Martina and Jakob Svensson. 2009. "Power to the People: Evidence
 		from a Randomized Field Experiment of a Community-Based Monitoring Project
-		in Uganda.” Quarterly Journal of Economics 124(2):735–769.
-	- Bjorkman, Martina and Jakob Svensson. 2010. “When Is Community-Based
+		in Uganda." Quarterly Journal of Economics 124(2):735–769.
+	- Bjorkman, Martina and Jakob Svensson. 2010. "When Is Community-Based
 		Monitoring Effective? Evidence from a Randomized Experiment in Primary
-		Health in Uganda.” Journal of the European Economic Association
+		Health in Uganda." Journal of the European Economic Association
 		8(2-3):571–581. Bjorkman Nyqvist, Martina, Damien de Walque and Jakob
-		Svensson. 2017. “Experimental Evidence on the Long-Run Impact of
-		Community-Based Monitoring.” American Economic Journal: Applied Economics
+		Svensson. 2017. "Experimental Evidence on the Long-Run Impact of
+		Community-Based Monitoring." American Economic Journal: Applied Economics
 		9(1):33–69.
@@
 * Banerjee, A. V., Banerji, R., Duflo, E., Glennerster, R., and Khemani, S.
-	2010. Pitfalls of Participatory Programs: Evidence from a Randomized
-		 Evaluation in Education in India. American Economic Journal: Economic
+	2010. "Pitfalls of Participatory Programs: Evidence from a Randomized
+		 Evaluation in Education in India." American Economic Journal: Economic
 		 Policy, 2(1):1–30.
-* Lieberman, E. S., Posner, D. N., and Tsai, L. L. 2014. Does Information Lead
+* Lieberman, E. S., Posner, D. N., and Tsai, L. L. 2014. "Does Information Lead
 	to More Active Citizenship? Evidence from an Education Intervention in Rural
-	Kenya. World Development, 60:69–83. Raffler, Pia, Dan Posner, and Doug
-	Parkerson. 2019. The Weakness of Bottom-up Accountability: Experimental
-	evidence from the Ugandan health sector. URL:
+	Kenya." World Development, 60:69–83. 
+* Raffler, Pia, Dan Posner, and Doug Parkerson. 2019. "The Weakness of Bottom-up
+	Accountability: Experimental Evidence from the Ugandan Health Sector." URL:
 	[`https://bit.ly/2L36vzI`](http://egap.org/sites/default/files/Posner%2C%20Dan_Paper.pdf)
@@
 better policy outcomes. The results are substantively important as well. First,
-we conduct this experiment in a middle-income country, Brazil, but which has
+we conduct this experiment in a middle-income country, Brazil, which has
 municipalities whose social indicators match both those of developed and
@@
 consequences in terms of long-run economic development, the household income
-composition, and woman empowerment.
+composition, and women empowerment.
 
@@
 
-Interventions’ dates: We had three interventions here:
+Interventions' dates: We ran two interventions:
 
@@
 
-**Assignment procedure**: The treatment here was assigned by the municipality
+**Assignment Procedure**: The treatment here was assigned by the municipality
 in the first intervention, and at the school level in the second and third
@@
 
-And then we checked whether the randomisation had one of the covariates
-selected here significantly predicting the random assignment. We presented a
-vector of acceptable random assignment in these grounds, and the Brazilian
-Transparency selected the one we are using in the first intervention.
+Then, we checked whether the one of the selected covariates is a significant
+predictor of the random assignment. We presented a vector of acceptable random
+assignment in these grounds, and Transparência Brasil selected the one we use
+in the first intervention.
 
@@
 3. Log of Total Federal Transfers to the Municipality in 2016
-4. IDEB Indicator for primary school quality (2015 Ministry of Education)
-5. IDEB Indicator for secondary school quality (2015 Ministry of Education)
-
-All the pre-treatment variables were not significant, as displayed in Section
+4. IDEB Indicator for Primary School Quality (2015 Ministry of Education)
+5. IDEB Indicator for Secondary School Quality (2015 Ministry of Education)
+
+None of the pre-treatment variables were significant, as shown in Section
 \ref{sec:bal-tests}.
@@
 
-* **Treatment groups**:
+* **Treatment Groups**:
 	- *Intervention 1*: Municipality with all schools funded by the Ministry of
@@
 
-* **Control groups**:
+* **Control Groups**:
 	- *Intervention 1*: Municipality with all schools funded by the Ministry of
@@
 
-* **Method of manipulation delivery**:
+* **Method of Manipulation Delivery**:
 	- *Intervention 1*: The municipalities in the treatment had all their school
@@
 4. Indicator for a construction finished during the impact evaluation period
-5. Indicator for a construction canceled during the impact evaluation period
+5. Indicator for a construction cancelled during the impact evaluation period
 6. Indicator for an updated conclusion date for the construction during the
@@
 
-Below follows the CONSORT chartflow:
+Below follows the CONSORT chart flow:
 
@@
 2. Full regressions using inverse probability weights
-3. Regression where we match the control group with a same-size treatment group on the proximity of covariates using genetic matching.
-
-All models use municipal-level cluster robust standard errors and state-level fixed effects. For all models, we also run regressions without clustering and without fixed effects.
-
-# Other information
+3. Regression where we match the control group with a same-size treatment group
+	 on the proximity of covariates using genetic matching.
+
+All models use municipal-level cluster robust standard errors and state-level
+fixed effects. For all models, we also run regressions without clusters or 
+fixed effects.
+
+# Other Information
 
@@
 
-* **Pre-registration**: this research has been pre-registered on the EGAP
+* **Pre-Registration**: this research has been pre-registered on the EGAP
 	pre-registry tool: <https://egap.org/registration/4505>.
 
-* **Replication materials**: The replication materials for this project are
+* **Replication Materials**: The replication materials for this project are
 	available here: <https://github.com/umbertomig/tdp-accountability>.
@@
 
-* **Conflict of interests**: The authors of this analysis declare that there
+* **Conflict of Interests**: The authors of this analysis declare that there
 	are no conflict of interest.
@@
 `MatchIt` package to improve covariate matching. Everything in this report is
-fully automated and can be reproduced using R Markdown.
+fully automated and can be reproduced using RMarkdown.
 
@@
 
-# Bibliography
+# References

### 2019-12-25 article/letter.Rmd
add letter, edit appendix

--- 2019-12-15 article/letter.Rmd
@@
 
-\noindent 2 December 2019
+\noindent 25 December 2019
 
@@
 
-\noindent We would like to thank you for the opportunity to revise our manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144).
-We have made many revisions to the paper along the lines suggested by the editor and the anonymous reviewer and we believe the manuscript has improved significantly as a result.
+\noindent We would like to thank you for the opportunity to revise our
+manuscript, "Bottom-Up Accountability and Public Service Provision: Evidence
+from a Field Experiment in Brazil" (Manuscript ID RAP-19-0144). We have made
+many revisions to the paper along the lines suggested by the editor and the
+anonymous reviewer and we believe the manuscript has improved significantly as
+a result.
 
-We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer.
-Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns.
-We explain the precautions we have taken to ensure that we correctly identify the effect of the TDP app on school outcomes.
-Second, we provide a thorough discussion of our additional data sources.
-More specifically, we show how the Brazilian Ministry of Education collects and publicises their data and indicate how our experiment uses that information to evaluate the robustness of our findings.
-We believe the new sections help give the results a clearer interpretation and strenghten our main arguments.
+We have worked specially hard to clarify the connection between information
+provision and mobilisation, a point emphasised by both the editor and the
+reviewer. Our efforts in that regard include, first, two sections in the online
+appendix with a detailed description of _Tá de Pé_'s functionalities and the
+associated Facebook campaigns. We explain the precautions we have taken to
+ensure that we correctly identify the effect of the TDP app on school outcomes.
+Second, we provide a thorough discussion of our additional data sources in
+sections 3 and 4 of the appendix. More specifically, we show how the Brazilian
+Ministry of Education collects and publicises their data and how we use that
+information to evaluate the robustness of our findings. We believe the new
+sections help give the results a clearer interpretation and strenghten our main
+arguments.
 
-Related, we have included a discussion regarding app usage as suggested by the reviewer.
-We have included information provided by Google Analytics not only on app downloads but also on app usage, which addresses another important concern raised by the reviewer.
-The data show that the app usage was significant, yet it was not enough to trigger any responses from local governments.
+Related, we have included information on app use and app downloads, which
+addresses another important concern raised by the reviewer. The data have been
+provided by Google Analytics and show that app usage was significant during the
+two interventions, yet the usage was not sufficient to trigger any responses
+from local governments.
 
-Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.
-We believe our paper now reflects our results more accurately.
+Lastly, we have rewritten some parts of the main text to highlight two points:
+1) that our experiment hinges on participation only; 2) that the effect of
+mobilisation and pressure on school construction outcomes require further
+analyses. We believe our paper now reflects our results more accurately.
 
-Below we discuss in more detail these and other changes we have made to the manuscript in response to comments from the editor and the reviewer.
-We thank the editor again for the opportunity to revise the manuscript, and the reviewer for his/her extremely helpful comments.
+Below we discuss in more detail these and other changes we have made to the
+manuscript in response to comments from the editor and the reviewer. We thank
+the editor again for the opportunity to revise the manuscript, and the reviewer
+for his/her extremely helpful comments.
 
-\vspace{.5cm}
-
-\noindent Sincerely,
-
-\vspace{.5cm}
+\vspace{.5cm} \noindent Sincerely,
 
@@
 
-**1)** The editor writes:
+\textbf{1)} The editor writes: "_The reviewer confirmed my own sense that the
+manuscript and underlying field experiment are interesting, although you will
+see that the reviewer suggests many ways the manuscript can be improved.  I am
+in full agreement with the reviewer that you need to reflect more deeply about
+the theory and evidence for why information provision via the app could be
+connected to mobilization, -- otherwise the null result is not interesting. As
+the reviewer notes, the null result could be due to a disconnect between
+information provision and action, or due to who selects into downloading the
+app._"
 
-\noindent 
-**Response:**
+\vspace{.5cm} \noindent \textbf{Response:}
 
-\begin{quotation}
-Lorem ipsum.
-\end{quotation}
+> We agree that the link between information provision and mobilisation was not
+clearly defined in the original manuscript. We believe the main issue lies in
+the lack of evidence for mobilisation, that is, we did not provide sufficient
+information about how users interacted with the application and whether they
+have used the app consistently. In the revised version of the manuscript, we
+provide data from Google Analytics which indicate that users did engage with
+the app. According to the service, the app had 6,092 active users in
+intervention 1 and gained 4,078 new users during intervention 2. On average,
+each user launched 60 sessions per app install, an indication of their actual
+engagement with the application. Moreover, the data also show that the app had
+more than 53,000 screen visualisations, with an average of 2.42 visualisations
+per user. We have added this information to the main text and to the online
+appendix. The additions are marked in \textbf{boldface}. We elaborate further
+on this issue in the response to Reviewer 1 below.
+
+# Reviewer 1 Comments and Responses
+
+**1)** Reviewer 1 writes: "[...] _My biggest concern is there is no discussion
+of the actual bottom-up accountability that may (or may not) have occurred._"
+
+\vspace{.5cm} \noindent \textbf{Response:}
+
+> We have made several changes to the main paper and the online appendix to
+address this important concern. First, we have added a new section to the
+appendix (B) in order to clarify how we designed and conducted the experiment.
+We copy the text below:
 
@@
 
-# Reviewer 1 Comments and Responses
+> **Appendix C -- Treatment Definition and Mechanism**
 
-**1)** Reviewer 1 writes:
+> _In this section, we explain in detail how the _Tá de Pé_ app works. The
+treatment involves the following procedures:_
 
-\noindent
-**Response:**
+> _1. Users download the app._
+
+> _2. Users access the app and add new information about school constructions
+	 near to their location._
+
+> _3. The app sends a message to the mayor's office requesting details about
+the project. If necessary, the message is also forwarded to other government
+oversight institutions such as the city council and the Brazilian Federal
+Comptroller (CGU). Below, we discuss the cases in which we forwarded the
+denounce to the authorities._
+
+> _4. If the pressure over the mayors has an effect, we expect to witness
+	 improvements on governmental data regarding the school construction
+	 progress._
+
+> _The treatment is a compounded treatment comprised of steps (2) to (4). To
+make sure that the only source of effect comes from step (2), we took the
+following precautions:_
+
+> _In step (1), we have implemented Facebook campaigns in municipalities that
+have school construction agreements with the Federal government. We did not
+discriminate any municipality in this step, and citizens living in
+municipalities in the treatment and in the control could equally have received
+the banners about the _Tá de Pé_ app. The Facebook campaign was not
+randomised._
+
+> _For step (3), we put a team of two data scientists to ensure that upon
+receiving a denounce, the mayor's office, the city council, and the Brazilian
+Federal Comptroller (CGU) would be notified. The decision making funnel was:_
+
+> _3.1. We notified the _Engineers without Borders_ (EWB) about the denounce
+and sent them the user-provided pictures and auxiliary information. They issued
+a report on how much the construction was likely to be delayed._
+
+> _3.2. After we had the EWB report, we notified the mayor's office in
+compliance with Brazil's Freedom of Information Act (FOI). We communicated that
+a citizen had anonymously made a denounce about a school (fully identifying the
+school construction that we were referring to), and that the Engineers without
+Borders found the construction delayed. We submitted a request for the mayor's
+office to provide an explanation on why the construction was delayed, and asked
+for updated statistics on when the construction will be finished. According to
+the FOI law, the mayor had twenty days to respond._
+
+> _3.3. If the response was deemed insufficient, we forwarded the denounce to
+the city council and to the Brazilian Federal Comptroller (CGU). As the
+denounce goes to these institutions, they can harm mayors by restricting access
+to Federal funds._
+
+> _3.4. At each stage, a Twitter bot constructed by Transparência Brasil
+(<https://twitter.com/tadepeapp>) reported the reception of a denounce and
+tracked the responses of the mayor, the city council, and the CGU._
+
+> _In step (4), we relied on administrative data by the Brazilian Ministry of
+Education. The Ministry of Education provides monthly data on school
+constructions build with Federal Government resources and shows how many of
+them are delayed across the country. We use the finishing dates reported by the
+municipality at the time they sign the agreement with the Federal Government as
+our measure of construction delays. This data helped us to keep the app
+updated. We selected outcomes six months before and after the treatment. The
+data were constantly updated by the Ministry of Education, and we found no red
+flags in the overall quality of their information._
+
+> _Therefore, steps (1), (3), and (4) were standardised and do not vary across
+the country. The only source of variation in our intervention should come from
+step (2)._
+
+> _In step (2), we applied the treatment by removing schools within
+municipalities out of the app. In the first intervention, which happened at the
+municipal level, we excluded all schools within a given randomly selected
+municipality. In the second intervention, we randomly excluded selected schools
+out of the app. Removing a school means that the school was in the dataset
+provided by the Brazilian Ministry of Education, but it did not show up in the
+app. Therefore, our treatment effect represents the school being present
+(treatment) or absent (control) in the app._
+
+> _We argue that the app promotes two crucial features of bottom-up
+accountability. First, it helps people to access information that would
+otherwise be available only in an obscure spreadsheet on the Ministry of
+Education website. Second, whenever people find this information troublesome,
+we are providing an easy way to them to act upon the information. As the _Tá de
+Pé_ design was intuitive and straightforward, we believe that most of
+Brazilians would find it easy to use the app._
+
+> _Moreover, the success of treatment does not require that everyone in the
+municipality uses it. The more usage means more pictures and denounces, and
+this represents more pressure over the mayors office, what could revert into a
+higher effect. However, just one denounce would be enough for the project to be
+successful, as the denounce can be directed to the Brazilian General
+Comptroller (CGU), and this could potentially deny future funding to the
+municipality._
+
+\noindent \textbf{2)} Reviewer 1 writes: "_The authors have devised a nice
+experiment and I believe their design to have been appropriately administrated.
+But the design hinges on several critical mechanisms that go largely
+undiscussed: not only must information be available to citizens such that they
+might participate in local oversight, but said citizens must 1) access the
+information and 2) act on said information. This is mentioned in the
+Discussion---that perhaps the app was insufficient to spur collective
+action---but that also seems like an empirical question the authors could
+feasibly address_. [...] _Once people downloaded the App, did they use it?_"
+
+> To answer these questions, we have added Google Analytics data on _Tá de
+Pé_'s download and usage. This provide reliable and exogenous data
+about our experimental manipulation and the effectiveness of the treatment. The
+data confirm that app usage was significant. We add the following paragraph to
+the main text to show user engagement (page 8):
 
 \newpage
-\setlength{\parindent}{0cm}
-\setlength{\parskip}{5pt}
+
+> _Data from Google Analytics suggest that users did engage with the TDP app.
+On average, each user launched 59.99 app sessions, which indicates their
+interest in the application. In total, the app had 53,928 screen
+visualisations, with an average of 2.42 screen visualisations per session._
+
+> We see that users not only downloaded the app but visualised
+different screens at each session. This means that users did check all pages of
+the app, including those with information about local school constructions.
+Moreover, figures 2 and 3 in the main text (pages 7 and 8) also show that the
+downloads were widespread across the country. Considering Brazil's large
+territory, we believe this is robust evidence of an effective treatment
+manipulation.
+
+> As we note in Appendix C, one denounce would be sufficient for the city
+council and the Federal Comptroller to start an investigation against the
+offending mayor. However, we do not find any substantial treatment effect in
+our two interventions. We have added three paragraphs to the Discussion section
+on possible explanations for the null effects (pages 12 and 13):
+
+> _What factors, then, are driving these results? It seems unlikely that the
+null results derive from flaws in the research design. First, our study is well
+powered. Although the treatment is indirect---the person has to download the
+app, find a school construction, and then report it---,we included a
+substantial number of schools in the treatment groups. Second, balance and
+manipulation tests indicate that the treatment allocation was successful, so we
+can rule out problems in the randomisation procedures. Third, data from
+Google Analytics confirm that citizens did use the app and provided information
+to our dataset. This indicates that the treatment manipulation was effective.
+In this sense, it is unlikely that our results derive from low user response.
+Fourth, after doing a series of robustness tests, we still find no firm
+evidence of treatment effect. Finally, note that the sign of the coefficients
+are frequently contrary to our theoretical expectations. This rules out a
+possible concern about statistical power with our small control group
+approach._
+
+> _We discuss some possible reasons why community monitoring did not work in
+our case. One plausible explanation is that individuals were unable to
+differentiate the effect of political corruption from those of spending cuts.
+Due to the severe economic crisis in 2014--2016, the Brazilian federal
+government introduced discretionary spending limits that affected public
+investment [@rossi2016impactos]. Politicians may argue that delays in school
+constructions are not derived from their misuse of government funds, but from
+the austerity measures. If this is the case, citizens will not blame local
+politicians for the underprovision of public goods. Consequently,
+representatives can dismiss individual requests as the issue is unlikely to
+escalate._
+
+> _The electoral cycle might also have decreased the potential effect of the
+treatment. As the experiment was fielded right after Brazil's municipal
+elections, incumbents might have disregarded the requests because they did not
+see the demands as politically costly in the short run. Having just taken
+office, mayors might have focused their attention to the formation of
+government coalitions or to budget concerns. Future research may evaluate how
+electoral dynamics interact with citizen oversight, potentially by replicating
+informational experiments in different stages of the political cycle._
+
+\noindent \textbf{3)} Reviewer 1 writes: "_Did the creators of the App
+actually gather information on school construction?_"
+
+> We have added a new section to the online appendix describing our data
+collection process (Appendix D). The section contains our data sources and a
+brief description of each outcome variables we employed in the paper. The
+variables we use were compiled by the Brazilian Ministry of Education. The new
+section is available below.
+
+> **Appendix D -- Outcome Data Collection**
+
+> _We collect the main outcomes using the data reported by the municipality to
+the Brazilian Ministry of Education. Note that this is the same data as the
+pre-treatment data that we use to feed in the app with delayed schools._
+
+> _The outcomes used in the paper are:_
+
+> _1. **Percentage of the project completed before the impact evaluation
+	 started**: This is a column in the Ministry of Education dataset. The data
+	 in this column were sampled in the beginning of the intervention._
+
+> _2. **Percentage of the project reported as completed by the end of the
+	 intervention period**: Another column in the Ministry of Education dataset.
+	 The data were sampled six months after the intervention._
+
+> _3. **Difference between the percentage reported as completed before and
+after the intervention**: The difference between (1) and (2) above. Note that
+according to @gerber2012field, this way to look into outcomes is positive, as
+having a pre-treatment covariate that highly predicts the outcome reduces the
+variance in the estimator considerably._
+
+> _4. **Dummy indicator for finished constructions**: The Ministry of Education
+	 dataset has a column with the construction status. We created a dummy to be
+	 one when the construction was reported as finished and zero otherwise. The
+	 data here were sampled six months after the intervention._
+
+> _5. **Dummy indicator for cancelled constructions**: Similarly, we created a
+	dummy variable from the Ministry of Education dataset indicating when the
+	construction was reported as cancelled. The data here were sampled six months
+	after the intervention._
+
+> _6. **Number of schools where construction companies updated the conclusion
+	 dates**: Lastly, the Ministry of Education dataset has a column with the
+	 construction estimated completion date. We took the completion dated
+	 reported before and six months after the intervention. If the dates
+	 differed, we coded as one, and zero otherwise._
+
+> _All these variables come from our manipulation of the Ministry of Education
+data. Collecting the outcomes in this way is superior than the alternative of
+gathering the data ourselves. First, we would not be able to manipulate the
+results and cherry-pick favourable results. Even if they have the best
+intentions, researchers may bias the results just by the choices they make in
+the data collection process. For instance, if we send an RA to collect the
+data, as she knows the app, she could unconsciously over-report positive
+results. This would bias our findings and undermine the credibility of our
+experiment. Second, using external data makes the results easily reproducible
+by other researchers. As the Ministry of Education has standardised data
+collection procedures, they greatly simplify and facilitate the reproduction of
+our findings._
+
+\noindent \textbf{4)} Reviewer 1 writes: "_Some of this basic information is
+fascinating, and two critical components to how we ought to interpret the
+results. For example, page 8 "The literature on bottom up accountability argues
+that more information about the shortcomings of public service provision will
+mobilise citizens who, in turn, would pressure state agents to produce better
+social policies. Our results do not lend support to that hypothesis." Your
+results suggest that providing information alone is not sufficient, but
+different analyses are required to evaluate the mobilization and pressure part
+of that equation._"
+
+> We fully agree with the reviewer and have changed the main text accordingly.
+We have rewritten several passages, from the abstract to the discussion, in
+order to highlight that our mechanism is indeed based on information provision
+and not exactly mobilisation. For instance, the first paragraph in the
+Discussion session has been rewritten as:
+
+> _In this paper, we discuss **whether delivering information to citizens via** a
+mobile phone application fosters ~~grassroots mobilisation~~ **community
+oversight** and political accountability in Brazil. Our two interventions show
+that the results are at best mixed. Although we find ~~an~~ **some treatment**
+effect on school cancelling rates in the first intervention, the app has no
+consistent impact on our outcomes of interest. These findings add to the
+studies that cast doubts on the relationship between bottom-up accountability
+and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does;
+@raffler2018weakness]._
+
+Similarly, we have changed the Introduction to:
+
+> _We use the TDP app to conduct two experimental interventions and test ~~its
+impact~~ **the impact of citizen oversight** on five outcomes related to school
+completion rates and complaints to public authorities. Overall, ~~our results
+show that~~ providing information to citizens has no consistent impact on
+policy outcomes._ [...] _Our results are in line with the
+latter group and suggest that local oversight is ineffective in altering
+government behaviour in Brazil._
+
+\noindent \textbf{5)} Reviewer 1 writes: "_A similar short coming is the lack
+of discussion of who downloaded the App, and if/how said characteristics
+correlate with municipal level predictors of school construction outcomes. It
+might be that the randomization "worked" at the municipal level (balance and
+manipulation tests suggests this is the case), but if the App was exclusively
+downloaded by teenagers (those most likely to be on Facebook, but least likely
+to care about public works information, and least likely to do something about
+it), then that could be the root of the problem. Indeed, the authors describe
+in the SI Appendix the ability to evaluate subsets of user data, I'm curious as
+to why they did not._"
+
+> The reviewer correctly points out that the usage of the app could have
+suffered from heterogeneous effects on the types of users achieved by the
+Facebook campaign. To clarify this point, first, we would like to note that the
+Facebook campaign was not randomised. This means that every municipality that
+had a delayed construction site in the Ministry of Education data was targeted,
+regardless of being in the treatment or the control group. In fact, the app
+could be downloaded in any Brazilian municipality, regardless of having a
+construction delayed on it. The App will automatically list the school sites
+closer to the user, even if the closest school is kilometres away from the
+user.
+
+> Second, the Brazilian countryside is still plagued by political violence
+against citizens acting against mayors. Because of this possibility, we decided
+to make the app completely anonymous. Although this carries a cost in terms of
+the analysis, it ensures that the citizens were not exposed in any way.
+Moreover, the randomization is known for washing out any the interference of
+any unobserved factor that could threat the identification of the causal
+effect. The success on observables reassures us that the randomisation was well
+performed, and probably eliminated the concern of heterogeneity from
+non-observables. However, we agree with the reviewer that the target public
+could be either outside Facebook, or being of a given demographic
+characteristic that we did not captured in our experiment.
+
+> We have also included further information on the Facebook campaign in the
+> Appendix (section E):
+
+> **Appendix E: Facebook Tá de Pé Campaign**
+
+> _The app by itself would probably not have had an effect on the
+responsiveness of mayors. To boost usage and publicize the app, Transparência
+Brasil ran 64 Facebook campaigns throughout the country. The Facebook campaign
+concentrates the bulk of the investments in the beginning of the intervention.
+The app download data is in the second panel of Figures 2 and 3. For the
+Facebook interaction, we have the following statistics:_
+
+> _1. Impressions_
+	- _Mean: 36052.69_
+	- _Total for all campaigns: 5,155,535_
+
+> _2. App Download link clicks:_
+	- _Mean:  24398.65_
+	- _Total for all campaigns: 1,951,892
+
+> _As we see from the actual download activity, the people who indeed
+downloaded the app were much fewer than these numbers would suggest._
+
+> _We have chosen Facebook because the platform offers an easy and cheap method
+to spread information. Moreover, according to the Statista website, Facebook is
+used by 70 million Brazilians (60% of the entire adult population), and the
+demographics largely match the demographics publicised by the Brazilian
+Institute of Geography and Statistics. For instance, see the following
+websites:_
+
+> _1. [Statista Total Facebook
+> Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)_
+
+> _2. [Statista Total Facebook Users by
+	 Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)_
+
+\noindent \textbf{6)} Reviewer 1 writes: "_In light of the aforementioned
+nuance that is lacking but ought to be improved, I encourage the authors to
+take care in how they describe their experiment, the treatment and what we can
+infer. For example, the first sentence of the abstract asks: “Does grassroots
+participation improve public service delivery?” The analysis hinges not on
+participation (something on which we have no information), but the possibility
+of oversight._ [...] _This is but one example, I would encourage the authors to
+carefully revise an already polished manuscript with these sorts of clarifying
+issues in mind._"
+
+> We agree with the reviewer and have followed his/her suggestions for revising
+the phrasing of some of our passages. We believe the text has been
+significantly improved as a result. The changes can be read in several parts of
+the main text, but we would like to share some examples here. For instance, the
+abstract now reads:
+
+> _Does ~~grassroots participation~~ **local oversight** improve public service
+> delivery? We study the effect of a mobile phone application that allows
+> citizens to monitor school construction projects in Brazilian municipalities.
+> ~~The app provides a platform where users can submit photos of construction
+> sites, consult independent engineers, and contact the mayor's office about
+> project delays.~~ **The app prompts users to submit data about construction
+> sites, sends such crowdsourced information to independent engineers, and
+> contacts the mayors' offices about project delays.** Our results show that
+> the app has a null impact on the school construction indicators.
+> Additionally, we find that politicians are unresponsive to individual
+> requests. The results question the impact of ~~local~~ **bottom-up**
+> monitoring on public service performance and suggest that interventions
+> targeted ~~at other groups~~ **to other groups, or focusing on different
+> issues,** may produce better policy outcomes._
+
+Our explanation of the results on page 9 has been rewritten as:
+
+> _We find that the app only has a small effect on cancellation rates. The TDP
+application increases the likelihood of cancelling the construction in 2.07
+percent. While this result goes in the opposite direction of our theoretical
+expectations, the finding is inconsistent and does not replicate in the second
+experiment. All other coefficients are not statistically significant at
+conventional levels. On the one hand, the results indicate that our placebo
+outcome, the percentage of the invested executed before the intervention,
+indeed behaves as predicted. On the other hand, we expected the five remaining
+outcomes to improve after the introduction of the app. The literature on
+bottom-up accountability argues that delivering more information about the
+shortcomings of public services provision will ~~mobilise citizens who, in
+turn, would pressure state agents to produce better social policies~~ **put
+citizens in a position where they can monitor state agents and improve provider
+behaviour** [@raffler2018weakness]. Our results do not lend support to that
+hypothesis._
+
+\noindent \textbf{7)} Reviewer 1 writes: "_Can you address possible
+cross-municipality contamination?_"
+
+> The reviewer finally questions us about the possibility of cross-municipality
+> contamination. This would mean that the existence of the app in a
+> municipality could make mayors in other municipalities to act and increase
+> their efforts toward getting the schools finished. She/He is correct that, if
+> this is the case, the null result should not be surprising. However, looking
+> into changes in outcomes in the control and the treatment we see no effect of
+> proximity. Moreover, municipalities in Brazil are much insulated, and mayors
+> usually belong to different parties. There are about 35 active parties in
+> Brazil, which makes cross-municipality contact and information sharing costly
+> and difficult. Therefore, we believe that this possibility is remote.
+
+We would like to thank Reviewer 1 for his/her helpful comments and suggestions.
+
+\setlength{\parindent}{0cm} \setlength{\parskip}{5pt}

### 2019-12-28 article/article.Rmd
small edits to article and letter

@@
 The first intervention was carried out from August 2017 to July 2018 using the
-Android version of TDP. The randomization was conduct at the municipal level.
+Android version of TDP. The randomisation was conducted at the municipal level.
 We randomly selected `r as.numeric(table(impact_evaluation_phase1$treat)[1])`
@@
 government indicator for secondary school quality. The data come from the
-Brazilian Ministry of Education and the Census. Balance tests show that the
-randomisation was successful and are available in the Supplementary Materials.
+Brazilian Ministry of Education and the 2010 Brazilian Census. Balance tests
+show that the randomisation was successful and are available in the
+Supplementary Materials.
 
@@
 average, each user launched `r format(round(mean(as.numeric(gsub('\\.', '',
-ga2$visualizacoes_de_tela))), 2), big.mark = ",")` app sessions, which
+ga2$visualizacoes_de_tela))), 1), big.mark = ",")` app sessions, which
 indicates their interest in the application. In total, the app had 
@@
 can rule out problems in the randomisation procedures. **Third, data from
-Google Analytics confirm that citizens did use the app and provided information
-to our dataset. This indicates that the treatment manipulation was effective.
-In this sense, it is unlikely that our results derive from low user response.**
-Fourth, after doing a series of robustness tests, we still find no firm
-evidence of treatment effect. Finally, note that the sign of the coefficients
-are frequently contrary to our theoretical expectations. This rules out
-a possible concern about statistical power with our small control group
-approach.
+Google Analytics confirm that citizens indeed used the app and provided
+information to our dataset. This indicates that the treatment manipulation was
+effective. In this sense, it is unlikely that our results derive from low user
+response.** Fourth, after doing a series of robustness tests, we still find no
+firm evidence of treatment effect. Finally, note that the sign of the
+coefficients are frequently contrary to our theoretical expectations. This
+rules out a possible concern about statistical power with our small control
+group approach.
 

### 2019-12-28 article/letter.Rmd
small edits to article and letter

@@
 
-\noindent 25 December 2019
+\noindent 28 December 2019
 
@@
 mobilisation and pressure on school construction outcomes require further
-analyses. We believe our paper now reflects our results more accurately.
+analyses. We believe the paper now reflects our results more accurately.
 
 Below we discuss in more detail these and other changes we have made to the
-manuscript in response to comments from the editor and the reviewer. We thank
-the editor again for the opportunity to revise the manuscript, and the reviewer
-for his/her extremely helpful comments.
+manuscript in response to comments we had received. We thank the editor again
+for the opportunity to revise the manuscript, and the reviewer for his/her
+extremely helpful comments.
 
@@
 address this important concern. First, we have added a new section to the
-appendix (B) in order to clarify how we designed and conducted the experiment.
+appendix in order to clarify how we designed and conducted the experiment.
 We copy the text below:
@@
 > To answer these questions, we have added Google Analytics data on _Tá de
-Pé_'s download and usage. This provide reliable and exogenous data
-about our experimental manipulation and the effectiveness of the treatment. The
-data confirm that app usage was significant. We add the following paragraph to
-the main text to show user engagement (page 8):
+Pé_'s download and usage. This provide exogenous and reliable data about our
+experimental manipulation and the effectiveness of the treatment. The data
+confirm that app usage was significant. We add the following paragraph to the
+main text to show user engagement (page 8):
 
@@
 > _Data from Google Analytics suggest that users did engage with the TDP app.
-On average, each user launched 59.99 app sessions, which indicates their
-interest in the application. In total, the app had 53,928 screen
-visualisations, with an average of 2.42 screen visualisations per session._
+On average, each user launched 60 app sessions, which indicates their interest
+in the application. In total, the app had 53,928 screen visualisations, with an
+average of 2.42 screen visualisations per session._
 
@@
 order to highlight that our mechanism is indeed based on information provision
-and not exactly mobilisation. For instance, the first paragraph in the
+and not mobilisation _per se_. For instance, the first paragraph in the
 Discussion session has been rewritten as:
@@
 government behaviour in Brazil._
+
+Other changes are marked as boldface in the main text.
+
+\vspace{.5cm}
 
@@
 
-Our explanation of the results on page 9 has been rewritten as:
+The Results section (page 9) has been rewritten as:
 
@@
 
-> The reviewer finally questions us about the possibility of cross-municipality
-> contamination. This would mean that the existence of the app in a
-> municipality could make mayors in other municipalities to act and increase
-> their efforts toward getting the schools finished. She/He is correct that, if
-> this is the case, the null result should not be surprising. However, looking
-> into changes in outcomes in the control and the treatment we see no effect of
-> proximity. Moreover, municipalities in Brazil are much insulated, and mayors
-> usually belong to different parties. There are about 35 active parties in
-> Brazil, which makes cross-municipality contact and information sharing costly
-> and difficult. Therefore, we believe that this possibility is remote.
+> Lastly, the reviewer questions us about the possibility of
+> cross-municipality contamination. This would mean that the existence of the
+> app in a municipality could make mayors in other municipalities to act and
+> increase their efforts toward getting the schools finished. She/He is correct
+> that, if this is the case, the null result should not be surprising. However,
+> looking into changes in outcomes in the control and the treatment we see no
+> effect of proximity. Moreover, municipalities in Brazil are much insulated,
+> and mayors usually belong to different parties. There are about 35 active
+> parties in Brazil, which makes cross-municipality contact and information
+> sharing costly and difficult. Therefore, we believe that this possibility is
+> remote.
 

### 2020-01-01 appendix/appendix.Rmd
add edits to appendix

@@
 
-In this section, we explain in detail how the _Tá de Pé_ app works. The
-treatment involves the following procedures:
-
-1. Users download the app.
-
-2. Users access the app and add new information about school constructions
-	 near to their location.
-
-3. The app sends a message to the mayor's office requesting details about the
-	 project. If necessary, the message is also forwarded to other government
+__In this section, we explain in detail how the _Tá de Pé_ app works. The
+treatment involves the following procedures:__
+
+**1. Users download the app.**
+
+**2. Users access the app and add new information about school constructions**
+**near to their location.**
+
+**3. The app sends a message to the mayor's office requesting details about
+the project. If necessary, the message is also forwarded to other government
 oversight institutions such as the city council and the Brazilian Federal
 Comptroller (CGU). Below, we discuss the cases in which we forwarded the
-	 denounce to the authorities.
-
-4. If the pressure over the mayors has an effect, we expect to witness
+denounce to the authorities.**
+
+**4. If the pressure over the mayors has an effect, we expect to witness
 	 improvements on governmental data regarding the school construction
-	 progress.
-
-The treatment is a compounded treatment comprised of steps (2) to (4). To make
-sure that the only source of effect comes from step (2), we took the following
-precautions:
-
-In step (1), we have implemented Facebook campaigns in municipalities that have
-school construction agreements with the Federal government. We did not
+	 progress.**
+
+**The treatment is a compounded treatment comprised of steps (2) to (4). To
+make sure that the only source of effect comes from step (2), we took the
+following precautions:**
+
+**In step (1), we have implemented Facebook campaigns in municipalities that
+have school construction agreements with the Federal government. We did not
 discriminate any municipality in this step, and citizens living in
 municipalities in the treatment and in the control could equally have received
-the banners about the _Tá de Pé_ app. The Facebook campaign was not randomised.
-
-For step (3), we put a team of two data scientists to ensure that upon
+the banners about the _Tá de Pé_ app. The Facebook campaign was not
+randomised.**
+
+**For step (3), we put a team of two data scientists to ensure that upon
 receiving a denounce, the mayor's office, the city council, and the Brazilian
-Federal Comptroller (CGU) would be notified. The decision making funnel was:
-
-3.1. We notified the _Engineers without Borders_ (EWB) about the denounce and
+Federal Comptroller (CGU) would be notified. The decision making funnel was:**
+
+**3.1. We notified the _Engineers without Borders_ (EWB) about the denounce and
 sent them the user-provided pictures and auxiliary information. They issued a
-report on how much the construction was likely to be delayed.
-
-3.2. After we had the EWB report, we notified the mayor's office in compliance
+report on how much the construction was likely to be delayed.**
+
+**3.2. After we had the EWB report, we notified the mayor's office in compliance
 with Brazil's Freedom of Information Act (FOI). We communicated that a citizen
@@
 updated statistics on when the construction will be finished. According to the
-FOI law, the mayor had twenty days to respond.
-
-3.3. If the response was deemed insufficient, we forwarded the denounce to
+FOI law, the mayor had twenty days to respond.**
+
+**3.3. If the response was deemed insufficient, we forwarded the denounce to
 the city council and to the Brazilian Federal Comptroller (CGU). As the
 denounce goes to these institutions, they can harm mayors by restricting access
-to Federal funds.
-
-3.4. At each stage, a Twitter bot constructed by Transparência Brasil
+to Federal funds.**
+
+**3.4. At each stage, a Twitter bot constructed by Transparência Brasil
 (<https://twitter.com/tadepeapp>) reported the reception of a denounce and
-tracked the responses of the mayor, the city council, and the CGU.
-
-In step (4), we relied on administrative data by the Brazilian Ministry of
+tracked the responses of the mayor, the city council, and the CGU.**
+
+**In step (4), we relied on administrative data by the Brazilian Ministry of
 Education. The Ministry of Education provides monthly data on school
@@
 data were constantly updated by the Ministry of Education, and we found no red
-flags in the overall quality of their information.
-
-Therefore, steps (1), (3), and (4) were standardised and do not vary across the
-country. The only source of variation in our intervention should come from step
-(2).
-
-In step (2), we applied the treatment by removing schools within municipalities
-out of the app. In the first intervention, which happened at the municipal
-level, we excluded all schools within a given randomly selected municipality.
-In the second intervention, we randomly excluded selected schools out of the
-app. Removing a school means that the school was in the dataset provided by the
-Brazilian Ministry of Education, but it did not show up in the app. Therefore,
-our treatment effect represents the school being present (treatment) or absent
-(control) in the app.
-
-We argue that the app promotes two crucial features of bottom-up
+flags in the overall quality of their information.**
+
+**Therefore, steps (1), (3), and (4) were standardised and do not vary across
+the country. The only source of variation in our intervention should come from
+step (2).**
+
+**In step (2), we applied the treatment by removing schools within
+municipalities out of the app. In the first intervention, which happened at the
+municipal level, we excluded all schools within a given randomly selected
+municipality. In the second intervention, we randomly excluded selected schools
+out of the app. Removing a school means that the school was in the dataset
+provided by the Brazilian Ministry of Education, but it did not show up in the
+app. Therefore, our treatment effect represents the school being present
+(treatment) or absent (control) in the app.**
+
+**We argue that the app promotes two crucial features of bottom-up
 accountability. First, it helps people to access information that would
@@
 Pé_ design was intuitive and straightforward, we believe that most of
-Brazilians would find it easy to use the app.
-
-Moreover, the success of treatment does not require that everyone in the
+Brazilians would find it easy to use the app.**
+
+**Moreover, the success of treatment does not require that everyone in the
 municipality uses it. The more usage means more pictures and denounces, and
@@
 Comptroller (CGU), and this could potentially deny future funding to the
-municipality.
+municipality.**
 
@@
 
-We collect the main outcomes using the data reported by the municipality to the
-Brazilian Ministry of Education. Note that this is the same data as the
-pre-treatment data that we use to feed in the app with delayed schools.
-
-The outcomes used in the paper are:
-
-1. **Percentage of the project completed before the impact evaluation
-	 started**: This is a column in the Ministry of Education dataset. The data
-	 in this column were sampled in the beginning of the intervention.
-
-2. **Percentage of the project reported as completed by the end of the
-	 intervention period**: Another column in the Ministry of Education
-	 dataset. The data were sampled six months after the intervention.
-
-3. **Difference between the percentage reported as completed before and after
-	 the intervention**: The difference between (1) and (2) above. Note
+**We collect the main outcomes using the data reported by the municipality to
+the Brazilian Ministry of Education. Note that this is the same data as the
+pre-treatment data that we use to feed in the app with delayed schools.**
+
+**The outcomes used in the paper are:**
+
+**1. Percentage of the project completed before the impact evaluation started:
+	 This is a column in the Ministry of Education dataset. The data in this
+	 column were sampled in the beginning of the intervention.**
+
+**2. Percentage of the project reported as completed by the end of the
+	 intervention period: Another column in the Ministry of Education dataset.
+	 The data were sampled six months after the intervention.**
+
+**3. Difference between the percentage reported as completed before and after
+	 the intervention: The difference between (1) and (2) above. Note
 	 that according to @gerber2012field, this way to look into outcomes is
 	 positive, as having a pre-treatment covariate that highly predicts the
-	 outcome reduces the variance in the estimator considerably.
-
-4. **Dummy indicator for finished constructions**: The Ministry of Education
+	 outcome reduces the variance in the estimator considerably.**
+
+**4. Dummy indicator for finished constructions: The Ministry of Education
 	 dataset has a column with the construction status. We created a dummy to be
 	 one when the construction was reported as finished and zero otherwise. The
-	 data here were sampled six months after the intervention.
-
-5. **Dummy indicator for cancelled constructions**: Similarly, we created a
+	 data here were sampled six months after the intervention.**
+
+**5. Dummy indicator for cancelled constructions: Similarly, we created a
 	dummy variable from the Ministry of Education dataset indicating when the
 	construction was reported as cancelled. The data here were sampled six months
-	after the intervention.
-
-6. **Number of schools where construction companies updated the conclusion
-	 dates**: Lastly, the Ministry of Education dataset has a column with the
+	after the intervention.**
+
+**6. Number of schools where construction companies updated the conclusion
+	 dates: Lastly, the Ministry of Education dataset has a column with the
 	 construction estimated completion date. We took the completion dated
 	 reported before and six months after the intervention. If the dates
-	 differed, we coded as one, and zero otherwise.
-
-All these variables come from our manipulation of the Ministry of Education
+	 differed, we coded as one, and zero otherwise.**
+
+**All these variables come from our manipulation of the Ministry of Education
 data. Collecting the outcomes in this way is superior than the alternative of
@@
 collection procedures, they greatly simplify and facilitate the reproduction of
-our findings.
+our findings.**
 
@@
 
-The app by itself would probably not have had an effect on the responsiveness
+**The app by itself would probably not have had an effect on the responsiveness
 of mayors. To boost usage and publicize the app, Transparência Brasil ran 64
@@
 download data is in the second panel of Figures 2 and 3. For the Facebook
-interaction, we have the following statistics:
-
-1. Impressions
-  - Mean: `r mean(fballt$impressoes)`
-  - Total for all campaigns: `r sum(fballt$impressoes)`
-
-2. App Download link clicks:
-  - Mean: `r mean(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
-  - Total for all campaigns: `r sum(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
-
-As we see from the actual download activity, the people who indeed downloaded
-the app were much fewer than these numbers would suggest.
-
-We have chosen Facebook because the platform offers an easy and cheap method to
-spread information. Moreover, according to the Statista website, Facebook is
+interaction, we have the following statistics:**
+
+**1. Impressions**
+- **Mean: `r format(round(mean(fballt$impressoes),2), big.mark = ",")`**
+	- **Total for all campaigns: `r format(sum(fballt$impressoes), big.mark = ",")`**
+
+**2. App Download link clicks:
+	- Mean: `r format(mean(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular']), big.mark = ",")`**
+  - **Total for all campaigns: `r format(sum(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular']), big.mark = ",")`**
+
+**As we see from the actual download activity, the people who indeed downloaded
+the app were much fewer than these numbers would suggest.**
+
+**We have chosen Facebook because the platform offers an easy and cheap method
+to spread information. Moreover, according to the Statista website, Facebook is
 used by 70 million Brazilians (60% of the entire adult population), and the
@@
 Institute of Geography and Statistics. For instance, see the following
-websites:
-
-1. [Statista Total Facebook Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
-2. [Statista Total Facebook Users by Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
+websites:**
+
+**1. [Statista Total Facebook
+Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)**
+
+**2. [Statista Total Facebook Users by
+	 Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)**
 

### 2020-01-01 appendix/appendix.Rmd
version 0.2

--- 2019-12-25 appendix/appendix.Rmd
@@
 author:
+- "Danilo Freire[^freire]"
+- "Manoel Galdino[^galdino]"
+- "Umberto Mignozzetti[^mignozzetti]"
 date: \today
@@
 
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown
+University, Providence, RI 02912, USA,
+[`danilofreire@brown.edu`](mailto:danilofreire@brown.edu),
+<http://danilofreire.github.io>, +1 (401) 584-2494. Corresponding author.
+
+[^galdino]: Executive Director, Transparência Brasil, São Paulo, SP, Brazil,
+[`mgaldino@transparencia.org.br`](mailto:mgaldino@transparencia.org.br),
+<https://www.transparencia.org.br>.
+
+[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São
+Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA,
+[`umberto.mig@nyu.edu`](mailto:umberto.mig@nyu.edu), <http://umbertomig.com>.
+
 \newpage
@@
 
-3. The app sends a message to the mayor's office requesting details about the
-	 project. If necessary, the message is also forwarded to other government
+3. The app sends a message to the mayor's office requesting details about
+the project. If necessary, the message is also forwarded to other government
 oversight institutions such as the city council and the Brazilian Federal
@@
 
-The treatment is a compounded treatment comprised of steps (2) to (4). To make
-sure that the only source of effect comes from step (2), we took the following
-precautions:
-
-In step (1), we have implemented Facebook campaigns in municipalities that have
-school construction agreements with the Federal government. We did not
+The treatment is a compounded treatment comprised of steps (2) to (4). To
+make sure that the only source of effect comes from step (2), we took the
+following precautions:
+
+In step (1), we have implemented Facebook campaigns in municipalities that
+have school construction agreements with the Federal government. We did not
 discriminate any municipality in this step, and citizens living in
@@
 
-Therefore, steps (1), (3), and (4) were standardised and do not vary across the
-country. The only source of variation in our intervention should come from step
-(2).
-
-In step (2), we applied the treatment by removing schools within municipalities
-out of the app. In the first intervention, which happened at the municipal
-level, we excluded all schools within a given randomly selected municipality.
-In the second intervention, we randomly excluded selected schools out of the
-app. Removing a school means that the school was in the dataset provided by the
-Brazilian Ministry of Education, but it did not show up in the app. Therefore,
-our treatment effect represents the school being present (treatment) or absent
-(control) in the app.
+Therefore, steps (1), (3), and (4) were standardised and do not vary across
+the country. The only source of variation in our intervention should come from
+step (2).
+
+In step (2), we applied the treatment by removing schools within
+municipalities out of the app. In the first intervention, which happened at the
+municipal level, we excluded all schools within a given randomly selected
+municipality. In the second intervention, we randomly excluded selected schools
+out of the app. Removing a school means that the school was in the dataset
+provided by the Brazilian Ministry of Education, but it did not show up in the
+app. Therefore, our treatment effect represents the school being present
+(treatment) or absent (control) in the app.
 
@@
 
-We collect the main outcomes using the data reported by the municipality to the
-Brazilian Ministry of Education. Note that this is the same data as the
+We collect the main outcomes using the data reported by the municipality to
+the Brazilian Ministry of Education. Note that this is the same data as the
 pre-treatment data that we use to feed in the app with delayed schools.
@@
 
-1. **Percentage of the project completed before the impact evaluation
-	 started**: This is a column in the Ministry of Education dataset. The data
-	 in this column were sampled in the beginning of the intervention.
-
-2. **Percentage of the project reported as completed by the end of the
-	 intervention period**: Another column in the Ministry of Education
-	 dataset. The data were sampled six months after the intervention.
-
-3. **Difference between the percentage reported as completed before and after
-	 the intervention**: The difference between (1) and (2) above. Note
+1. Percentage of the project completed before the impact evaluation started:
+	 This is a column in the Ministry of Education dataset. The data in this
+	 column were sampled in the beginning of the intervention.
+
+2. Percentage of the project reported as completed by the end of the
+	 intervention period: Another column in the Ministry of Education dataset.
+	 The data were sampled six months after the intervention.
+
+3. Difference between the percentage reported as completed before and after
+	 the intervention: The difference between (1) and (2) above. Note
 	 that according to @gerber2012field, this way to look into outcomes is
@@
 
-4. **Dummy indicator for finished constructions**: The Ministry of Education
+4. Dummy indicator for finished constructions: The Ministry of Education
 	 dataset has a column with the construction status. We created a dummy to be
@@
 
-5. **Dummy indicator for cancelled constructions**: Similarly, we created a
+5. Dummy indicator for cancelled constructions: Similarly, we created a
 	dummy variable from the Ministry of Education dataset indicating when the
@@
 
-6. **Number of schools where construction companies updated the conclusion
-	 dates**: Lastly, the Ministry of Education dataset has a column with the
+6. Number of schools where construction companies updated the conclusion
+	 dates: Lastly, the Ministry of Education dataset has a column with the
 	 construction estimated completion date. We took the completion dated
@@
 1. Impressions
-  - Mean: `r mean(fballt$impressoes)`
-  - Total for all campaigns: `r sum(fballt$impressoes)`
+- Mean: `r format(round(mean(fballt$impressoes),2), big.mark = ",")`
+	- Total for all campaigns: `r format(sum(fballt$impressoes), big.mark = ",")`
 
 2. App Download link clicks:
-  - Mean: `r mean(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
-  - Total for all campaigns: `r sum(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular'])`
+	- Mean: `r format(mean(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular']), big.mark = ",")`
+  - Total for all campaigns: `r format(sum(fballt$impressoes[fballt$tipo_de_resultado=='Instalações do aplicativo para celular']), big.mark = ",")`
 
@@
 
-We have chosen Facebook because the platform offers an easy and cheap method to
-spread information. Moreover, according to the Statista website, Facebook is
+We have chosen Facebook because the platform offers an easy and cheap method
+to spread information. Moreover, according to the Statista website, Facebook is
 used by 70 million Brazilians (60% of the entire adult population), and the
@@
 
-1. [Statista Total Facebook Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
-2. [Statista Total Facebook Users by Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
+1. [Statista Total Facebook
+	 Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
+
+2. [Statista Total Facebook Users by
+	 Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
 

### 2020-01-01 article/article.Rmd
version 0.2

@@
 author:
+- "Danilo Freire[^freire]"
+- "Manoel Galdino[^galdino]"
+- "Umberto Mignozzetti[^mignozzetti]"
 date: \today
-abstract: "Does ~~grassroots participation~~ **local oversight** improve public service delivery?
+abstract: "Does local oversight improve public service delivery?
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
-~~The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.~~ **The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.** Our results show that the app has a null impact on the school construction indicators.
+The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.
+Our results show that the app has a null impact on the school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
-The results question the impact of ~~local~~ **bottom-up** monitoring on public service performance and suggest that interventions targeted ~~at other groups~~ **to other groups, or focusing on different issues,** may produce better policy outcomes."
+The results question the impact of bottom-up monitoring on public service performance and suggest that interventions targeted to other groups, or focusing on different issues, may produce better policy outcomes."
 abstractspacing: double
@@
 [@finer1941administrative; @mulgan2000accountability; @o1990bureaucratic]. Past
-studies show that accountability has a positive impact on governance; ~~as~~ it
+studies show that accountability has a positive impact on governance; it
 ensures that politicians act on behalf of voters [@freire2010ngp;
@@
 
-However, accountability ~~systems take many forms~~ **mechanisms extend beyond
-elections.** One promising model is that of _bottom-up monitoring_, in which
-citizens receive information about the shortcomings of a given project so they
-can evaluate and pressure underperforming public officials [@kosack2014does;
-@molina2016community; @raffler2018weakness]. Proponents argue that bottom-up
-accountability is effective because: 1) constituents have first-hand
-information about the outcomes of local policies; 2) citizens have incentives
-to attack corruption that directly affects themselves; 3) policy-makers are
-sensitive to social punishment from their own communities [@serra2011combining,
-570]. In this regard, bottom-up accountability offers a potential solution to
-the principal-agent dilemma in public service by aligning the interests of
-state officials with those of the constituency they serve [@barro1973control;
+However, accountability mechanisms extend beyond elections. One promising model
+is that of _bottom-up monitoring_, in which citizens receive information about
+the shortcomings of a given project so they can evaluate and pressure
+underperforming public officials [@kosack2014does; @molina2016community;
+@raffler2018weakness]. Proponents argue that bottom-up accountability is
+effective because: 1) constituents have first-hand information about the
+outcomes of local policies; 2) citizens have incentives to attack corruption
+that directly affects themselves; 3) policy-makers are sensitive to social
+punishment from their own communities [@serra2011combining, 570]. In this
+regard, bottom-up accountability offers a potential solution to the
+principal-agent dilemma in public service by aligning the interests of state
+officials with those of the constituency they serve [@barro1973control;
 @raffler2018weakness].
@@
 
-We use the TDP app to conduct two experimental interventions and test ~~its
-impact~~ **the impact of citizen oversight** on five outcomes related to school
-completion rates and complaints to public authorities. Overall, ~~our results
-show that~~ providing information to citizens has no consistent impact on
-policy outcomes. In the first experiment, we find that the TDP app increased
-the likelihood of construction cancellation by 2 percent, but the result does
-not replicate. The remaining five models have null results. In our second
-intervention, none of the estimations reach conventional levels of statistical
-significance. Importantly, all coefficients are small, what suggests that even
-if the TDP app had a significant effect on the outcomes, its substantive impact
-would be ~~virtually~~ negligible.
+We use the TDP app to conduct two experimental interventions and test the
+impact of citizen oversight on five outcomes related to school completion rates
+and complaints to public authorities. Overall, providing information to
+citizens has no consistent impact on policy outcomes. In the first experiment,
+we find that the TDP app increased the likelihood of construction cancellation
+by 2 percent, but the result does not replicate. The remaining five models have
+null results. In our second intervention, none of the estimations reach
+conventional levels of statistical significance. Importantly, all coefficients
+are small, what suggests that even if the TDP app had a significant effect on
+the outcomes, its substantive impact would be negligible.
 
 The findings raise questions about the ability of citizens to hold
-representatives accountable using bottom-up ~~strategies~~ **monitoring**. 
-\sout{Although studies like} **On the one hand,** @bjorkman2009power,
-@lagunes2018guardians, and @reinikka2005fighting report better policy outcomes
-after providing information to local communities. ~~our findings are closer
-to~~ **On the other hand,** @banerjee2010pitfalls, @keefer2014mass,
-@lieberman2014does, @bjorkman2017experimental, @olken2007monitoring, and
-@raffler2018weakness, find little evidence that information-based interventions
-lead to greater government responsiveness. **Our results are in line with the
-latter group and suggest that local oversight is ineffective in altering
-government behaviour in Brazil.**
+representatives accountable using bottom-up monitoring. On the one hand,
+@bjorkman2009power, @lagunes2018guardians, and @reinikka2005fighting report
+better policy outcomes after providing information to local communities. On the
+other hand, @banerjee2010pitfalls, @keefer2014mass, @lieberman2014does,
+@bjorkman2017experimental, @olken2007monitoring, and @raffler2018weakness, find
+little evidence that information-based interventions lead to greater government
+responsiveness. Our results are in line with the latter group and suggest that
+local oversight is ineffective in altering government behaviour in Brazil.
 
@@
 cancelled constructions; 6) the number of schools where construction companies
-updated the conclusion dates. ~~In terms of expectations,~~ Table
-\ref{tab:outcomes} depicts the expected effects for each of the studied
-outcomes[^more-details].
-
-[^more-details]: **Please refer to the Online Appendix for further details on
-the treatment implementation and the coding of the outcome variables.**
+updated the conclusion dates. Table \ref{tab:outcomes} depicts the expected
+effects for each of the studied outcomes[^more-details].
+
+[^more-details]: Please refer to the Online Appendix for further details on the
+treatment implementation and the coding of the outcome variables.
 
@@
 during the Facebook TDP campaign, launched in October 2017, then diminish in
-the following months. **Overall, 
+the following months. Overall, 
 `r format(sum(ga$novos_usuarios[ga$phase1==1]), big.mark = ",")` users
-downloaded the app during intervention 1.**
-
-```{r man1, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
+downloaded the app during intervention 1.
+
+```{r man1, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=3.8, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1.
 The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to July 2018.'}
@@
 The second intervention is similar to intervention 1 in all but three
-characteristics. First, the TDP app was **then** available for both Android and
-iOS devices. Second, we randomised the intervention at the school level, with
+characteristics. First, the TDP app was then available for both Android and iOS
+devices. Second, we randomised the intervention at the school level, with 
 `r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
@@
 after intervention 2 starts, and a second spike around December. 
-**The app gained 
+The app gained 
 `r format(sum(ga$novos_usuarios[ga$phase1==0]), big.mark = ",")` new users
 during intervention 2. The number of downloads is smaller in this second
-intervention as there was no associated social media campaign in that period.**
+intervention as there was no associated social media campaign in that period.
 
@@
 
-**Data from Google Analytics suggest that users did engage with the TDP app. On
+Data from Google Analytics suggest that users did engage with the TDP app. On
 average, each user launched `r format(round(mean(as.numeric(gsub('\\.', '',
@@
 `r round(mean(as.numeric(gsub(',', '.', ga2$telas_sessao))), 2)` screen
-visualisations per session.**
+visualisations per session.
 
@@
 delivering more information about the shortcomings of public services provision
-will ~~mobilise citizens who, in turn, would pressure state agents to produce
-better social policies~~ **put citizens in a position where they can monitor
-state agents and improve provider behaviour** [@raffler2018weakness]. Our
-results do not lend support to that hypothesis.
+will put citizens in a position where they can monitor state agents and improve
+provider behaviour [@raffler2018weakness]. Our results do not lend support to
+that hypothesis.
 
@@
 school construction outcomes we investigate here, we find little evidence that
-grassroots monitoring works in the context of school constructions in Brazil.
+local monitoring works in the context of school constructions in Brazil.
 
@@
 
-In this paper, we discuss **whether delivering information to citizens via** a
-mobile phone application fosters ~~grassroots mobilisation~~ **community
-oversight** and political accountability in Brazil. Our two interventions show
-that the results are at best mixed. Although we find ~~an~~ **some treatment**
-effect on school cancelling rates in the first intervention, the app has no
-consistent impact on our outcomes of interest. These findings add to the
-studies that cast doubts on the relationship between bottom-up accountability
-and local policy performance [e.g., @banerjee2010pitfalls; @lieberman2014does;
+In this paper, we discuss a mobile phone application fosters community
+oversight and political accountability in Brazil. Our two interventions show
+that the results are at best mixed. Although we find some treatment effect on
+school cancelling rates in the first intervention, the app has no consistent
+impact on our outcomes of interest. These findings add to the studies that cast
+doubts on the relationship between bottom-up accountability and local policy
+performance [e.g., @banerjee2010pitfalls; @lieberman2014does;
 @raffler2018weakness].
@@
 manipulation tests indicate that the treatment allocation was successful, so we
-can rule out problems in the randomisation procedures. **Third, data from
+can rule out problems in the randomisation procedures. Third, data from
 Google Analytics confirm that citizens indeed used the app and provided
@@
 effective. In this sense, it is unlikely that our results derive from low user
-response.** Fourth, after doing a series of robustness tests, we still find no
+response. Fourth, after doing a series of robustness tests, we still find no
 firm evidence of treatment effect. Finally, note that the sign of the
@@
 
-**We discuss some possible reasons why community monitoring did not work in our
-case**. ~~A~~ **One** plausible explanation is that individuals were unable to
+We discuss some possible reasons why community monitoring did not work in our
+case. One plausible explanation is that individuals were unable to
 differentiate the effect of political corruption from those of spending cuts.
@@
 government introduced discretionary spending limits that affected public
-investment [@rossi2016impactos]. Politicians may argue that
-delays in school constructions are not derived from their misuse of government
-funds, but from the austerity measures. If this is the case, citizens will not
-blame local politicians for the underprovision of public goods. Consequently,
+investment [@rossi2016impactos]. Politicians may argue that delays in school
+constructions are not derived from their misuse of government funds, but from
+the austerity measures. If this is the case, citizens will not blame local
+politicians for the underprovision of public goods. Consequently,
 representatives can dismiss individual requests as the issue is unlikely to
@@
 
-**The electoral cycle might also have decreased the potential effect of the
+The electoral cycle might also have decreased the potential effect of the
 treatment. As the experiment was fielded right after Brazil's municipal
@@
 electoral dynamics interact with citizen oversight, potentially by replicating
-informational experiments in different stages of the political cycle.**
-
-\sout{Moreover, it is possible that a mobile app like TDP is simply not
-sufficient to promote collective action. Raffler et al (2018, 29) point
-out several reasons why information interventions does not lead to higher
-pressure on public agents, such as citizens' apathy towards their ability to
-make public agents accountable, lack of official channels to support popular
-demands, or that constituents have more pressing needs than monitoring
-representatives. Furthermore, individuals may also believe they are better off
-by free-riding on other users of the TDP app, thus reaping the benefits of
-having faster school constructions without incurring personal costs (Olson
-1965).}
+informational experiments in different stages of the political cycle.
 
@@
 derived from this study is that interventions targeting elite groups, such as
-lobbyists or civil servants, might render better ~~policy~~ **school
-construction** outcomes than those focused at the ~~grassroots levels~~
-**community level**. Another core lesson is that although digital interventions
-are promising means to deliver information, perhaps they do not have the same
-impact as personal, face-to-face communication. Since many developing countries
-share Brazil's issues with education provision, the shortcomings we describe
-here serve as warnings for future interventions. Finally, whether this study
-generalises beyond school constructions to other bottom-up programs, and to
-other contexts, remains to be studied.
-
+lobbyists or civil servants, might render better school construction outcomes
+than those focused at the community level. Another core lesson is that although
+digital interventions are promising means to deliver information, perhaps they
+do not have the same impact as personal, face-to-face communication. Since many
+developing countries share Brazil's issues with education provision, the
+shortcomings we describe here serve as warnings for future interventions.
+Finally, whether this study generalises beyond school constructions to other
+bottom-up programs, and to other contexts, remains to be studied.
+
+\newpage
 \setlength{\parindent}{0cm} 

### 2020-01-03 appendix/appendix.Rmd
version 0.2.1, small edits

--- 2020-01-01 appendix/appendix.Rmd
@@
 The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.
-Our results show that the app has a null impact on the school construction indicators.
+Our results show that the app has a null impact on school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
-The results question the impact of bottom-up monitoring on public service performance and suggest that interventions targeted to other groups, or focusing on different issues, may produce better policy outcomes."
+The results question the impact of bottom-up monitoring on public service performance and suggest that interventions targeted at other groups, or focused on different issues, may produce better policy outcomes."
 abstractspacing: double
@@
 **The treatment is a compounded treatment comprised of steps (2) to (4). To
-make sure that the only source of effect comes from step (2), we took the
+make sure that the only source of the effect comes from step (2), we took the
 following precautions:**
@@
 found the construction delayed. We submitted a request for the mayor's office
-to provide an explanation on why the construction was delayed, and asked for
+to provide an explanation on why the construction was delayed and asked for
 updated statistics on when the construction will be finished. According to the
@@
 Education website. Second, whenever people find this information troublesome,
-we are providing an easy way to them to act upon the information. As the _Tá de
-Pé_ design was intuitive and straightforward, we believe that most of
+we are providing an easy way for them to act upon the information. As the _Tá
+de Pé_ design was intuitive and straightforward, we believe that most
 Brazilians would find it easy to use the app.**
@@
 municipality uses it. The more usage means more pictures and denounces, and
-this represents more pressure over the mayors office, what could revert into a
-higher effect. However, just one denounce would be enough for the project to be
-successful, as the denounce can be directed to the Brazilian General
+this represents more pressure over the mayors' office, which could revert into
+a higher effect. However, just one denounce would be enough for the project to
+be successful, as the denounce can be directed to the Brazilian General
 Comptroller (CGU), and this could potentially deny future funding to the
@@
 	 This is a column in the Ministry of Education dataset. The data in this
-	 column were sampled in the beginning of the intervention.**
+	 column were sampled at the beginning of the intervention.**
 
@@
 **All these variables come from our manipulation of the Ministry of Education
-data. Collecting the outcomes in this way is superior than the alternative of
+data. Collecting the outcomes in this way is superior to the alternative of
 gathering the data ourselves. First, we would not be able to manipulate the
@@
 Facebook campaigns throughout the country. The Facebook campaign concentrates
-the bulk of the investments in the beginning of the intervention. The app
+the bulk of the investments at the beginning of the intervention. The app
 download data is in the second panel of Figures 2 and 3. For the Facebook

### 2020-01-03 article/article.Rmd
version 0.2.1, small edits

--- 2019-12-28 article/article.Rmd
@@
 We study the effect of a mobile phone application that allows citizens to monitor school construction projects in Brazilian municipalities.
-~~The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.~~ **The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.** Our results show that the app has a null impact on the school construction indicators.
+~~The app provides a platform where users can submit photos of construction sites, consult independent engineers, and contact the mayor's office about project delays.~~ **The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.** Our results show that the app has a null impact on school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
-The results question the impact of ~~local~~ **bottom-up** monitoring on public service performance and suggest that interventions targeted ~~at other groups~~ **to other groups, or focusing on different issues,** may produce better policy outcomes."
+The results question the impact of ~~local~~ **bottom-up** monitoring on public service performance and suggest that interventions targeted at other groups, or focused on different issues, may produce better policy outcomes."
 abstractspacing: double
@@
 policy outcomes. In the first experiment, we find that the TDP app increased
-the likelihood of construction cancellation by 2 percent, but the result does
+the likelihood of construction cancellation by 2 per cent, but the result does
 not replicate. The remaining five models have null results. In our second
@@
 powered. Although the treatment is indirect---the person has to download the
-app, find a school construction, and then report it---,we included
-a substantial number of schools in the treatment groups. Second, balance and
+app, find a school construction, and then report it---, we included a
+substantial number of schools in the treatment groups. Second, balance and
 manipulation tests indicate that the treatment allocation was successful, so we
@@
 response.** Fourth, after doing a series of robustness tests, we still find no
-firm evidence of treatment effect. Finally, note that the sign of the
+firm evidence of treatment effect. Finally, note that the signs of the
 coefficients are frequently contrary to our theoretical expectations. This
@@
 delays in school constructions are not derived from their misuse of government
-funds, but from the austerity measures. If this is the case, citizens will not
+funds but from the austerity measures. If this is the case, citizens will not
 blame local politicians for the underprovision of public goods. Consequently,
@@
 see the demands as politically costly in the short run. Having just taken
-office, mayors might have focused their attention to the formation of
+office, mayors might have focused their attention on the formation of
 government coalitions or to budget concerns. Future research may evaluate how

### 2020-01-03 article/letter.Rmd
version 0.2.1, small edits

@@
 
-\noindent 28 December 2019
+\noindent 3 January, 2020
 
@@
 
-We have worked specially hard to clarify the connection between information
+We have worked especially hard to clarify the connection between information
 provision and mobilisation, a point emphasised by both the editor and the
@@
 information to evaluate the robustness of our findings. We believe the new
-sections help give the results a clearer interpretation and strenghten our main
+sections help give the results a clearer interpretation and strengthen our main
 arguments.
@@
 Borders found the construction delayed. We submitted a request for the mayor's
-office to provide an explanation on why the construction was delayed, and asked
+office to provide an explanation on why the construction was delayed and asked
 for updated statistics on when the construction will be finished. According to
@@
 Education website. Second, whenever people find this information troublesome,
-we are providing an easy way to them to act upon the information. As the _Tá de
-Pé_ design was intuitive and straightforward, we believe that most of
+we are providing an easy way for them to act upon the information. As the _Tá
+de Pé_ design was intuitive and straightforward, we believe that most 
 Brazilians would find it easy to use the app._
@@
 > To answer these questions, we have added Google Analytics data on _Tá de
-Pé_'s download and usage. This provide exogenous and reliable data about our
+Pé_'s download and usage. This provides exogenous and reliable data about our
 experimental manipulation and the effectiveness of the treatment. The data
@@
 downloads were widespread across the country. Considering Brazil's large
-territory, we believe this is robust evidence of an effective treatment
+territory, we believe this is robust evidence of effective treatment
 manipulation.
@@
 investment [@rossi2016impactos]. Politicians may argue that delays in school
-constructions are not derived from their misuse of government funds, but from
+constructions are not derived from their misuse of government funds but from
 the austerity measures. If this is the case, citizens will not blame local
@@
 	 started**: This is a column in the Ministry of Education dataset. The data
-	 in this column were sampled in the beginning of the intervention._
+	 in this column were sampled at the beginning of the intervention._
 
@@
 > _All these variables come from our manipulation of the Ministry of Education
-data. Collecting the outcomes in this way is superior than the alternative of
+data. Collecting the outcomes in this way is superior to the alternative of
 gathering the data ourselves. First, we would not be able to manipulate the
@@
 the analysis, it ensures that the citizens were not exposed in any way.
-Moreover, the randomization is known for washing out any the interference of
-any unobserved factor that could threat the identification of the causal
+Moreover, the randomisation is known for washing out any the interference of
+any unobserved factor that could threaten the identification of the causal
 effect. The success on observables reassures us that the randomisation was well
@@
 non-observables. However, we agree with the reviewer that the target public
-could be either outside Facebook, or being of a given demographic
-characteristic that we did not captured in our experiment.
+could be either outside Facebook or being of a given demographic
+characteristic that we did not capture in our experiment.
 
@@
 Brasil ran 64 Facebook campaigns throughout the country. The Facebook campaign
-concentrates the bulk of the investments in the beginning of the intervention.
+concentrates the bulk of the investments at the beginning of the intervention.
 The app download data is in the second panel of Figures 2 and 3. For the

### 2020-01-03 appendix/appendix.Rmd
version 0.2.1, small edits

--- 2020-01-01 appendix/appendix.Rmd
@@
 The treatment is a compounded treatment comprised of steps (2) to (4). To
-make sure that the only source of effect comes from step (2), we took the
+make sure that the only source of the effect comes from step (2), we took the
 following precautions:
@@
 Education website. Second, whenever people find this information troublesome,
-we are providing an easy way to them to act upon the information. As the _Tá de
-Pé_ design was intuitive and straightforward, we believe that most of
+we are providing an easy way for them to act upon the information. As the _Tá
+de Pé_ design was intuitive and straightforward, we believe that most
 Brazilians would find it easy to use the app.
@@
 	 This is a column in the Ministry of Education dataset. The data in this
-	 column were sampled in the beginning of the intervention.
+	 column were sampled at the beginning of the intervention.
 
@@
 All these variables come from our manipulation of the Ministry of Education
-data. Collecting the outcomes in this way is superior than the alternative of
+data. Collecting the outcomes in this way is superior to the alternative of
 gathering the data ourselves. First, we would not be able to manipulate the
@@
 1. Impressions
-- Mean: `r format(round(mean(fballt$impressoes),2), big.mark = ",")`
 	- Total for all campaigns: `r format(sum(fballt$impressoes), big.mark = ",")`
@@
 
-1. [Statista Total Facebook
-	 Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
-
-2. [Statista Total Facebook Users by
-	 Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
+1. [Statista Total Facebook Users](https://www.statista.com/statistics/244936/number-of-facebook-users-in-brazil/)
+
+2. [Statista Total Facebook Users by Age](https://www.statista.com/statistics/866282/facebook-user-share-brazil-age/)
 

### 2020-01-03 article/article.Rmd
version 0.2.1, small edits

--- 2020-01-01 article/article.Rmd
@@
 The app prompts users to submit data about construction sites, sends such crowdsourced information to independent engineers, and contacts the mayors' offices about project delays.
-Our results show that the app has a null impact on the school construction indicators.
+Our results show that the app has a null impact on school construction indicators.
 Additionally, we find that politicians are unresponsive to individual requests.
-The results question the impact of bottom-up monitoring on public service performance and suggest that interventions targeted to other groups, or focusing on different issues, may produce better policy outcomes."
+The results question the impact of  bottom-up monitoring on public service performance and suggest that interventions targeted at other groups, or focused on different issues, may produce better policy outcomes."
 abstractspacing: double
@@
 we find that the TDP app increased the likelihood of construction cancellation
-by 2 percent, but the result does not replicate. The remaining five models have
-null results. In our second intervention, none of the estimations reach
+by 2 per cent, but the result does not replicate. The remaining five models
+have null results. In our second intervention, none of the estimations reach
 conventional levels of statistical significance. Importantly, all coefficients
@@
 school construction outcomes we investigate here, we find little evidence that
-local monitoring works in the context of school constructions in Brazil.
+grassroots monitoring works in the context of school constructions in Brazil.
 
@@
 
-In this paper, we discuss a mobile phone application fosters community
-oversight and political accountability in Brazil. Our two interventions show
-that the results are at best mixed. Although we find some treatment effect on
-school cancelling rates in the first intervention, the app has no consistent
-impact on our outcomes of interest. These findings add to the studies that cast
-doubts on the relationship between bottom-up accountability and local policy
-performance [e.g., @banerjee2010pitfalls; @lieberman2014does;
-@raffler2018weakness].
+In this paper, we discuss whether delivering information to citizens via a
+mobile phone application fosters community oversight and political
+accountability in Brazil. Our two interventions show that the results are at
+best mixed. Although we find some treatment effect on school cancelling rates
+in the first intervention, the app has no consistent impact on our outcomes of
+interest. These findings add to the studies that cast doubts on the
+relationship between bottom-up accountability and local policy performance
+[e.g., @banerjee2010pitfalls; @lieberman2014does; @raffler2018weakness].
 
@@
 response. Fourth, after doing a series of robustness tests, we still find no
-firm evidence of treatment effect. Finally, note that the sign of the
+firm evidence of treatment effect. Finally, note that the signs of the
 coefficients are frequently contrary to our theoretical expectations. This
@@
 
-\newpage
 \setlength{\parindent}{0cm}

### 2020-02-25 article/article.Rmd
fix a few typos

@@
 conventional levels of statistical significance. Importantly, all coefficients
-are small, what suggests that even if the TDP app had a significant effect on
+are small, which suggests that even if the TDP app had a significant effect on
 the outcomes, its substantive impact would be negligible.
@@
 
-Transparência Brazil built the app in from January to March 2017 and tested it
+Transparência Brazil built the app from January to March 2017 and tested it
 in May of that year. The first stable Android version was deployed on Google
@@
 The TDP also received feedback from Brazilian computer scientists and policy
-analists. In 2017 and 2018, Transparência Brasil announced two team programming
+analysts. In 2017 and 2018, Transparência Brasil announced two team programming
 competitions, called 'Tá de Pé Hackathons', where contributors could fix code
@@
 unfinished), and whether the municipality spent more on school construction
-that the distribution median. Finally, the intervention period lasted from
+than the distribution median. Finally, the intervention period lasted from
 August 2018 to July 2019.
@@
 We find that the app only has a small effect on cancellation rates. The TDP
-application increases the likelihood of cancelling the construction in 
-`r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent. While this result
+application increases the likelihood of cancelling the construction by `r
+round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent. While this result
 goes in the opposite direction of our theoretical expectations, the finding is
@@
 Table \ref{tab:results2} shows the results of the second intervention. The
-treatment does not have a statistically significant effect on any our outcomes
-of interest, including the placebo. This raises further questions about the
-effect of the TDP app on school completion. Note that the effect signs are also
-inconsistent with improving the outcomes, what demonstrates that our results do
-not derive from low statistical power or the reduced control group size.
+treatment does not have a statistically significant effect on any of our
+outcomes of interest, including the placebo. This raises further questions
+about the effect of the TDP app on school completion. Note that the effect
+signs are also inconsistent with improving the outcomes, which demonstrates
+that our results do not derive from low statistical power or the reduced
+control group size.
 
